### 2021-01-16 main.tex
Add 2nd arXiv version (version after reviewer)

\documentclass[A4]{amsart}

\usepackage{amsmath, amssymb, amsfonts}
\usepackage{tikz-cd}
\usepackage{graphics}
\usepackage[bookmarks=true, linktocpage=true,
bookmarksnumbered=true, breaklinks=true,
pdfstartview=FitH, hyperfigures=false,
plainpages=false, naturalnames=true,
colorlinks=true, pagebackref=true,
pdfpagelabels]{hyperref}
\hypersetup{
	colorlinks,
	citecolor=blue,
	filecolor=blue,
	linkcolor=blue,
	urlcolor=blue
}
\usepackage[alphabetic]{amsrefs}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\End}{\mathrm{End}}
\DeclareMathOperator*{\colim}{colim}

\include{figures}

\setlength{\textwidth}{\paperwidth}
\addtolength{\textwidth}{-1.6in}
\setlength{\textheight}{\paperheight}
\addtolength{\textheight}{-1.8in}
\calclayout

\begin{document}

\title{Chain level Steenrod operations}

\author[R. Kaufmann]{Ralph M.\ Kaufmann}
\address{Department of Mathematics, Department of Physics and Astronomy, Purdue University}
\email{rkaufman@purdue.edu}

\author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
\address{Laboratory for Topology and Neuroscience, École Polytechnique Fédérale de Lausanne, Switzerland}
\address{Department of Mathematics, University of Notre Dame du Lac, Notre Dame, IN, USA}
\email{amedinam@nd.edu}
\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Max Plank Institute for Mathematics.}

\subjclass[2010]{55S05, 55U05, 55S10, 55S12; 55-04, 55U15, 55S15}
\keywords{Steenrod operations, Dyer-Lashof operations, simplicial cochains, cubical cochains}

\begin{abstract}
	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander-Whitney's chain approximation to the diagonal. Later, following a viewpoint developed by Adem, Steenrod defined his homonymous operations for all primes using the homology of symmetric groups. This approach enhanced the conceptual understanding of the operations and allowed for many advances but lacked the concreteness of their definition at~$2$. In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having a definition of Steenrod operations that can be effectively computed in specific examples has become a key issue. This article provides such definition, at all primes, for well known $E_\infty$-algebras including the cochains of spaces expressed via simplicial or cubical cell structures.
\end{abstract}

\maketitle

\tableofcontents

\section{Introduction}

The role Steenrod operations play in Stable Homotopy Theory is hard to overstate. The reason is that, given the representability of the cohomology functor, these operations together with the Bockstein homomorphism can be used to give a complete description of the algebraic structure naturally present on the mop-$p$ \mbox{cohomology} algebra of spaces. For the even prime, Steenrod squares were introduced in \cite{steenrod47products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander-Whitney's chain approximation to the diagonal. Later, for odd primes,	their definition was given non-effectively using arguments based on the mod-$p$ homology of symmetric groups \cites{steenrod53symmetric, steenrod53cyclic, steenrod62operations}. This viewpoint enhanced the conceptual understanding of the operations and allowed for many advances \cites{adem1952iteration, milnor1958dual, adams1995stable}, but lacked the concreteness of their definition at~$2$.

In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- the need to have a definition of Steenrod operations that can be effectively computed in specific examples has gain considerable importance. In Applied Topology, the use of Persistence Homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage,chan2013topology,lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of Persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}. In Quantum Field Theory, the BRST formalism \cites{BRS,Tyutin,KugoOjima} introduced cohomology to deal with gauge symmetries, and was further developed in the BV-formalism \cite{BV}. Master equations, introduced there, are also needed for the construction of viable actions in String Field Theory \cite{Zwiebach}, where fundamental chains are involved. The chain level viewpoint for the study of homology operations was brought to the forefront by String Topology \cite{Sullivanoverview}, and as served as a major driver of innovation \cites{TZ, hoch2}. The cubical viewpoint appears in physics naturally in the theory of renomalization \cite{KreimerCubical}; while Steenrod cup-$i$ products are utilized in the construction of effective actions of gapped systems \cite{kapustin2017fermionic}. This connection with physics motivated the development of effective versions of spin bordism \cites{brumfiel2016pontrjagin, brumfiel2018pontrjagin}, which prominently feature Steenrod cup-$i$ products and Cartan coboundaries.

As in \cite{may70generalapproach}, we take a more general approach to Steenrod operations that also includes Araki-Kudo-Dyer-Lashof operations on the mod-$p$ homology of infinite loop spaces \cites{araki56squaring, dyer62lashof}. We use the language of operads \cite{may72geometry}  to describe at the chain level the integral structure required to define (co)homology operations at every prime. We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod-$p$ homology of their algebras; these are the Barratt-Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads. Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical products generalizing the \mbox{cup-$i$} products of Steenrod to every prime. An alternative approach based on the Eilenberg-Zilber contraction can be found in \cite{gonzalez2005hpt}. Up to now, although its existence is warrantied by acyclic model argument \cite{eilenberg1953acyclic}, no $E_\infty$-structure was known on the cochains of cubical sets. Using an $E_\infty$-bialgebra structure on the chains of the interval we effectively construct an $U(\mathcal M)$-algebra structure on them, and as a consequence provide a description of Steenrod products for cochains of cubical sets as well. The $p=2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2018axiomatic}, and in the cubical setting to the cup-$i$ products of  Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l-Pilarczy \cite{pilarczyk2016cubical}.

We also contribute to a growing body of open source software \cites{manero2020effective, pilarczyk2015contraction, sagemath} resulting from an effort to rewrite key concepts from Homotopy Theory in effective forms. Uses in Applied Topology are motivating some of this work \cite{tauzin2020giottotda}, but the impetus also comes from Voevodsky's program for a comprehensive, computational foundation of mathematics based on the homotopical interpretation of type theory \cite{bauer2017hott}. A \texttt{Python} implementation of all the constructions in this article can be found in A.M-M.'s website.\footnote{Currently hosted at \url{https://www.medina-mardones.com/}}

An outline of the article is described next. We first introduce, in Section~2, the conventions we will follow regarding chain complexes, simplicial sets and cubical sets. Then, in Section~3, we review the key notions from group homology we will use for cyclic and symmetric groups. Section~4 is devoted to the language of operads and related structures that we use, in Section~5, to define an integral structure at the chain level inducing Steenrod operations for every prime. Section~6, the bulk of this work, presents effective constructions of Steenrod-Adem structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads. It also describes a natural $U(\mathcal M)$-algebra structure on the cochains of simplicial and cubical sets inducing natural Steenrod-Adem structures on them.
We end, in Section~7, with an overview of some connections of this work to important geometric and combinatorial structures, and provide an outline of future research directions.

\section*{Acknowledgement}

The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Greg Brumfiel, Dev Sinha, Jens Kjaer, Calista Bernard, and Andy Putnam, for insightful discussions and valuable comments, and to the anonymous referee for many helpful suggestions.

\section{Preliminaries}

\subsection{Chain complexes}
\label{ssec: chain cpx}

Let $R$ be a ring. We denote by $(\mathbf{Ch}_R, \otimes, R)$ the symmetric monoidal category of homologically graded chain complexes of $R$-modules. The set of $R$-linear maps between chain complexes as well as the tensor product of chain complexes are regarded as chain complexes in the usual way:
\begin{equation*}
\Hom(A, A^\prime)_n = \big\{f \ |\ a \in A_m \Rightarrow f(a) \in A^\prime_{m+n} \big\}, \qquad
\partial f = \partial \circ f - (-1)^{|f|}f \circ \partial,
\end{equation*}
\begin{equation*}
(A \otimes A^\prime)_n = \bigoplus_{p + q = n} A_p \otimes A^\prime_q, \qquad \partial (a \otimes a^\prime) = \partial a \otimes a^\prime + (-1)^{|a|} a \otimes \partial a^\prime.
\end{equation*}
We embed the category of $R$-modules as the full subcategory of $\mathbf{Ch}_R$ with objects concentrated in degree $0$. The endofunctor $\Hom(-, R)$ is referred to as the \textit{linear duality functor}. We notice that if a chain complex is concentrated in non-negative degrees then its linear dual is on non-positive ones.

The rings we will mostly be interested in are the group rings $\Z[\mathrm G]$ and $\mathbb{F}_p[\mathrm G]$ of finite groups, where $p$ is prime and $\mathbb{F}_p$ is the field with $p$ elements.

\subsection{Simplicial sets}

The \textit{simplex category} $\triangle$ is defined to have an object $[n] = \{0, \dots, n\}$ for every $n \in \mathbb{N}$ and a morphism $[m] \to [n]$ for each order-preserving function from $[m]$ to $[n]$. The morphisms $\delta_i : [n-1] \to [n]$ and $\sigma_i : [n+1] \to [n]$ defined for $0 \leq i \leq n$ by
\begin{equation*}
\delta_i(k) = 
\begin{cases} k & k < i, \\ k+1 & i \leq k, \end{cases}
\quad \text{ and } \quad
\sigma_i(k) = 
\begin{cases} k & k \leq i, \\ k-1 & i < k, \end{cases}
\end{equation*} 
generate all morphisms in the simplex category.

A \textit{simplicial set} $X$ is a contravariant functor from the simplex category to the category of sets and a simplicial map is a natural transformation between two simplicial sets. As is customary we use the notation
\begin{equation*}
X\big( [n] \big) = X_n, \qquad X(\delta_i) = d_i, \qquad X(\sigma_i) = s_i,
\end{equation*}
and refer to elements in the image of any $s_i$ as \textit{degenerate}.

For each $n \in \mathbb{N}$, the simplicial set $\triangle^n$ is defined by
\begin{equation*}
\triangle^n_k  = \Hom_{\triangle} \big( [k], [n] \big), \qquad 
d_i(x) = x \circ \delta_i, \qquad 
s_i(x) = x \circ \sigma_i,
\end{equation*}
and any simplicial set can be expressed as a colimit of these
\begin{equation*}
X = \colim_{\triangle^n \to X} \triangle^n.
\end{equation*}
We represent the non-degenerate elements of $\triangle^n_k$ as an increasing sequence $[v_0, \dots, v_k]$ of non-negative integers each less than or equal to $n$.

The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: 
\begin{equation*}
N_\bullet(X; R)_n = \frac{R \{ X_n \}}{R \{ s(X_{n-1}) \}}
\end{equation*}
where $s(X_{n-1}) = \bigcup_{i=0}^{n-1} s_i(X_{n-1})$, and $\partial_n : N_*(X)_n \to N_*(X)_{n-1}$ is given by
\begin{equation*}
\partial_n = \sum_{i=0}^{n} (-1)^id_{i}.
\end{equation*}
The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.

It is convenient to emphasize that
\begin{equation*}
N_\bullet(X; R) = \colim_{\triangle^n \to X} N_\bullet(\triangle^n; R).
\end{equation*}

\subsection{Cubical sets}

The \textit{cube category} $\square$ is the free strict monoidal category with a \textit{bipointed object}
\begin{equation*}
\begin{tikzcd}
1 \arrow[r, bend left, "\delta^0"] \arrow[r, bend right, "\delta^1"'] & 2 \arrow[r, "\sigma"] & 1
\end{tikzcd}
\end{equation*}
such that $\sigma \circ \delta^0 = \sigma \circ \delta^1 = \mathrm{id}$. Explicitly, it contains an object $2^n$ for each non-negative integer $n$ and its morphisms are generated by the \textit{coface} and \textit{codegeneracy maps} defined by
\begin{align*}
\delta_i^\varepsilon & = \mathrm{id}_{2^{i-1}} \times \delta^\varepsilon \times \mathrm{id}_{2^{n-1-i}} \colon 2^{n-1} \to 2^n, \\
\sigma_i & = \mathrm{id}_{2^{i-1}} \times \, \sigma \times \mathrm{id}_{2^{n-i}} \colon 2^{n} \to 2^{n-1}.
\end{align*}

A \textit{cubical set} $X$ is a contravariant functor from the cube category to the category of sets and a cubical map is a natural transformation between two cubical sets. As is customary, we use the notation
\begin{equation*}
X\big( 2^n \big) = X_n \qquad X(\delta^\varepsilon_i) = d^\varepsilon_i \qquad X(\sigma_i) = s_i,
\end{equation*}
and refer to elements in the image of any $s_i$ as \textit{degenerate}.

For each $n \in \mathbb{N}$, the cubical set $\square^n$ is defined by
\begin{equation*}
\square^n_k  = \Hom_{\square} \big( 2^k, 2^n \big), \qquad 
d^\varepsilon_i(x) = x \circ \delta^\varepsilon_i, \qquad 
s_i(x) = x \circ \sigma_i,
\end{equation*}
notice that iteratively
\begin{equation*}
\square^n = \overbrace{\square^1 \times \cdots \times \square^1}^{n \text{ times }}.
\end{equation*}
We represent the non-degenerate elements of $\square^n$ as sequences $x_1 \cdots\, x_n$ with each $x_i \in \{[0], [1], [0,1]\}$. Any cubical set can be expressed as a colimit of these
\begin{equation*}
X = \colim_{\square^n \to X} \square^n.
\end{equation*}

The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: The chain complex $N_\bullet(\square^1)$ is simply the cellular chain complex of the interval,
isomorphic to
\begin{equation*}
\begin{tikzcd} [column sep = small, row sep = 0.1pt]
R\{[0], [1]\}  & \arrow[l] R\{[0,1]\} \\
{[1] - [0]} & \arrow[l, |->] \left[0,1\right].
\end{tikzcd}
\end{equation*}
Set
\begin{equation} \label{eq: chains on I^n}
N_\bullet(\square^n; R) = N_\bullet(\square^1; R)^{\otimes n}
\end{equation}
and define
\begin{equation*}
N_\bullet(X; R) = \colim_{\square^n \to X} N_\bullet(\square^n; R).
\end{equation*}

The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.

\section{Group homology}
\label{sec: goup homology}

Fixing notation, let $\mathrm{S}_n$ be the symmetric group of $n$ elements and $\mathrm{C}_n$ be the cyclic group of order $n$ thought of as the subgroup of $\mathrm{S}_n$ generated by an element~$\rho$. We denote this inclusion by $\iota : \mathrm C_r \to \mathrm S_r$.

A \textit{resolution} in $\mathbf{Ch}_R$ is a quasi-isomorphism $P \to M$ with each $P_n$ a free \mbox{$R$-module}. We will use the fact, explained in Section 6.5 of \cite{jacobson1989algebra}, that such resolutions exist for any chain complex $M$ concentrated in non-negatively degrees, in particular, for the monoidal unit $R$.

Let $\mathrm G$ be a group and $M$ an $R[\mathrm G]$-module, we define the \textit{homology of $\mathrm G$ with coefficients in $M$}, denoted $H(\mathrm G; M)$, as the homology of any chain complex $P \otimes_{R[\mathrm G]} M$ with $P \to R$ a resolution. We will be particularly interested in the case when $M = \mathbb F_p(q)$ is the trivial or sign $\mathbb F_p[\mathrm{S}_n]$-module depending on the parity of~$q$.

We now review the group homology of finite cyclic groups. For any ring $R$ the elements
\begin{align} \label{eq: T and R definition}
T &= \rho - 1, \\
N &= 1 + \rho + \cdots + \rho^{n-1},
\end{align}
in $R[\mathrm{C}_n]$ generate the ideal of annihilators of each other. Therefore, the chain complex $\mathcal W(n)$ concentrated in non-negative degrees with $\mathcal W(n)_d$ the free $\Z[\mathrm{C}_n]$-module generated by one element $e_d$, and differential
\begin{equation*}
\partial(e_d) = \begin{cases}
Te_{d-1} & d \text{ odd,} \\
Ne_{d-1} & d \text{ even,}
\end{cases}
\end{equation*}
defines a resolution $\mathcal W(n) \to R$ in $\mathbf{Ch}_{R[\mathrm{C}_n]}$. It follow from a straightforward computation that for any prime $p$ and integer $q$
\begin{equation*}
H_i(\mathrm{C}_n; \mathbb{F}_p(q)) = \mathbb{F}_p.
\end{equation*}

The homology of $\mathrm{S}_n$ is harder to compute. With untwisted coefficients, the method of computation followed by several authors was to prove the injectivity of this homology into that of the infinite symmetric group and take advantage of a natural Hopf algebra structure on it. A powerful result stemming from the deep connection of this question with infinite loop space theory, is the existence of a homology isomorphism of spaces
\begin{equation*}
\Z \times B\mathrm{S}_\infty \to Q(S^0) = \Omega^\infty \Sigma^\infty (S^0)
\end{equation*}
credited to Dyer-Lashof \cite{dyer62lashof}, Barratt-Priddy and Quillen \cite{barratt1972priddy}.

In this work, we are interested in the mod-$p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite{adem2004milgram} Corollary VI.1.4, is detected by the inclusion $\iota : \mathrm{C}_p \to \mathrm{S}_p$ whose homological kernel is described next.

\begin{lemma} \label{lem: Thom's theorem}
	Let $p$ be an odd prime and $q$ an integer. Consider
	\begin{equation*}
	(\iota_\ast)_n : H_n(\mathrm{C}_p; \mathbb{F}_p(q)) \to H_n(\mathrm{S}_p; \mathbb{F}_p(q))
	\end{equation*}
	then
	\begin{enumerate}
		\item If $q$ is even, $(\iota_\ast)_n = 0$ unless $n = 2t(p-1)$ or $n = 2t(p-1) - 1$,
		\item If $q$ is odd, $(\iota_\ast)_n = 0$ unless $n = (2t+1)(p-1)$ or $n = (2t+1)(p-1)-1$,
	\end{enumerate}
	for some integer $t$.
\end{lemma}

\begin{proof}
	This is proven as Theorem 4.1 in \cite{steenrod53cyclic} where Thom is also credited with a different proof.
\end{proof}

In section 5 we will see how the cohomology of symmetric groups defines operations on algebras that are commutative up to coherent homotopies. Preparing for that, we first developed the language of $\Gamma$-modules and operads, where the integral structure defining Steenrod operations is clearly expressed.

\section{$\Gamma$-modules, operads and PROPs}

In this section we set up a framework in which the structure responsible for Steenrod operations becomes most transparent. Given our applications, we consider $\mathbf{Ch}_R$ as the base category, remarking that all definitions in this section apply to general closed symmetric monoidal categories.

\subsection{$\Gamma$-modules}
Recall that a group $\mathrm G$ can be thought of as a category with a single object and only invertible morphisms, and that a chain complex of left (resp. right) $R[\mathrm G]$-modules is the same as a covariant (resp. contravariant) functor from $\mathrm G$ to $\mathbf{Ch}_R$. Right actions are more commonly used in the literature of operads so we emphasize that perspective. Taking inverses allows for the switch between these two conventions.

A \textit{groupoid} is a small category where all morphisms are invertible.
\begin{definition}
	A \textit{$\Gamma$-module} is a contravariant functor to $\mathbf{Ch}_R$ from a groupoid $\Gamma$ with objects the natural numbers and morphisms satisfying $\Gamma(r,s) = \emptyset$ for $r \neq s$. We denote the category of $\Gamma$-modules and natural transformations by $\mathbf{Ch}_R^\Gamma$.
\end{definition}

We are mostly interested in two examples of $\Gamma$-modules, those associated to the groupoids $\mathrm{S}$ and $\mathrm{C}$ defined by
\begin{equation*}
\mathrm{S}(r, r) = \mathrm{S}_r, \qquad
\mathrm{C}(r,r) = \mathrm{C}_r,
\end{equation*}
for every $r \in \mathbb{N}$. The inclusion $\mathrm{C}_r \to \mathrm{S}_r$ induces a forgetful functor
\begin{equation*}
\begin{tikzcd} [column sep = small]
\mathbf{Ch}_R^\mathrm{S}  \arrow[r] & \mathbf{Ch}_R^\mathrm{C}.
\end{tikzcd}
\end{equation*}

Given an object $A$ in $\mathbf{Ch}_R$ there are two important $\Gamma$-modules associated to it; an $\mathrm{S}$-module known as \textit{endomorphism $\mathrm{S}$-module} $\End_A$, and an $\mathrm{S}^{op}$-module known as \textit{coendomorphism $\mathrm{S}$-module} $\End^A$. These are defined by
\begin{align*}	
\End_A(r) &= \Hom(A^{\otimes r},A), \\
\End^A(r) &= \Hom(A,A^{\otimes r}),
\end{align*}
with respective right and left actions defined by permutation of tensor factors.

Another groupoid of importance to us is $\mathrm{S} \times \mathrm{S}^{op}$. Contravariant functors from it to $\mathbf{Ch}_R$ are called \textit{$\mathrm{S}$-bimodules} and their functor category is denoted $\mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}}$. Notice that the inclusions
define forgetful functors
\begin{equation*}
\begin{tikzcd}[column sep=small, row sep=tiny]
& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"'] \arrow[dr, "U_2"] & \\
\mathbf{Ch}_R^{\mathrm{S}} &  & \mathbf{Ch}_R^{\mathrm{S}^{op}},
\end{tikzcd}
\end{equation*}
and that for any object $A$ in $\mathbf{Ch}_R$, the canonical \textit{endomorphism bimodule}
\begin{equation*}
\End_A^A(r, s) = \Hom(A^{\otimes r}, A^{\otimes s})
\end{equation*}
forgets to $\End_A$ and $\End^A$.

Using the groupoid automorphism sending every morphisms to its inverse we can identify $\Gamma$- and $\Gamma^{op}$- modules. In particular, the statement claiming that the linear duality functor induces a morphism of $\mathrm{S}$-modules
\begin{equation*}
\End^A \to \End_{\Hom(A, R)}
\end{equation*}
for every object $A$ in $\mathbf{Ch}_R$ is well defined and easily verified using this identification.

A \textit{resolution} in $\mathbf{Ch}_R^\Gamma$ is a morphism $\phi$ of $\Gamma$-modules such that $\phi(r)$ is a resolution in the category of chain complexes of $R[\Gamma_r]$-modules for each $r \in \mathbb{N}$. A $\Gamma$-module $\mathcal R$ is said to be $E_\infty$ if $\mathcal R(0) = R$ and there exists a resolution $\mathcal R \to \underline{R}$ where $\underline{R}$ is the object in $\mathbf{Ch}_R^\Gamma$ defined by $\underline{R}(r) = R$ and $\underline{R}(\gamma) = \mathrm{id}_R$ for every $r \in \mathbb{N}$ and $\gamma \in \Gamma_r$.

\begin{definition} \label{def: minimal cyclic resolution}
	The \textit{minimal} $E_\infty$-$\mathrm{C}$-\textit{module} $\mathcal W$ is the functor in $\mathbf{Ch}_R^\mathrm{C}$ assigning to $r$ the chain complex
	\begin{equation*}
	\begin{tikzcd} [column sep = .5cm]
	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] \cdots
	\end{tikzcd}
	\end{equation*}
	concentrated in non-negative degrees.
\end{definition}

\subsection{Operads and PROPs}

Operads an PROPs are respectively $\mathrm{S}$-modules and \mbox{$\mathrm{S}$-bimodules} enriched with further compositional structure. These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a PROP.

Succinctly, an operad $\mathcal O$ is an $\mathrm{S}$-module together with a collection of $R$-linear maps
\begin{equation*}
\mathcal O(r) \otimes \mathcal O(s) \to \mathcal O(r+s-1)
\end{equation*}
satisfying suitable associativity, equivariance and unitality conditions. A PROP $\mathcal P$ is an $\mathrm{S}$-bimodule together with two types of compositions; horizontal
\begin{equation*}
\mathcal P(r_1, s_1) \otimes \mathcal P(r_2, s_2) \to \mathcal P(r_1 + r_2, s_1 + s_2)
\end{equation*}
and vertical
\begin{equation*}
\mathcal P(r,s) \otimes \mathcal P(s, t) \to \mathcal P(r, t)
\end{equation*}
satisfying their own versions of associativity, equivariance and unitality. For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008operads}.

We have already mentioned that for any chain complex $A$, the $\mathrm{S}$-module $\End_A$ is naturally an operad and the $\mathrm{S}$-bimodule $\End_A^A$ is naturally a PROP. We add that considering $\End^A$ as an $\mathrm{S}$-module, its compositional structure also defines an operad structure on it.

We remark that the compositional structure of a PROP $\mathcal P$ restricts to operad structures on $U_1(\mathcal P)$ and $U_2(\mathcal P)$.

The type of operads that we are most interested in are $E_\infty$-operads which, as we will discuss in the next section, are used to describe commutativity up to coherent homotopies.

\begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}]
	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a PROP $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
\end{definition}

\subsection{Algebras, coalgebra and bialgebras}

A morphisms of operads or of PROPs is simply a morphisms of their underlying $\mathrm{S}$-modules or $\mathrm{S}$-bimodules preserving the respective compositional structures.

Given a chain complex $A$, an operad $\mathcal O$ and a PROP $\mathcal P$. An $\mathcal O$-\textit{algebra} (resp. $\mathcal O$-\textit{coalgebra}) structure on $A$ is an operad morphism $\mathcal O \to \End_A$ (resp. $\mathcal O \to \End^A$), and a $\mathcal P$-\textit{bialgebra} structure on $A$ is a PROP morphism $\mathcal P \to \End_A^A$.

We remark that the linear duality functor naturally transforms an $\mathcal O$-coalgebra structure on a chain complex into an $\mathcal O$-algebra structure on its dual.

Algebras over $E_\infty$-operads are the central objects of study in this work. To develop intuition for them, let us consider a chain complex $A$ with an algebra structure over $\underline{R}$, thought of as an operad with all compositions corresponding to the identity map $R \to R$. The $\underline{R}$-algebra structure on $A$ is generated by a linear map $\mu \colon A \otimes A \to A$ which is (strictly) commutative and associative, and a linear map $\eta \colon R \to A$ that determines a (two-sided) unit for $\mu$. Since $E_\infty$-operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies. The two main examples to keep in mind are the cochains of spaces and the chains of infinite loops spaces.

\section{Steenrod-Adem structures}

We now introduce an operadic formulation of a structure giving rise to Steenrod operations at every prime. It is based on \cites{steenrod47products, steenrod53symmetric, steenrod53cyclic, may70generalapproach}, and takes a viewpoint that emphasizes the integral structure needed to define them and prove their relations at every prime. For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}.

\begin{definition} \label{def: Steenrod-Adem structure}
	A \textit{Steenrod-Adem structure} on an operad $\mathcal O$ is a 
	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad
	\begin{equation*}
	\begin{tikzcd}[column sep = normal, row sep = small]
	& \mathcal R \arrow[dr, "\phi", out=0] & \\
	\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \mathcal O
	\end{tikzcd}
	\end{equation*}
	such that $\iota$ is a quasi-isomorphism and $\phi$ a morphism of operads.
\end{definition}

\begin{remark} \label{rmk: Deligne conjecture}
	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$. In this language, a choice of factorization for a Steenrod-Adem structure defines in particular a \textit{commutative multiplication}.
\end{remark}

\begin{definition}
	Let $A$ be a chain complex. A Steenrod-Adem structure on $\mathrm{End}_A$ is referred to as one on $A$. Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod} $(r, i)$-\textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
\end{definition}

\begin{remark}
	Restricting a Steenrod-Adem structure on a chain complex $A$ to a given arity $r$ corresponds to specifying a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$. This pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ introduced in \cite{may70generalapproach} Definition 2.1. Furthermore, the restriction to arity $r^2$ enhances this pair to an \textit{Adem object} as described in Definition 4.1 loc. cit.
\end{remark}

A Steenrod-Adem structure on a chain complex $A$ allows us to define operations on its $\mathbb{F}_p$-homology for every prime $p$. These operations are structurally different if $p$ is even or odd. Using the previous Remark, the definitions below recover Steenrod's original definition for the cohomology of spaces and that of Araki-Kudo-Dyer-Lashof operations for the homology of infinite loop spaces.

For the rest of this section $A$ is a chain complex equipped with a Steenrod-Adem structure.

\begin{definition}
	For any prime $p$, the $\mathbb{F}_p$-linear map
	\begin{equation*}
	D^p_i : (A \otimes \mathbb{F}_p) \to (A \otimes \mathbb{F}_p)
	\end{equation*}
	is defined by sending $a$ to the Steenrod \mbox{$(p, i)$-product} of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
\end{definition}

We notice that if $a$ is of degree $q$ then $D^p_i(a)$ is of degree $q + (p-1)q + i$.

\begin{definition}
	For any integer $s$, the \textit{Steenrod operation}
	\begin{equation*}
	P_s : H_\bullet(A; \mathbb{F}_2) \to H_{\bullet + s}(A; \mathbb{F}_2)
	\end{equation*}
	is defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_2)$ of degree $q$ to the class represented by $D^2_{s-q}(a)$.
\end{definition}

Notice that the Steenrod squares are determined by the Steenrod $(2,i)$-products with $\mathbb{F}_2$-coefficients. These binary operations are known as cup-$i$ products. In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod $\big(p, k(p-1)-\varepsilon\big)$-products for $\varepsilon \in \{0,1\}$. We can explain the appearance of these specific Steenrod products as follows. The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even an $(2t+1)(p-1) - \varepsilon$ if $q$ is odd. According to Lemma \ref{lem: Thom's theorem}, these are the only homologically non-trivial cases.

\begin{definition} \label{def: Steenrod operations at odd prime}
	For any integer $s$, the \textit{Steenrod operations}
	\begin{equation*}
	P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1)}(A; \mathbb{F}_p)
	\end{equation*}
	and
	\begin{equation*}
	\beta P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1) - 1}(A; \mathbb{F}_p)
	\end{equation*}
	are defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_p)$ of degree $q$ to the classes represented respectively for $\varepsilon \in\{0,1\}$ by
	\begin{equation*}
	(-1)^s \nu(q) D^p_{(2s-q)(p-1)-\varepsilon}(a)
	\end{equation*}
	where $\nu(q) = (-1)^{q(q-1)m/2}(m!)^q$ and $m = (p-1)/2$.
\end{definition}

\begin{remark}
	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq. 6.1. in \cite{steenrod53cyclic}). The notation $\beta P_s$ is motivated by the relationship of this operator and the Bockstein of the reduction $\mathbb Z \to \mathbb Z/p\mathbb Z$.
\end{remark}

Steenrod operations satisfy the Cartan and Adem relations. Below we state the subset of these relations that is most commonly used and refer to Sections 2 and 4 of \cite{may70generalapproach} for a complete list and proofs.
\begin{lemma}
	Let $A$ be equipped with a Steenrod-Adem structure. If $[\alpha], [\beta] \in H(A;\mathbb{F}_p)$ then
	\begin{equation*}
	P_s\big([\alpha] [\beta]\big) = \sum_{i+j=s} P_i\big( [\alpha] \big) P_j\big( [\beta] \big),
	\end{equation*}
	and
	\begin{itemize}
		\item If $p = 2$ and $a > 2b$
		\begin{equation*}
		P_{a}P_{b} = \sum_i {2i-a \choose a-b-i-1} P_{a+b-i}P_i,
		\end{equation*}
		\item If $p > 2$ and $a > pb$
		\begin{equation*}
		P_{a}P_{b} = \sum_i (-1)^{a+i}{pi-a \choose a-(p-1)b-i-1} P_{a+b-i}P_i.
		\end{equation*}
	\end{itemize}		
\end{lemma}

\begin{proof}
	These are proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
\end{proof}

For the even prime, proofs at the chain level of these formulae have been given in \cite{medina2020cartan,brumfiel2020cochain}. For a different operadic approach to Steenrod operations at the even prime please consult \cite{chataur2005adem-cartan}.

For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$, which we use in subsections 6.4 and 6.5.

\section{Effective constructions}
\label{sec: effective constructions}

In this section we construct explicit Steenrod-Adem structures on three well know combinatorial $E_\infty$-operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-PROP $\mathcal M$ \cite{medina2020prop1}. We also define natural and effective Steenrod-Adem structure on the normalized cochains of any simplicial or cubical set, by describing a $U(\mathcal M)$-algebra structures on it.

Figure~\ref{fig: bigsummary} presents a diagrammatical representation of the constructions in this section.

\begin{figure}
	\begin{tikzcd}
	& & & U(\mathcal M) \arrow[dddr, bend left=10, "\phi^\triangle"'] \arrow[dddrr, bend left=20, "\phi^\square"'] & & \\
	& & \mathcal X \arrow[ru, "SL"] & & & \\
	& \mathcal E \arrow[ur, "TR"] & & & & \\
	\mathcal W \arrow[rrrr, "\psi^\triangle", bend right=10] \arrow[rrrrr, "\psi^\square", bend right=20] \arrow[ur, "\psi_{\mathcal E}"] \arrow[uurr, "\psi_{\mathcal X}"', bend right=35, pos=.6] \arrow[uuurrr, "\psi_{U(\mathcal M)}"', bend right=45, pos=0.6] & & & & \End_{N^\bullet(X)} & \End_{N^\bullet(X)}
	\end{tikzcd}
	\caption{Summary of effective constructions: Steenrod-Adem structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural Steenrod-Adem structures on the normalized chains of simplicial and cubical sets. We are abusing notation since the maps $TR$ and $SL$ required different sign conventions.}
	\label{fig: bigsummary}
\end{figure}

\subsection{Barratt-Eccles operad} In this subsection we effectively describe a Steenrod-Adem structure on the Barratt-Eccles operad.

We begin by reviewing the $\mathrm{S}$-module structure underlying the Barratt-Eccles operad and, since will not use it in this work, refer to \cite{berger04combinatorial} for a description of if composition structure. For a non-negative integer $r$ define the simplicial set $E(\mathrm S_r)$ by 
\begin{equation} \label{eq: milnor model of symmetric}
\begin{split}
E(\mathrm S_r)_n &= \{ (\sigma_0, \dots, \sigma_n)\ |\ \sigma_i \in \mathrm{S}_r\}, \\
d_i(\sigma_0, \dots, \sigma_n) &= (\sigma_0, \dots, \widehat{\sigma}_i, \dots, \sigma_n), \\
s_i(\sigma_0, \dots, \sigma_n) &= (\sigma_0, \dots, \sigma_i, \sigma_i, \dots, \sigma_n) \\
\end{split}
\end{equation}
with a left $\mathrm S_r$-action given by
\begin{equation*}
\sigma (\sigma_0, \dots, \sigma_n) = (\sigma \sigma_0, \dots, \sigma \sigma_n).
\end{equation*} 
The chain complex resulting from applying the functor of normalized integral chains to it is denoted $\mathcal E(r)$, which corresponds to the arity $r$ part of the Barratt-Eccles operad.

\begin{definition} \label{def: Steenrod-Adem on Barratt-Eccles}
	For every $r \geq 0$, let $\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined on basis elements by 
	\begin{equation*}
	\psi_{\mathcal E}(r)(e_{n}) = \begin{cases}
	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \rho^{r_2}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m, \\
	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m+1,
	\end{cases}
	\end{equation*}
	where the sum is over all $r_1, \dots, r_m \in \{0, \dots, r-1\}$.
\end{definition}

\begin{theorem} \label{thm: Steenrod-Adem on Barratt-Eccles}
	The morphism of $\mathrm{C}$-modules
	\begin{equation*}
	\psi_{\mathcal E} \colon \mathcal W \to \mathcal E
	\end{equation*}
	defines a Steenrod-Adem structure on the Barratt-Eccles operad.
\end{theorem}

\begin{proof}
	This theorem follows from a computation which we defer to the appendix.
\end{proof}

\begin{example}
	Table \ref{fig: Barratt-Eccles Steenrod products} shows $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$.
\end{example}

\begin{table}[h]
	\centering
	\resizebox{0.8\columnwidth}{!}{%
		\renewcommand{\arraystretch}{1.2}
		\begin{tabular}{|c||c|c|c|}
			\hline
			$r$ & $n=2$ & $n=3$ & $n=4$ \\
			\hline
			2 & (0,1,0) & (0,1,0,1) & (0,1,0,1,0) \\
			\hline
			3 & (0,1,2) + (0,2,0) & (0,1,2,0) + (0,1,0,1) & \phantom{+} (0,1,2,0,1) + (0,1,2,1,2) \\
			& & & + (0,2,0,1,2) + (0,2,0,2,0) \\
			\hline
			4 & (0,1,2) + (0,2,3) & (0,1,2,3) + (0,1,3,0) & \phantom{+} (0,1,2,3,0) + (0,1,2,0,1) \\
			& + (0,3,0) & + (0,1,0,1) & 
			+ (0,1,2,1,2) + (0,2,3,0,1) \\
			& & & + (0,2,3,1,2) + (0,2,3,2,3) \\
			& & & + (0,3,0,1,2) + (0,3,0,2,3) \\
			& & & + (0,3,0,3,0) \\
			\hline  
		\end{tabular}
	}
	\vspace*{3pt}
	\caption{The elements $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$ where we are denoting $(\rho^{r_0}, \dots, \rho^{r_n})$ simply by $(r_0, \dots, r_n)$.}
	\label{fig: Barratt-Eccles Steenrod products}
\end{table}

\begin{remark}
	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota : \mathrm C_r \to \mathrm S_r$ induces a simplicial map $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ which extends to a quasi-isomorphism of $\mathrm C$-modules
	\begin{equation*}
	N_\bullet E(\iota) : N_\bullet E(\mathrm C) \to N_\bullet E(\mathrm S) = \mathcal E,
	\end{equation*}
	factoring
	\begin{equation*}
	\psi_{\mathcal E} :
	\begin{tikzcd}
	\mathcal W \arrow[r, "\phi_{\mathrm C}"] &[-3pt] N_\bullet E(\mathrm C) \arrow[r, "N_\bullet E(\iota)"] &[5pt] \mathcal E.
	\end{tikzcd}
	\end{equation*}
\end{remark}

\subsection{Surjection operad}

In this subsection we introduce a Steenrod-Adem structures on the surjection operad. There are two widely used sign conventions for this operad respectively due to McClure-Smith \cite{mcclure03cochain} and Berger-Fresse \cite{berger04combinatorial}. Using the Berger-Fresse convention, we can define a Steenrod-Adem structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}. We define an Steenrod-Adem structure on the surjection operad in a convention independent way which recovers the table reduction Steenrod-Adem structure in the Berger-Fresse case.

Let us start by recalling the definition of the surjection operad. For a non-negative integer $r$ let $\mathcal X(r)_n$ be the free abelian group generated by all functions from $\{1, \dots, n+r\}$ to $\{1, \dots, r\}$ modulo the subgroup generated by degenerate functions, i.e., those which are either non-surjective or have a pair of equal consecutive values. We only describe the McClure-Smith convention since we refer to it in subsequent sections. The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s : \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top dimensional generator in the chain complex
\begin{equation} \label{eq: surjection boundary}
\bigotimes_{i = 1}^r N_\bullet \big( \triangle^{s^{-1}(i)}; \Z \big).
\end{equation}
Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at the time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on. Since we do not use the composition structure we refer to \cite{mcclure03cochain} for it.

Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure-Smith to prove $\mathcal X$ is an $E_\infty$-operad and whose introduction is credited to Benson \cite{benson1998rep}. Let the maps $i,\ p$ and $s$ be defined on basis elements, represented by sequences, as follows: $i : \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p : \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s : \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
with a 1, then the new sequence is degenerate so $s$ takes it to $0$. These maps satisfy
\begin{equation*}
p  i = \mathrm{id}
\qquad \text{ and } \qquad
\mathrm{id} - i  p = \partial s + s \partial.
\end{equation*}
These maps define a contraction of $\mathcal X(r)$ onto $\mathcal X(1) \cong \Z$ with homotopy $h = s + i\, s\, p + \cdots + i^{r-1} s\, p^{r-1}$, satisfying
\begin{equation*}
\partial h + h \partial = \mathrm{id} - i^{r-1}\,p^{r-1}.
\end{equation*}

\begin{definition} \label{def: Steenrod-Adem on surjection}
	For every $r \geq 0$, let $\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined recursively on basis elements by
	\begin{align*}
	\psi_{\mathcal X}(r)(e_0) & = (1, \dots, r), \\
	\psi_{\mathcal X}(r)(e_{2m+1}) & = h\,T\,\psi_{\mathcal X}(r)(e_{2m}), \\
	\psi_{\mathcal X}(r)(e_{2m}) & = h\,N\,\psi_{\mathcal X}(r)(e_{2m-1}),
	\end{align*}
	where $T$ and $R$ are defined in \eqref{eq: T and R definition}.
\end{definition}

\begin{theorem} \label{thm: Steenrod-Adem on surjection MS convention}
	The morphism of $\mathrm{C}$-modules
	\begin{equation*}
	\psi_{\mathcal X} \colon \mathcal W \to \mathcal X
	\end{equation*}
	defines a Steenrod-Adem structure on the Surjection operad.
\end{theorem}

\begin{proof}
	This theorem follows from a computation which we defer to the appendix.
\end{proof}

For the rest of the paper we use the McClure-Smith convention.

\begin{example}
	Table \ref{fig: surjection Steenrod products} shows $\psi_{\mathcal X}(r)(e_n)$ for small values of $r$ and $n$.
\end{example}

\begin{table}[h]
	\centering
	\resizebox{\columnwidth}{!}{%
		\renewcommand{\arraystretch}{1.3}
		\begin{tabular}{|c||c|c|c|}
			\hline
			$r$& $n=2$ & $n=3$ & $n=4$ \\
			\hline
			2 & (1,2,1,2) & (1,2,1,2,1) & (1,2,1,2,1,2) \\
			\hline
			3 & (1,2,3,1,2) + (1,3,1,2,3) & (1,2,3,1,2,3) + (1,2,1,2,3,1)  & \phantom{+} (1,2,3,1,2,3,1) + (1,2,3,2,3,1,2) \\
			& + (1,2,3,2,3) & + (1,2,3,1,3,1) & + (1,2,3,1,2,1,2) + (1,3,1,2,3,1,2) \\
			& & & + (1,3,1,3,1,2,3) + (1,2,3,2,3,2,3) \\
			& & & + (1,3,1,2,3,2,3) \\
			\hline
			4 & \phantom{+} (1,2,3,4,1,2) + (1,3,4,1,2,3) & \phantom{+} (1,2,3,4,1,2,3) + (1,2,4,1,2,3,4) & \\
			& + (1,2,3,4,2,3) + (1,4,1,2,3,4) & + (1,2,3,4,1,3,4) + (1,2,1,2,3,4,1) & 25 \text{ terms } \\
			& + (1,2,4,2,3,4) + (1,2,3,4,3,4) & + (1,2,3,1,3,4,1) + (1,2,3,4,1,4,1) & \\
			\hline  
		\end{tabular}
	}
	\vspace*{2pt}
	\caption{The values of $\psi_{\mathcal X}(r)(e_n)$ for small values of $r$ and $n$.}
	\label{fig: surjection Steenrod products}
\end{table}

\subsection{The finitely presented $E_\infty$-PROP $\mathcal M$}

We start by reviewing the finitely presented $E_\infty$-PROP introduced in \cite{medina2020prop1}. Let $\mathcal M$ be the PROP generated by 
\begin{equation*}
\counit \in \mathcal M(1,0)_0, \hspace*{.6cm} \coproduct \in \mathcal M(1,2)_0, \hspace*{.6cm} \product \in \mathcal M(2,1)_1,
\end{equation*}
with boundary
\begin{equation*}
\partial\ \counit = 0, \hspace*{.6cm} \partial \ \coproduct = 0, \hspace*{.6cm} \partial \ \product = \ \boundary \, ,
\end{equation*}
and restricted by the relations
\begin{equation*}
\productcounit, \hspace*{.6cm} \leftcounitality \, , \hspace*{.6cm} \rightcounitality \, .
\end{equation*}

Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$-prop in the terminology of Bordmann-Vogt \cite{boardman1973homotopy}. More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$-operad. For the remainder of this article we write $U(\mathcal M)$ instead of $U_2(\mathcal M)$.

We will define a Steenrod-Adem structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the Steenrod-Adem structure $\psi_{\mathcal X} : \mathcal W \to \mathcal X$ with a morphism of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact)
\begin{equation*}
SL \colon \mathcal X \to U(\mathcal M)
\end{equation*}
that we now define. Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element
\begin{center}
	\begin{tikzpicture}[scale=.85]
	\draw (0,0)--(0,-.6) node[below]{$\scriptstyle 1$};
	\draw (0,0)--(.5,.5);
	\draw (-.3, .3)-- (-.2,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_1$};
	\draw (-.5,.5)--(0,0);
	\node at (.11,.4){$...$};

	\node at (1,0){$\scriptstyle \cdots$};
	\node at (1,-.9){$\scriptstyle \cdots$};

	\draw (2,0)--(2,-.68) node[below]{$\scriptstyle r$};
	\draw (2,0)--(2.5,.5);
	\draw (1.7, .3)-- (1.8,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_r$};
	\draw (1.5,.5)--(2,0);
	\node at (2.11,.4){$...$};

	\draw (1,2.5)--(1,3) node[above]{$\scriptstyle 1$};
	\draw (1,2.5)--(0,2) node[below]{$\scriptstyle 1$};
	\draw (.25,2.125)--(.5,2) node[below]{$\scriptstyle 2$};
	\draw (.5,2.25)--(1,2) node[below]{$\scriptstyle 3$};
	\draw (1,2.5)--(2,2) node[below]{\quad $\scriptstyle n + r$};
	\node at (1.5,1.75){$...$};

	\node at (1,1.3) {$\vdots$};

	\node at (2.85,0){};
	\end{tikzpicture}
\end{center}
that has no internal vertices and such that the $n+r$ strands at the top are orderly connected to the strands at the bottom following the values of $s$.

It can be directly verified using the presentation of $\mathcal M$ that the boundary of $SL(s)$ is obtained by removing strands one at the time in the order they are attached at the bottom. This is precisely the image of $SL(\partial s)$ according to \eqref{eq: surjection boundary}. Furthermore, relabeling the bottom edges agrees with the permutation of preimages of the associated surjection. Since both operads have the homology of a point and $(1, \dots, r)$ is sent to a representative of a homology generator we have proven the following

\begin{theorem} \label{thm: Steenrod-Adem on U(M)}
	The composition $\psi_{U(\mathcal M)}$
	\begin{equation*}
	\begin{tikzcd}[column sep = normal]
	\mathcal W \arrow[r, "\psi_{\mathcal X}"] & \mathcal X \arrow[r, "SL"] & U(\mathcal M)
	\end{tikzcd}
	\end{equation*}
	defines a Steenrod-Adem structure on $U(\mathcal M)$.
\end{theorem}

\begin{example}
	Figure \ref{fig: cup 0,1,2} shows $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$.
\end{example}

\begin{figure}[h]
	\centering
	\boxed{
		\begin{tikzpicture}[scale=.55]
		\draw (1,3.7) to (1,3);

		\draw (1,3) to [out=205, in=90] (0,0);
		\draw (1,3) to [out=-25, in=90] (2,0);

		\node at (1,-.5){$n=0$};
		\end{tikzpicture}\hspace*{1cm}
		\begin{tikzpicture}[scale=.55]
		\draw (1,3.7) to (1,3);

		\draw (1,3) to [out=205, in=90] (0,0);

		\draw [shorten >= 0cm] (.6,2.73) to [out=-100, in=90] (2,0);
		%\draw [shorten <= 0cm] (1,1.5) to [out=-60, in=90] (2,0);

		\draw [shorten >= .15cm] (1,3) to [out=-25, in=30, distance=1.1cm] (1,1.5);
		\draw [shorten <= .1cm] (1,1.5) to [out=210, in=20] (0,1);

		\node at (1,-.5){$n=1$};
		\end{tikzpicture}\hspace*{1cm}
		\begin{tikzpicture}[scale=.55]
		\draw (1,3.7) to (1,3);

		\draw (1,3) to [out=205, in=90] (0,0);
		\draw (1,3) to [out=-25, in=90] (2,0);

		\draw [shorten >= 0cm] (.6,2.73) to [out=210, in=135] (1,1.5);
		\draw [shorten <= 0cm] (1,1.5) to [out=-45, in=170] (2,1);

		\draw [shorten >= .1cm] (1.4,2.73) to [out=-30, in=45] (1,1.5);
		\draw [shorten <= .1cm] (1,1.5) to [out=-135, in=10] (0,1);

		\node at (1,-.5){$n=2$};
		\end{tikzpicture}
	}
	\caption{The values of $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$.}
	\label{fig: cup 0,1,2}
\end{figure}

\subsection{Cochains of simplicial sets}

In this subsection we introduce a natural Steenrod-Adem structure on the normalized cochains of any simplicial set $X$. Since a Steenrod-Adem structure was constructed in the previous section for $U(\mathcal M)$, we only need to describe a natural $U(\mathcal M)$-algebra structure on $N^\bullet(X)$. Using the linear duality functor, it suffices to construct a natural $U(\mathcal M)$-coalgebra structure on $N_\bullet(X)$ which, in turn, can be derived via a Kan extension argument from one on each $N_\bullet(\triangle^n)$. We obtain these coalgebra structures by restricting a full $\mathcal M$-bialgebra structure. An $\mathcal M$-bialgebra structure is specified by three linear maps, the images of the generators
\begin{equation*}
\counit, \quad \coproduct, \quad \product,
\end{equation*}
satisfying the relations in the presentation of $\mathcal M$. For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
(1) The counit $\epsilon \in \Hom(N_\bullet(\triangle^n), \Z)$ by
\begin{equation*}
\epsilon \big( [v_0, \dots, v_q] \big) = \begin{cases} 1 & \text{ if } q = 0, \\ 0 & \text{ if } q>0. \end{cases}
\end{equation*}
(2) The coproduct $\Delta \in \Hom(N_\bullet(\triangle^n), N_\bullet(\triangle^n)^{\otimes2})$ by
\begin{equation*}
\Delta \big( [v_0, \dots, v_q] \big) = \sum_{i=0}^q [v_0, \dots, v_i] \otimes [v_i, \dots, v_q].
\end{equation*}
(3) The product $\ast \in \Hom(N_\bullet(\triangle^n)^{\otimes 2}, N_\bullet(\triangle^n))$ by
\begin{equation*}
\left[v_0, \dots, v_p \right] \ast \left[v_{p+1}, \dots, v_q\right] = \begin{cases} (-1)^{p+|\pi|} \left[v_{\pi(0)}, \dots, v_{\pi(q)}\right] & \text{ if } v_i \neq v_j \text{ for } i \neq j, \\
0 & \text{ if not}, \end{cases}
\end{equation*}
where $\pi$ is the permutation that orders the totally ordered set of vertices, and $(-1)^{|\pi|}$ its sign.

\begin{theorem} \label{thm: simplicial chain bialgebra}
	For every $n \in \mathbb{N}$, the assignment
	\begin{equation*}
	\counit \mapsto \epsilon, \quad \coproduct \mapsto \Delta, \quad \product \mapsto \ast,
	\end{equation*}
	defines a natural $\mathcal M$-bialgebra structure  on $N_\bullet(\triangle^n)$.
\end{theorem}

\begin{proof}
	This statement is proven as Theorem 4.2 in \cite{medina2020prop1}.
\end{proof}

\begin{definition}
	Let $X$ be a simplicial set. Denote by $\phi^\triangle : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem \ref{thm: simplicial chain bialgebra}.
\end{definition}

\begin{theorem}
	The commutative diagram
	\begin{equation*}
	\begin{tikzcd}[column sep = small, row sep = small]
	&[18pt] U(\mathcal M) \arrow[dr, "\phi^\triangle", out=0] &[-0pt] \\
	\mathcal W \arrow[ur, "\psi_{U(\mathcal M)}", in=180] \arrow[rr, "\psi^\triangle"] & & \mathrm{End}_{N^\bullet (X)}
	\end{tikzcd}
	\end{equation*}
	defines a natural Steenrod-Adem structure on $N^\bullet(X)$ for any simplicial set $X$.
\end{theorem}

\begin{remark}
	The $E_\infty$-structure we described in Theorem \ref{thm: simplicial chain bialgebra}, depending solely on three fundamental maps, recovers the coalgebra structures of McClure-Smith \cite{mcclure03cochain} and, up to signs, that of Berger-Fresse \cite{berger04combinatorial}.
\end{remark}

\begin{example}
	Let us consider the prime $2$. The value $P^1(x)\big([0,1,2,3,4]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^4)$ is equal to the value of $x^{\otimes 2}$ acting on
	\begin{align*}
	[0, 1, 2, 3] \otimes [0, 1, 3, 4] \ +\  & 
	[0, 2, 3, 4] \otimes [0, 1, 2, 4] \\ \ +\ 
	[0, 1, 2, 3] \otimes [1, 2, 3, 4] \ +\ &
	[0, 1, 3, 4] \otimes [1, 2, 3, 4].
	\end{align*}
	Similarly, the value of $P^2(y)\big([0,1,2,3,4,5,6,7]\big)$ for a homogeneous cocycle $y$ in $N^{-5}(\triangle^7)$ is equal to the value of $y^{\otimes 2}$ acting on
	\begin{align*}
	[0, 1, 2, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] & \ +\
	[0, 1, 2, 3, 6, 7] \otimes [0, 1, 3, 4, 5, 6] \\ \ +\ 
	[0, 1, 2, 3, 4, 7] \otimes [0, 1, 4, 5, 6, 7] & \ +\ 
	[0, 2, 3, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] \\ \ +\ 
	[0, 2, 3, 4, 6, 7] \otimes [0, 1, 2, 4, 5, 6] & \ +\ 
	[0, 2, 3, 4, 5, 7] \otimes [0, 1, 2, 5, 6, 7] \\ \ +\ 
	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] & \ +\ 
	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 5, 6] \\ \ +\ 
	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 6, 7] & \ +\ 
	[0, 1, 2, 3, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
	[0, 1, 2, 3, 4, 7] \otimes [1, 2, 4, 5, 6, 7] & \ +\ 
	[0, 1, 3, 4, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
	[0, 1, 3, 4, 5, 7] \otimes [1, 2, 3, 5, 6, 7] & \ +\ 
	[0, 1, 4, 5, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
	[0, 1, 4, 5, 6, 7] \otimes [1, 2, 3, 4, 6, 7] & \ +\ 
	[0, 1, 2, 3, 4, 7] \otimes [2, 3, 4, 5, 6, 7] \\ \ +\ 
	[0, 1, 2, 4, 5, 7] \otimes [2, 3, 4, 5, 6, 7] & \ +\ 
	[0, 1, 2, 5, 6, 7] \otimes [2, 3, 4, 5, 6, 7].
	\end{align*}
\end{example}

\begin{example}
	Let us consider the prime $3$. The value $\beta P^1(x)\big([0,1,2,3,4,5,6,7,8]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^8)$ is equal to the value of $x^{\otimes 3}$ acting on
	\begin{align*}
	& \,-\, [0, 6, 7, 8] \otimes [0, 1, 2, 3] \otimes [3, 4, 5, 6] \,+\, [0, 1, 7, 8] \otimes [1, 2, 3, 4] \otimes [4, 5, 6, 7] \\ & \,-\, [0, 1, 2, 8] \otimes [2, 3, 4, 5] \otimes [5, 6, 7, 8].
	\end{align*}
	Similarly, the value of $P^1(y)\big([0,1,\dots,7]\big)$ for a homogeneous cocycle $y$ in $N^{-3}(\triangle^7)$ is equal to the value of $y^{\otimes 3}$ acting on
	\begin{align*}
	& \,-\, [0,3,4,5] \otimes [0,5,6,7] \otimes [0,1,2,3] \,-\, [0,4,5,6] \otimes [0,1,6,7] \otimes [1,2,3,4] \\ & \,-\, [0,5,6,7] \otimes [0,1,2,7] \otimes [2,3,4,5] \,-\, [0,1,4,5] \otimes [1,5,6,7] \otimes [1,2,3,4] \\ & \,+\, [0,1,5,6] \otimes [1,2,6,7] \otimes [2,3,4,5] \,-\, [0,1,6,7] \otimes [1,2,3,7] \otimes [3,4,5,6] \\ & \,-\, [0,1,2,5] \otimes [2,5,6,7] \otimes [2,3,4,5] \,-\, [0,1,2,6] \otimes [2,3,6,7] \otimes [3,4,5,6] \\ & \,-\, [0,1,2,7] \otimes [2,3,4,7] \otimes [4,5,6,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [0,1,6,7] \\ & \,+\, [0,2,3,4] \otimes [4,5,6,7] \otimes [0,1,2,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [1,2,6,7] \\ & \,-\, [0,1,3,4] \otimes [4,5,6,7] \otimes [1,2,3,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [2,3,6,7] \\ & \,+\, [0,1,2,4] \otimes [4,5,6,7] \otimes [2,3,4,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [3,4,6,7] \\ & \,-\, [0,1,2,3] \otimes [3,5,6,7] \otimes [3,4,5,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [4,5,6,7] \\ & \,+\, [0,1,2,3] \otimes [3,4,6,7] \otimes [4,5,6,7].
	\end{align*}
\end{example}

\subsection{Cochains of cubical sets}

In this subsection we introduce a natural Steenrod-Adem structure on the normalized cochains of any cubical set. It follows the structure of the previous subsection closely. By the same considerations, the desired construction will follow from a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$. These are determined by three linear maps satisfying the relations in the presentation of $\mathcal M$. For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
(1) The counit $\epsilon \in \Hom(N_\bullet(\square^n), \Z)$ by
\begin{equation*}
\epsilon \left( x_1 \otimes \cdots \otimes x_d \right) = \epsilon(x_1) \cdots \, \epsilon(x_n),
\end{equation*}
where
\begin{equation*}
\epsilon([0]) = \epsilon([1]) = 1, \qquad \epsilon([0, 1]) = 0.
\end{equation*} \vspace*{-6pt} \\
(2) The coproduct $\Delta \in \Hom \left( N_\bullet(\square^n), N_\bullet(\square^n)^{\otimes 2} \right)$ by
\begin{equation*}	
\Delta (x_1 \otimes \cdots \otimes x_n) = 	
\sum \pm \left( x_1^{(1)} \otimes \cdots \otimes x_n^{(1)} \right) \otimes 	
\left( x_1^{(2)} \otimes \cdots \otimes x_n^{(2)} \right),	
\end{equation*}	
where the sign is determined using the Koszul convention, and we are using Sweedler's notation
\begin{equation*}	
\Delta(x_i) = \sum x_i^{(1)} \otimes x_i^{(2)}
\end{equation*}
for the chain map $\Delta \colon N_\bullet(\square^1) \to N_\bullet(\square^1)^{\otimes 2}$ defined by
\begin{equation*}
\Delta([0]) = [0] \otimes [0], \quad \Delta([1]) = [1] \otimes [1], \quad \Delta([0, 1]) = [0] \otimes [0, 1] + [0, 1] \otimes [1].
\end{equation*}
Using that $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$, $\Delta$ is the composition
\begin{equation*}
\begin{tikzcd}
N_\bullet(\square^1)^{\otimes n} \arrow[r, "\Delta^{\otimes n}"] & \left( N_\bullet(\square^1)^{\otimes 2}  \right)^{\otimes n} \arrow[r, "sh"] & \left( N_\bullet(\square^1)^{\otimes n} \right)^{\otimes 2}
\end{tikzcd}
\end{equation*}
where $sh$ is the shuffle map that places tensor factors in odd position first. \vspace*{5pt} \\
(3) The product $\ast \in \Hom(N_\bullet(\square^n)^{\otimes 2}, N_\bullet(\square^n))$ by
\begin{align*}
(x_1 \otimes \cdots \otimes x_n) \ast (y_1 \otimes \cdots \otimes y_n) =
(-1)^{|x|} \sum_{i=1}^n x_{<i} \epsilon(y_{<i}) \otimes x_i \ast y_i \otimes \epsilon(x_{>i})y_{>i},
\end{align*}
where
\begin{align*}
x_{<i} & = x_1 \otimes \cdots \otimes x_{i-1}, &
y_{<i} & = y_1 \otimes \cdots \otimes y_{i-1}, \\
x_{>i} & = x_{i+1} \otimes \cdots \otimes x_n, & 
y_{>i} & = y_{i+1} \otimes \cdots \otimes y_n,
\end{align*}
with the convention
\begin{equation*}
x_{<1} = y_{<1} = x_{>n} = y_{>n} = 1 \in \Z,
\end{equation*}
and the only non-zero values of $x_i \ast y_i$ are
\begin{equation*}
\ast([0] \otimes [1]) = [0, 1], \qquad  \ast([1] \otimes [0]) = -[0, 1].
\end{equation*}

\begin{theorem} \label{thm: cubical chain bialgebra}
	For every $n \in \mathbb{N}$, the assignment
	\begin{equation*}
	\counit \mapsto \epsilon, \quad \coproduct \mapsto \Delta, \quad \product \mapsto \ast,
	\end{equation*}
	defines a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$.
\end{theorem}

\begin{proof}
	We present a proof of this statement in the appendix.
\end{proof}

\begin{remark}
	We saw that for simplicial sets a natural algebraic $E_\infty$-structure was determined by basic maps in the standard simplices. For cubical sets, one such structure is constructed by naturally extending three maps defined just on the interval. 
\end{remark}

\begin{definition}
	Let $X$ be a cubical set. Denote by $\phi^\square : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem~\ref{thm: cubical chain bialgebra}.
\end{definition}

\begin{theorem}
	The commutative diagram
	\begin{equation*}
	\begin{tikzcd}[column sep = small, row sep = small]
	&[18pt] U(\mathcal M) \arrow[dr, "\phi^\square", out=0] &[-0pt] \\
	\mathcal W \arrow[ur, "\psi_{U(\mathcal M)}", in=180] \arrow[rr, "\psi^\square"] & & \End_{N^\bullet (X)}
	\end{tikzcd}
	\end{equation*}
	defines a natural Steenrod-Adem structure on $N^\bullet(X)$ for any cubical set $X$.
\end{theorem}

\begin{example}
	Let us consider the prime $2$. The value $P^1(x)\big([01]^{4}\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\square^4)$ is equal to the value of $x^{\otimes 2}$ acting on
	\begin{align*}&
	[01]1[01][01] \otimes [01][01]0[01]\,+\,
	[01][01][01]0 \otimes [01]0[01][01]\,+\, \\&
	[01][01][01]0 \otimes 1[01][01][01]\,+\,
	[01][01]1[01] \otimes [01]0[01][01]\,+\, \\&
	[01][01]1[01] \otimes 1[01][01][01]\,+\,
	[01][01][01]0 \otimes [01][01]1[01]\,+\, \\&
	[01][01]0[01] \otimes [01][01][01]1\,+\,
	[01]1[01][01] \otimes [01][01][01]1\,+\, \\&
	0[01][01][01] \otimes [01][01][01]1\,+\,
	0[01][01][01] \otimes [01][01]0[01]\,+\, \\&
	0[01][01][01] \otimes [01]1[01][01]\,+\,
	[01]0[01][01] \otimes 1[01][01][01].\,\phantom{+}\,
	\end{align*}
\end{example}

\begin{example}
	Let us consider the prime $3$. The value of $\beta P^0(x)\big([01]^2\big)$ for a homogeneous cocycle $x$ in $N^{-1}(\square^2)$ is equal to the value of $x^{\otimes 3}$ acting on
	\begin{align*}
	\,-\, [01]1 \otimes [01]0 \otimes 1[01] \,-\, 0[01] \otimes [01]0 \otimes 1[01] + [01]1 \otimes 0[01] \otimes [01]1 + 0[01] \otimes 0[01] \otimes [01]1.
	\end{align*}
\end{example}

\section{Outlook}
This article looked at Steenrod operations from an algebraic viewpoint, a subject with rich geometric and combinatorial components as well. For example, \cite{Postnikov} and \cite{medina2018prop2} independently introduced equivalent geometric representations of the cup-$i$ products in terms of stabilized arc surfaces \cite{KLP} and weighted ribbon graphs respectively. In fact, an entire $E_\infty$-operad (PROP) is constructed geometrically in this way. We can also interpret the Steenrod-Adem structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups ---a key ingredient in Definition \ref{def: minimal cyclic resolution}--- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.

In Higher Category Theory, the paper \cite{medina2020globular} constructs a functor producing strict \mbox{$\infty$-cat}egories from group-like cup-$i$ coalgebras in a manner similar to \cite{steiner2004omega}. In particular, the cup-$i$ constructions described in this article for standard simplices and cubes define, respectively, the Street nerve and cubical nerve of strict $\infty$-categories. We anticipate that the more general Steenrod $(p,i)$-products constructed in this work will also have deep combinatorial interpretations.

There is a functorial approach to the theory using the formalism of Feynman categories \cite{feynman},
which renders all the structures and notions natural. This includes cyclic, planar cyclic as well as Berger's pre-operads \cite{BergerRecog}. Their interplay is of independent interest \cite{BergerKaufmann,feyrep} and will be linked directly to the constructions of this paper.

In this article we have not focused on the operations that exist non-trivially for \mbox{$E_n$-algebras} with $n$ finite, see part III of \cite{may76homology}. A treatement close to ours for the $E_2$ case was given in \cite{Tourtchine}. Effective constructions for these Dyer-Lashof-Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang,sinha2013littledisks,berger04combinatorial,ayala2014configuration} and higher categories \cite{Bathigher,BalFiedSchwVogt,Rezkhigher}, and will appear elsewhere.

\newpage
\appendix
\section{Proofs}

\subsection{Theorem \ref{thm: Steenrod-Adem on Barratt-Eccles}}

We prove that the $\Z[\mathrm{C}_r]$-linear map
\begin{equation*}
\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)
\end{equation*}
introduced in Definition \ref{def: Steenrod-Adem on Barratt-Eccles} is a chain map for every $r \geq 0$. We simplify notation and write $\psi$ instead of $\psi_{\mathcal E}(r)$. To show $\psi$ is a chain map we proceed by induction. Notice that
\begin{equation*}
\psi(\partial e_0) = 0 = \partial \psi(e_0)
\end{equation*}
and assume $\psi(\partial e_{k-1}) = \partial \psi(e_{k-1})$. If $k = 2n$ we have
\begin{align*}
\partial \psi(e_{2n}) & = 
\partial \sum_{r_1, \dots, r_n} 
\big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
\partial \sum_{r_2, \dots, r_n} \sum_{r_1 = 0}^{p-1}
\big(\rho^0, \rho^{r_1} \, (\rho^0, \rho^{1}, \dots, \rho^{r_n-r_1}, \rho^{r_n - r_1 +1}) \big) \\ & =
\partial \sum_{r_2, \dots, r_n}
\big(\rho^0, N\, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1}) \big) \\ & =
\sum_{r_2, \dots, r_n}
N\, \big( \rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1} \big) \\ & -
\sum_{r_2, \dots, r_n}
\big(\rho^0, \partial \, N \, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n+1}) \big) \\ & =
N \psi(e_{2n-1}) - (\rho^0, \partial N \psi (e_{2n-1})) \\ & =
\psi(N e_{2n-1}) - (\rho^0, \psi (\partial N e_{2n-1})) \\ & =
\psi(\partial e_{2n}) - (\rho^0, \psi (\partial^2 e_{2n})) \\ & =
\psi(\partial e_{2n}).
\end{align*}
If $k = 2n+1$ we have
\begin{align*}
\partial \psi(e_{2n+1}) & = 
\partial \sum_{r_1, \dots, r_n} 
\big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
\partial \sum_{r_1, \dots, r_n}
\big(\rho^0, \rho^{1} \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
\partial \sum_{r_1, \dots, r_n}
\big(\rho^0, T\, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
\sum_{r_1, \dots, r_n}
T \, \big( \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n} \big) \\ & -
\sum_{r_1, \dots, r_n}
\big(\rho^0, \partial \, T \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
T \psi(e_{2n}) - (\rho^0, \partial T \psi (e_{2n})) \\ & =
\psi(T e_{2n}) - (\rho^0, \psi (\partial T e_{2n})) \\ & =
\psi(\partial e_{2n+1}) - (\rho^0, \psi (\partial^2 e_{2n+1})) \\ & =
\psi(\partial e_{2n+1})
\end{align*}
where for the third equality we used that for any $r_1, \dots, r_n$
\begin{equation*}
(\rho^0, \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) = 0.
\end{equation*}
This map is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0)$ represents a generator of the homology.

\subsection{Theorem \ref{thm: Steenrod-Adem on surjection MS convention}}

\begin{proof}
	We prove that the $\Z[\mathrm{C}_r]$-linear map
	\begin{equation*}
	\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)
	\end{equation*}
	introduced in Definition \ref{def: Steenrod-Adem on surjection} is a chain map for every $r \geq 0$. We simplify notation and write $\psi$ instead of $\psi_{\mathcal X}(r)$. To show $\psi$ is a chain map we proceed by induction. Notice that
	\begin{equation*}
	\psi(\partial e_0) = 0 = \partial \psi(e_0)
	\end{equation*}
	and assume $\psi(\partial e_{n-1}) = \partial \psi(e_{n-1})$. For $n = 2m+1$ we have
	\begin{align*}
	\partial \psi(e_{2m+1}) 
	& =
	\partial\, h\, T\, \psi(e_{2m}) \big) \\
	& =
	T\, \psi(e_{2m}) - i^{r-1} p^{r-1}\, \psi(e_{2m}) -
	h\, \partial\, T\, \psi(e_{2m}) \big) \\
	& =
	T\, \psi(e_{2m}) - 
	h\, T\, \psi(\partial\, e_{2m}) \big) \\
	& =
	T\, \psi(e_{2m}) - 
	h\, \psi(T\,N\, e_{2m-1}) \big) \\
	& = 
	T \psi(e_{2m}).
	\end{align*}
	For $n = 2m$ the proof is analogous. The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ is a generator of the homology.
\end{proof}

\subsection{Theorem \ref{thm: cubical chain bialgebra}}

The only non-trivial relation we need to verify is
\begin{equation*}
\partial \product = \, \boundary \, .
\end{equation*}
Let us consider two basis elements of $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$
\begin{align*}
x & = x_1 \otimes \cdots \otimes x_n, \\
y & = y_1 \otimes \cdots \otimes y_n.
\end{align*}
We need to show that
\begin{equation*}
\partial (x \otimes y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y = \epsilon(x) y - \epsilon(y) x.
\end{equation*}
We have
\begin{equation*}
x \ast y = \sum (-1)^{|x|} \epsilon(y_{<i})x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i})y_{>i}
\end{equation*}
and
\begin{align*}
\partial(x \ast y) & = 
\sum (-1)^{|x|} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
\sum (-1)^{|x|+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes \partial (x_i \ast y_i) \otimes \epsilon(x_{>i}) y_{>i} \\ & -
\sum (-1)^{|x|+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
\end{align*}
Since
\begin{equation*}
|x| = |x_{<i}| + |x_i| + |x_{>i}|, \quad \epsilon(x_{>i}) \neq 0 \Leftrightarrow |x_{>i}| = 0, \quad \partial(x_i \ast y_i) \neq 0 \Rightarrow |x_i| = 0,
\end{equation*}
we have
\begin{equation} \label{eq: boundary of product 1}
\begin{split}
\partial(x \ast y) & = 
\sum (-1)^{|x|} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
\sum \epsilon(y_{<i}) x_{<i} \otimes \partial (x_i \ast y_i) \otimes \epsilon(x_{>i}) y_{>i} \\ & -
\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
\end{split}
\end{equation}
We also have
\begin{align*}
\partial x \ast y & = 
\sum (-1)^{|x|-1} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
\sum (-1)^{|x|-1+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes \partial x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
\sum (-1)^{|x|-1+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(\partial x_{>i}) y_{>i}.
\end{align*}
Since
\begin{equation*}
\epsilon(\partial x_{>i}) = 0, \quad \partial x_i \neq 0 \Leftrightarrow |x_i| = 1,
\end{equation*}
we have
\begin{equation} \label{eq: boundary of product 2}
\begin{split}
\partial x \ast y & = 
\sum (-1)^{|x|-1} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
\sum \epsilon(y_{<i}) x_{<i} \otimes \partial x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i}.
\end{split}
\end{equation}
We also have
\begin{align*}
(-1)^{|x|} x \ast \partial y & = 
\sum \epsilon(\partial y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
\sum (-1)^{|y_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast \partial y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
\sum (-1)^{|y_{<i}|+|y_i|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i},
\end{align*}
which is equivalent to
\begin{equation} \label{eq: boundary of product 3}
\begin{split}
(-1)^{|x|} x \ast \partial y & = 
\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast \partial y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
\end{split}
\end{equation}
Putting identities \eqref{eq: boundary of product 1}, \eqref{eq: boundary of product 2} and \eqref{eq: boundary of product 3} together, we get
\begin{multline*}
\partial (x \otimes y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y =
\sum \epsilon(y_{<i}) x_{<i} \otimes \big(\partial(x_i \ast y_i) + \partial x_i \ast y_i + x_i \ast \partial y_i\big) \otimes \epsilon(x_{>i}) y_{>i}.
\end{multline*}
Since
\begin{equation*}
\partial(x_i \ast y_i) + \partial x_i \ast y_i + x_i \ast \partial y_i = \epsilon(x_i)y_i - \epsilon(y_i)x_i,
\end{equation*}
we have
\begin{align*}
\partial (x \otimes y) + \partial x \ast y + & (-1)^{|x|}x \ast \partial y \\ = &
\sum \epsilon(y_{<i}) x_{<i} \otimes \epsilon(x_{\geq i}) y_{\geq i} - \epsilon(y_{\leq i}) x_{\leq i} \otimes \epsilon(x_{>i}) y_{>i} \\ = &
\epsilon(x)y - \epsilon(y)x,
\end{align*}
as desired, where the last equality follows from a telescopic sum argument.

\bibliographystyle{alpha} 
\bibliography{bib}

\end{document}

### 2021-04-14 main.tex
Fix typos spotted by Federico's

@@
 We now review the group homology of finite cyclic groups. For any ring $R$ the elements
-\begin{align} \label{eq: T and R definition}
+\begin{equation} \label{eq: T and R definition}
+\begin{split}
 T &= \rho - 1, \\
 N &= 1 + \rho + \cdots + \rho^{n-1},
-\end{align}
+\end{split}
+\end{equation}
 in $R[\mathrm{C}_n]$ generate the ideal of annihilators of each other.
@@
 \begin{equation*}
-H_i(\mathrm{C}_n; \mathbb{F}_p(q)) = \mathbb{F}_p.
+H_i(\mathrm{C}_p; \mathbb{F}_p(q)) = \mathbb{F}_p.
 \end{equation*}
@@
 	\begin{tikzcd} [column sep = .5cm]
-	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] \cdots
+	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,T"'] \cdots
 	\end{tikzcd}
@@
 	\end{align*}
-	where $T$ and $R$ are defined in \eqref{eq: T and R definition}.
+	where $T$ and $N$ are defined in \eqref{eq: T and R definition}.
 \end{definition}
@@
 
-For the rest of the paper we use the McClure-Smith convention.
+For the rest of the paper we use the McClure-Smith sign convention on $\mathcal X$.
 
@@
 \begin{equation*}
-\partial (x \otimes y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y = \epsilon(x) y - \epsilon(y) x.
+\partial (x \ast y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y = \epsilon(x) y - \epsilon(y) x.
 \end{equation*}
@@
 \begin{align*}
-\partial (x \otimes y) + \partial x \ast y + & (-1)^{|x|}x \ast \partial y \\ = &
+\partial (x \ast y) + \partial x \ast y + & (-1)^{|x|}x \ast \partial y \\ = &
 \sum \epsilon(y_{<i}) x_{<i} \otimes \epsilon(x_{\geq i}) y_{\geq i} - \epsilon(y_{\leq i}) x_{\leq i} \otimes \epsilon(x_{>i}) y_{>i} \\ = &

### 2021-05-07 effective.tex
Split sections into files

--- 2021-04-14 main.tex
@@
-\documentclass[A4]{amsart}
-
-\usepackage{amsmath, amssymb, amsfonts}
-\usepackage{tikz-cd}
-\usepackage{graphics}
-\usepackage[bookmarks=true, linktocpage=true,
-bookmarksnumbered=true, breaklinks=true,
-pdfstartview=FitH, hyperfigures=false,
-plainpages=false, naturalnames=true,
-colorlinks=true, pagebackref=true,
-pdfpagelabels]{hyperref}
-\hypersetup{
-	colorlinks,
-	citecolor=blue,
-	filecolor=blue,
-	linkcolor=blue,
-	urlcolor=blue
-}
-\usepackage[alphabetic]{amsrefs}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\Hom}{\mathrm{Hom}}
-\newcommand{\End}{\mathrm{End}}
-\DeclareMathOperator*{\colim}{colim}
-
-\include{figures}
-
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.6in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
-\calclayout
-
-\begin{document}
-
-\title{Chain level Steenrod operations}
-
-\author[R. Kaufmann]{Ralph M.\ Kaufmann}
-\address{Department of Mathematics, Department of Physics and Astronomy, Purdue University}
-\email{rkaufman@purdue.edu}
-
-\author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
-\address{Laboratory for Topology and Neuroscience, École Polytechnique Fédérale de Lausanne, Switzerland}
-\address{Department of Mathematics, University of Notre Dame du Lac, Notre Dame, IN, USA}
-\email{amedinam@nd.edu}
-\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Max Plank Institute for Mathematics.}
-
-\subjclass[2010]{55S05, 55U05, 55S10, 55S12; 55-04, 55U15, 55S15}
-\keywords{Steenrod operations, Dyer-Lashof operations, simplicial cochains, cubical cochains}
-
-\begin{abstract}
-	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander-Whitney's chain approximation to the diagonal.
-Later, following a viewpoint developed by Adem, Steenrod defined his homonymous operations for all primes using the homology of symmetric groups.
-This approach enhanced the conceptual understanding of the operations and allowed for many advances but lacked the concreteness of their definition at~$2$.
-In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having a definition of Steenrod operations that can be effectively computed in specific examples has become a key issue.
-This article provides such definition, at all primes, for well known $E_\infty$-algebras including the cochains of spaces expressed via simplicial or cubical cell structures.
-\end{abstract}
-
-\maketitle
-
-\tableofcontents
-
-\section{Introduction}
-
-The role Steenrod operations play in Stable Homotopy Theory is hard to overstate.
-The reason is that, given the representability of the cohomology functor, these operations together with the Bockstein homomorphism can be used to give a complete description of the algebraic structure naturally present on the mop-$p$ \mbox{cohomology} algebra of spaces.
-For the even prime, Steenrod squares were introduced in \cite{steenrod47products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander-Whitney's chain approximation to the diagonal.
-Later, for odd primes,	their definition was given non-effectively using arguments based on the mod-$p$ homology of symmetric groups \cites{steenrod53symmetric, steenrod53cyclic, steenrod62operations}.
-This viewpoint enhanced the conceptual understanding of the operations and allowed for many advances \cites{adem1952iteration, milnor1958dual, adams1995stable}, but lacked the concreteness of their definition at~$2$.
-
-In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- the need to have a definition of Steenrod operations that can be effectively computed in specific examples has gain considerable importance.
-In Applied Topology, the use of Persistence Homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage,chan2013topology,lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of Persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
-In Quantum Field Theory, the BRST formalism \cites{BRS,Tyutin,KugoOjima} introduced cohomology to deal with gauge symmetries, and was further developed in the BV-formalism \cite{BV}.
-Master equations, introduced there, are also needed for the construction of viable actions in String Field Theory \cite{Zwiebach}, where fundamental chains are involved.
-The chain level viewpoint for the study of homology operations was brought to the forefront by String Topology \cite{Sullivanoverview}, and as served as a major driver of innovation \cites{TZ, hoch2}.
-The cubical viewpoint appears in physics naturally in the theory of renomalization \cite{KreimerCubical}; while Steenrod cup-$i$ products are utilized in the construction of effective actions of gapped systems \cite{kapustin2017fermionic}.
-This connection with physics motivated the development of effective versions of spin bordism \cites{brumfiel2016pontrjagin, brumfiel2018pontrjagin}, which prominently feature Steenrod cup-$i$ products and Cartan coboundaries.
-
-As in \cite{may70generalapproach}, we take a more general approach to Steenrod operations that also includes Araki-Kudo-Dyer-Lashof operations on the mod-$p$ homology of infinite loop spaces \cites{araki56squaring, dyer62lashof}.
-We use the language of operads \cite{may72geometry}  to describe at the chain level the integral structure required to define (co)homology operations at every prime.
-We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod-$p$ homology of their algebras; these are the Barratt-Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
-Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical products generalizing the \mbox{cup-$i$} products of Steenrod to every prime.
-An alternative approach based on the Eilenberg-Zilber contraction can be found in \cite{gonzalez2005hpt}.
-Up to now, although its existence is warrantied by acyclic model argument \cite{eilenberg1953acyclic}, no $E_\infty$-structure was known on the cochains of cubical sets.
-Using an $E_\infty$-bialgebra structure on the chains of the interval we effectively construct an $U(\mathcal M)$-algebra structure on them, and as a consequence provide a description of Steenrod products for cochains of cubical sets as well.
-The $p=2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2018axiomatic}, and in the cubical setting to the cup-$i$ products of  Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l-Pilarczy \cite{pilarczyk2016cubical}.
-
-We also contribute to a growing body of open source software \cites{manero2020effective, pilarczyk2015contraction, sagemath} resulting from an effort to rewrite key concepts from Homotopy Theory in effective forms.
-Uses in Applied Topology are motivating some of this work \cite{tauzin2020giottotda}, but the impetus also comes from Voevodsky's program for a comprehensive, computational foundation of mathematics based on the homotopical interpretation of type theory \cite{bauer2017hott}.
-A \texttt{Python} implementation of all the constructions in this article can be found in A.M-M.'s website.\footnote{Currently hosted at \url{https://www.medina-mardones.com/}}
-
-An outline of the article is described next.
-We first introduce, in Section~2, the conventions we will follow regarding chain complexes, simplicial sets and cubical sets.
-Then, in Section~3, we review the key notions from group homology we will use for cyclic and symmetric groups.
-Section~4 is devoted to the language of operads and related structures that we use, in Section~5, to define an integral structure at the chain level inducing Steenrod operations for every prime.
-Section~6, the bulk of this work, presents effective constructions of Steenrod-Adem structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
-It also describes a natural $U(\mathcal M)$-algebra structure on the cochains of simplicial and cubical sets inducing natural Steenrod-Adem structures on them.
-We end, in Section~7, with an overview of some connections of this work to important geometric and combinatorial structures, and provide an outline of future research directions.
-
-\section*{Acknowledgement}
-
-The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Greg Brumfiel, Dev Sinha, Jens Kjaer, Calista Bernard, and Andy Putnam, for insightful discussions and valuable comments, and to the anonymous referee for many helpful suggestions.
-
-\section{Preliminaries}
-
-\subsection{Chain complexes}
-\label{ssec: chain cpx}
-
-Let $R$ be a ring.
-We denote by $(\mathbf{Ch}_R, \otimes, R)$ the symmetric monoidal category of homologically graded chain complexes of $R$-modules.
-The set of $R$-linear maps between chain complexes as well as the tensor product of chain complexes are regarded as chain complexes in the usual way:
-\begin{equation*}
-\Hom(A, A^\prime)_n = \big\{f \ |\ a \in A_m \Rightarrow f(a) \in A^\prime_{m+n} \big\}, \qquad
-\partial f = \partial \circ f - (-1)^{|f|}f \circ \partial,
-\end{equation*}
-\begin{equation*}
-(A \otimes A^\prime)_n = \bigoplus_{p + q = n} A_p \otimes A^\prime_q, \qquad \partial (a \otimes a^\prime) = \partial a \otimes a^\prime + (-1)^{|a|} a \otimes \partial a^\prime.
-\end{equation*}
-We embed the category of $R$-modules as the full subcategory of $\mathbf{Ch}_R$ with objects concentrated in degree $0$.
-The endofunctor $\Hom(-, R)$ is referred to as the \textit{linear duality functor}.
-We notice that if a chain complex is concentrated in non-negative degrees then its linear dual is on non-positive ones.
-
-The rings we will mostly be interested in are the group rings $\Z[\mathrm G]$ and $\mathbb{F}_p[\mathrm G]$ of finite groups, where $p$ is prime and $\mathbb{F}_p$ is the field with $p$ elements.
-
-\subsection{Simplicial sets}
-
-The \textit{simplex category} $\triangle$ is defined to have an object $[n] = \{0, \dots, n\}$ for every $n \in \mathbb{N}$ and a morphism $[m] \to [n]$ for each order-preserving function from $[m]$ to $[n]$.
-The morphisms $\delta_i : [n-1] \to [n]$ and $\sigma_i : [n+1] \to [n]$ defined for $0 \leq i \leq n$ by
-\begin{equation*}
-\delta_i(k) = 
-\begin{cases} k & k < i, \\ k+1 & i \leq k, \end{cases}
-\quad \text{ and } \quad
-\sigma_i(k) = 
-\begin{cases} k & k \leq i, \\ k-1 & i < k, \end{cases}
-\end{equation*} 
-generate all morphisms in the simplex category.
-
-A \textit{simplicial set} $X$ is a contravariant functor from the simplex category to the category of sets and a simplicial map is a natural transformation between two simplicial sets.
-As is customary we use the notation
-\begin{equation*}
-X\big( [n] \big) = X_n, \qquad X(\delta_i) = d_i, \qquad X(\sigma_i) = s_i,
-\end{equation*}
-and refer to elements in the image of any $s_i$ as \textit{degenerate}.
-
-For each $n \in \mathbb{N}$, the simplicial set $\triangle^n$ is defined by
-\begin{equation*}
-\triangle^n_k  = \Hom_{\triangle} \big( [k], [n] \big), \qquad 
-d_i(x) = x \circ \delta_i, \qquad 
-s_i(x) = x \circ \sigma_i,
-\end{equation*}
-and any simplicial set can be expressed as a colimit of these
-\begin{equation*}
-X = \colim_{\triangle^n \to X} \triangle^n.
-\end{equation*}
-We represent the non-degenerate elements of $\triangle^n_k$ as an increasing sequence $[v_0, \dots, v_k]$ of non-negative integers each less than or equal to $n$.
-
-The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: 
-\begin{equation*}
-N_\bullet(X; R)_n = \frac{R \{ X_n \}}{R \{ s(X_{n-1}) \}}
-\end{equation*}
-where $s(X_{n-1}) = \bigcup_{i=0}^{n-1} s_i(X_{n-1})$, and $\partial_n : N_*(X)_n \to N_*(X)_{n-1}$ is given by
-\begin{equation*}
-\partial_n = \sum_{i=0}^{n} (-1)^id_{i}.
-\end{equation*}
-The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.
-
-It is convenient to emphasize that
-\begin{equation*}
-N_\bullet(X; R) = \colim_{\triangle^n \to X} N_\bullet(\triangle^n; R).
-\end{equation*}
-
-\subsection{Cubical sets}
-
-The \textit{cube category} $\square$ is the free strict monoidal category with a \textit{bipointed object}
-\begin{equation*}
-\begin{tikzcd}
-1 \arrow[r, bend left, "\delta^0"] \arrow[r, bend right, "\delta^1"'] & 2 \arrow[r, "\sigma"] & 1
-\end{tikzcd}
-\end{equation*}
-such that $\sigma \circ \delta^0 = \sigma \circ \delta^1 = \mathrm{id}$.
-Explicitly, it contains an object $2^n$ for each non-negative integer $n$ and its morphisms are generated by the \textit{coface} and \textit{codegeneracy maps} defined by
-\begin{align*}
-\delta_i^\varepsilon & = \mathrm{id}_{2^{i-1}} \times \delta^\varepsilon \times \mathrm{id}_{2^{n-1-i}} \colon 2^{n-1} \to 2^n, \\
-\sigma_i & = \mathrm{id}_{2^{i-1}} \times \, \sigma \times \mathrm{id}_{2^{n-i}} \colon 2^{n} \to 2^{n-1}.
-\end{align*}
-
-A \textit{cubical set} $X$ is a contravariant functor from the cube category to the category of sets and a cubical map is a natural transformation between two cubical sets.
-As is customary, we use the notation
-\begin{equation*}
-X\big( 2^n \big) = X_n \qquad X(\delta^\varepsilon_i) = d^\varepsilon_i \qquad X(\sigma_i) = s_i,
-\end{equation*}
-and refer to elements in the image of any $s_i$ as \textit{degenerate}.
-
-For each $n \in \mathbb{N}$, the cubical set $\square^n$ is defined by
-\begin{equation*}
-\square^n_k  = \Hom_{\square} \big( 2^k, 2^n \big), \qquad 
-d^\varepsilon_i(x) = x \circ \delta^\varepsilon_i, \qquad 
-s_i(x) = x \circ \sigma_i,
-\end{equation*}
-notice that iteratively
-\begin{equation*}
-\square^n = \overbrace{\square^1 \times \cdots \times \square^1}^{n \text{ times }}.
-\end{equation*}
-We represent the non-degenerate elements of $\square^n$ as sequences $x_1 \cdots\, x_n$ with each $x_i \in \{[0], [1], [0,1]\}$. Any cubical set can be expressed as a colimit of these
-\begin{equation*}
-X = \colim_{\square^n \to X} \square^n.
-\end{equation*}
-
-The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: The chain complex $N_\bullet(\square^1)$ is simply the cellular chain complex of the interval,
-isomorphic to
-\begin{equation*}
-\begin{tikzcd} [column sep = small, row sep = 0.1pt]
-R\{[0], [1]\}  & \arrow[l] R\{[0,1]\} \\
-{[1] - [0]} & \arrow[l, |->] \left[0,1\right].
-\end{tikzcd}
-\end{equation*}
-Set
-\begin{equation} \label{eq: chains on I^n}
-N_\bullet(\square^n; R) = N_\bullet(\square^1; R)^{\otimes n}
-\end{equation}
-and define
-\begin{equation*}
-N_\bullet(X; R) = \colim_{\square^n \to X} N_\bullet(\square^n; R).
-\end{equation*}
-
-The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.
-
-\section{Group homology}
-\label{sec: goup homology}
-
-Fixing notation, let $\mathrm{S}_n$ be the symmetric group of $n$ elements and $\mathrm{C}_n$ be the cyclic group of order $n$ thought of as the subgroup of $\mathrm{S}_n$ generated by an element~$\rho$.
-We denote this inclusion by $\iota : \mathrm C_r \to \mathrm S_r$.
-
-A \textit{resolution} in $\mathbf{Ch}_R$ is a quasi-isomorphism $P \to M$ with each $P_n$ a free \mbox{$R$-module}.
-We will use the fact, explained in Section 6.5 of \cite{jacobson1989algebra}, that such resolutions exist for any chain complex $M$ concentrated in non-negatively degrees, in particular, for the monoidal unit $R$.
-
-Let $\mathrm G$ be a group and $M$ an $R[\mathrm G]$-module, we define the \textit{homology of $\mathrm G$ with coefficients in $M$}, denoted $H(\mathrm G; M)$, as the homology of any chain complex $P \otimes_{R[\mathrm G]} M$ with $P \to R$ a resolution.
-We will be particularly interested in the case when $M = \mathbb F_p(q)$ is the trivial or sign $\mathbb F_p[\mathrm{S}_n]$-module depending on the parity of~$q$.
-
-We now review the group homology of finite cyclic groups. For any ring $R$ the elements
-\begin{equation} \label{eq: T and R definition}
-\begin{split}
-T &= \rho - 1, \\
-N &= 1 + \rho + \cdots + \rho^{n-1},
-\end{split}
-\end{equation}
-in $R[\mathrm{C}_n]$ generate the ideal of annihilators of each other.
-Therefore, the chain complex $\mathcal W(n)$ concentrated in non-negative degrees with $\mathcal W(n)_d$ the free $\Z[\mathrm{C}_n]$-module generated by one element $e_d$, and differential
-\begin{equation*}
-\partial(e_d) = \begin{cases}
-Te_{d-1} & d \text{ odd,} \\
-Ne_{d-1} & d \text{ even,}
-\end{cases}
-\end{equation*}
-defines a resolution $\mathcal W(n) \to R$ in $\mathbf{Ch}_{R[\mathrm{C}_n]}$. It follow from a straightforward computation that for any prime $p$ and integer $q$
-\begin{equation*}
-H_i(\mathrm{C}_p; \mathbb{F}_p(q)) = \mathbb{F}_p.
-\end{equation*}
-
-The homology of $\mathrm{S}_n$ is harder to compute.
-With untwisted coefficients, the method of computation followed by several authors was to prove the injectivity of this homology into that of the infinite symmetric group and take advantage of a natural Hopf algebra structure on it.
-A powerful result stemming from the deep connection of this question with infinite loop space theory, is the existence of a homology isomorphism of spaces
-\begin{equation*}
-\Z \times B\mathrm{S}_\infty \to Q(S^0) = \Omega^\infty \Sigma^\infty (S^0)
-\end{equation*}
-credited to Dyer-Lashof \cite{dyer62lashof}, Barratt-Priddy and Quillen \cite{barratt1972priddy}.
-
-In this work, we are interested in the mod-$p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite{adem2004milgram} Corollary VI.1.4, is detected by the inclusion $\iota : \mathrm{C}_p \to \mathrm{S}_p$ whose homological kernel is described next.
-
-\begin{lemma} \label{lem: Thom's theorem}
-	Let $p$ be an odd prime and $q$ an integer. Consider
-	\begin{equation*}
-	(\iota_\ast)_n : H_n(\mathrm{C}_p; \mathbb{F}_p(q)) \to H_n(\mathrm{S}_p; \mathbb{F}_p(q))
-	\end{equation*}
-	then
-	\begin{enumerate}
-		\item If $q$ is even, $(\iota_\ast)_n = 0$ unless $n = 2t(p-1)$ or $n = 2t(p-1) - 1$,
-		\item If $q$ is odd, $(\iota_\ast)_n = 0$ unless $n = (2t+1)(p-1)$ or $n = (2t+1)(p-1)-1$,
-	\end{enumerate}
-	for some integer $t$.
-\end{lemma}
-
-\begin{proof}
-	This is proven as Theorem 4.1 in \cite{steenrod53cyclic} where Thom is also credited with a different proof.
-\end{proof}
-
-In section 5 we will see how the cohomology of symmetric groups defines operations on algebras that are commutative up to coherent homotopies.
-Preparing for that, we first developed the language of $\Gamma$-modules and operads, where the integral structure defining Steenrod operations is clearly expressed.
-
-\section{$\Gamma$-modules, operads and PROPs}
-
-In this section we set up a framework in which the structure responsible for Steenrod operations becomes most transparent.
-Given our applications, we consider $\mathbf{Ch}_R$ as the base category, remarking that all definitions in this section apply to general closed symmetric monoidal categories.
-
-\subsection{$\Gamma$-modules}
-Recall that a group $\mathrm G$ can be thought of as a category with a single object and only invertible morphisms, and that a chain complex of left (resp.
-right) $R[\mathrm G]$-modules is the same as a covariant (resp.
-contravariant) functor from $\mathrm G$ to $\mathbf{Ch}_R$.
-Right actions are more commonly used in the literature of operads so we emphasize that perspective.
-Taking inverses allows for the switch between these two conventions.
-
-A \textit{groupoid} is a small category where all morphisms are invertible.
-\begin{definition}
-	A \textit{$\Gamma$-module} is a contravariant functor to $\mathbf{Ch}_R$ from a groupoid $\Gamma$ with objects the natural numbers and morphisms satisfying $\Gamma(r,s) = \emptyset$ for $r \neq s$.
-We denote the category of $\Gamma$-modules and natural transformations by $\mathbf{Ch}_R^\Gamma$.
-\end{definition}
-
-We are mostly interested in two examples of $\Gamma$-modules, those associated to the groupoids $\mathrm{S}$ and $\mathrm{C}$ defined by
-\begin{equation*}
-\mathrm{S}(r, r) = \mathrm{S}_r, \qquad
-\mathrm{C}(r,r) = \mathrm{C}_r,
-\end{equation*}
-for every $r \in \mathbb{N}$. The inclusion $\mathrm{C}_r \to \mathrm{S}_r$ induces a forgetful functor
-\begin{equation*}
-\begin{tikzcd} [column sep = small]
-\mathbf{Ch}_R^\mathrm{S}  \arrow[r] & \mathbf{Ch}_R^\mathrm{C}.
-\end{tikzcd}
-\end{equation*}
-
-Given an object $A$ in $\mathbf{Ch}_R$ there are two important $\Gamma$-modules associated to it; an $\mathrm{S}$-module known as \textit{endomorphism $\mathrm{S}$-module} $\End_A$, and an $\mathrm{S}^{op}$-module known as \textit{coendomorphism $\mathrm{S}$-module} $\End^A$.
-These are defined by
-\begin{align*}	
-\End_A(r) &= \Hom(A^{\otimes r},A), \\
-\End^A(r) &= \Hom(A,A^{\otimes r}),
-\end{align*}
-with respective right and left actions defined by permutation of tensor factors.
-
-Another groupoid of importance to us is $\mathrm{S} \times \mathrm{S}^{op}$.
-Contravariant functors from it to $\mathbf{Ch}_R$ are called \textit{$\mathrm{S}$-bimodules} and their functor category is denoted $\mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}}$.
-Notice that the inclusions
-define forgetful functors
-\begin{equation*}
-\begin{tikzcd}[column sep=small, row sep=tiny]
-& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"'] \arrow[dr, "U_2"] & \\
-\mathbf{Ch}_R^{\mathrm{S}} &  & \mathbf{Ch}_R^{\mathrm{S}^{op}},
-\end{tikzcd}
-\end{equation*}
-and that for any object $A$ in $\mathbf{Ch}_R$, the canonical \textit{endomorphism bimodule}
-\begin{equation*}
-\End_A^A(r, s) = \Hom(A^{\otimes r}, A^{\otimes s})
-\end{equation*}
-forgets to $\End_A$ and $\End^A$.
-
-Using the groupoid automorphism sending every morphisms to its inverse we can identify $\Gamma$- and $\Gamma^{op}$- modules.
-In particular, the statement claiming that the linear duality functor induces a morphism of $\mathrm{S}$-modules
-\begin{equation*}
-\End^A \to \End_{\Hom(A, R)}
-\end{equation*}
-for every object $A$ in $\mathbf{Ch}_R$ is well defined and easily verified using this identification.
-
-A \textit{resolution} in $\mathbf{Ch}_R^\Gamma$ is a morphism $\phi$ of $\Gamma$-modules such that $\phi(r)$ is a resolution in the category of chain complexes of $R[\Gamma_r]$-modules for each $r \in \mathbb{N}$.
-A $\Gamma$-module $\mathcal R$ is said to be $E_\infty$ if $\mathcal R(0) = R$ and there exists a resolution $\mathcal R \to \underline{R}$ where $\underline{R}$ is the object in $\mathbf{Ch}_R^\Gamma$ defined by $\underline{R}(r) = R$ and $\underline{R}(\gamma) = \mathrm{id}_R$ for every $r \in \mathbb{N}$ and $\gamma \in \Gamma_r$.
-
-\begin{definition} \label{def: minimal cyclic resolution}
-	The \textit{minimal} $E_\infty$-$\mathrm{C}$-\textit{module} $\mathcal W$ is the functor in $\mathbf{Ch}_R^\mathrm{C}$ assigning to $r$ the chain complex
-	\begin{equation*}
-	\begin{tikzcd} [column sep = .5cm]
-	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,T"'] \cdots
-	\end{tikzcd}
-	\end{equation*}
-	concentrated in non-negative degrees.
-\end{definition}
-
-\subsection{Operads and PROPs}
-
-Operads an PROPs are respectively $\mathrm{S}$-modules and \mbox{$\mathrm{S}$-bimodules} enriched with further compositional structure.
-These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a PROP.
-
-Succinctly, an operad $\mathcal O$ is an $\mathrm{S}$-module together with a collection of $R$-linear maps
-\begin{equation*}
-\mathcal O(r) \otimes \mathcal O(s) \to \mathcal O(r+s-1)
-\end{equation*}
-satisfying suitable associativity, equivariance and unitality conditions. A PROP $\mathcal P$ is an $\mathrm{S}$-bimodule together with two types of compositions; horizontal
-\begin{equation*}
-\mathcal P(r_1, s_1) \otimes \mathcal P(r_2, s_2) \to \mathcal P(r_1 + r_2, s_1 + s_2)
-\end{equation*}
-and vertical
-\begin{equation*}
-\mathcal P(r,s) \otimes \mathcal P(s, t) \to \mathcal P(r, t)
-\end{equation*}
-satisfying their own versions of associativity, equivariance and unitality. For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008operads}.
-
-We have already mentioned that for any chain complex $A$, the $\mathrm{S}$-module $\End_A$ is naturally an operad and the $\mathrm{S}$-bimodule $\End_A^A$ is naturally a PROP.
-We add that considering $\End^A$ as an $\mathrm{S}$-module, its compositional structure also defines an operad structure on it.
-
-We remark that the compositional structure of a PROP $\mathcal P$ restricts to operad structures on $U_1(\mathcal P)$ and $U_2(\mathcal P)$.
-
-The type of operads that we are most interested in are $E_\infty$-operads which, as we will discuss in the next section, are used to describe commutativity up to coherent homotopies.
-
-\begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}]
-	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a PROP $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
-\end{definition}
-
-\subsection{Algebras, coalgebra and bialgebras}
-
-A morphisms of operads or of PROPs is simply a morphisms of their underlying $\mathrm{S}$-modules or $\mathrm{S}$-bimodules preserving the respective compositional structures.
-
-Given a chain complex $A$, an operad $\mathcal O$ and a PROP $\mathcal P$.
-An $\mathcal O$-\textit{algebra} (resp.
-$\mathcal O$-\textit{coalgebra}) structure on $A$ is an operad morphism $\mathcal O \to \End_A$ (resp.
-$\mathcal O \to \End^A$), and a $\mathcal P$-\textit{bialgebra} structure on $A$ is a PROP morphism $\mathcal P \to \End_A^A$.
-
-We remark that the linear duality functor naturally transforms an $\mathcal O$-coalgebra structure on a chain complex into an $\mathcal O$-algebra structure on its dual.
-
-Algebras over $E_\infty$-operads are the central objects of study in this work.
-To develop intuition for them, let us consider a chain complex $A$ with an algebra structure over $\underline{R}$, thought of as an operad with all compositions corresponding to the identity map $R \to R$.
-The $\underline{R}$-algebra structure on $A$ is generated by a linear map $\mu \colon A \otimes A \to A$ which is (strictly) commutative and associative, and a linear map $\eta \colon R \to A$ that determines a (two-sided) unit for $\mu$.
-Since $E_\infty$-operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies.
-The two main examples to keep in mind are the cochains of spaces and the chains of infinite loops spaces.
-
-\section{Steenrod-Adem structures}
-
-We now introduce an operadic formulation of a structure giving rise to Steenrod operations at every prime.
-It is based on \cites{steenrod47products, steenrod53symmetric, steenrod53cyclic, may70generalapproach}, and takes a viewpoint that emphasizes the integral structure needed to define them and prove their relations at every prime.
-For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}.
-
-\begin{definition} \label{def: Steenrod-Adem structure}
-	A \textit{Steenrod-Adem structure} on an operad $\mathcal O$ is a 
-	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad
-	\begin{equation*}
-	\begin{tikzcd}[column sep = normal, row sep = small]
-	& \mathcal R \arrow[dr, "\phi", out=0] & \\
-	\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \mathcal O
-	\end{tikzcd}
-	\end{equation*}
-	such that $\iota$ is a quasi-isomorphism and $\phi$ a morphism of operads.
-\end{definition}
-
-\begin{remark} \label{rmk: Deligne conjecture}
-	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$.
-In this language, a choice of factorization for a Steenrod-Adem structure defines in particular a \textit{commutative multiplication}.
-\end{remark}
-
-\begin{definition}
-	Let $A$ be a chain complex.
-A Steenrod-Adem structure on $\mathrm{End}_A$ is referred to as one on $A$.
-Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod} $(r, i)$-\textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
-\end{definition}
-
-\begin{remark}
-	Restricting a Steenrod-Adem structure on a chain complex $A$ to a given arity $r$ corresponds to specifying a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$.
-This pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ introduced in \cite{may70generalapproach} Definition 2.1.
-Furthermore, the restriction to arity $r^2$ enhances this pair to an \textit{Adem object} as described in Definition 4.1 loc.
-cit.
-\end{remark}
-
-A Steenrod-Adem structure on a chain complex $A$ allows us to define operations on its $\mathbb{F}_p$-homology for every prime $p$.
-These operations are structurally different if $p$ is even or odd.
-Using the previous Remark, the definitions below recover Steenrod's original definition for the cohomology of spaces and that of Araki-Kudo-Dyer-Lashof operations for the homology of infinite loop spaces.
-
-For the rest of this section $A$ is a chain complex equipped with a Steenrod-Adem structure.
-
-\begin{definition}
-	For any prime $p$, the $\mathbb{F}_p$-linear map
-	\begin{equation*}
-	D^p_i : (A \otimes \mathbb{F}_p) \to (A \otimes \mathbb{F}_p)
-	\end{equation*}
-	is defined by sending $a$ to the Steenrod \mbox{$(p, i)$-product} of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
-\end{definition}
-
-We notice that if $a$ is of degree $q$ then $D^p_i(a)$ is of degree $q + (p-1)q + i$.
-
-\begin{definition}
-	For any integer $s$, the \textit{Steenrod operation}
-	\begin{equation*}
-	P_s : H_\bullet(A; \mathbb{F}_2) \to H_{\bullet + s}(A; \mathbb{F}_2)
-	\end{equation*}
-	is defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_2)$ of degree $q$ to the class represented by $D^2_{s-q}(a)$.
-\end{definition}
-
-Notice that the Steenrod squares are determined by the Steenrod $(2,i)$-products with $\mathbb{F}_2$-coefficients.
-These binary operations are known as cup-$i$ products.
-In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod $\big(p, k(p-1)-\varepsilon\big)$-products for $\varepsilon \in \{0,1\}$.
-We can explain the appearance of these specific Steenrod products as follows.
-The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even an $(2t+1)(p-1) - \varepsilon$ if $q$ is odd.
-According to Lemma \ref{lem: Thom's theorem}, these are the only homologically non-trivial cases.
-
-\begin{definition} \label{def: Steenrod operations at odd prime}
-	For any integer $s$, the \textit{Steenrod operations}
-	\begin{equation*}
-	P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1)}(A; \mathbb{F}_p)
-	\end{equation*}
-	and
-	\begin{equation*}
-	\beta P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1) - 1}(A; \mathbb{F}_p)
-	\end{equation*}
-	are defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_p)$ of degree $q$ to the classes represented respectively for $\varepsilon \in\{0,1\}$ by
-	\begin{equation*}
-	(-1)^s \nu(q) D^p_{(2s-q)(p-1)-\varepsilon}(a)
-	\end{equation*}
-	where $\nu(q) = (-1)^{q(q-1)m/2}(m!)^q$ and $m = (p-1)/2$.
-\end{definition}
-
-\begin{remark}
-	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq.
-6.1.
-in \cite{steenrod53cyclic}).
-The notation $\beta P_s$ is motivated by the relationship of this operator and the Bockstein of the reduction $\mathbb Z \to \mathbb Z/p\mathbb Z$.
-\end{remark}
-
-Steenrod operations satisfy the Cartan and Adem relations.
-Below we state the subset of these relations that is most commonly used and refer to Sections 2 and 4 of \cite{may70generalapproach} for a complete list and proofs.
-\begin{lemma}
-	Let $A$ be equipped with a Steenrod-Adem structure. If $[\alpha], [\beta] \in H(A;\mathbb{F}_p)$ then
-	\begin{equation*}
-	P_s\big([\alpha] [\beta]\big) = \sum_{i+j=s} P_i\big( [\alpha] \big) P_j\big( [\beta] \big),
-	\end{equation*}
-	and
-	\begin{itemize}
-		\item If $p = 2$ and $a > 2b$
-		\begin{equation*}
-		P_{a}P_{b} = \sum_i {2i-a \choose a-b-i-1} P_{a+b-i}P_i,
-		\end{equation*}
-		\item If $p > 2$ and $a > pb$
-		\begin{equation*}
-		P_{a}P_{b} = \sum_i (-1)^{a+i}{pi-a \choose a-(p-1)b-i-1} P_{a+b-i}P_i.
-		\end{equation*}
-	\end{itemize}		
-\end{lemma}
-
-\begin{proof}
-	These are proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
-\end{proof}
-
-For the even prime, proofs at the chain level of these formulae have been given in \cite{medina2020cartan,brumfiel2020cochain}.
-For a different operadic approach to Steenrod operations at the even prime please consult \cite{chataur2005adem-cartan}.
-
-For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$, which we use in subsections 6.4 and 6.5.
-
-\section{Effective constructions}
-\label{sec: effective constructions}
+\section{Effective constructions} \label{s:effective constructions}
 
@@
 \end{example}
-
-\section{Outlook}
-This article looked at Steenrod operations from an algebraic viewpoint, a subject with rich geometric and combinatorial components as well.
-For example, \cite{Postnikov} and \cite{medina2018prop2} independently introduced equivalent geometric representations of the cup-$i$ products in terms of stabilized arc surfaces \cite{KLP} and weighted ribbon graphs respectively.
-In fact, an entire $E_\infty$-operad (PROP) is constructed geometrically in this way.
-We can also interpret the Steenrod-Adem structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups ---a key ingredient in Definition \ref{def: minimal cyclic resolution}--- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.
-
-In Higher Category Theory, the paper \cite{medina2020globular} constructs a functor producing strict \mbox{$\infty$-cat}egories from group-like cup-$i$ coalgebras in a manner similar to \cite{steiner2004omega}.
-In particular, the cup-$i$ constructions described in this article for standard simplices and cubes define, respectively, the Street nerve and cubical nerve of strict $\infty$-categories.
-We anticipate that the more general Steenrod $(p,i)$-products constructed in this work will also have deep combinatorial interpretations.
-
-There is a functorial approach to the theory using the formalism of Feynman categories \cite{feynman},
-which renders all the structures and notions natural.
-This includes cyclic, planar cyclic as well as Berger's pre-operads \cite{BergerRecog}.
-Their interplay is of independent interest \cite{BergerKaufmann,feyrep} and will be linked directly to the constructions of this paper.
-
-In this article we have not focused on the operations that exist non-trivially for \mbox{$E_n$-algebras} with $n$ finite, see part III of \cite{may76homology}.
-A treatement close to ours for the $E_2$ case was given in \cite{Tourtchine}.
-Effective constructions for these Dyer-Lashof-Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang,sinha2013littledisks,berger04combinatorial,ayala2014configuration} and higher categories \cite{Bathigher,BalFiedSchwVogt,Rezkhigher}, and will appear elsewhere.
-
-\newpage
-\appendix
-\section{Proofs}
-
-\subsection{Theorem \ref{thm: Steenrod-Adem on Barratt-Eccles}}
-
-We prove that the $\Z[\mathrm{C}_r]$-linear map
-\begin{equation*}
-\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)
-\end{equation*}
-introduced in Definition \ref{def: Steenrod-Adem on Barratt-Eccles} is a chain map for every $r \geq 0$.
-We simplify notation and write $\psi$ instead of $\psi_{\mathcal E}(r)$.
-To show $\psi$ is a chain map we proceed by induction.
-Notice that
-\begin{equation*}
-\psi(\partial e_0) = 0 = \partial \psi(e_0)
-\end{equation*}
-and assume $\psi(\partial e_{k-1}) = \partial \psi(e_{k-1})$. If $k = 2n$ we have
-\begin{align*}
-\partial \psi(e_{2n}) & = 
-\partial \sum_{r_1, \dots, r_n} 
-\big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
-\partial \sum_{r_2, \dots, r_n} \sum_{r_1 = 0}^{p-1}
-\big(\rho^0, \rho^{r_1} \, (\rho^0, \rho^{1}, \dots, \rho^{r_n-r_1}, \rho^{r_n - r_1 +1}) \big) \\ & =
-\partial \sum_{r_2, \dots, r_n}
-\big(\rho^0, N\, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1}) \big) \\ & =
-\sum_{r_2, \dots, r_n}
-N\, \big( \rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1} \big) \\ & -
-\sum_{r_2, \dots, r_n}
-\big(\rho^0, \partial \, N \, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n+1}) \big) \\ & =
-N \psi(e_{2n-1}) - (\rho^0, \partial N \psi (e_{2n-1})) \\ & =
-\psi(N e_{2n-1}) - (\rho^0, \psi (\partial N e_{2n-1})) \\ & =
-\psi(\partial e_{2n}) - (\rho^0, \psi (\partial^2 e_{2n})) \\ & =
-\psi(\partial e_{2n}).
-\end{align*}
-If $k = 2n+1$ we have
-\begin{align*}
-\partial \psi(e_{2n+1}) & = 
-\partial \sum_{r_1, \dots, r_n} 
-\big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
-\partial \sum_{r_1, \dots, r_n}
-\big(\rho^0, \rho^{1} \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-\partial \sum_{r_1, \dots, r_n}
-\big(\rho^0, T\, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-\sum_{r_1, \dots, r_n}
-T \, \big( \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n} \big) \\ & -
-\sum_{r_1, \dots, r_n}
-\big(\rho^0, \partial \, T \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-T \psi(e_{2n}) - (\rho^0, \partial T \psi (e_{2n})) \\ & =
-\psi(T e_{2n}) - (\rho^0, \psi (\partial T e_{2n})) \\ & =
-\psi(\partial e_{2n+1}) - (\rho^0, \psi (\partial^2 e_{2n+1})) \\ & =
-\psi(\partial e_{2n+1})
-\end{align*}
-where for the third equality we used that for any $r_1, \dots, r_n$
-\begin{equation*}
-(\rho^0, \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) = 0.
-\end{equation*}
-This map is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0)$ represents a generator of the homology.
-
-\subsection{Theorem \ref{thm: Steenrod-Adem on surjection MS convention}}
-
-\begin{proof}
-	We prove that the $\Z[\mathrm{C}_r]$-linear map
-	\begin{equation*}
-	\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)
-	\end{equation*}
-	introduced in Definition \ref{def: Steenrod-Adem on surjection} is a chain map for every $r \geq 0$.
-We simplify notation and write $\psi$ instead of $\psi_{\mathcal X}(r)$.
-To show $\psi$ is a chain map we proceed by induction.
-Notice that
-	\begin{equation*}
-	\psi(\partial e_0) = 0 = \partial \psi(e_0)
-	\end{equation*}
-	and assume $\psi(\partial e_{n-1}) = \partial \psi(e_{n-1})$. For $n = 2m+1$ we have
-	\begin{align*}
-	\partial \psi(e_{2m+1}) 
-	& =
-	\partial\, h\, T\, \psi(e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - i^{r-1} p^{r-1}\, \psi(e_{2m}) -
-	h\, \partial\, T\, \psi(e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - 
-	h\, T\, \psi(\partial\, e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - 
-	h\, \psi(T\,N\, e_{2m-1}) \big) \\
-	& = 
-	T \psi(e_{2m}).
-	\end{align*}
-	For $n = 2m$ the proof is analogous. The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ is a generator of the homology.
-\end{proof}
-
-\subsection{Theorem \ref{thm: cubical chain bialgebra}}
-
-The only non-trivial relation we need to verify is
-\begin{equation*}
-\partial \product = \, \boundary \, .
-\end{equation*}
-Let us consider two basis elements of $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$
-\begin{align*}
-x & = x_1 \otimes \cdots \otimes x_n, \\
-y & = y_1 \otimes \cdots \otimes y_n.
-\end{align*}
-We need to show that
-\begin{equation*}
-\partial (x \ast y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y = \epsilon(x) y - \epsilon(y) x.
-\end{equation*}
-We have
-\begin{equation*}
-x \ast y = \sum (-1)^{|x|} \epsilon(y_{<i})x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i})y_{>i}
-\end{equation*}
-and
-\begin{align*}
-\partial(x \ast y) & = 
-\sum (-1)^{|x|} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes \partial (x_i \ast y_i) \otimes \epsilon(x_{>i}) y_{>i} \\ & -
-\sum (-1)^{|x|+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{align*}
-Since
-\begin{equation*}
-|x| = |x_{<i}| + |x_i| + |x_{>i}|, \quad \epsilon(x_{>i}) \neq 0 \Leftrightarrow |x_{>i}| = 0, \quad \partial(x_i \ast y_i) \neq 0 \Rightarrow |x_i| = 0,
-\end{equation*}
-we have
-\begin{equation} \label{eq: boundary of product 1}
-\begin{split}
-\partial(x \ast y) & = 
-\sum (-1)^{|x|} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes \partial (x_i \ast y_i) \otimes \epsilon(x_{>i}) y_{>i} \\ & -
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{split}
-\end{equation}
-We also have
-\begin{align*}
-\partial x \ast y & = 
-\sum (-1)^{|x|-1} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|-1+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes \partial x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|-1+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(\partial x_{>i}) y_{>i}.
-\end{align*}
-Since
-\begin{equation*}
-\epsilon(\partial x_{>i}) = 0, \quad \partial x_i \neq 0 \Leftrightarrow |x_i| = 1,
-\end{equation*}
-we have
-\begin{equation} \label{eq: boundary of product 2}
-\begin{split}
-\partial x \ast y & = 
-\sum (-1)^{|x|-1} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes \partial x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i}.
-\end{split}
-\end{equation}
-We also have
-\begin{align*}
-(-1)^{|x|} x \ast \partial y & = 
-\sum \epsilon(\partial y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|y_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast \partial y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|y_{<i}|+|y_i|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i},
-\end{align*}
-which is equivalent to
-\begin{equation} \label{eq: boundary of product 3}
-\begin{split}
-(-1)^{|x|} x \ast \partial y & = 
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast \partial y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{split}
-\end{equation}
-Putting identities \eqref{eq: boundary of product 1}, \eqref{eq: boundary of product 2} and \eqref{eq: boundary of product 3} together, we get
-\begin{multline*}
-\partial (x \otimes y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y =
-\sum \epsilon(y_{<i}) x_{<i} \otimes \big(\partial(x_i \ast y_i) + \partial x_i \ast y_i + x_i \ast \partial y_i\big) \otimes \epsilon(x_{>i}) y_{>i}.
-\end{multline*}
-Since
-\begin{equation*}
-\partial(x_i \ast y_i) + \partial x_i \ast y_i + x_i \ast \partial y_i = \epsilon(x_i)y_i - \epsilon(y_i)x_i,
-\end{equation*}
-we have
-\begin{align*}
-\partial (x \ast y) + \partial x \ast y + & (-1)^{|x|}x \ast \partial y \\ = &
-\sum \epsilon(y_{<i}) x_{<i} \otimes \epsilon(x_{\geq i}) y_{\geq i} - \epsilon(y_{\leq i}) x_{\leq i} \otimes \epsilon(x_{>i}) y_{>i} \\ = &
-\epsilon(x)y - \epsilon(y)x,
-\end{align*}
-as desired, where the last equality follows from a telescopic sum argument.
-
-\bibliographystyle{alpha} 
-\bibliography{bib}
-
-\end{document}

### 2021-05-07 groups.tex
Split sections into files

--- 2021-04-14 main.tex
@@
-\documentclass[A4]{amsart}
-
-\usepackage{amsmath, amssymb, amsfonts}
-\usepackage{tikz-cd}
-\usepackage{graphics}
-\usepackage[bookmarks=true, linktocpage=true,
-bookmarksnumbered=true, breaklinks=true,
-pdfstartview=FitH, hyperfigures=false,
-plainpages=false, naturalnames=true,
-colorlinks=true, pagebackref=true,
-pdfpagelabels]{hyperref}
-\hypersetup{
-	colorlinks,
-	citecolor=blue,
-	filecolor=blue,
-	linkcolor=blue,
-	urlcolor=blue
-}
-\usepackage[alphabetic]{amsrefs}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\Hom}{\mathrm{Hom}}
-\newcommand{\End}{\mathrm{End}}
-\DeclareMathOperator*{\colim}{colim}
-
-\include{figures}
-
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.6in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
-\calclayout
-
-\begin{document}
-
-\title{Chain level Steenrod operations}
-
-\author[R. Kaufmann]{Ralph M.\ Kaufmann}
-\address{Department of Mathematics, Department of Physics and Astronomy, Purdue University}
-\email{rkaufman@purdue.edu}
-
-\author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
-\address{Laboratory for Topology and Neuroscience, École Polytechnique Fédérale de Lausanne, Switzerland}
-\address{Department of Mathematics, University of Notre Dame du Lac, Notre Dame, IN, USA}
-\email{amedinam@nd.edu}
-\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Max Plank Institute for Mathematics.}
-
-\subjclass[2010]{55S05, 55U05, 55S10, 55S12; 55-04, 55U15, 55S15}
-\keywords{Steenrod operations, Dyer-Lashof operations, simplicial cochains, cubical cochains}
-
-\begin{abstract}
-	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander-Whitney's chain approximation to the diagonal.
-Later, following a viewpoint developed by Adem, Steenrod defined his homonymous operations for all primes using the homology of symmetric groups.
-This approach enhanced the conceptual understanding of the operations and allowed for many advances but lacked the concreteness of their definition at~$2$.
-In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having a definition of Steenrod operations that can be effectively computed in specific examples has become a key issue.
-This article provides such definition, at all primes, for well known $E_\infty$-algebras including the cochains of spaces expressed via simplicial or cubical cell structures.
-\end{abstract}
-
-\maketitle
-
-\tableofcontents
-
-\section{Introduction}
-
-The role Steenrod operations play in Stable Homotopy Theory is hard to overstate.
-The reason is that, given the representability of the cohomology functor, these operations together with the Bockstein homomorphism can be used to give a complete description of the algebraic structure naturally present on the mop-$p$ \mbox{cohomology} algebra of spaces.
-For the even prime, Steenrod squares were introduced in \cite{steenrod47products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander-Whitney's chain approximation to the diagonal.
-Later, for odd primes,	their definition was given non-effectively using arguments based on the mod-$p$ homology of symmetric groups \cites{steenrod53symmetric, steenrod53cyclic, steenrod62operations}.
-This viewpoint enhanced the conceptual understanding of the operations and allowed for many advances \cites{adem1952iteration, milnor1958dual, adams1995stable}, but lacked the concreteness of their definition at~$2$.
-
-In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- the need to have a definition of Steenrod operations that can be effectively computed in specific examples has gain considerable importance.
-In Applied Topology, the use of Persistence Homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage,chan2013topology,lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of Persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
-In Quantum Field Theory, the BRST formalism \cites{BRS,Tyutin,KugoOjima} introduced cohomology to deal with gauge symmetries, and was further developed in the BV-formalism \cite{BV}.
-Master equations, introduced there, are also needed for the construction of viable actions in String Field Theory \cite{Zwiebach}, where fundamental chains are involved.
-The chain level viewpoint for the study of homology operations was brought to the forefront by String Topology \cite{Sullivanoverview}, and as served as a major driver of innovation \cites{TZ, hoch2}.
-The cubical viewpoint appears in physics naturally in the theory of renomalization \cite{KreimerCubical}; while Steenrod cup-$i$ products are utilized in the construction of effective actions of gapped systems \cite{kapustin2017fermionic}.
-This connection with physics motivated the development of effective versions of spin bordism \cites{brumfiel2016pontrjagin, brumfiel2018pontrjagin}, which prominently feature Steenrod cup-$i$ products and Cartan coboundaries.
-
-As in \cite{may70generalapproach}, we take a more general approach to Steenrod operations that also includes Araki-Kudo-Dyer-Lashof operations on the mod-$p$ homology of infinite loop spaces \cites{araki56squaring, dyer62lashof}.
-We use the language of operads \cite{may72geometry}  to describe at the chain level the integral structure required to define (co)homology operations at every prime.
-We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod-$p$ homology of their algebras; these are the Barratt-Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
-Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical products generalizing the \mbox{cup-$i$} products of Steenrod to every prime.
-An alternative approach based on the Eilenberg-Zilber contraction can be found in \cite{gonzalez2005hpt}.
-Up to now, although its existence is warrantied by acyclic model argument \cite{eilenberg1953acyclic}, no $E_\infty$-structure was known on the cochains of cubical sets.
-Using an $E_\infty$-bialgebra structure on the chains of the interval we effectively construct an $U(\mathcal M)$-algebra structure on them, and as a consequence provide a description of Steenrod products for cochains of cubical sets as well.
-The $p=2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2018axiomatic}, and in the cubical setting to the cup-$i$ products of  Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l-Pilarczy \cite{pilarczyk2016cubical}.
-
-We also contribute to a growing body of open source software \cites{manero2020effective, pilarczyk2015contraction, sagemath} resulting from an effort to rewrite key concepts from Homotopy Theory in effective forms.
-Uses in Applied Topology are motivating some of this work \cite{tauzin2020giottotda}, but the impetus also comes from Voevodsky's program for a comprehensive, computational foundation of mathematics based on the homotopical interpretation of type theory \cite{bauer2017hott}.
-A \texttt{Python} implementation of all the constructions in this article can be found in A.M-M.'s website.\footnote{Currently hosted at \url{https://www.medina-mardones.com/}}
-
-An outline of the article is described next.
-We first introduce, in Section~2, the conventions we will follow regarding chain complexes, simplicial sets and cubical sets.
-Then, in Section~3, we review the key notions from group homology we will use for cyclic and symmetric groups.
-Section~4 is devoted to the language of operads and related structures that we use, in Section~5, to define an integral structure at the chain level inducing Steenrod operations for every prime.
-Section~6, the bulk of this work, presents effective constructions of Steenrod-Adem structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
-It also describes a natural $U(\mathcal M)$-algebra structure on the cochains of simplicial and cubical sets inducing natural Steenrod-Adem structures on them.
-We end, in Section~7, with an overview of some connections of this work to important geometric and combinatorial structures, and provide an outline of future research directions.
-
-\section*{Acknowledgement}
-
-The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Greg Brumfiel, Dev Sinha, Jens Kjaer, Calista Bernard, and Andy Putnam, for insightful discussions and valuable comments, and to the anonymous referee for many helpful suggestions.
-
-\section{Preliminaries}
-
-\subsection{Chain complexes}
-\label{ssec: chain cpx}
-
-Let $R$ be a ring.
-We denote by $(\mathbf{Ch}_R, \otimes, R)$ the symmetric monoidal category of homologically graded chain complexes of $R$-modules.
-The set of $R$-linear maps between chain complexes as well as the tensor product of chain complexes are regarded as chain complexes in the usual way:
-\begin{equation*}
-\Hom(A, A^\prime)_n = \big\{f \ |\ a \in A_m \Rightarrow f(a) \in A^\prime_{m+n} \big\}, \qquad
-\partial f = \partial \circ f - (-1)^{|f|}f \circ \partial,
-\end{equation*}
-\begin{equation*}
-(A \otimes A^\prime)_n = \bigoplus_{p + q = n} A_p \otimes A^\prime_q, \qquad \partial (a \otimes a^\prime) = \partial a \otimes a^\prime + (-1)^{|a|} a \otimes \partial a^\prime.
-\end{equation*}
-We embed the category of $R$-modules as the full subcategory of $\mathbf{Ch}_R$ with objects concentrated in degree $0$.
-The endofunctor $\Hom(-, R)$ is referred to as the \textit{linear duality functor}.
-We notice that if a chain complex is concentrated in non-negative degrees then its linear dual is on non-positive ones.
-
-The rings we will mostly be interested in are the group rings $\Z[\mathrm G]$ and $\mathbb{F}_p[\mathrm G]$ of finite groups, where $p$ is prime and $\mathbb{F}_p$ is the field with $p$ elements.
-
-\subsection{Simplicial sets}
-
-The \textit{simplex category} $\triangle$ is defined to have an object $[n] = \{0, \dots, n\}$ for every $n \in \mathbb{N}$ and a morphism $[m] \to [n]$ for each order-preserving function from $[m]$ to $[n]$.
-The morphisms $\delta_i : [n-1] \to [n]$ and $\sigma_i : [n+1] \to [n]$ defined for $0 \leq i \leq n$ by
-\begin{equation*}
-\delta_i(k) = 
-\begin{cases} k & k < i, \\ k+1 & i \leq k, \end{cases}
-\quad \text{ and } \quad
-\sigma_i(k) = 
-\begin{cases} k & k \leq i, \\ k-1 & i < k, \end{cases}
-\end{equation*} 
-generate all morphisms in the simplex category.
-
-A \textit{simplicial set} $X$ is a contravariant functor from the simplex category to the category of sets and a simplicial map is a natural transformation between two simplicial sets.
-As is customary we use the notation
-\begin{equation*}
-X\big( [n] \big) = X_n, \qquad X(\delta_i) = d_i, \qquad X(\sigma_i) = s_i,
-\end{equation*}
-and refer to elements in the image of any $s_i$ as \textit{degenerate}.
-
-For each $n \in \mathbb{N}$, the simplicial set $\triangle^n$ is defined by
-\begin{equation*}
-\triangle^n_k  = \Hom_{\triangle} \big( [k], [n] \big), \qquad 
-d_i(x) = x \circ \delta_i, \qquad 
-s_i(x) = x \circ \sigma_i,
-\end{equation*}
-and any simplicial set can be expressed as a colimit of these
-\begin{equation*}
-X = \colim_{\triangle^n \to X} \triangle^n.
-\end{equation*}
-We represent the non-degenerate elements of $\triangle^n_k$ as an increasing sequence $[v_0, \dots, v_k]$ of non-negative integers each less than or equal to $n$.
-
-The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: 
-\begin{equation*}
-N_\bullet(X; R)_n = \frac{R \{ X_n \}}{R \{ s(X_{n-1}) \}}
-\end{equation*}
-where $s(X_{n-1}) = \bigcup_{i=0}^{n-1} s_i(X_{n-1})$, and $\partial_n : N_*(X)_n \to N_*(X)_{n-1}$ is given by
-\begin{equation*}
-\partial_n = \sum_{i=0}^{n} (-1)^id_{i}.
-\end{equation*}
-The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.
-
-It is convenient to emphasize that
-\begin{equation*}
-N_\bullet(X; R) = \colim_{\triangle^n \to X} N_\bullet(\triangle^n; R).
-\end{equation*}
-
-\subsection{Cubical sets}
-
-The \textit{cube category} $\square$ is the free strict monoidal category with a \textit{bipointed object}
-\begin{equation*}
-\begin{tikzcd}
-1 \arrow[r, bend left, "\delta^0"] \arrow[r, bend right, "\delta^1"'] & 2 \arrow[r, "\sigma"] & 1
-\end{tikzcd}
-\end{equation*}
-such that $\sigma \circ \delta^0 = \sigma \circ \delta^1 = \mathrm{id}$.
-Explicitly, it contains an object $2^n$ for each non-negative integer $n$ and its morphisms are generated by the \textit{coface} and \textit{codegeneracy maps} defined by
-\begin{align*}
-\delta_i^\varepsilon & = \mathrm{id}_{2^{i-1}} \times \delta^\varepsilon \times \mathrm{id}_{2^{n-1-i}} \colon 2^{n-1} \to 2^n, \\
-\sigma_i & = \mathrm{id}_{2^{i-1}} \times \, \sigma \times \mathrm{id}_{2^{n-i}} \colon 2^{n} \to 2^{n-1}.
-\end{align*}
-
-A \textit{cubical set} $X$ is a contravariant functor from the cube category to the category of sets and a cubical map is a natural transformation between two cubical sets.
-As is customary, we use the notation
-\begin{equation*}
-X\big( 2^n \big) = X_n \qquad X(\delta^\varepsilon_i) = d^\varepsilon_i \qquad X(\sigma_i) = s_i,
-\end{equation*}
-and refer to elements in the image of any $s_i$ as \textit{degenerate}.
-
-For each $n \in \mathbb{N}$, the cubical set $\square^n$ is defined by
-\begin{equation*}
-\square^n_k  = \Hom_{\square} \big( 2^k, 2^n \big), \qquad 
-d^\varepsilon_i(x) = x \circ \delta^\varepsilon_i, \qquad 
-s_i(x) = x \circ \sigma_i,
-\end{equation*}
-notice that iteratively
-\begin{equation*}
-\square^n = \overbrace{\square^1 \times \cdots \times \square^1}^{n \text{ times }}.
-\end{equation*}
-We represent the non-degenerate elements of $\square^n$ as sequences $x_1 \cdots\, x_n$ with each $x_i \in \{[0], [1], [0,1]\}$. Any cubical set can be expressed as a colimit of these
-\begin{equation*}
-X = \colim_{\square^n \to X} \square^n.
-\end{equation*}
-
-The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: The chain complex $N_\bullet(\square^1)$ is simply the cellular chain complex of the interval,
-isomorphic to
-\begin{equation*}
-\begin{tikzcd} [column sep = small, row sep = 0.1pt]
-R\{[0], [1]\}  & \arrow[l] R\{[0,1]\} \\
-{[1] - [0]} & \arrow[l, |->] \left[0,1\right].
-\end{tikzcd}
-\end{equation*}
-Set
-\begin{equation} \label{eq: chains on I^n}
-N_\bullet(\square^n; R) = N_\bullet(\square^1; R)^{\otimes n}
-\end{equation}
-and define
-\begin{equation*}
-N_\bullet(X; R) = \colim_{\square^n \to X} N_\bullet(\square^n; R).
-\end{equation*}
-
-The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.
-
-\section{Group homology}
-\label{sec: goup homology}
+\section{Group homology} \label{s:goup homology}
 
@@
 Preparing for that, we first developed the language of $\Gamma$-modules and operads, where the integral structure defining Steenrod operations is clearly expressed.
-
-\section{$\Gamma$-modules, operads and PROPs}
-
-In this section we set up a framework in which the structure responsible for Steenrod operations becomes most transparent.
-Given our applications, we consider $\mathbf{Ch}_R$ as the base category, remarking that all definitions in this section apply to general closed symmetric monoidal categories.
-
-\subsection{$\Gamma$-modules}
-Recall that a group $\mathrm G$ can be thought of as a category with a single object and only invertible morphisms, and that a chain complex of left (resp.
-right) $R[\mathrm G]$-modules is the same as a covariant (resp.
-contravariant) functor from $\mathrm G$ to $\mathbf{Ch}_R$.
-Right actions are more commonly used in the literature of operads so we emphasize that perspective.
-Taking inverses allows for the switch between these two conventions.
-
-A \textit{groupoid} is a small category where all morphisms are invertible.
-\begin{definition}
-	A \textit{$\Gamma$-module} is a contravariant functor to $\mathbf{Ch}_R$ from a groupoid $\Gamma$ with objects the natural numbers and morphisms satisfying $\Gamma(r,s) = \emptyset$ for $r \neq s$.
-We denote the category of $\Gamma$-modules and natural transformations by $\mathbf{Ch}_R^\Gamma$.
-\end{definition}
-
-We are mostly interested in two examples of $\Gamma$-modules, those associated to the groupoids $\mathrm{S}$ and $\mathrm{C}$ defined by
-\begin{equation*}
-\mathrm{S}(r, r) = \mathrm{S}_r, \qquad
-\mathrm{C}(r,r) = \mathrm{C}_r,
-\end{equation*}
-for every $r \in \mathbb{N}$. The inclusion $\mathrm{C}_r \to \mathrm{S}_r$ induces a forgetful functor
-\begin{equation*}
-\begin{tikzcd} [column sep = small]
-\mathbf{Ch}_R^\mathrm{S}  \arrow[r] & \mathbf{Ch}_R^\mathrm{C}.
-\end{tikzcd}
-\end{equation*}
-
-Given an object $A$ in $\mathbf{Ch}_R$ there are two important $\Gamma$-modules associated to it; an $\mathrm{S}$-module known as \textit{endomorphism $\mathrm{S}$-module} $\End_A$, and an $\mathrm{S}^{op}$-module known as \textit{coendomorphism $\mathrm{S}$-module} $\End^A$.
-These are defined by
-\begin{align*}	
-\End_A(r) &= \Hom(A^{\otimes r},A), \\
-\End^A(r) &= \Hom(A,A^{\otimes r}),
-\end{align*}
-with respective right and left actions defined by permutation of tensor factors.
-
-Another groupoid of importance to us is $\mathrm{S} \times \mathrm{S}^{op}$.
-Contravariant functors from it to $\mathbf{Ch}_R$ are called \textit{$\mathrm{S}$-bimodules} and their functor category is denoted $\mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}}$.
-Notice that the inclusions
-define forgetful functors
-\begin{equation*}
-\begin{tikzcd}[column sep=small, row sep=tiny]
-& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"'] \arrow[dr, "U_2"] & \\
-\mathbf{Ch}_R^{\mathrm{S}} &  & \mathbf{Ch}_R^{\mathrm{S}^{op}},
-\end{tikzcd}
-\end{equation*}
-and that for any object $A$ in $\mathbf{Ch}_R$, the canonical \textit{endomorphism bimodule}
-\begin{equation*}
-\End_A^A(r, s) = \Hom(A^{\otimes r}, A^{\otimes s})
-\end{equation*}
-forgets to $\End_A$ and $\End^A$.
-
-Using the groupoid automorphism sending every morphisms to its inverse we can identify $\Gamma$- and $\Gamma^{op}$- modules.
-In particular, the statement claiming that the linear duality functor induces a morphism of $\mathrm{S}$-modules
-\begin{equation*}
-\End^A \to \End_{\Hom(A, R)}
-\end{equation*}
-for every object $A$ in $\mathbf{Ch}_R$ is well defined and easily verified using this identification.
-
-A \textit{resolution} in $\mathbf{Ch}_R^\Gamma$ is a morphism $\phi$ of $\Gamma$-modules such that $\phi(r)$ is a resolution in the category of chain complexes of $R[\Gamma_r]$-modules for each $r \in \mathbb{N}$.
-A $\Gamma$-module $\mathcal R$ is said to be $E_\infty$ if $\mathcal R(0) = R$ and there exists a resolution $\mathcal R \to \underline{R}$ where $\underline{R}$ is the object in $\mathbf{Ch}_R^\Gamma$ defined by $\underline{R}(r) = R$ and $\underline{R}(\gamma) = \mathrm{id}_R$ for every $r \in \mathbb{N}$ and $\gamma \in \Gamma_r$.
-
-\begin{definition} \label{def: minimal cyclic resolution}
-	The \textit{minimal} $E_\infty$-$\mathrm{C}$-\textit{module} $\mathcal W$ is the functor in $\mathbf{Ch}_R^\mathrm{C}$ assigning to $r$ the chain complex
-	\begin{equation*}
-	\begin{tikzcd} [column sep = .5cm]
-	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,T"'] \cdots
-	\end{tikzcd}
-	\end{equation*}
-	concentrated in non-negative degrees.
-\end{definition}
-
-\subsection{Operads and PROPs}
-
-Operads an PROPs are respectively $\mathrm{S}$-modules and \mbox{$\mathrm{S}$-bimodules} enriched with further compositional structure.
-These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a PROP.
-
-Succinctly, an operad $\mathcal O$ is an $\mathrm{S}$-module together with a collection of $R$-linear maps
-\begin{equation*}
-\mathcal O(r) \otimes \mathcal O(s) \to \mathcal O(r+s-1)
-\end{equation*}
-satisfying suitable associativity, equivariance and unitality conditions. A PROP $\mathcal P$ is an $\mathrm{S}$-bimodule together with two types of compositions; horizontal
-\begin{equation*}
-\mathcal P(r_1, s_1) \otimes \mathcal P(r_2, s_2) \to \mathcal P(r_1 + r_2, s_1 + s_2)
-\end{equation*}
-and vertical
-\begin{equation*}
-\mathcal P(r,s) \otimes \mathcal P(s, t) \to \mathcal P(r, t)
-\end{equation*}
-satisfying their own versions of associativity, equivariance and unitality. For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008operads}.
-
-We have already mentioned that for any chain complex $A$, the $\mathrm{S}$-module $\End_A$ is naturally an operad and the $\mathrm{S}$-bimodule $\End_A^A$ is naturally a PROP.
-We add that considering $\End^A$ as an $\mathrm{S}$-module, its compositional structure also defines an operad structure on it.
-
-We remark that the compositional structure of a PROP $\mathcal P$ restricts to operad structures on $U_1(\mathcal P)$ and $U_2(\mathcal P)$.
-
-The type of operads that we are most interested in are $E_\infty$-operads which, as we will discuss in the next section, are used to describe commutativity up to coherent homotopies.
-
-\begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}]
-	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a PROP $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
-\end{definition}
-
-\subsection{Algebras, coalgebra and bialgebras}
-
-A morphisms of operads or of PROPs is simply a morphisms of their underlying $\mathrm{S}$-modules or $\mathrm{S}$-bimodules preserving the respective compositional structures.
-
-Given a chain complex $A$, an operad $\mathcal O$ and a PROP $\mathcal P$.
-An $\mathcal O$-\textit{algebra} (resp.
-$\mathcal O$-\textit{coalgebra}) structure on $A$ is an operad morphism $\mathcal O \to \End_A$ (resp.
-$\mathcal O \to \End^A$), and a $\mathcal P$-\textit{bialgebra} structure on $A$ is a PROP morphism $\mathcal P \to \End_A^A$.
-
-We remark that the linear duality functor naturally transforms an $\mathcal O$-coalgebra structure on a chain complex into an $\mathcal O$-algebra structure on its dual.
-
-Algebras over $E_\infty$-operads are the central objects of study in this work.
-To develop intuition for them, let us consider a chain complex $A$ with an algebra structure over $\underline{R}$, thought of as an operad with all compositions corresponding to the identity map $R \to R$.
-The $\underline{R}$-algebra structure on $A$ is generated by a linear map $\mu \colon A \otimes A \to A$ which is (strictly) commutative and associative, and a linear map $\eta \colon R \to A$ that determines a (two-sided) unit for $\mu$.
-Since $E_\infty$-operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies.
-The two main examples to keep in mind are the cochains of spaces and the chains of infinite loops spaces.
-
-\section{Steenrod-Adem structures}
-
-We now introduce an operadic formulation of a structure giving rise to Steenrod operations at every prime.
-It is based on \cites{steenrod47products, steenrod53symmetric, steenrod53cyclic, may70generalapproach}, and takes a viewpoint that emphasizes the integral structure needed to define them and prove their relations at every prime.
-For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}.
-
-\begin{definition} \label{def: Steenrod-Adem structure}
-	A \textit{Steenrod-Adem structure} on an operad $\mathcal O$ is a 
-	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad
-	\begin{equation*}
-	\begin{tikzcd}[column sep = normal, row sep = small]
-	& \mathcal R \arrow[dr, "\phi", out=0] & \\
-	\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \mathcal O
-	\end{tikzcd}
-	\end{equation*}
-	such that $\iota$ is a quasi-isomorphism and $\phi$ a morphism of operads.
-\end{definition}
-
-\begin{remark} \label{rmk: Deligne conjecture}
-	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$.
-In this language, a choice of factorization for a Steenrod-Adem structure defines in particular a \textit{commutative multiplication}.
-\end{remark}
-
-\begin{definition}
-	Let $A$ be a chain complex.
-A Steenrod-Adem structure on $\mathrm{End}_A$ is referred to as one on $A$.
-Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod} $(r, i)$-\textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
-\end{definition}
-
-\begin{remark}
-	Restricting a Steenrod-Adem structure on a chain complex $A$ to a given arity $r$ corresponds to specifying a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$.
-This pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ introduced in \cite{may70generalapproach} Definition 2.1.
-Furthermore, the restriction to arity $r^2$ enhances this pair to an \textit{Adem object} as described in Definition 4.1 loc.
-cit.
-\end{remark}
-
-A Steenrod-Adem structure on a chain complex $A$ allows us to define operations on its $\mathbb{F}_p$-homology for every prime $p$.
-These operations are structurally different if $p$ is even or odd.
-Using the previous Remark, the definitions below recover Steenrod's original definition for the cohomology of spaces and that of Araki-Kudo-Dyer-Lashof operations for the homology of infinite loop spaces.
-
-For the rest of this section $A$ is a chain complex equipped with a Steenrod-Adem structure.
-
-\begin{definition}
-	For any prime $p$, the $\mathbb{F}_p$-linear map
-	\begin{equation*}
-	D^p_i : (A \otimes \mathbb{F}_p) \to (A \otimes \mathbb{F}_p)
-	\end{equation*}
-	is defined by sending $a$ to the Steenrod \mbox{$(p, i)$-product} of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
-\end{definition}
-
-We notice that if $a$ is of degree $q$ then $D^p_i(a)$ is of degree $q + (p-1)q + i$.
-
-\begin{definition}
-	For any integer $s$, the \textit{Steenrod operation}
-	\begin{equation*}
-	P_s : H_\bullet(A; \mathbb{F}_2) \to H_{\bullet + s}(A; \mathbb{F}_2)
-	\end{equation*}
-	is defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_2)$ of degree $q$ to the class represented by $D^2_{s-q}(a)$.
-\end{definition}
-
-Notice that the Steenrod squares are determined by the Steenrod $(2,i)$-products with $\mathbb{F}_2$-coefficients.
-These binary operations are known as cup-$i$ products.
-In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod $\big(p, k(p-1)-\varepsilon\big)$-products for $\varepsilon \in \{0,1\}$.
-We can explain the appearance of these specific Steenrod products as follows.
-The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even an $(2t+1)(p-1) - \varepsilon$ if $q$ is odd.
-According to Lemma \ref{lem: Thom's theorem}, these are the only homologically non-trivial cases.
-
-\begin{definition} \label{def: Steenrod operations at odd prime}
-	For any integer $s$, the \textit{Steenrod operations}
-	\begin{equation*}
-	P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1)}(A; \mathbb{F}_p)
-	\end{equation*}
-	and
-	\begin{equation*}
-	\beta P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1) - 1}(A; \mathbb{F}_p)
-	\end{equation*}
-	are defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_p)$ of degree $q$ to the classes represented respectively for $\varepsilon \in\{0,1\}$ by
-	\begin{equation*}
-	(-1)^s \nu(q) D^p_{(2s-q)(p-1)-\varepsilon}(a)
-	\end{equation*}
-	where $\nu(q) = (-1)^{q(q-1)m/2}(m!)^q$ and $m = (p-1)/2$.
-\end{definition}
-
-\begin{remark}
-	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq.
-6.1.
-in \cite{steenrod53cyclic}).
-The notation $\beta P_s$ is motivated by the relationship of this operator and the Bockstein of the reduction $\mathbb Z \to \mathbb Z/p\mathbb Z$.
-\end{remark}
-
-Steenrod operations satisfy the Cartan and Adem relations.
-Below we state the subset of these relations that is most commonly used and refer to Sections 2 and 4 of \cite{may70generalapproach} for a complete list and proofs.
-\begin{lemma}
-	Let $A$ be equipped with a Steenrod-Adem structure. If $[\alpha], [\beta] \in H(A;\mathbb{F}_p)$ then
-	\begin{equation*}
-	P_s\big([\alpha] [\beta]\big) = \sum_{i+j=s} P_i\big( [\alpha] \big) P_j\big( [\beta] \big),
-	\end{equation*}
-	and
-	\begin{itemize}
-		\item If $p = 2$ and $a > 2b$
-		\begin{equation*}
-		P_{a}P_{b} = \sum_i {2i-a \choose a-b-i-1} P_{a+b-i}P_i,
-		\end{equation*}
-		\item If $p > 2$ and $a > pb$
-		\begin{equation*}
-		P_{a}P_{b} = \sum_i (-1)^{a+i}{pi-a \choose a-(p-1)b-i-1} P_{a+b-i}P_i.
-		\end{equation*}
-	\end{itemize}		
-\end{lemma}
-
-\begin{proof}
-	These are proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
-\end{proof}
-
-For the even prime, proofs at the chain level of these formulae have been given in \cite{medina2020cartan,brumfiel2020cochain}.
-For a different operadic approach to Steenrod operations at the even prime please consult \cite{chataur2005adem-cartan}.
-
-For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$, which we use in subsections 6.4 and 6.5.
-
-\section{Effective constructions}
-\label{sec: effective constructions}
-
-In this section we construct explicit Steenrod-Adem structures on three well know combinatorial $E_\infty$-operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-PROP $\mathcal M$ \cite{medina2020prop1}.
-We also define natural and effective Steenrod-Adem structure on the normalized cochains of any simplicial or cubical set, by describing a $U(\mathcal M)$-algebra structures on it.
-
-Figure~\ref{fig: bigsummary} presents a diagrammatical representation of the constructions in this section.
-
-\begin{figure}
-	\begin{tikzcd}
-	& & & U(\mathcal M) \arrow[dddr, bend left=10, "\phi^\triangle"'] \arrow[dddrr, bend left=20, "\phi^\square"'] & & \\
-	& & \mathcal X \arrow[ru, "SL"] & & & \\
-	& \mathcal E \arrow[ur, "TR"] & & & & \\
-	\mathcal W \arrow[rrrr, "\psi^\triangle", bend right=10] \arrow[rrrrr, "\psi^\square", bend right=20] \arrow[ur, "\psi_{\mathcal E}"] \arrow[uurr, "\psi_{\mathcal X}"', bend right=35, pos=.6] \arrow[uuurrr, "\psi_{U(\mathcal M)}"', bend right=45, pos=0.6] & & & & \End_{N^\bullet(X)} & \End_{N^\bullet(X)}
-	\end{tikzcd}
-	\caption{Summary of effective constructions: Steenrod-Adem structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural Steenrod-Adem structures on the normalized chains of simplicial and cubical sets.
-We are abusing notation since the maps $TR$ and $SL$ required different sign conventions.}
-	\label{fig: bigsummary}
-\end{figure}
-
-\subsection{Barratt-Eccles operad} In this subsection we effectively describe a Steenrod-Adem structure on the Barratt-Eccles operad.
-
-We begin by reviewing the $\mathrm{S}$-module structure underlying the Barratt-Eccles operad and, since will not use it in this work, refer to \cite{berger04combinatorial} for a description of if composition structure.
-For a non-negative integer $r$ define the simplicial set $E(\mathrm S_r)$ by
-\begin{equation} \label{eq: milnor model of symmetric}
-\begin{split}
-E(\mathrm S_r)_n &= \{ (\sigma_0, \dots, \sigma_n)\ |\ \sigma_i \in \mathrm{S}_r\}, \\
-d_i(\sigma_0, \dots, \sigma_n) &= (\sigma_0, \dots, \widehat{\sigma}_i, \dots, \sigma_n), \\
-s_i(\sigma_0, \dots, \sigma_n) &= (\sigma_0, \dots, \sigma_i, \sigma_i, \dots, \sigma_n) \\
-\end{split}
-\end{equation}
-with a left $\mathrm S_r$-action given by
-\begin{equation*}
-\sigma (\sigma_0, \dots, \sigma_n) = (\sigma \sigma_0, \dots, \sigma \sigma_n).
-\end{equation*} 
-The chain complex resulting from applying the functor of normalized integral chains to it is denoted $\mathcal E(r)$, which corresponds to the arity $r$ part of the Barratt-Eccles operad.
-
-\begin{definition} \label{def: Steenrod-Adem on Barratt-Eccles}
-	For every $r \geq 0$, let $\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined on basis elements by 
-	\begin{equation*}
-	\psi_{\mathcal E}(r)(e_{n}) = \begin{cases}
-	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \rho^{r_2}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m, \\
-	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m+1,
-	\end{cases}
-	\end{equation*}
-	where the sum is over all $r_1, \dots, r_m \in \{0, \dots, r-1\}$.
-\end{definition}
-
-\begin{theorem} \label{thm: Steenrod-Adem on Barratt-Eccles}
-	The morphism of $\mathrm{C}$-modules
-	\begin{equation*}
-	\psi_{\mathcal E} \colon \mathcal W \to \mathcal E
-	\end{equation*}
-	defines a Steenrod-Adem structure on the Barratt-Eccles operad.
-\end{theorem}
-
-\begin{proof}
-	This theorem follows from a computation which we defer to the appendix.
-\end{proof}
-
-\begin{example}
-	Table \ref{fig: Barratt-Eccles Steenrod products} shows $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$.
-\end{example}
-
-\begin{table}[h]
-	\centering
-	\resizebox{0.8\columnwidth}{!}{%
-		\renewcommand{\arraystretch}{1.2}
-		\begin{tabular}{|c||c|c|c|}
-			\hline
-			$r$ & $n=2$ & $n=3$ & $n=4$ \\
-			\hline
-			2 & (0,1,0) & (0,1,0,1) & (0,1,0,1,0) \\
-			\hline
-			3 & (0,1,2) + (0,2,0) & (0,1,2,0) + (0,1,0,1) & \phantom{+} (0,1,2,0,1) + (0,1,2,1,2) \\
-			& & & + (0,2,0,1,2) + (0,2,0,2,0) \\
-			\hline
-			4 & (0,1,2) + (0,2,3) & (0,1,2,3) + (0,1,3,0) & \phantom{+} (0,1,2,3,0) + (0,1,2,0,1) \\
-			& + (0,3,0) & + (0,1,0,1) & 
-			+ (0,1,2,1,2) + (0,2,3,0,1) \\
-			& & & + (0,2,3,1,2) + (0,2,3,2,3) \\
-			& & & + (0,3,0,1,2) + (0,3,0,2,3) \\
-			& & & + (0,3,0,3,0) \\
-			\hline  
-		\end{tabular}
-	}
-	\vspace*{3pt}
-	\caption{The elements $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$ where we are denoting $(\rho^{r_0}, \dots, \rho^{r_n})$ simply by $(r_0, \dots, r_n)$.}
-	\label{fig: Barratt-Eccles Steenrod products}
-\end{table}
-
-\begin{remark}
-	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota : \mathrm C_r \to \mathrm S_r$ induces a simplicial map $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ which extends to a quasi-isomorphism of $\mathrm C$-modules
-	\begin{equation*}
-	N_\bullet E(\iota) : N_\bullet E(\mathrm C) \to N_\bullet E(\mathrm S) = \mathcal E,
-	\end{equation*}
-	factoring
-	\begin{equation*}
-	\psi_{\mathcal E} :
-	\begin{tikzcd}
-	\mathcal W \arrow[r, "\phi_{\mathrm C}"] &[-3pt] N_\bullet E(\mathrm C) \arrow[r, "N_\bullet E(\iota)"] &[5pt] \mathcal E.
-	\end{tikzcd}
-	\end{equation*}
-\end{remark}
-
-\subsection{Surjection operad}
-
-In this subsection we introduce a Steenrod-Adem structures on the surjection operad.
-There are two widely used sign conventions for this operad respectively due to McClure-Smith \cite{mcclure03cochain} and Berger-Fresse \cite{berger04combinatorial}.
-Using the Berger-Fresse convention, we can define a Steenrod-Adem structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}.
-We define an Steenrod-Adem structure on the surjection operad in a convention independent way which recovers the table reduction Steenrod-Adem structure in the Berger-Fresse case.
-
-Let us start by recalling the definition of the surjection operad.
-For a non-negative integer $r$ let $\mathcal X(r)_n$ be the free abelian group generated by all functions from $\{1, \dots, n+r\}$ to $\{1, \dots, r\}$ modulo the subgroup generated by degenerate functions, i.e., those which are either non-surjective or have a pair of equal consecutive values.
-We only describe the McClure-Smith convention since we refer to it in subsequent sections.
-The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s : \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top dimensional generator in the chain complex
-\begin{equation} \label{eq: surjection boundary}
-\bigotimes_{i = 1}^r N_\bullet \big( \triangle^{s^{-1}(i)}; \Z \big).
-\end{equation}
-Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at the time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on.
-Since we do not use the composition structure we refer to \cite{mcclure03cochain} for it.
-
-Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure-Smith to prove $\mathcal X$ is an $E_\infty$-operad and whose introduction is credited to Benson \cite{benson1998rep}.
-Let the maps $i,\ p$ and $s$ be defined on basis elements, represented by sequences, as follows: $i : \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p : \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s : \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
-with a 1, then the new sequence is degenerate so $s$ takes it to $0$. These maps satisfy
-\begin{equation*}
-p  i = \mathrm{id}
-\qquad \text{ and } \qquad
-\mathrm{id} - i  p = \partial s + s \partial.
-\end{equation*}
-These maps define a contraction of $\mathcal X(r)$ onto $\mathcal X(1) \cong \Z$ with homotopy $h = s + i\, s\, p + \cdots + i^{r-1} s\, p^{r-1}$, satisfying
-\begin{equation*}
-\partial h + h \partial = \mathrm{id} - i^{r-1}\,p^{r-1}.
-\end{equation*}
-
-\begin{definition} \label{def: Steenrod-Adem on surjection}
-	For every $r \geq 0$, let $\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined recursively on basis elements by
-	\begin{align*}
-	\psi_{\mathcal X}(r)(e_0) & = (1, \dots, r), \\
-	\psi_{\mathcal X}(r)(e_{2m+1}) & = h\,T\,\psi_{\mathcal X}(r)(e_{2m}), \\
-	\psi_{\mathcal X}(r)(e_{2m}) & = h\,N\,\psi_{\mathcal X}(r)(e_{2m-1}),
-	\end{align*}
-	where $T$ and $N$ are defined in \eqref{eq: T and R definition}.
-\end{definition}
-
-\begin{theorem} \label{thm: Steenrod-Adem on surjection MS convention}
-	The morphism of $\mathrm{C}$-modules
-	\begin{equation*}
-	\psi_{\mathcal X} \colon \mathcal W \to \mathcal X
-	\end{equation*}
-	defines a Steenrod-Adem structure on the Surjection operad.
-\end{theorem}
-
-\begin{proof}
-	This theorem follows from a computation which we defer to the appendix.
-\end{proof}
-
-For the rest of the paper we use the McClure-Smith sign convention on $\mathcal X$.
-
-\begin{example}
-	Table \ref{fig: surjection Steenrod products} shows $\psi_{\mathcal X}(r)(e_n)$ for small values of $r$ and $n$.
-\end{example}
-
-\begin{table}[h]
-	\centering
-	\resizebox{\columnwidth}{!}{%
-		\renewcommand{\arraystretch}{1.3}
-		\begin{tabular}{|c||c|c|c|}
-			\hline
-			$r$& $n=2$ & $n=3$ & $n=4$ \\
-			\hline
-			2 & (1,2,1,2) & (1,2,1,2,1) & (1,2,1,2,1,2) \\
-			\hline
-			3 & (1,2,3,1,2) + (1,3,1,2,3) & (1,2,3,1,2,3) + (1,2,1,2,3,1)  & \phantom{+} (1,2,3,1,2,3,1) + (1,2,3,2,3,1,2) \\
-			& + (1,2,3,2,3) & + (1,2,3,1,3,1) & + (1,2,3,1,2,1,2) + (1,3,1,2,3,1,2) \\
-			& & & + (1,3,1,3,1,2,3) + (1,2,3,2,3,2,3) \\
-			& & & + (1,3,1,2,3,2,3) \\
-			\hline
-			4 & \phantom{+} (1,2,3,4,1,2) + (1,3,4,1,2,3) & \phantom{+} (1,2,3,4,1,2,3) + (1,2,4,1,2,3,4) & \\
-			& + (1,2,3,4,2,3) + (1,4,1,2,3,4) & + (1,2,3,4,1,3,4) + (1,2,1,2,3,4,1) & 25 \text{ terms } \\
-			& + (1,2,4,2,3,4) + (1,2,3,4,3,4) & + (1,2,3,1,3,4,1) + (1,2,3,4,1,4,1) & \\
-			\hline  
-		\end{tabular}
-	}
-	\vspace*{2pt}
-	\caption{The values of $\psi_{\mathcal X}(r)(e_n)$ for small values of $r$ and $n$.}
-	\label{fig: surjection Steenrod products}
-\end{table}
-
-\subsection{The finitely presented $E_\infty$-PROP $\mathcal M$}
-
-We start by reviewing the finitely presented $E_\infty$-PROP introduced in \cite{medina2020prop1}. Let $\mathcal M$ be the PROP generated by 
-\begin{equation*}
-\counit \in \mathcal M(1,0)_0, \hspace*{.6cm} \coproduct \in \mathcal M(1,2)_0, \hspace*{.6cm} \product \in \mathcal M(2,1)_1,
-\end{equation*}
-with boundary
-\begin{equation*}
-\partial\ \counit = 0, \hspace*{.6cm} \partial \ \coproduct = 0, \hspace*{.6cm} \partial \ \product = \ \boundary \, ,
-\end{equation*}
-and restricted by the relations
-\begin{equation*}
-\productcounit, \hspace*{.6cm} \leftcounitality \, , \hspace*{.6cm} \rightcounitality \, .
-\end{equation*}
-
-Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$-prop in the terminology of Bordmann-Vogt \cite{boardman1973homotopy}.
-More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$-operad.
-For the remainder of this article we write $U(\mathcal M)$ instead of $U_2(\mathcal M)$.
-
-We will define a Steenrod-Adem structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the Steenrod-Adem structure $\psi_{\mathcal X} : \mathcal W \to \mathcal X$ with a morphism of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact)
-\begin{equation*}
-SL \colon \mathcal X \to U(\mathcal M)
-\end{equation*}
-that we now define. Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element
-\begin{center}
-	\begin{tikzpicture}[scale=.85]
-	\draw (0,0)--(0,-.6) node[below]{$\scriptstyle 1$};
-	\draw (0,0)--(.5,.5);
-	\draw (-.3, .3)-- (-.2,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_1$};
-	\draw (-.5,.5)--(0,0);
-	\node at (.11,.4){$...$};
-
-	\node at (1,0){$\scriptstyle \cdots$};
-	\node at (1,-.9){$\scriptstyle \cdots$};
-
-	\draw (2,0)--(2,-.68) node[below]{$\scriptstyle r$};
-	\draw (2,0)--(2.5,.5);
-	\draw (1.7, .3)-- (1.8,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_r$};
-	\draw (1.5,.5)--(2,0);
-	\node at (2.11,.4){$...$};
-
-	\draw (1,2.5)--(1,3) node[above]{$\scriptstyle 1$};
-	\draw (1,2.5)--(0,2) node[below]{$\scriptstyle 1$};
-	\draw (.25,2.125)--(.5,2) node[below]{$\scriptstyle 2$};
-	\draw (.5,2.25)--(1,2) node[below]{$\scriptstyle 3$};
-	\draw (1,2.5)--(2,2) node[below]{\quad $\scriptstyle n + r$};
-	\node at (1.5,1.75){$...$};
-
-	\node at (1,1.3) {$\vdots$};
-
-	\node at (2.85,0){};
-	\end{tikzpicture}
-\end{center}
-that has no internal vertices and such that the $n+r$ strands at the top are orderly connected to the strands at the bottom following the values of $s$.
-
-It can be directly verified using the presentation of $\mathcal M$ that the boundary of $SL(s)$ is obtained by removing strands one at the time in the order they are attached at the bottom.
-This is precisely the image of $SL(\partial s)$ according to \eqref{eq: surjection boundary}.
-Furthermore, relabeling the bottom edges agrees with the permutation of preimages of the associated surjection.
-Since both operads have the homology of a point and $(1, \dots, r)$ is sent to a representative of a homology generator we have proven the following
-
-\begin{theorem} \label{thm: Steenrod-Adem on U(M)}
-	The composition $\psi_{U(\mathcal M)}$
-	\begin{equation*}
-	\begin{tikzcd}[column sep = normal]
-	\mathcal W \arrow[r, "\psi_{\mathcal X}"] & \mathcal X \arrow[r, "SL"] & U(\mathcal M)
-	\end{tikzcd}
-	\end{equation*}
-	defines a Steenrod-Adem structure on $U(\mathcal M)$.
-\end{theorem}
-
-\begin{example}
-	Figure \ref{fig: cup 0,1,2} shows $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$.
-\end{example}
-
-\begin{figure}[h]
-	\centering
-	\boxed{
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-		\draw (1,3) to [out=-25, in=90] (2,0);
-
-		\node at (1,-.5){$n=0$};
-		\end{tikzpicture}\hspace*{1cm}
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-
-		\draw [shorten >= 0cm] (.6,2.73) to [out=-100, in=90] (2,0);
-		%\draw [shorten <= 0cm] (1,1.5) to [out=-60, in=90] (2,0);
-
-		\draw [shorten >= .15cm] (1,3) to [out=-25, in=30, distance=1.1cm] (1,1.5);
-		\draw [shorten <= .1cm] (1,1.5) to [out=210, in=20] (0,1);
-
-		\node at (1,-.5){$n=1$};
-		\end{tikzpicture}\hspace*{1cm}
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-		\draw (1,3) to [out=-25, in=90] (2,0);
-
-		\draw [shorten >= 0cm] (.6,2.73) to [out=210, in=135] (1,1.5);
-		\draw [shorten <= 0cm] (1,1.5) to [out=-45, in=170] (2,1);
-
-		\draw [shorten >= .1cm] (1.4,2.73) to [out=-30, in=45] (1,1.5);
-		\draw [shorten <= .1cm] (1,1.5) to [out=-135, in=10] (0,1);
-
-		\node at (1,-.5){$n=2$};
-		\end{tikzpicture}
-	}
-	\caption{The values of $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$.}
-	\label{fig: cup 0,1,2}
-\end{figure}
-
-\subsection{Cochains of simplicial sets}
-
-In this subsection we introduce a natural Steenrod-Adem structure on the normalized cochains of any simplicial set $X$.
-Since a Steenrod-Adem structure was constructed in the previous section for $U(\mathcal M)$, we only need to describe a natural $U(\mathcal M)$-algebra structure on $N^\bullet(X)$.
-Using the linear duality functor, it suffices to construct a natural $U(\mathcal M)$-coalgebra structure on $N_\bullet(X)$ which, in turn, can be derived via a Kan extension argument from one on each $N_\bullet(\triangle^n)$.
-We obtain these coalgebra structures by restricting a full $\mathcal M$-bialgebra structure.
-An $\mathcal M$-bialgebra structure is specified by three linear maps, the images of the generators
-\begin{equation*}
-\counit, \quad \coproduct, \quad \product,
-\end{equation*}
-satisfying the relations in the presentation of $\mathcal M$. For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
-(1) The counit $\epsilon \in \Hom(N_\bullet(\triangle^n), \Z)$ by
-\begin{equation*}
-\epsilon \big( [v_0, \dots, v_q] \big) = \begin{cases} 1 & \text{ if } q = 0, \\ 0 & \text{ if } q>0. \end{cases}
-\end{equation*}
-(2) The coproduct $\Delta \in \Hom(N_\bullet(\triangle^n), N_\bullet(\triangle^n)^{\otimes2})$ by
-\begin{equation*}
-\Delta \big( [v_0, \dots, v_q] \big) = \sum_{i=0}^q [v_0, \dots, v_i] \otimes [v_i, \dots, v_q].
-\end{equation*}
-(3) The product $\ast \in \Hom(N_\bullet(\triangle^n)^{\otimes 2}, N_\bullet(\triangle^n))$ by
-\begin{equation*}
-\left[v_0, \dots, v_p \right] \ast \left[v_{p+1}, \dots, v_q\right] = \begin{cases} (-1)^{p+|\pi|} \left[v_{\pi(0)}, \dots, v_{\pi(q)}\right] & \text{ if } v_i \neq v_j \text{ for } i \neq j, \\
-0 & \text{ if not}, \end{cases}
-\end{equation*}
-where $\pi$ is the permutation that orders the totally ordered set of vertices, and $(-1)^{|\pi|}$ its sign.
-
-\begin{theorem} \label{thm: simplicial chain bialgebra}
-	For every $n \in \mathbb{N}$, the assignment
-	\begin{equation*}
-	\counit \mapsto \epsilon, \quad \coproduct \mapsto \Delta, \quad \product \mapsto \ast,
-	\end{equation*}
-	defines a natural $\mathcal M$-bialgebra structure  on $N_\bullet(\triangle^n)$.
-\end{theorem}
-
-\begin{proof}
-	This statement is proven as Theorem 4.2 in \cite{medina2020prop1}.
-\end{proof}
-
-\begin{definition}
-	Let $X$ be a simplicial set.
-Denote by $\phi^\triangle : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem \ref{thm: simplicial chain bialgebra}.
-\end{definition}
-
-\begin{theorem}
-	The commutative diagram
-	\begin{equation*}
-	\begin{tikzcd}[column sep = small, row sep = small]
-	&[18pt] U(\mathcal M) \arrow[dr, "\phi^\triangle", out=0] &[-0pt] \\
-	\mathcal W \arrow[ur, "\psi_{U(\mathcal M)}", in=180] \arrow[rr, "\psi^\triangle"] & & \mathrm{End}_{N^\bullet (X)}
-	\end{tikzcd}
-	\end{equation*}
-	defines a natural Steenrod-Adem structure on $N^\bullet(X)$ for any simplicial set $X$.
-\end{theorem}
-
-\begin{remark}
-	The $E_\infty$-structure we described in Theorem \ref{thm: simplicial chain bialgebra}, depending solely on three fundamental maps, recovers the coalgebra structures of McClure-Smith \cite{mcclure03cochain} and, up to signs, that of Berger-Fresse \cite{berger04combinatorial}.
-\end{remark}
-
-\begin{example}
-	Let us consider the prime $2$. The value $P^1(x)\big([0,1,2,3,4]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^4)$ is equal to the value of $x^{\otimes 2}$ acting on
-	\begin{align*}
-	[0, 1, 2, 3] \otimes [0, 1, 3, 4] \ +\  & 
-	[0, 2, 3, 4] \otimes [0, 1, 2, 4] \\ \ +\ 
-	[0, 1, 2, 3] \otimes [1, 2, 3, 4] \ +\ &
-	[0, 1, 3, 4] \otimes [1, 2, 3, 4].
-	\end{align*}
-	Similarly, the value of $P^2(y)\big([0,1,2,3,4,5,6,7]\big)$ for a homogeneous cocycle $y$ in $N^{-5}(\triangle^7)$ is equal to the value of $y^{\otimes 2}$ acting on
-	\begin{align*}
-	[0, 1, 2, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] & \ +\
-	[0, 1, 2, 3, 6, 7] \otimes [0, 1, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 2, 3, 4, 7] \otimes [0, 1, 4, 5, 6, 7] & \ +\ 
-	[0, 2, 3, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] \\ \ +\ 
-	[0, 2, 3, 4, 6, 7] \otimes [0, 1, 2, 4, 5, 6] & \ +\ 
-	[0, 2, 3, 4, 5, 7] \otimes [0, 1, 2, 5, 6, 7] \\ \ +\ 
-	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] & \ +\ 
-	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 5, 6] \\ \ +\ 
-	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 6, 7] & \ +\ 
-	[0, 1, 2, 3, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 2, 3, 4, 7] \otimes [1, 2, 4, 5, 6, 7] & \ +\ 
-	[0, 1, 3, 4, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 3, 4, 5, 7] \otimes [1, 2, 3, 5, 6, 7] & \ +\ 
-	[0, 1, 4, 5, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 4, 5, 6, 7] \otimes [1, 2, 3, 4, 6, 7] & \ +\ 
-	[0, 1, 2, 3, 4, 7] \otimes [2, 3, 4, 5, 6, 7] \\ \ +\ 
-	[0, 1, 2, 4, 5, 7] \otimes [2, 3, 4, 5, 6, 7] & \ +\ 
-	[0, 1, 2, 5, 6, 7] \otimes [2, 3, 4, 5, 6, 7].
-	\end{align*}
-\end{example}
-
-\begin{example}
-	Let us consider the prime $3$. The value $\beta P^1(x)\big([0,1,2,3,4,5,6,7,8]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^8)$ is equal to the value of $x^{\otimes 3}$ acting on
-	\begin{align*}
-	& \,-\, [0, 6, 7, 8] \otimes [0, 1, 2, 3] \otimes [3, 4, 5, 6] \,+\, [0, 1, 7, 8] \otimes [1, 2, 3, 4] \otimes [4, 5, 6, 7] \\ & \,-\, [0, 1, 2, 8] \otimes [2, 3, 4, 5] \otimes [5, 6, 7, 8].
-	\end{align*}
-	Similarly, the value of $P^1(y)\big([0,1,\dots,7]\big)$ for a homogeneous cocycle $y$ in $N^{-3}(\triangle^7)$ is equal to the value of $y^{\otimes 3}$ acting on
-	\begin{align*}
-	& \,-\, [0,3,4,5] \otimes [0,5,6,7] \otimes [0,1,2,3] \,-\, [0,4,5,6] \otimes [0,1,6,7] \otimes [1,2,3,4] \\ & \,-\, [0,5,6,7] \otimes [0,1,2,7] \otimes [2,3,4,5] \,-\, [0,1,4,5] \otimes [1,5,6,7] \otimes [1,2,3,4] \\ & \,+\, [0,1,5,6] \otimes [1,2,6,7] \otimes [2,3,4,5] \,-\, [0,1,6,7] \otimes [1,2,3,7] \otimes [3,4,5,6] \\ & \,-\, [0,1,2,5] \otimes [2,5,6,7] \otimes [2,3,4,5] \,-\, [0,1,2,6] \otimes [2,3,6,7] \otimes [3,4,5,6] \\ & \,-\, [0,1,2,7] \otimes [2,3,4,7] \otimes [4,5,6,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [0,1,6,7] \\ & \,+\, [0,2,3,4] \otimes [4,5,6,7] \otimes [0,1,2,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [1,2,6,7] \\ & \,-\, [0,1,3,4] \otimes [4,5,6,7] \otimes [1,2,3,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [2,3,6,7] \\ & \,+\, [0,1,2,4] \otimes [4,5,6,7] \otimes [2,3,4,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [3,4,6,7] \\ & \,-\, [0,1,2,3] \otimes [3,5,6,7] \otimes [3,4,5,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [4,5,6,7] \\ & \,+\, [0,1,2,3] \otimes [3,4,6,7] \otimes [4,5,6,7].
-	\end{align*}
-\end{example}
-
-\subsection{Cochains of cubical sets}
-
-In this subsection we introduce a natural Steenrod-Adem structure on the normalized cochains of any cubical set.
-It follows the structure of the previous subsection closely.
-By the same considerations, the desired construction will follow from a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$.
-These are determined by three linear maps satisfying the relations in the presentation of $\mathcal M$.
-For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
-(1) The counit $\epsilon \in \Hom(N_\bullet(\square^n), \Z)$ by
-\begin{equation*}
-\epsilon \left( x_1 \otimes \cdots \otimes x_d \right) = \epsilon(x_1) \cdots \, \epsilon(x_n),
-\end{equation*}
-where
-\begin{equation*}
-\epsilon([0]) = \epsilon([1]) = 1, \qquad \epsilon([0, 1]) = 0.
-\end{equation*} \vspace*{-6pt} \\
-(2) The coproduct $\Delta \in \Hom \left( N_\bullet(\square^n), N_\bullet(\square^n)^{\otimes 2} \right)$ by
-\begin{equation*}	
-\Delta (x_1 \otimes \cdots \otimes x_n) = 	
-\sum \pm \left( x_1^{(1)} \otimes \cdots \otimes x_n^{(1)} \right) \otimes 	
-\left( x_1^{(2)} \otimes \cdots \otimes x_n^{(2)} \right),	
-\end{equation*}	
-where the sign is determined using the Koszul convention, and we are using Sweedler's notation
-\begin{equation*}	
-\Delta(x_i) = \sum x_i^{(1)} \otimes x_i^{(2)}
-\end{equation*}
-for the chain map $\Delta \colon N_\bullet(\square^1) \to N_\bullet(\square^1)^{\otimes 2}$ defined by
-\begin{equation*}
-\Delta([0]) = [0] \otimes [0], \quad \Delta([1]) = [1] \otimes [1], \quad \Delta([0, 1]) = [0] \otimes [0, 1] + [0, 1] \otimes [1].
-\end{equation*}
-Using that $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$, $\Delta$ is the composition
-\begin{equation*}
-\begin{tikzcd}
-N_\bullet(\square^1)^{\otimes n} \arrow[r, "\Delta^{\otimes n}"] & \left( N_\bullet(\square^1)^{\otimes 2}  \right)^{\otimes n} \arrow[r, "sh"] & \left( N_\bullet(\square^1)^{\otimes n} \right)^{\otimes 2}
-\end{tikzcd}
-\end{equation*}
-where $sh$ is the shuffle map that places tensor factors in odd position first. \vspace*{5pt} \\
-(3) The product $\ast \in \Hom(N_\bullet(\square^n)^{\otimes 2}, N_\bullet(\square^n))$ by
-\begin{align*}
-(x_1 \otimes \cdots \otimes x_n) \ast (y_1 \otimes \cdots \otimes y_n) =
-(-1)^{|x|} \sum_{i=1}^n x_{<i} \epsilon(y_{<i}) \otimes x_i \ast y_i \otimes \epsilon(x_{>i})y_{>i},
-\end{align*}
-where
-\begin{align*}
-x_{<i} & = x_1 \otimes \cdots \otimes x_{i-1}, &
-y_{<i} & = y_1 \otimes \cdots \otimes y_{i-1}, \\
-x_{>i} & = x_{i+1} \otimes \cdots \otimes x_n, & 
-y_{>i} & = y_{i+1} \otimes \cdots \otimes y_n,
-\end{align*}
-with the convention
-\begin{equation*}
-x_{<1} = y_{<1} = x_{>n} = y_{>n} = 1 \in \Z,
-\end{equation*}
-and the only non-zero values of $x_i \ast y_i$ are
-\begin{equation*}
-\ast([0] \otimes [1]) = [0, 1], \qquad  \ast([1] \otimes [0]) = -[0, 1].
-\end{equation*}
-
-\begin{theorem} \label{thm: cubical chain bialgebra}
-	For every $n \in \mathbb{N}$, the assignment
-	\begin{equation*}
-	\counit \mapsto \epsilon, \quad \coproduct \mapsto \Delta, \quad \product \mapsto \ast,
-	\end{equation*}
-	defines a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$.
-\end{theorem}
-
-\begin{proof}
-	We present a proof of this statement in the appendix.
-\end{proof}
-
-\begin{remark}
-	We saw that for simplicial sets a natural algebraic $E_\infty$-structure was determined by basic maps in the standard simplices.
-For cubical sets, one such structure is constructed by naturally extending three maps defined just on the interval.
-\end{remark}
-
-\begin{definition}
-	Let $X$ be a cubical set.
-Denote by $\phi^\square : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem~\ref{thm: cubical chain bialgebra}.
-\end{definition}
-
-\begin{theorem}
-	The commutative diagram
-	\begin{equation*}
-	\begin{tikzcd}[column sep = small, row sep = small]
-	&[18pt] U(\mathcal M) \arrow[dr, "\phi^\square", out=0] &[-0pt] \\
-	\mathcal W \arrow[ur, "\psi_{U(\mathcal M)}", in=180] \arrow[rr, "\psi^\square"] & & \End_{N^\bullet (X)}
-	\end{tikzcd}
-	\end{equation*}
-	defines a natural Steenrod-Adem structure on $N^\bullet(X)$ for any cubical set $X$.
-\end{theorem}
-
-\begin{example}
-	Let us consider the prime $2$. The value $P^1(x)\big([01]^{4}\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\square^4)$ is equal to the value of $x^{\otimes 2}$ acting on
-	\begin{align*}&
-	[01]1[01][01] \otimes [01][01]0[01]\,+\,
-	[01][01][01]0 \otimes [01]0[01][01]\,+\, \\&
-	[01][01][01]0 \otimes 1[01][01][01]\,+\,
-	[01][01]1[01] \otimes [01]0[01][01]\,+\, \\&
-	[01][01]1[01] \otimes 1[01][01][01]\,+\,
-	[01][01][01]0 \otimes [01][01]1[01]\,+\, \\&
-	[01][01]0[01] \otimes [01][01][01]1\,+\,
-	[01]1[01][01] \otimes [01][01][01]1\,+\, \\&
-	0[01][01][01] \otimes [01][01][01]1\,+\,
-	0[01][01][01] \otimes [01][01]0[01]\,+\, \\&
-	0[01][01][01] \otimes [01]1[01][01]\,+\,
-	[01]0[01][01] \otimes 1[01][01][01].\,\phantom{+}\,
-	\end{align*}
-\end{example}
-
-\begin{example}
-	Let us consider the prime $3$. The value of $\beta P^0(x)\big([01]^2\big)$ for a homogeneous cocycle $x$ in $N^{-1}(\square^2)$ is equal to the value of $x^{\otimes 3}$ acting on
-	\begin{align*}
-	\,-\, [01]1 \otimes [01]0 \otimes 1[01] \,-\, 0[01] \otimes [01]0 \otimes 1[01] + [01]1 \otimes 0[01] \otimes [01]1 + 0[01] \otimes 0[01] \otimes [01]1.
-	\end{align*}
-\end{example}
-
-\section{Outlook}
-This article looked at Steenrod operations from an algebraic viewpoint, a subject with rich geometric and combinatorial components as well.
-For example, \cite{Postnikov} and \cite{medina2018prop2} independently introduced equivalent geometric representations of the cup-$i$ products in terms of stabilized arc surfaces \cite{KLP} and weighted ribbon graphs respectively.
-In fact, an entire $E_\infty$-operad (PROP) is constructed geometrically in this way.
-We can also interpret the Steenrod-Adem structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups ---a key ingredient in Definition \ref{def: minimal cyclic resolution}--- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.
-
-In Higher Category Theory, the paper \cite{medina2020globular} constructs a functor producing strict \mbox{$\infty$-cat}egories from group-like cup-$i$ coalgebras in a manner similar to \cite{steiner2004omega}.
-In particular, the cup-$i$ constructions described in this article for standard simplices and cubes define, respectively, the Street nerve and cubical nerve of strict $\infty$-categories.
-We anticipate that the more general Steenrod $(p,i)$-products constructed in this work will also have deep combinatorial interpretations.
-
-There is a functorial approach to the theory using the formalism of Feynman categories \cite{feynman},
-which renders all the structures and notions natural.
-This includes cyclic, planar cyclic as well as Berger's pre-operads \cite{BergerRecog}.
-Their interplay is of independent interest \cite{BergerKaufmann,feyrep} and will be linked directly to the constructions of this paper.
-
-In this article we have not focused on the operations that exist non-trivially for \mbox{$E_n$-algebras} with $n$ finite, see part III of \cite{may76homology}.
-A treatement close to ours for the $E_2$ case was given in \cite{Tourtchine}.
-Effective constructions for these Dyer-Lashof-Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang,sinha2013littledisks,berger04combinatorial,ayala2014configuration} and higher categories \cite{Bathigher,BalFiedSchwVogt,Rezkhigher}, and will appear elsewhere.
-
-\newpage
-\appendix
-\section{Proofs}
-
-\subsection{Theorem \ref{thm: Steenrod-Adem on Barratt-Eccles}}
-
-We prove that the $\Z[\mathrm{C}_r]$-linear map
-\begin{equation*}
-\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)
-\end{equation*}
-introduced in Definition \ref{def: Steenrod-Adem on Barratt-Eccles} is a chain map for every $r \geq 0$.
-We simplify notation and write $\psi$ instead of $\psi_{\mathcal E}(r)$.
-To show $\psi$ is a chain map we proceed by induction.
-Notice that
-\begin{equation*}
-\psi(\partial e_0) = 0 = \partial \psi(e_0)
-\end{equation*}
-and assume $\psi(\partial e_{k-1}) = \partial \psi(e_{k-1})$. If $k = 2n$ we have
-\begin{align*}
-\partial \psi(e_{2n}) & = 
-\partial \sum_{r_1, \dots, r_n} 
-\big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
-\partial \sum_{r_2, \dots, r_n} \sum_{r_1 = 0}^{p-1}
-\big(\rho^0, \rho^{r_1} \, (\rho^0, \rho^{1}, \dots, \rho^{r_n-r_1}, \rho^{r_n - r_1 +1}) \big) \\ & =
-\partial \sum_{r_2, \dots, r_n}
-\big(\rho^0, N\, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1}) \big) \\ & =
-\sum_{r_2, \dots, r_n}
-N\, \big( \rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1} \big) \\ & -
-\sum_{r_2, \dots, r_n}
-\big(\rho^0, \partial \, N \, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n+1}) \big) \\ & =
-N \psi(e_{2n-1}) - (\rho^0, \partial N \psi (e_{2n-1})) \\ & =
-\psi(N e_{2n-1}) - (\rho^0, \psi (\partial N e_{2n-1})) \\ & =
-\psi(\partial e_{2n}) - (\rho^0, \psi (\partial^2 e_{2n})) \\ & =
-\psi(\partial e_{2n}).
-\end{align*}
-If $k = 2n+1$ we have
-\begin{align*}
-\partial \psi(e_{2n+1}) & = 
-\partial \sum_{r_1, \dots, r_n} 
-\big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
-\partial \sum_{r_1, \dots, r_n}
-\big(\rho^0, \rho^{1} \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-\partial \sum_{r_1, \dots, r_n}
-\big(\rho^0, T\, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-\sum_{r_1, \dots, r_n}
-T \, \big( \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n} \big) \\ & -
-\sum_{r_1, \dots, r_n}
-\big(\rho^0, \partial \, T \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-T \psi(e_{2n}) - (\rho^0, \partial T \psi (e_{2n})) \\ & =
-\psi(T e_{2n}) - (\rho^0, \psi (\partial T e_{2n})) \\ & =
-\psi(\partial e_{2n+1}) - (\rho^0, \psi (\partial^2 e_{2n+1})) \\ & =
-\psi(\partial e_{2n+1})
-\end{align*}
-where for the third equality we used that for any $r_1, \dots, r_n$
-\begin{equation*}
-(\rho^0, \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) = 0.
-\end{equation*}
-This map is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0)$ represents a generator of the homology.
-
-\subsection{Theorem \ref{thm: Steenrod-Adem on surjection MS convention}}
-
-\begin{proof}
-	We prove that the $\Z[\mathrm{C}_r]$-linear map
-	\begin{equation*}
-	\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)
-	\end{equation*}
-	introduced in Definition \ref{def: Steenrod-Adem on surjection} is a chain map for every $r \geq 0$.
-We simplify notation and write $\psi$ instead of $\psi_{\mathcal X}(r)$.
-To show $\psi$ is a chain map we proceed by induction.
-Notice that
-	\begin{equation*}
-	\psi(\partial e_0) = 0 = \partial \psi(e_0)
-	\end{equation*}
-	and assume $\psi(\partial e_{n-1}) = \partial \psi(e_{n-1})$. For $n = 2m+1$ we have
-	\begin{align*}
-	\partial \psi(e_{2m+1}) 
-	& =
-	\partial\, h\, T\, \psi(e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - i^{r-1} p^{r-1}\, \psi(e_{2m}) -
-	h\, \partial\, T\, \psi(e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - 
-	h\, T\, \psi(\partial\, e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - 
-	h\, \psi(T\,N\, e_{2m-1}) \big) \\
-	& = 
-	T \psi(e_{2m}).
-	\end{align*}
-	For $n = 2m$ the proof is analogous. The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ is a generator of the homology.
-\end{proof}
-
-\subsection{Theorem \ref{thm: cubical chain bialgebra}}
-
-The only non-trivial relation we need to verify is
-\begin{equation*}
-\partial \product = \, \boundary \, .
-\end{equation*}
-Let us consider two basis elements of $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$
-\begin{align*}
-x & = x_1 \otimes \cdots \otimes x_n, \\
-y & = y_1 \otimes \cdots \otimes y_n.
-\end{align*}
-We need to show that
-\begin{equation*}
-\partial (x \ast y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y = \epsilon(x) y - \epsilon(y) x.
-\end{equation*}
-We have
-\begin{equation*}
-x \ast y = \sum (-1)^{|x|} \epsilon(y_{<i})x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i})y_{>i}
-\end{equation*}
-and
-\begin{align*}
-\partial(x \ast y) & = 
-\sum (-1)^{|x|} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes \partial (x_i \ast y_i) \otimes \epsilon(x_{>i}) y_{>i} \\ & -
-\sum (-1)^{|x|+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{align*}
-Since
-\begin{equation*}
-|x| = |x_{<i}| + |x_i| + |x_{>i}|, \quad \epsilon(x_{>i}) \neq 0 \Leftrightarrow |x_{>i}| = 0, \quad \partial(x_i \ast y_i) \neq 0 \Rightarrow |x_i| = 0,
-\end{equation*}
-we have
-\begin{equation} \label{eq: boundary of product 1}
-\begin{split}
-\partial(x \ast y) & = 
-\sum (-1)^{|x|} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes \partial (x_i \ast y_i) \otimes \epsilon(x_{>i}) y_{>i} \\ & -
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{split}
-\end{equation}
-We also have
-\begin{align*}
-\partial x \ast y & = 
-\sum (-1)^{|x|-1} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|-1+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes \partial x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|-1+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(\partial x_{>i}) y_{>i}.
-\end{align*}
-Since
-\begin{equation*}
-\epsilon(\partial x_{>i}) = 0, \quad \partial x_i \neq 0 \Leftrightarrow |x_i| = 1,
-\end{equation*}
-we have
-\begin{equation} \label{eq: boundary of product 2}
-\begin{split}
-\partial x \ast y & = 
-\sum (-1)^{|x|-1} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes \partial x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i}.
-\end{split}
-\end{equation}
-We also have
-\begin{align*}
-(-1)^{|x|} x \ast \partial y & = 
-\sum \epsilon(\partial y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|y_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast \partial y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|y_{<i}|+|y_i|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i},
-\end{align*}
-which is equivalent to
-\begin{equation} \label{eq: boundary of product 3}
-\begin{split}
-(-1)^{|x|} x \ast \partial y & = 
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast \partial y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{split}
-\end{equation}
-Putting identities \eqref{eq: boundary of product 1}, \eqref{eq: boundary of product 2} and \eqref{eq: boundary of product 3} together, we get
-\begin{multline*}
-\partial (x \otimes y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y =
-\sum \epsilon(y_{<i}) x_{<i} \otimes \big(\partial(x_i \ast y_i) + \partial x_i \ast y_i + x_i \ast \partial y_i\big) \otimes \epsilon(x_{>i}) y_{>i}.
-\end{multline*}
-Since
-\begin{equation*}
-\partial(x_i \ast y_i) + \partial x_i \ast y_i + x_i \ast \partial y_i = \epsilon(x_i)y_i - \epsilon(y_i)x_i,
-\end{equation*}
-we have
-\begin{align*}
-\partial (x \ast y) + \partial x \ast y + & (-1)^{|x|}x \ast \partial y \\ = &
-\sum \epsilon(y_{<i}) x_{<i} \otimes \epsilon(x_{\geq i}) y_{\geq i} - \epsilon(y_{\leq i}) x_{\leq i} \otimes \epsilon(x_{>i}) y_{>i} \\ = &
-\epsilon(x)y - \epsilon(y)x,
-\end{align*}
-as desired, where the last equality follows from a telescopic sum argument.
-
-\bibliographystyle{alpha} 
-\bibliography{bib}
-
-\end{document}

### 2021-05-07 introduction.tex
Split sections into files

--- 2021-01-16 main.tex
@@
-\documentclass[A4]{amsart}
-
-\usepackage{amsmath, amssymb, amsfonts}
-\usepackage{tikz-cd}
-\usepackage{graphics}
-\usepackage[bookmarks=true, linktocpage=true,
-bookmarksnumbered=true, breaklinks=true,
-pdfstartview=FitH, hyperfigures=false,
-plainpages=false, naturalnames=true,
-colorlinks=true, pagebackref=true,
-pdfpagelabels]{hyperref}
-\hypersetup{
-	colorlinks,
-	citecolor=blue,
-	filecolor=blue,
-	linkcolor=blue,
-	urlcolor=blue
-}
-\usepackage[alphabetic]{amsrefs}
-
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\Hom}{\mathrm{Hom}}
-\newcommand{\End}{\mathrm{End}}
-\DeclareMathOperator*{\colim}{colim}
-
-\include{figures}
-
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.6in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
-\calclayout
-
-\begin{document}
-
-\title{Chain level Steenrod operations}
-
-\author[R. Kaufmann]{Ralph M.\ Kaufmann}
-\address{Department of Mathematics, Department of Physics and Astronomy, Purdue University}
-\email{rkaufman@purdue.edu}
-
-\author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
-\address{Laboratory for Topology and Neuroscience, École Polytechnique Fédérale de Lausanne, Switzerland}
-\address{Department of Mathematics, University of Notre Dame du Lac, Notre Dame, IN, USA}
-\email{amedinam@nd.edu}
-\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Max Plank Institute for Mathematics.}
-
-\subjclass[2010]{55S05, 55U05, 55S10, 55S12; 55-04, 55U15, 55S15}
-\keywords{Steenrod operations, Dyer-Lashof operations, simplicial cochains, cubical cochains}
-
-\begin{abstract}
-	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander-Whitney's chain approximation to the diagonal.
-Later, following a viewpoint developed by Adem, Steenrod defined his homonymous operations for all primes using the homology of symmetric groups.
-This approach enhanced the conceptual understanding of the operations and allowed for many advances but lacked the concreteness of their definition at~$2$.
-In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having a definition of Steenrod operations that can be effectively computed in specific examples has become a key issue.
-This article provides such definition, at all primes, for well known $E_\infty$-algebras including the cochains of spaces expressed via simplicial or cubical cell structures.
-\end{abstract}
-
-\maketitle
-
-\tableofcontents
-
 \section{Introduction}
@@
 The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Greg Brumfiel, Dev Sinha, Jens Kjaer, Calista Bernard, and Andy Putnam, for insightful discussions and valuable comments, and to the anonymous referee for many helpful suggestions.
-
-\section{Preliminaries}
-
-\subsection{Chain complexes}
-\label{ssec: chain cpx}
-
-Let $R$ be a ring.
-We denote by $(\mathbf{Ch}_R, \otimes, R)$ the symmetric monoidal category of homologically graded chain complexes of $R$-modules.
-The set of $R$-linear maps between chain complexes as well as the tensor product of chain complexes are regarded as chain complexes in the usual way:
-\begin{equation*}
-\Hom(A, A^\prime)_n = \big\{f \ |\ a \in A_m \Rightarrow f(a) \in A^\prime_{m+n} \big\}, \qquad
-\partial f = \partial \circ f - (-1)^{|f|}f \circ \partial,
-\end{equation*}
-\begin{equation*}
-(A \otimes A^\prime)_n = \bigoplus_{p + q = n} A_p \otimes A^\prime_q, \qquad \partial (a \otimes a^\prime) = \partial a \otimes a^\prime + (-1)^{|a|} a \otimes \partial a^\prime.
-\end{equation*}
-We embed the category of $R$-modules as the full subcategory of $\mathbf{Ch}_R$ with objects concentrated in degree $0$.
-The endofunctor $\Hom(-, R)$ is referred to as the \textit{linear duality functor}.
-We notice that if a chain complex is concentrated in non-negative degrees then its linear dual is on non-positive ones.
-
-The rings we will mostly be interested in are the group rings $\Z[\mathrm G]$ and $\mathbb{F}_p[\mathrm G]$ of finite groups, where $p$ is prime and $\mathbb{F}_p$ is the field with $p$ elements.
-
-\subsection{Simplicial sets}
-
-The \textit{simplex category} $\triangle$ is defined to have an object $[n] = \{0, \dots, n\}$ for every $n \in \mathbb{N}$ and a morphism $[m] \to [n]$ for each order-preserving function from $[m]$ to $[n]$.
-The morphisms $\delta_i : [n-1] \to [n]$ and $\sigma_i : [n+1] \to [n]$ defined for $0 \leq i \leq n$ by
-\begin{equation*}
-\delta_i(k) = 
-\begin{cases} k & k < i, \\ k+1 & i \leq k, \end{cases}
-\quad \text{ and } \quad
-\sigma_i(k) = 
-\begin{cases} k & k \leq i, \\ k-1 & i < k, \end{cases}
-\end{equation*} 
-generate all morphisms in the simplex category.
-
-A \textit{simplicial set} $X$ is a contravariant functor from the simplex category to the category of sets and a simplicial map is a natural transformation between two simplicial sets.
-As is customary we use the notation
-\begin{equation*}
-X\big( [n] \big) = X_n, \qquad X(\delta_i) = d_i, \qquad X(\sigma_i) = s_i,
-\end{equation*}
-and refer to elements in the image of any $s_i$ as \textit{degenerate}.
-
-For each $n \in \mathbb{N}$, the simplicial set $\triangle^n$ is defined by
-\begin{equation*}
-\triangle^n_k  = \Hom_{\triangle} \big( [k], [n] \big), \qquad 
-d_i(x) = x \circ \delta_i, \qquad 
-s_i(x) = x \circ \sigma_i,
-\end{equation*}
-and any simplicial set can be expressed as a colimit of these
-\begin{equation*}
-X = \colim_{\triangle^n \to X} \triangle^n.
-\end{equation*}
-We represent the non-degenerate elements of $\triangle^n_k$ as an increasing sequence $[v_0, \dots, v_k]$ of non-negative integers each less than or equal to $n$.
-
-The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: 
-\begin{equation*}
-N_\bullet(X; R)_n = \frac{R \{ X_n \}}{R \{ s(X_{n-1}) \}}
-\end{equation*}
-where $s(X_{n-1}) = \bigcup_{i=0}^{n-1} s_i(X_{n-1})$, and $\partial_n : N_*(X)_n \to N_*(X)_{n-1}$ is given by
-\begin{equation*}
-\partial_n = \sum_{i=0}^{n} (-1)^id_{i}.
-\end{equation*}
-The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.
-
-It is convenient to emphasize that
-\begin{equation*}
-N_\bullet(X; R) = \colim_{\triangle^n \to X} N_\bullet(\triangle^n; R).
-\end{equation*}
-
-\subsection{Cubical sets}
-
-The \textit{cube category} $\square$ is the free strict monoidal category with a \textit{bipointed object}
-\begin{equation*}
-\begin{tikzcd}
-1 \arrow[r, bend left, "\delta^0"] \arrow[r, bend right, "\delta^1"'] & 2 \arrow[r, "\sigma"] & 1
-\end{tikzcd}
-\end{equation*}
-such that $\sigma \circ \delta^0 = \sigma \circ \delta^1 = \mathrm{id}$.
-Explicitly, it contains an object $2^n$ for each non-negative integer $n$ and its morphisms are generated by the \textit{coface} and \textit{codegeneracy maps} defined by
-\begin{align*}
-\delta_i^\varepsilon & = \mathrm{id}_{2^{i-1}} \times \delta^\varepsilon \times \mathrm{id}_{2^{n-1-i}} \colon 2^{n-1} \to 2^n, \\
-\sigma_i & = \mathrm{id}_{2^{i-1}} \times \, \sigma \times \mathrm{id}_{2^{n-i}} \colon 2^{n} \to 2^{n-1}.
-\end{align*}
-
-A \textit{cubical set} $X$ is a contravariant functor from the cube category to the category of sets and a cubical map is a natural transformation between two cubical sets.
-As is customary, we use the notation
-\begin{equation*}
-X\big( 2^n \big) = X_n \qquad X(\delta^\varepsilon_i) = d^\varepsilon_i \qquad X(\sigma_i) = s_i,
-\end{equation*}
-and refer to elements in the image of any $s_i$ as \textit{degenerate}.
-
-For each $n \in \mathbb{N}$, the cubical set $\square^n$ is defined by
-\begin{equation*}
-\square^n_k  = \Hom_{\square} \big( 2^k, 2^n \big), \qquad 
-d^\varepsilon_i(x) = x \circ \delta^\varepsilon_i, \qquad 
-s_i(x) = x \circ \sigma_i,
-\end{equation*}
-notice that iteratively
-\begin{equation*}
-\square^n = \overbrace{\square^1 \times \cdots \times \square^1}^{n \text{ times }}.
-\end{equation*}
-We represent the non-degenerate elements of $\square^n$ as sequences $x_1 \cdots\, x_n$ with each $x_i \in \{[0], [1], [0,1]\}$. Any cubical set can be expressed as a colimit of these
-\begin{equation*}
-X = \colim_{\square^n \to X} \square^n.
-\end{equation*}
-
-The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: The chain complex $N_\bullet(\square^1)$ is simply the cellular chain complex of the interval,
-isomorphic to
-\begin{equation*}
-\begin{tikzcd} [column sep = small, row sep = 0.1pt]
-R\{[0], [1]\}  & \arrow[l] R\{[0,1]\} \\
-{[1] - [0]} & \arrow[l, |->] \left[0,1\right].
-\end{tikzcd}
-\end{equation*}
-Set
-\begin{equation} \label{eq: chains on I^n}
-N_\bullet(\square^n; R) = N_\bullet(\square^1; R)^{\otimes n}
-\end{equation}
-and define
-\begin{equation*}
-N_\bullet(X; R) = \colim_{\square^n \to X} N_\bullet(\square^n; R).
-\end{equation*}
-
-The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.
-
-\section{Group homology}
-\label{sec: goup homology}
-
-Fixing notation, let $\mathrm{S}_n$ be the symmetric group of $n$ elements and $\mathrm{C}_n$ be the cyclic group of order $n$ thought of as the subgroup of $\mathrm{S}_n$ generated by an element~$\rho$.
-We denote this inclusion by $\iota : \mathrm C_r \to \mathrm S_r$.
-
-A \textit{resolution} in $\mathbf{Ch}_R$ is a quasi-isomorphism $P \to M$ with each $P_n$ a free \mbox{$R$-module}.
-We will use the fact, explained in Section 6.5 of \cite{jacobson1989algebra}, that such resolutions exist for any chain complex $M$ concentrated in non-negatively degrees, in particular, for the monoidal unit $R$.
-
-Let $\mathrm G$ be a group and $M$ an $R[\mathrm G]$-module, we define the \textit{homology of $\mathrm G$ with coefficients in $M$}, denoted $H(\mathrm G; M)$, as the homology of any chain complex $P \otimes_{R[\mathrm G]} M$ with $P \to R$ a resolution.
-We will be particularly interested in the case when $M = \mathbb F_p(q)$ is the trivial or sign $\mathbb F_p[\mathrm{S}_n]$-module depending on the parity of~$q$.
-
-We now review the group homology of finite cyclic groups. For any ring $R$ the elements
-\begin{align} \label{eq: T and R definition}
-T &= \rho - 1, \\
-N &= 1 + \rho + \cdots + \rho^{n-1},
-\end{align}
-in $R[\mathrm{C}_n]$ generate the ideal of annihilators of each other.
-Therefore, the chain complex $\mathcal W(n)$ concentrated in non-negative degrees with $\mathcal W(n)_d$ the free $\Z[\mathrm{C}_n]$-module generated by one element $e_d$, and differential
-\begin{equation*}
-\partial(e_d) = \begin{cases}
-Te_{d-1} & d \text{ odd,} \\
-Ne_{d-1} & d \text{ even,}
-\end{cases}
-\end{equation*}
-defines a resolution $\mathcal W(n) \to R$ in $\mathbf{Ch}_{R[\mathrm{C}_n]}$. It follow from a straightforward computation that for any prime $p$ and integer $q$
-\begin{equation*}
-H_i(\mathrm{C}_n; \mathbb{F}_p(q)) = \mathbb{F}_p.
-\end{equation*}
-
-The homology of $\mathrm{S}_n$ is harder to compute.
-With untwisted coefficients, the method of computation followed by several authors was to prove the injectivity of this homology into that of the infinite symmetric group and take advantage of a natural Hopf algebra structure on it.
-A powerful result stemming from the deep connection of this question with infinite loop space theory, is the existence of a homology isomorphism of spaces
-\begin{equation*}
-\Z \times B\mathrm{S}_\infty \to Q(S^0) = \Omega^\infty \Sigma^\infty (S^0)
-\end{equation*}
-credited to Dyer-Lashof \cite{dyer62lashof}, Barratt-Priddy and Quillen \cite{barratt1972priddy}.
-
-In this work, we are interested in the mod-$p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite{adem2004milgram} Corollary VI.1.4, is detected by the inclusion $\iota : \mathrm{C}_p \to \mathrm{S}_p$ whose homological kernel is described next.
-
-\begin{lemma} \label{lem: Thom's theorem}
-	Let $p$ be an odd prime and $q$ an integer. Consider
-	\begin{equation*}
-	(\iota_\ast)_n : H_n(\mathrm{C}_p; \mathbb{F}_p(q)) \to H_n(\mathrm{S}_p; \mathbb{F}_p(q))
-	\end{equation*}
-	then
-	\begin{enumerate}
-		\item If $q$ is even, $(\iota_\ast)_n = 0$ unless $n = 2t(p-1)$ or $n = 2t(p-1) - 1$,
-		\item If $q$ is odd, $(\iota_\ast)_n = 0$ unless $n = (2t+1)(p-1)$ or $n = (2t+1)(p-1)-1$,
-	\end{enumerate}
-	for some integer $t$.
-\end{lemma}
-
-\begin{proof}
-	This is proven as Theorem 4.1 in \cite{steenrod53cyclic} where Thom is also credited with a different proof.
-\end{proof}
-
-In section 5 we will see how the cohomology of symmetric groups defines operations on algebras that are commutative up to coherent homotopies.
-Preparing for that, we first developed the language of $\Gamma$-modules and operads, where the integral structure defining Steenrod operations is clearly expressed.
-
-\section{$\Gamma$-modules, operads and PROPs}
-
-In this section we set up a framework in which the structure responsible for Steenrod operations becomes most transparent.
-Given our applications, we consider $\mathbf{Ch}_R$ as the base category, remarking that all definitions in this section apply to general closed symmetric monoidal categories.
-
-\subsection{$\Gamma$-modules}
-Recall that a group $\mathrm G$ can be thought of as a category with a single object and only invertible morphisms, and that a chain complex of left (resp.
-right) $R[\mathrm G]$-modules is the same as a covariant (resp.
-contravariant) functor from $\mathrm G$ to $\mathbf{Ch}_R$.
-Right actions are more commonly used in the literature of operads so we emphasize that perspective.
-Taking inverses allows for the switch between these two conventions.
-
-A \textit{groupoid} is a small category where all morphisms are invertible.
-\begin{definition}
-	A \textit{$\Gamma$-module} is a contravariant functor to $\mathbf{Ch}_R$ from a groupoid $\Gamma$ with objects the natural numbers and morphisms satisfying $\Gamma(r,s) = \emptyset$ for $r \neq s$.
-We denote the category of $\Gamma$-modules and natural transformations by $\mathbf{Ch}_R^\Gamma$.
-\end{definition}
-
-We are mostly interested in two examples of $\Gamma$-modules, those associated to the groupoids $\mathrm{S}$ and $\mathrm{C}$ defined by
-\begin{equation*}
-\mathrm{S}(r, r) = \mathrm{S}_r, \qquad
-\mathrm{C}(r,r) = \mathrm{C}_r,
-\end{equation*}
-for every $r \in \mathbb{N}$. The inclusion $\mathrm{C}_r \to \mathrm{S}_r$ induces a forgetful functor
-\begin{equation*}
-\begin{tikzcd} [column sep = small]
-\mathbf{Ch}_R^\mathrm{S}  \arrow[r] & \mathbf{Ch}_R^\mathrm{C}.
-\end{tikzcd}
-\end{equation*}
-
-Given an object $A$ in $\mathbf{Ch}_R$ there are two important $\Gamma$-modules associated to it; an $\mathrm{S}$-module known as \textit{endomorphism $\mathrm{S}$-module} $\End_A$, and an $\mathrm{S}^{op}$-module known as \textit{coendomorphism $\mathrm{S}$-module} $\End^A$.
-These are defined by
-\begin{align*}	
-\End_A(r) &= \Hom(A^{\otimes r},A), \\
-\End^A(r) &= \Hom(A,A^{\otimes r}),
-\end{align*}
-with respective right and left actions defined by permutation of tensor factors.
-
-Another groupoid of importance to us is $\mathrm{S} \times \mathrm{S}^{op}$.
-Contravariant functors from it to $\mathbf{Ch}_R$ are called \textit{$\mathrm{S}$-bimodules} and their functor category is denoted $\mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}}$.
-Notice that the inclusions
-define forgetful functors
-\begin{equation*}
-\begin{tikzcd}[column sep=small, row sep=tiny]
-& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"'] \arrow[dr, "U_2"] & \\
-\mathbf{Ch}_R^{\mathrm{S}} &  & \mathbf{Ch}_R^{\mathrm{S}^{op}},
-\end{tikzcd}
-\end{equation*}
-and that for any object $A$ in $\mathbf{Ch}_R$, the canonical \textit{endomorphism bimodule}
-\begin{equation*}
-\End_A^A(r, s) = \Hom(A^{\otimes r}, A^{\otimes s})
-\end{equation*}
-forgets to $\End_A$ and $\End^A$.
-
-Using the groupoid automorphism sending every morphisms to its inverse we can identify $\Gamma$- and $\Gamma^{op}$- modules.
-In particular, the statement claiming that the linear duality functor induces a morphism of $\mathrm{S}$-modules
-\begin{equation*}
-\End^A \to \End_{\Hom(A, R)}
-\end{equation*}
-for every object $A$ in $\mathbf{Ch}_R$ is well defined and easily verified using this identification.
-
-A \textit{resolution} in $\mathbf{Ch}_R^\Gamma$ is a morphism $\phi$ of $\Gamma$-modules such that $\phi(r)$ is a resolution in the category of chain complexes of $R[\Gamma_r]$-modules for each $r \in \mathbb{N}$.
-A $\Gamma$-module $\mathcal R$ is said to be $E_\infty$ if $\mathcal R(0) = R$ and there exists a resolution $\mathcal R \to \underline{R}$ where $\underline{R}$ is the object in $\mathbf{Ch}_R^\Gamma$ defined by $\underline{R}(r) = R$ and $\underline{R}(\gamma) = \mathrm{id}_R$ for every $r \in \mathbb{N}$ and $\gamma \in \Gamma_r$.
-
-\begin{definition} \label{def: minimal cyclic resolution}
-	The \textit{minimal} $E_\infty$-$\mathrm{C}$-\textit{module} $\mathcal W$ is the functor in $\mathbf{Ch}_R^\mathrm{C}$ assigning to $r$ the chain complex
-	\begin{equation*}
-	\begin{tikzcd} [column sep = .5cm]
-	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] \cdots
-	\end{tikzcd}
-	\end{equation*}
-	concentrated in non-negative degrees.
-\end{definition}
-
-\subsection{Operads and PROPs}
-
-Operads an PROPs are respectively $\mathrm{S}$-modules and \mbox{$\mathrm{S}$-bimodules} enriched with further compositional structure.
-These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a PROP.
-
-Succinctly, an operad $\mathcal O$ is an $\mathrm{S}$-module together with a collection of $R$-linear maps
-\begin{equation*}
-\mathcal O(r) \otimes \mathcal O(s) \to \mathcal O(r+s-1)
-\end{equation*}
-satisfying suitable associativity, equivariance and unitality conditions. A PROP $\mathcal P$ is an $\mathrm{S}$-bimodule together with two types of compositions; horizontal
-\begin{equation*}
-\mathcal P(r_1, s_1) \otimes \mathcal P(r_2, s_2) \to \mathcal P(r_1 + r_2, s_1 + s_2)
-\end{equation*}
-and vertical
-\begin{equation*}
-\mathcal P(r,s) \otimes \mathcal P(s, t) \to \mathcal P(r, t)
-\end{equation*}
-satisfying their own versions of associativity, equivariance and unitality. For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008operads}.
-
-We have already mentioned that for any chain complex $A$, the $\mathrm{S}$-module $\End_A$ is naturally an operad and the $\mathrm{S}$-bimodule $\End_A^A$ is naturally a PROP.
-We add that considering $\End^A$ as an $\mathrm{S}$-module, its compositional structure also defines an operad structure on it.
-
-We remark that the compositional structure of a PROP $\mathcal P$ restricts to operad structures on $U_1(\mathcal P)$ and $U_2(\mathcal P)$.
-
-The type of operads that we are most interested in are $E_\infty$-operads which, as we will discuss in the next section, are used to describe commutativity up to coherent homotopies.
-
-\begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}]
-	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a PROP $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
-\end{definition}
-
-\subsection{Algebras, coalgebra and bialgebras}
-
-A morphisms of operads or of PROPs is simply a morphisms of their underlying $\mathrm{S}$-modules or $\mathrm{S}$-bimodules preserving the respective compositional structures.
-
-Given a chain complex $A$, an operad $\mathcal O$ and a PROP $\mathcal P$.
-An $\mathcal O$-\textit{algebra} (resp.
-$\mathcal O$-\textit{coalgebra}) structure on $A$ is an operad morphism $\mathcal O \to \End_A$ (resp.
-$\mathcal O \to \End^A$), and a $\mathcal P$-\textit{bialgebra} structure on $A$ is a PROP morphism $\mathcal P \to \End_A^A$.
-
-We remark that the linear duality functor naturally transforms an $\mathcal O$-coalgebra structure on a chain complex into an $\mathcal O$-algebra structure on its dual.
-
-Algebras over $E_\infty$-operads are the central objects of study in this work.
-To develop intuition for them, let us consider a chain complex $A$ with an algebra structure over $\underline{R}$, thought of as an operad with all compositions corresponding to the identity map $R \to R$.
-The $\underline{R}$-algebra structure on $A$ is generated by a linear map $\mu \colon A \otimes A \to A$ which is (strictly) commutative and associative, and a linear map $\eta \colon R \to A$ that determines a (two-sided) unit for $\mu$.
-Since $E_\infty$-operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies.
-The two main examples to keep in mind are the cochains of spaces and the chains of infinite loops spaces.
-
-\section{Steenrod-Adem structures}
-
-We now introduce an operadic formulation of a structure giving rise to Steenrod operations at every prime.
-It is based on \cites{steenrod47products, steenrod53symmetric, steenrod53cyclic, may70generalapproach}, and takes a viewpoint that emphasizes the integral structure needed to define them and prove their relations at every prime.
-For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}.
-
-\begin{definition} \label{def: Steenrod-Adem structure}
-	A \textit{Steenrod-Adem structure} on an operad $\mathcal O$ is a 
-	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad
-	\begin{equation*}
-	\begin{tikzcd}[column sep = normal, row sep = small]
-	& \mathcal R \arrow[dr, "\phi", out=0] & \\
-	\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \mathcal O
-	\end{tikzcd}
-	\end{equation*}
-	such that $\iota$ is a quasi-isomorphism and $\phi$ a morphism of operads.
-\end{definition}
-
-\begin{remark} \label{rmk: Deligne conjecture}
-	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$.
-In this language, a choice of factorization for a Steenrod-Adem structure defines in particular a \textit{commutative multiplication}.
-\end{remark}
-
-\begin{definition}
-	Let $A$ be a chain complex.
-A Steenrod-Adem structure on $\mathrm{End}_A$ is referred to as one on $A$.
-Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod} $(r, i)$-\textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
-\end{definition}
-
-\begin{remark}
-	Restricting a Steenrod-Adem structure on a chain complex $A$ to a given arity $r$ corresponds to specifying a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$.
-This pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ introduced in \cite{may70generalapproach} Definition 2.1.
-Furthermore, the restriction to arity $r^2$ enhances this pair to an \textit{Adem object} as described in Definition 4.1 loc.
-cit.
-\end{remark}
-
-A Steenrod-Adem structure on a chain complex $A$ allows us to define operations on its $\mathbb{F}_p$-homology for every prime $p$.
-These operations are structurally different if $p$ is even or odd.
-Using the previous Remark, the definitions below recover Steenrod's original definition for the cohomology of spaces and that of Araki-Kudo-Dyer-Lashof operations for the homology of infinite loop spaces.
-
-For the rest of this section $A$ is a chain complex equipped with a Steenrod-Adem structure.
-
-\begin{definition}
-	For any prime $p$, the $\mathbb{F}_p$-linear map
-	\begin{equation*}
-	D^p_i : (A \otimes \mathbb{F}_p) \to (A \otimes \mathbb{F}_p)
-	\end{equation*}
-	is defined by sending $a$ to the Steenrod \mbox{$(p, i)$-product} of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
-\end{definition}
-
-We notice that if $a$ is of degree $q$ then $D^p_i(a)$ is of degree $q + (p-1)q + i$.
-
-\begin{definition}
-	For any integer $s$, the \textit{Steenrod operation}
-	\begin{equation*}
-	P_s : H_\bullet(A; \mathbb{F}_2) \to H_{\bullet + s}(A; \mathbb{F}_2)
-	\end{equation*}
-	is defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_2)$ of degree $q$ to the class represented by $D^2_{s-q}(a)$.
-\end{definition}
-
-Notice that the Steenrod squares are determined by the Steenrod $(2,i)$-products with $\mathbb{F}_2$-coefficients.
-These binary operations are known as cup-$i$ products.
-In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod $\big(p, k(p-1)-\varepsilon\big)$-products for $\varepsilon \in \{0,1\}$.
-We can explain the appearance of these specific Steenrod products as follows.
-The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even an $(2t+1)(p-1) - \varepsilon$ if $q$ is odd.
-According to Lemma \ref{lem: Thom's theorem}, these are the only homologically non-trivial cases.
-
-\begin{definition} \label{def: Steenrod operations at odd prime}
-	For any integer $s$, the \textit{Steenrod operations}
-	\begin{equation*}
-	P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1)}(A; \mathbb{F}_p)
-	\end{equation*}
-	and
-	\begin{equation*}
-	\beta P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1) - 1}(A; \mathbb{F}_p)
-	\end{equation*}
-	are defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_p)$ of degree $q$ to the classes represented respectively for $\varepsilon \in\{0,1\}$ by
-	\begin{equation*}
-	(-1)^s \nu(q) D^p_{(2s-q)(p-1)-\varepsilon}(a)
-	\end{equation*}
-	where $\nu(q) = (-1)^{q(q-1)m/2}(m!)^q$ and $m = (p-1)/2$.
-\end{definition}
-
-\begin{remark}
-	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq.
-6.1.
-in \cite{steenrod53cyclic}).
-The notation $\beta P_s$ is motivated by the relationship of this operator and the Bockstein of the reduction $\mathbb Z \to \mathbb Z/p\mathbb Z$.
-\end{remark}
-
-Steenrod operations satisfy the Cartan and Adem relations.
-Below we state the subset of these relations that is most commonly used and refer to Sections 2 and 4 of \cite{may70generalapproach} for a complete list and proofs.
-\begin{lemma}
-	Let $A$ be equipped with a Steenrod-Adem structure. If $[\alpha], [\beta] \in H(A;\mathbb{F}_p)$ then
-	\begin{equation*}
-	P_s\big([\alpha] [\beta]\big) = \sum_{i+j=s} P_i\big( [\alpha] \big) P_j\big( [\beta] \big),
-	\end{equation*}
-	and
-	\begin{itemize}
-		\item If $p = 2$ and $a > 2b$
-		\begin{equation*}
-		P_{a}P_{b} = \sum_i {2i-a \choose a-b-i-1} P_{a+b-i}P_i,
-		\end{equation*}
-		\item If $p > 2$ and $a > pb$
-		\begin{equation*}
-		P_{a}P_{b} = \sum_i (-1)^{a+i}{pi-a \choose a-(p-1)b-i-1} P_{a+b-i}P_i.
-		\end{equation*}
-	\end{itemize}		
-\end{lemma}
-
-\begin{proof}
-	These are proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
-\end{proof}
-
-For the even prime, proofs at the chain level of these formulae have been given in \cite{medina2020cartan,brumfiel2020cochain}.
-For a different operadic approach to Steenrod operations at the even prime please consult \cite{chataur2005adem-cartan}.
-
-For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$, which we use in subsections 6.4 and 6.5.
-
-\section{Effective constructions}
-\label{sec: effective constructions}
-
-In this section we construct explicit Steenrod-Adem structures on three well know combinatorial $E_\infty$-operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-PROP $\mathcal M$ \cite{medina2020prop1}.
-We also define natural and effective Steenrod-Adem structure on the normalized cochains of any simplicial or cubical set, by describing a $U(\mathcal M)$-algebra structures on it.
-
-Figure~\ref{fig: bigsummary} presents a diagrammatical representation of the constructions in this section.
-
-\begin{figure}
-	\begin{tikzcd}
-	& & & U(\mathcal M) \arrow[dddr, bend left=10, "\phi^\triangle"'] \arrow[dddrr, bend left=20, "\phi^\square"'] & & \\
-	& & \mathcal X \arrow[ru, "SL"] & & & \\
-	& \mathcal E \arrow[ur, "TR"] & & & & \\
-	\mathcal W \arrow[rrrr, "\psi^\triangle", bend right=10] \arrow[rrrrr, "\psi^\square", bend right=20] \arrow[ur, "\psi_{\mathcal E}"] \arrow[uurr, "\psi_{\mathcal X}"', bend right=35, pos=.6] \arrow[uuurrr, "\psi_{U(\mathcal M)}"', bend right=45, pos=0.6] & & & & \End_{N^\bullet(X)} & \End_{N^\bullet(X)}
-	\end{tikzcd}
-	\caption{Summary of effective constructions: Steenrod-Adem structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural Steenrod-Adem structures on the normalized chains of simplicial and cubical sets.
-We are abusing notation since the maps $TR$ and $SL$ required different sign conventions.}
-	\label{fig: bigsummary}
-\end{figure}
-
-\subsection{Barratt-Eccles operad} In this subsection we effectively describe a Steenrod-Adem structure on the Barratt-Eccles operad.
-
-We begin by reviewing the $\mathrm{S}$-module structure underlying the Barratt-Eccles operad and, since will not use it in this work, refer to \cite{berger04combinatorial} for a description of if composition structure.
-For a non-negative integer $r$ define the simplicial set $E(\mathrm S_r)$ by
-\begin{equation} \label{eq: milnor model of symmetric}
-\begin{split}
-E(\mathrm S_r)_n &= \{ (\sigma_0, \dots, \sigma_n)\ |\ \sigma_i \in \mathrm{S}_r\}, \\
-d_i(\sigma_0, \dots, \sigma_n) &= (\sigma_0, \dots, \widehat{\sigma}_i, \dots, \sigma_n), \\
-s_i(\sigma_0, \dots, \sigma_n) &= (\sigma_0, \dots, \sigma_i, \sigma_i, \dots, \sigma_n) \\
-\end{split}
-\end{equation}
-with a left $\mathrm S_r$-action given by
-\begin{equation*}
-\sigma (\sigma_0, \dots, \sigma_n) = (\sigma \sigma_0, \dots, \sigma \sigma_n).
-\end{equation*} 
-The chain complex resulting from applying the functor of normalized integral chains to it is denoted $\mathcal E(r)$, which corresponds to the arity $r$ part of the Barratt-Eccles operad.
-
-\begin{definition} \label{def: Steenrod-Adem on Barratt-Eccles}
-	For every $r \geq 0$, let $\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined on basis elements by 
-	\begin{equation*}
-	\psi_{\mathcal E}(r)(e_{n}) = \begin{cases}
-	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \rho^{r_2}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m, \\
-	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m+1,
-	\end{cases}
-	\end{equation*}
-	where the sum is over all $r_1, \dots, r_m \in \{0, \dots, r-1\}$.
-\end{definition}
-
-\begin{theorem} \label{thm: Steenrod-Adem on Barratt-Eccles}
-	The morphism of $\mathrm{C}$-modules
-	\begin{equation*}
-	\psi_{\mathcal E} \colon \mathcal W \to \mathcal E
-	\end{equation*}
-	defines a Steenrod-Adem structure on the Barratt-Eccles operad.
-\end{theorem}
-
-\begin{proof}
-	This theorem follows from a computation which we defer to the appendix.
-\end{proof}
-
-\begin{example}
-	Table \ref{fig: Barratt-Eccles Steenrod products} shows $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$.
-\end{example}
-
-\begin{table}[h]
-	\centering
-	\resizebox{0.8\columnwidth}{!}{%
-		\renewcommand{\arraystretch}{1.2}
-		\begin{tabular}{|c||c|c|c|}
-			\hline
-			$r$ & $n=2$ & $n=3$ & $n=4$ \\
-			\hline
-			2 & (0,1,0) & (0,1,0,1) & (0,1,0,1,0) \\
-			\hline
-			3 & (0,1,2) + (0,2,0) & (0,1,2,0) + (0,1,0,1) & \phantom{+} (0,1,2,0,1) + (0,1,2,1,2) \\
-			& & & + (0,2,0,1,2) + (0,2,0,2,0) \\
-			\hline
-			4 & (0,1,2) + (0,2,3) & (0,1,2,3) + (0,1,3,0) & \phantom{+} (0,1,2,3,0) + (0,1,2,0,1) \\
-			& + (0,3,0) & + (0,1,0,1) & 
-			+ (0,1,2,1,2) + (0,2,3,0,1) \\
-			& & & + (0,2,3,1,2) + (0,2,3,2,3) \\
-			& & & + (0,3,0,1,2) + (0,3,0,2,3) \\
-			& & & + (0,3,0,3,0) \\
-			\hline  
-		\end{tabular}
-	}
-	\vspace*{3pt}
-	\caption{The elements $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$ where we are denoting $(\rho^{r_0}, \dots, \rho^{r_n})$ simply by $(r_0, \dots, r_n)$.}
-	\label{fig: Barratt-Eccles Steenrod products}
-\end{table}
-
-\begin{remark}
-	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota : \mathrm C_r \to \mathrm S_r$ induces a simplicial map $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ which extends to a quasi-isomorphism of $\mathrm C$-modules
-	\begin{equation*}
-	N_\bullet E(\iota) : N_\bullet E(\mathrm C) \to N_\bullet E(\mathrm S) = \mathcal E,
-	\end{equation*}
-	factoring
-	\begin{equation*}
-	\psi_{\mathcal E} :
-	\begin{tikzcd}
-	\mathcal W \arrow[r, "\phi_{\mathrm C}"] &[-3pt] N_\bullet E(\mathrm C) \arrow[r, "N_\bullet E(\iota)"] &[5pt] \mathcal E.
-	\end{tikzcd}
-	\end{equation*}
-\end{remark}
-
-\subsection{Surjection operad}
-
-In this subsection we introduce a Steenrod-Adem structures on the surjection operad.
-There are two widely used sign conventions for this operad respectively due to McClure-Smith \cite{mcclure03cochain} and Berger-Fresse \cite{berger04combinatorial}.
-Using the Berger-Fresse convention, we can define a Steenrod-Adem structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}.
-We define an Steenrod-Adem structure on the surjection operad in a convention independent way which recovers the table reduction Steenrod-Adem structure in the Berger-Fresse case.
-
-Let us start by recalling the definition of the surjection operad.
-For a non-negative integer $r$ let $\mathcal X(r)_n$ be the free abelian group generated by all functions from $\{1, \dots, n+r\}$ to $\{1, \dots, r\}$ modulo the subgroup generated by degenerate functions, i.e., those which are either non-surjective or have a pair of equal consecutive values.
-We only describe the McClure-Smith convention since we refer to it in subsequent sections.
-The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s : \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top dimensional generator in the chain complex
-\begin{equation} \label{eq: surjection boundary}
-\bigotimes_{i = 1}^r N_\bullet \big( \triangle^{s^{-1}(i)}; \Z \big).
-\end{equation}
-Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at the time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on.
-Since we do not use the composition structure we refer to \cite{mcclure03cochain} for it.
-
-Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure-Smith to prove $\mathcal X$ is an $E_\infty$-operad and whose introduction is credited to Benson \cite{benson1998rep}.
-Let the maps $i,\ p$ and $s$ be defined on basis elements, represented by sequences, as follows: $i : \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p : \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s : \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
-with a 1, then the new sequence is degenerate so $s$ takes it to $0$. These maps satisfy
-\begin{equation*}
-p  i = \mathrm{id}
-\qquad \text{ and } \qquad
-\mathrm{id} - i  p = \partial s + s \partial.
-\end{equation*}
-These maps define a contraction of $\mathcal X(r)$ onto $\mathcal X(1) \cong \Z$ with homotopy $h = s + i\, s\, p + \cdots + i^{r-1} s\, p^{r-1}$, satisfying
-\begin{equation*}
-\partial h + h \partial = \mathrm{id} - i^{r-1}\,p^{r-1}.
-\end{equation*}
-
-\begin{definition} \label{def: Steenrod-Adem on surjection}
-	For every $r \geq 0$, let $\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined recursively on basis elements by
-	\begin{align*}
-	\psi_{\mathcal X}(r)(e_0) & = (1, \dots, r), \\
-	\psi_{\mathcal X}(r)(e_{2m+1}) & = h\,T\,\psi_{\mathcal X}(r)(e_{2m}), \\
-	\psi_{\mathcal X}(r)(e_{2m}) & = h\,N\,\psi_{\mathcal X}(r)(e_{2m-1}),
-	\end{align*}
-	where $T$ and $R$ are defined in \eqref{eq: T and R definition}.
-\end{definition}
-
-\begin{theorem} \label{thm: Steenrod-Adem on surjection MS convention}
-	The morphism of $\mathrm{C}$-modules
-	\begin{equation*}
-	\psi_{\mathcal X} \colon \mathcal W \to \mathcal X
-	\end{equation*}
-	defines a Steenrod-Adem structure on the Surjection operad.
-\end{theorem}
-
-\begin{proof}
-	This theorem follows from a computation which we defer to the appendix.
-\end{proof}
-
-For the rest of the paper we use the McClure-Smith convention.
-
-\begin{example}
-	Table \ref{fig: surjection Steenrod products} shows $\psi_{\mathcal X}(r)(e_n)$ for small values of $r$ and $n$.
-\end{example}
-
-\begin{table}[h]
-	\centering
-	\resizebox{\columnwidth}{!}{%
-		\renewcommand{\arraystretch}{1.3}
-		\begin{tabular}{|c||c|c|c|}
-			\hline
-			$r$& $n=2$ & $n=3$ & $n=4$ \\
-			\hline
-			2 & (1,2,1,2) & (1,2,1,2,1) & (1,2,1,2,1,2) \\
-			\hline
-			3 & (1,2,3,1,2) + (1,3,1,2,3) & (1,2,3,1,2,3) + (1,2,1,2,3,1)  & \phantom{+} (1,2,3,1,2,3,1) + (1,2,3,2,3,1,2) \\
-			& + (1,2,3,2,3) & + (1,2,3,1,3,1) & + (1,2,3,1,2,1,2) + (1,3,1,2,3,1,2) \\
-			& & & + (1,3,1,3,1,2,3) + (1,2,3,2,3,2,3) \\
-			& & & + (1,3,1,2,3,2,3) \\
-			\hline
-			4 & \phantom{+} (1,2,3,4,1,2) + (1,3,4,1,2,3) & \phantom{+} (1,2,3,4,1,2,3) + (1,2,4,1,2,3,4) & \\
-			& + (1,2,3,4,2,3) + (1,4,1,2,3,4) & + (1,2,3,4,1,3,4) + (1,2,1,2,3,4,1) & 25 \text{ terms } \\
-			& + (1,2,4,2,3,4) + (1,2,3,4,3,4) & + (1,2,3,1,3,4,1) + (1,2,3,4,1,4,1) & \\
-			\hline  
-		\end{tabular}
-	}
-	\vspace*{2pt}
-	\caption{The values of $\psi_{\mathcal X}(r)(e_n)$ for small values of $r$ and $n$.}
-	\label{fig: surjection Steenrod products}
-\end{table}
-
-\subsection{The finitely presented $E_\infty$-PROP $\mathcal M$}
-
-We start by reviewing the finitely presented $E_\infty$-PROP introduced in \cite{medina2020prop1}. Let $\mathcal M$ be the PROP generated by 
-\begin{equation*}
-\counit \in \mathcal M(1,0)_0, \hspace*{.6cm} \coproduct \in \mathcal M(1,2)_0, \hspace*{.6cm} \product \in \mathcal M(2,1)_1,
-\end{equation*}
-with boundary
-\begin{equation*}
-\partial\ \counit = 0, \hspace*{.6cm} \partial \ \coproduct = 0, \hspace*{.6cm} \partial \ \product = \ \boundary \, ,
-\end{equation*}
-and restricted by the relations
-\begin{equation*}
-\productcounit, \hspace*{.6cm} \leftcounitality \, , \hspace*{.6cm} \rightcounitality \, .
-\end{equation*}
-
-Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$-prop in the terminology of Bordmann-Vogt \cite{boardman1973homotopy}.
-More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$-operad.
-For the remainder of this article we write $U(\mathcal M)$ instead of $U_2(\mathcal M)$.
-
-We will define a Steenrod-Adem structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the Steenrod-Adem structure $\psi_{\mathcal X} : \mathcal W \to \mathcal X$ with a morphism of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact)
-\begin{equation*}
-SL \colon \mathcal X \to U(\mathcal M)
-\end{equation*}
-that we now define. Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element
-\begin{center}
-	\begin{tikzpicture}[scale=.85]
-	\draw (0,0)--(0,-.6) node[below]{$\scriptstyle 1$};
-	\draw (0,0)--(.5,.5);
-	\draw (-.3, .3)-- (-.2,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_1$};
-	\draw (-.5,.5)--(0,0);
-	\node at (.11,.4){$...$};
-
-	\node at (1,0){$\scriptstyle \cdots$};
-	\node at (1,-.9){$\scriptstyle \cdots$};
-
-	\draw (2,0)--(2,-.68) node[below]{$\scriptstyle r$};
-	\draw (2,0)--(2.5,.5);
-	\draw (1.7, .3)-- (1.8,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_r$};
-	\draw (1.5,.5)--(2,0);
-	\node at (2.11,.4){$...$};
-
-	\draw (1,2.5)--(1,3) node[above]{$\scriptstyle 1$};
-	\draw (1,2.5)--(0,2) node[below]{$\scriptstyle 1$};
-	\draw (.25,2.125)--(.5,2) node[below]{$\scriptstyle 2$};
-	\draw (.5,2.25)--(1,2) node[below]{$\scriptstyle 3$};
-	\draw (1,2.5)--(2,2) node[below]{\quad $\scriptstyle n + r$};
-	\node at (1.5,1.75){$...$};
-
-	\node at (1,1.3) {$\vdots$};
-
-	\node at (2.85,0){};
-	\end{tikzpicture}
-\end{center}
-that has no internal vertices and such that the $n+r$ strands at the top are orderly connected to the strands at the bottom following the values of $s$.
-
-It can be directly verified using the presentation of $\mathcal M$ that the boundary of $SL(s)$ is obtained by removing strands one at the time in the order they are attached at the bottom.
-This is precisely the image of $SL(\partial s)$ according to \eqref{eq: surjection boundary}.
-Furthermore, relabeling the bottom edges agrees with the permutation of preimages of the associated surjection.
-Since both operads have the homology of a point and $(1, \dots, r)$ is sent to a representative of a homology generator we have proven the following
-
-\begin{theorem} \label{thm: Steenrod-Adem on U(M)}
-	The composition $\psi_{U(\mathcal M)}$
-	\begin{equation*}
-	\begin{tikzcd}[column sep = normal]
-	\mathcal W \arrow[r, "\psi_{\mathcal X}"] & \mathcal X \arrow[r, "SL"] & U(\mathcal M)
-	\end{tikzcd}
-	\end{equation*}
-	defines a Steenrod-Adem structure on $U(\mathcal M)$.
-\end{theorem}
-
-\begin{example}
-	Figure \ref{fig: cup 0,1,2} shows $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$.
-\end{example}
-
-\begin{figure}[h]
-	\centering
-	\boxed{
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-		\draw (1,3) to [out=-25, in=90] (2,0);
-
-		\node at (1,-.5){$n=0$};
-		\end{tikzpicture}\hspace*{1cm}
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-
-		\draw [shorten >= 0cm] (.6,2.73) to [out=-100, in=90] (2,0);
-		%\draw [shorten <= 0cm] (1,1.5) to [out=-60, in=90] (2,0);
-
-		\draw [shorten >= .15cm] (1,3) to [out=-25, in=30, distance=1.1cm] (1,1.5);
-		\draw [shorten <= .1cm] (1,1.5) to [out=210, in=20] (0,1);
-
-		\node at (1,-.5){$n=1$};
-		\end{tikzpicture}\hspace*{1cm}
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-		\draw (1,3) to [out=-25, in=90] (2,0);
-
-		\draw [shorten >= 0cm] (.6,2.73) to [out=210, in=135] (1,1.5);
-		\draw [shorten <= 0cm] (1,1.5) to [out=-45, in=170] (2,1);
-
-		\draw [shorten >= .1cm] (1.4,2.73) to [out=-30, in=45] (1,1.5);
-		\draw [shorten <= .1cm] (1,1.5) to [out=-135, in=10] (0,1);
-
-		\node at (1,-.5){$n=2$};
-		\end{tikzpicture}
-	}
-	\caption{The values of $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$.}
-	\label{fig: cup 0,1,2}
-\end{figure}
-
-\subsection{Cochains of simplicial sets}
-
-In this subsection we introduce a natural Steenrod-Adem structure on the normalized cochains of any simplicial set $X$.
-Since a Steenrod-Adem structure was constructed in the previous section for $U(\mathcal M)$, we only need to describe a natural $U(\mathcal M)$-algebra structure on $N^\bullet(X)$.
-Using the linear duality functor, it suffices to construct a natural $U(\mathcal M)$-coalgebra structure on $N_\bullet(X)$ which, in turn, can be derived via a Kan extension argument from one on each $N_\bullet(\triangle^n)$.
-We obtain these coalgebra structures by restricting a full $\mathcal M$-bialgebra structure.
-An $\mathcal M$-bialgebra structure is specified by three linear maps, the images of the generators
-\begin{equation*}
-\counit, \quad \coproduct, \quad \product,
-\end{equation*}
-satisfying the relations in the presentation of $\mathcal M$. For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
-(1) The counit $\epsilon \in \Hom(N_\bullet(\triangle^n), \Z)$ by
-\begin{equation*}
-\epsilon \big( [v_0, \dots, v_q] \big) = \begin{cases} 1 & \text{ if } q = 0, \\ 0 & \text{ if } q>0. \end{cases}
-\end{equation*}
-(2) The coproduct $\Delta \in \Hom(N_\bullet(\triangle^n), N_\bullet(\triangle^n)^{\otimes2})$ by
-\begin{equation*}
-\Delta \big( [v_0, \dots, v_q] \big) = \sum_{i=0}^q [v_0, \dots, v_i] \otimes [v_i, \dots, v_q].
-\end{equation*}
-(3) The product $\ast \in \Hom(N_\bullet(\triangle^n)^{\otimes 2}, N_\bullet(\triangle^n))$ by
-\begin{equation*}
-\left[v_0, \dots, v_p \right] \ast \left[v_{p+1}, \dots, v_q\right] = \begin{cases} (-1)^{p+|\pi|} \left[v_{\pi(0)}, \dots, v_{\pi(q)}\right] & \text{ if } v_i \neq v_j \text{ for } i \neq j, \\
-0 & \text{ if not}, \end{cases}
-\end{equation*}
-where $\pi$ is the permutation that orders the totally ordered set of vertices, and $(-1)^{|\pi|}$ its sign.
-
-\begin{theorem} \label{thm: simplicial chain bialgebra}
-	For every $n \in \mathbb{N}$, the assignment
-	\begin{equation*}
-	\counit \mapsto \epsilon, \quad \coproduct \mapsto \Delta, \quad \product \mapsto \ast,
-	\end{equation*}
-	defines a natural $\mathcal M$-bialgebra structure  on $N_\bullet(\triangle^n)$.
-\end{theorem}
-
-\begin{proof}
-	This statement is proven as Theorem 4.2 in \cite{medina2020prop1}.
-\end{proof}
-
-\begin{definition}
-	Let $X$ be a simplicial set.
-Denote by $\phi^\triangle : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem \ref{thm: simplicial chain bialgebra}.
-\end{definition}
-
-\begin{theorem}
-	The commutative diagram
-	\begin{equation*}
-	\begin{tikzcd}[column sep = small, row sep = small]
-	&[18pt] U(\mathcal M) \arrow[dr, "\phi^\triangle", out=0] &[-0pt] \\
-	\mathcal W \arrow[ur, "\psi_{U(\mathcal M)}", in=180] \arrow[rr, "\psi^\triangle"] & & \mathrm{End}_{N^\bullet (X)}
-	\end{tikzcd}
-	\end{equation*}
-	defines a natural Steenrod-Adem structure on $N^\bullet(X)$ for any simplicial set $X$.
-\end{theorem}
-
-\begin{remark}
-	The $E_\infty$-structure we described in Theorem \ref{thm: simplicial chain bialgebra}, depending solely on three fundamental maps, recovers the coalgebra structures of McClure-Smith \cite{mcclure03cochain} and, up to signs, that of Berger-Fresse \cite{berger04combinatorial}.
-\end{remark}
-
-\begin{example}
-	Let us consider the prime $2$. The value $P^1(x)\big([0,1,2,3,4]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^4)$ is equal to the value of $x^{\otimes 2}$ acting on
-	\begin{align*}
-	[0, 1, 2, 3] \otimes [0, 1, 3, 4] \ +\  & 
-	[0, 2, 3, 4] \otimes [0, 1, 2, 4] \\ \ +\ 
-	[0, 1, 2, 3] \otimes [1, 2, 3, 4] \ +\ &
-	[0, 1, 3, 4] \otimes [1, 2, 3, 4].
-	\end{align*}
-	Similarly, the value of $P^2(y)\big([0,1,2,3,4,5,6,7]\big)$ for a homogeneous cocycle $y$ in $N^{-5}(\triangle^7)$ is equal to the value of $y^{\otimes 2}$ acting on
-	\begin{align*}
-	[0, 1, 2, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] & \ +\
-	[0, 1, 2, 3, 6, 7] \otimes [0, 1, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 2, 3, 4, 7] \otimes [0, 1, 4, 5, 6, 7] & \ +\ 
-	[0, 2, 3, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] \\ \ +\ 
-	[0, 2, 3, 4, 6, 7] \otimes [0, 1, 2, 4, 5, 6] & \ +\ 
-	[0, 2, 3, 4, 5, 7] \otimes [0, 1, 2, 5, 6, 7] \\ \ +\ 
-	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] & \ +\ 
-	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 5, 6] \\ \ +\ 
-	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 6, 7] & \ +\ 
-	[0, 1, 2, 3, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 2, 3, 4, 7] \otimes [1, 2, 4, 5, 6, 7] & \ +\ 
-	[0, 1, 3, 4, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 3, 4, 5, 7] \otimes [1, 2, 3, 5, 6, 7] & \ +\ 
-	[0, 1, 4, 5, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 4, 5, 6, 7] \otimes [1, 2, 3, 4, 6, 7] & \ +\ 
-	[0, 1, 2, 3, 4, 7] \otimes [2, 3, 4, 5, 6, 7] \\ \ +\ 
-	[0, 1, 2, 4, 5, 7] \otimes [2, 3, 4, 5, 6, 7] & \ +\ 
-	[0, 1, 2, 5, 6, 7] \otimes [2, 3, 4, 5, 6, 7].
-	\end{align*}
-\end{example}
-
-\begin{example}
-	Let us consider the prime $3$. The value $\beta P^1(x)\big([0,1,2,3,4,5,6,7,8]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^8)$ is equal to the value of $x^{\otimes 3}$ acting on
-	\begin{align*}
-	& \,-\, [0, 6, 7, 8] \otimes [0, 1, 2, 3] \otimes [3, 4, 5, 6] \,+\, [0, 1, 7, 8] \otimes [1, 2, 3, 4] \otimes [4, 5, 6, 7] \\ & \,-\, [0, 1, 2, 8] \otimes [2, 3, 4, 5] \otimes [5, 6, 7, 8].
-	\end{align*}
-	Similarly, the value of $P^1(y)\big([0,1,\dots,7]\big)$ for a homogeneous cocycle $y$ in $N^{-3}(\triangle^7)$ is equal to the value of $y^{\otimes 3}$ acting on
-	\begin{align*}
-	& \,-\, [0,3,4,5] \otimes [0,5,6,7] \otimes [0,1,2,3] \,-\, [0,4,5,6] \otimes [0,1,6,7] \otimes [1,2,3,4] \\ & \,-\, [0,5,6,7] \otimes [0,1,2,7] \otimes [2,3,4,5] \,-\, [0,1,4,5] \otimes [1,5,6,7] \otimes [1,2,3,4] \\ & \,+\, [0,1,5,6] \otimes [1,2,6,7] \otimes [2,3,4,5] \,-\, [0,1,6,7] \otimes [1,2,3,7] \otimes [3,4,5,6] \\ & \,-\, [0,1,2,5] \otimes [2,5,6,7] \otimes [2,3,4,5] \,-\, [0,1,2,6] \otimes [2,3,6,7] \otimes [3,4,5,6] \\ & \,-\, [0,1,2,7] \otimes [2,3,4,7] \otimes [4,5,6,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [0,1,6,7] \\ & \,+\, [0,2,3,4] \otimes [4,5,6,7] \otimes [0,1,2,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [1,2,6,7] \\ & \,-\, [0,1,3,4] \otimes [4,5,6,7] \otimes [1,2,3,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [2,3,6,7] \\ & \,+\, [0,1,2,4] \otimes [4,5,6,7] \otimes [2,3,4,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [3,4,6,7] \\ & \,-\, [0,1,2,3] \otimes [3,5,6,7] \otimes [3,4,5,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [4,5,6,7] \\ & \,+\, [0,1,2,3] \otimes [3,4,6,7] \otimes [4,5,6,7].
-	\end{align*}
-\end{example}
-
-\subsection{Cochains of cubical sets}
-
-In this subsection we introduce a natural Steenrod-Adem structure on the normalized cochains of any cubical set.
-It follows the structure of the previous subsection closely.
-By the same considerations, the desired construction will follow from a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$.
-These are determined by three linear maps satisfying the relations in the presentation of $\mathcal M$.
-For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
-(1) The counit $\epsilon \in \Hom(N_\bullet(\square^n), \Z)$ by
-\begin{equation*}
-\epsilon \left( x_1 \otimes \cdots \otimes x_d \right) = \epsilon(x_1) \cdots \, \epsilon(x_n),
-\end{equation*}
-where
-\begin{equation*}
-\epsilon([0]) = \epsilon([1]) = 1, \qquad \epsilon([0, 1]) = 0.
-\end{equation*} \vspace*{-6pt} \\
-(2) The coproduct $\Delta \in \Hom \left( N_\bullet(\square^n), N_\bullet(\square^n)^{\otimes 2} \right)$ by
-\begin{equation*}	
-\Delta (x_1 \otimes \cdots \otimes x_n) = 	
-\sum \pm \left( x_1^{(1)} \otimes \cdots \otimes x_n^{(1)} \right) \otimes 	
-\left( x_1^{(2)} \otimes \cdots \otimes x_n^{(2)} \right),	
-\end{equation*}	
-where the sign is determined using the Koszul convention, and we are using Sweedler's notation
-\begin{equation*}	
-\Delta(x_i) = \sum x_i^{(1)} \otimes x_i^{(2)}
-\end{equation*}
-for the chain map $\Delta \colon N_\bullet(\square^1) \to N_\bullet(\square^1)^{\otimes 2}$ defined by
-\begin{equation*}
-\Delta([0]) = [0] \otimes [0], \quad \Delta([1]) = [1] \otimes [1], \quad \Delta([0, 1]) = [0] \otimes [0, 1] + [0, 1] \otimes [1].
-\end{equation*}
-Using that $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$, $\Delta$ is the composition
-\begin{equation*}
-\begin{tikzcd}
-N_\bullet(\square^1)^{\otimes n} \arrow[r, "\Delta^{\otimes n}"] & \left( N_\bullet(\square^1)^{\otimes 2}  \right)^{\otimes n} \arrow[r, "sh"] & \left( N_\bullet(\square^1)^{\otimes n} \right)^{\otimes 2}
-\end{tikzcd}
-\end{equation*}
-where $sh$ is the shuffle map that places tensor factors in odd position first. \vspace*{5pt} \\
-(3) The product $\ast \in \Hom(N_\bullet(\square^n)^{\otimes 2}, N_\bullet(\square^n))$ by
-\begin{align*}
-(x_1 \otimes \cdots \otimes x_n) \ast (y_1 \otimes \cdots \otimes y_n) =
-(-1)^{|x|} \sum_{i=1}^n x_{<i} \epsilon(y_{<i}) \otimes x_i \ast y_i \otimes \epsilon(x_{>i})y_{>i},
-\end{align*}
-where
-\begin{align*}
-x_{<i} & = x_1 \otimes \cdots \otimes x_{i-1}, &
-y_{<i} & = y_1 \otimes \cdots \otimes y_{i-1}, \\
-x_{>i} & = x_{i+1} \otimes \cdots \otimes x_n, & 
-y_{>i} & = y_{i+1} \otimes \cdots \otimes y_n,
-\end{align*}
-with the convention
-\begin{equation*}
-x_{<1} = y_{<1} = x_{>n} = y_{>n} = 1 \in \Z,
-\end{equation*}
-and the only non-zero values of $x_i \ast y_i$ are
-\begin{equation*}
-\ast([0] \otimes [1]) = [0, 1], \qquad  \ast([1] \otimes [0]) = -[0, 1].
-\end{equation*}
-
-\begin{theorem} \label{thm: cubical chain bialgebra}
-	For every $n \in \mathbb{N}$, the assignment
-	\begin{equation*}
-	\counit \mapsto \epsilon, \quad \coproduct \mapsto \Delta, \quad \product \mapsto \ast,
-	\end{equation*}
-	defines a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$.
-\end{theorem}
-
-\begin{proof}
-	We present a proof of this statement in the appendix.
-\end{proof}
-
-\begin{remark}
-	We saw that for simplicial sets a natural algebraic $E_\infty$-structure was determined by basic maps in the standard simplices.
-For cubical sets, one such structure is constructed by naturally extending three maps defined just on the interval.
-\end{remark}
-
-\begin{definition}
-	Let $X$ be a cubical set.
-Denote by $\phi^\square : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem~\ref{thm: cubical chain bialgebra}.
-\end{definition}
-
-\begin{theorem}
-	The commutative diagram
-	\begin{equation*}
-	\begin{tikzcd}[column sep = small, row sep = small]
-	&[18pt] U(\mathcal M) \arrow[dr, "\phi^\square", out=0] &[-0pt] \\
-	\mathcal W \arrow[ur, "\psi_{U(\mathcal M)}", in=180] \arrow[rr, "\psi^\square"] & & \End_{N^\bullet (X)}
-	\end{tikzcd}
-	\end{equation*}
-	defines a natural Steenrod-Adem structure on $N^\bullet(X)$ for any cubical set $X$.
-\end{theorem}
-
-\begin{example}
-	Let us consider the prime $2$. The value $P^1(x)\big([01]^{4}\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\square^4)$ is equal to the value of $x^{\otimes 2}$ acting on
-	\begin{align*}&
-	[01]1[01][01] \otimes [01][01]0[01]\,+\,
-	[01][01][01]0 \otimes [01]0[01][01]\,+\, \\&
-	[01][01][01]0 \otimes 1[01][01][01]\,+\,
-	[01][01]1[01] \otimes [01]0[01][01]\,+\, \\&
-	[01][01]1[01] \otimes 1[01][01][01]\,+\,
-	[01][01][01]0 \otimes [01][01]1[01]\,+\, \\&
-	[01][01]0[01] \otimes [01][01][01]1\,+\,
-	[01]1[01][01] \otimes [01][01][01]1\,+\, \\&
-	0[01][01][01] \otimes [01][01][01]1\,+\,
-	0[01][01][01] \otimes [01][01]0[01]\,+\, \\&
-	0[01][01][01] \otimes [01]1[01][01]\,+\,
-	[01]0[01][01] \otimes 1[01][01][01].\,\phantom{+}\,
-	\end{align*}
-\end{example}
-
-\begin{example}
-	Let us consider the prime $3$. The value of $\beta P^0(x)\big([01]^2\big)$ for a homogeneous cocycle $x$ in $N^{-1}(\square^2)$ is equal to the value of $x^{\otimes 3}$ acting on
-	\begin{align*}
-	\,-\, [01]1 \otimes [01]0 \otimes 1[01] \,-\, 0[01] \otimes [01]0 \otimes 1[01] + [01]1 \otimes 0[01] \otimes [01]1 + 0[01] \otimes 0[01] \otimes [01]1.
-	\end{align*}
-\end{example}
-
-\section{Outlook}
-This article looked at Steenrod operations from an algebraic viewpoint, a subject with rich geometric and combinatorial components as well.
-For example, \cite{Postnikov} and \cite{medina2018prop2} independently introduced equivalent geometric representations of the cup-$i$ products in terms of stabilized arc surfaces \cite{KLP} and weighted ribbon graphs respectively.
-In fact, an entire $E_\infty$-operad (PROP) is constructed geometrically in this way.
-We can also interpret the Steenrod-Adem structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups ---a key ingredient in Definition \ref{def: minimal cyclic resolution}--- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.
-
-In Higher Category Theory, the paper \cite{medina2020globular} constructs a functor producing strict \mbox{$\infty$-cat}egories from group-like cup-$i$ coalgebras in a manner similar to \cite{steiner2004omega}.
-In particular, the cup-$i$ constructions described in this article for standard simplices and cubes define, respectively, the Street nerve and cubical nerve of strict $\infty$-categories.
-We anticipate that the more general Steenrod $(p,i)$-products constructed in this work will also have deep combinatorial interpretations.
-
-There is a functorial approach to the theory using the formalism of Feynman categories \cite{feynman},
-which renders all the structures and notions natural.
-This includes cyclic, planar cyclic as well as Berger's pre-operads \cite{BergerRecog}.
-Their interplay is of independent interest \cite{BergerKaufmann,feyrep} and will be linked directly to the constructions of this paper.
-
-In this article we have not focused on the operations that exist non-trivially for \mbox{$E_n$-algebras} with $n$ finite, see part III of \cite{may76homology}.
-A treatement close to ours for the $E_2$ case was given in \cite{Tourtchine}.
-Effective constructions for these Dyer-Lashof-Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang,sinha2013littledisks,berger04combinatorial,ayala2014configuration} and higher categories \cite{Bathigher,BalFiedSchwVogt,Rezkhigher}, and will appear elsewhere.
-
-\newpage
-\appendix
-\section{Proofs}
-
-\subsection{Theorem \ref{thm: Steenrod-Adem on Barratt-Eccles}}
-
-We prove that the $\Z[\mathrm{C}_r]$-linear map
-\begin{equation*}
-\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)
-\end{equation*}
-introduced in Definition \ref{def: Steenrod-Adem on Barratt-Eccles} is a chain map for every $r \geq 0$.
-We simplify notation and write $\psi$ instead of $\psi_{\mathcal E}(r)$.
-To show $\psi$ is a chain map we proceed by induction.
-Notice that
-\begin{equation*}
-\psi(\partial e_0) = 0 = \partial \psi(e_0)
-\end{equation*}
-and assume $\psi(\partial e_{k-1}) = \partial \psi(e_{k-1})$. If $k = 2n$ we have
-\begin{align*}
-\partial \psi(e_{2n}) & = 
-\partial \sum_{r_1, \dots, r_n} 
-\big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
-\partial \sum_{r_2, \dots, r_n} \sum_{r_1 = 0}^{p-1}
-\big(\rho^0, \rho^{r_1} \, (\rho^0, \rho^{1}, \dots, \rho^{r_n-r_1}, \rho^{r_n - r_1 +1}) \big) \\ & =
-\partial \sum_{r_2, \dots, r_n}
-\big(\rho^0, N\, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1}) \big) \\ & =
-\sum_{r_2, \dots, r_n}
-N\, \big( \rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1} \big) \\ & -
-\sum_{r_2, \dots, r_n}
-\big(\rho^0, \partial \, N \, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n+1}) \big) \\ & =
-N \psi(e_{2n-1}) - (\rho^0, \partial N \psi (e_{2n-1})) \\ & =
-\psi(N e_{2n-1}) - (\rho^0, \psi (\partial N e_{2n-1})) \\ & =
-\psi(\partial e_{2n}) - (\rho^0, \psi (\partial^2 e_{2n})) \\ & =
-\psi(\partial e_{2n}).
-\end{align*}
-If $k = 2n+1$ we have
-\begin{align*}
-\partial \psi(e_{2n+1}) & = 
-\partial \sum_{r_1, \dots, r_n} 
-\big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
-\partial \sum_{r_1, \dots, r_n}
-\big(\rho^0, \rho^{1} \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-\partial \sum_{r_1, \dots, r_n}
-\big(\rho^0, T\, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-\sum_{r_1, \dots, r_n}
-T \, \big( \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n} \big) \\ & -
-\sum_{r_1, \dots, r_n}
-\big(\rho^0, \partial \, T \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-T \psi(e_{2n}) - (\rho^0, \partial T \psi (e_{2n})) \\ & =
-\psi(T e_{2n}) - (\rho^0, \psi (\partial T e_{2n})) \\ & =
-\psi(\partial e_{2n+1}) - (\rho^0, \psi (\partial^2 e_{2n+1})) \\ & =
-\psi(\partial e_{2n+1})
-\end{align*}
-where for the third equality we used that for any $r_1, \dots, r_n$
-\begin{equation*}
-(\rho^0, \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) = 0.
-\end{equation*}
-This map is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0)$ represents a generator of the homology.
-
-\subsection{Theorem \ref{thm: Steenrod-Adem on surjection MS convention}}
-
-\begin{proof}
-	We prove that the $\Z[\mathrm{C}_r]$-linear map
-	\begin{equation*}
-	\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)
-	\end{equation*}
-	introduced in Definition \ref{def: Steenrod-Adem on surjection} is a chain map for every $r \geq 0$.
-We simplify notation and write $\psi$ instead of $\psi_{\mathcal X}(r)$.
-To show $\psi$ is a chain map we proceed by induction.
-Notice that
-	\begin{equation*}
-	\psi(\partial e_0) = 0 = \partial \psi(e_0)
-	\end{equation*}
-	and assume $\psi(\partial e_{n-1}) = \partial \psi(e_{n-1})$. For $n = 2m+1$ we have
-	\begin{align*}
-	\partial \psi(e_{2m+1}) 
-	& =
-	\partial\, h\, T\, \psi(e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - i^{r-1} p^{r-1}\, \psi(e_{2m}) -
-	h\, \partial\, T\, \psi(e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - 
-	h\, T\, \psi(\partial\, e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - 
-	h\, \psi(T\,N\, e_{2m-1}) \big) \\
-	& = 
-	T \psi(e_{2m}).
-	\end{align*}
-	For $n = 2m$ the proof is analogous. The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ is a generator of the homology.
-\end{proof}
-
-\subsection{Theorem \ref{thm: cubical chain bialgebra}}
-
-The only non-trivial relation we need to verify is
-\begin{equation*}
-\partial \product = \, \boundary \, .
-\end{equation*}
-Let us consider two basis elements of $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$
-\begin{align*}
-x & = x_1 \otimes \cdots \otimes x_n, \\
-y & = y_1 \otimes \cdots \otimes y_n.
-\end{align*}
-We need to show that
-\begin{equation*}
-\partial (x \otimes y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y = \epsilon(x) y - \epsilon(y) x.
-\end{equation*}
-We have
-\begin{equation*}
-x \ast y = \sum (-1)^{|x|} \epsilon(y_{<i})x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i})y_{>i}
-\end{equation*}
-and
-\begin{align*}
-\partial(x \ast y) & = 
-\sum (-1)^{|x|} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes \partial (x_i \ast y_i) \otimes \epsilon(x_{>i}) y_{>i} \\ & -
-\sum (-1)^{|x|+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{align*}
-Since
-\begin{equation*}
-|x| = |x_{<i}| + |x_i| + |x_{>i}|, \quad \epsilon(x_{>i}) \neq 0 \Leftrightarrow |x_{>i}| = 0, \quad \partial(x_i \ast y_i) \neq 0 \Rightarrow |x_i| = 0,
-\end{equation*}
-we have
-\begin{equation} \label{eq: boundary of product 1}
-\begin{split}
-\partial(x \ast y) & = 
-\sum (-1)^{|x|} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes \partial (x_i \ast y_i) \otimes \epsilon(x_{>i}) y_{>i} \\ & -
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{split}
-\end{equation}
-We also have
-\begin{align*}
-\partial x \ast y & = 
-\sum (-1)^{|x|-1} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|-1+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes \partial x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|-1+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(\partial x_{>i}) y_{>i}.
-\end{align*}
-Since
-\begin{equation*}
-\epsilon(\partial x_{>i}) = 0, \quad \partial x_i \neq 0 \Leftrightarrow |x_i| = 1,
-\end{equation*}
-we have
-\begin{equation} \label{eq: boundary of product 2}
-\begin{split}
-\partial x \ast y & = 
-\sum (-1)^{|x|-1} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes \partial x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i}.
-\end{split}
-\end{equation}
-We also have
-\begin{align*}
-(-1)^{|x|} x \ast \partial y & = 
-\sum \epsilon(\partial y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|y_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast \partial y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|y_{<i}|+|y_i|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i},
-\end{align*}
-which is equivalent to
-\begin{equation} \label{eq: boundary of product 3}
-\begin{split}
-(-1)^{|x|} x \ast \partial y & = 
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast \partial y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{split}
-\end{equation}
-Putting identities \eqref{eq: boundary of product 1}, \eqref{eq: boundary of product 2} and \eqref{eq: boundary of product 3} together, we get
-\begin{multline*}
-\partial (x \otimes y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y =
-\sum \epsilon(y_{<i}) x_{<i} \otimes \big(\partial(x_i \ast y_i) + \partial x_i \ast y_i + x_i \ast \partial y_i\big) \otimes \epsilon(x_{>i}) y_{>i}.
-\end{multline*}
-Since
-\begin{equation*}
-\partial(x_i \ast y_i) + \partial x_i \ast y_i + x_i \ast \partial y_i = \epsilon(x_i)y_i - \epsilon(y_i)x_i,
-\end{equation*}
-we have
-\begin{align*}
-\partial (x \otimes y) + \partial x \ast y + & (-1)^{|x|}x \ast \partial y \\ = &
-\sum \epsilon(y_{<i}) x_{<i} \otimes \epsilon(x_{\geq i}) y_{\geq i} - \epsilon(y_{\leq i}) x_{\leq i} \otimes \epsilon(x_{>i}) y_{>i} \\ = &
-\epsilon(x)y - \epsilon(y)x,
-\end{align*}
-as desired, where the last equality follows from a telescopic sum argument.
-
-\bibliographystyle{alpha} 
-\bibliography{bib}
-
-\end{document}

### 2021-05-07 main.tex
Split sections into files

--- 2021-01-16 main.tex
@@
 \tableofcontents
-
-\section{Introduction}
-
-The role Steenrod operations play in Stable Homotopy Theory is hard to overstate.
-The reason is that, given the representability of the cohomology functor, these operations together with the Bockstein homomorphism can be used to give a complete description of the algebraic structure naturally present on the mop-$p$ \mbox{cohomology} algebra of spaces.
-For the even prime, Steenrod squares were introduced in \cite{steenrod47products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander-Whitney's chain approximation to the diagonal.
-Later, for odd primes,	their definition was given non-effectively using arguments based on the mod-$p$ homology of symmetric groups \cites{steenrod53symmetric, steenrod53cyclic, steenrod62operations}.
-This viewpoint enhanced the conceptual understanding of the operations and allowed for many advances \cites{adem1952iteration, milnor1958dual, adams1995stable}, but lacked the concreteness of their definition at~$2$.
-
-In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- the need to have a definition of Steenrod operations that can be effectively computed in specific examples has gain considerable importance.
-In Applied Topology, the use of Persistence Homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage,chan2013topology,lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of Persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
-In Quantum Field Theory, the BRST formalism \cites{BRS,Tyutin,KugoOjima} introduced cohomology to deal with gauge symmetries, and was further developed in the BV-formalism \cite{BV}.
-Master equations, introduced there, are also needed for the construction of viable actions in String Field Theory \cite{Zwiebach}, where fundamental chains are involved.
-The chain level viewpoint for the study of homology operations was brought to the forefront by String Topology \cite{Sullivanoverview}, and as served as a major driver of innovation \cites{TZ, hoch2}.
-The cubical viewpoint appears in physics naturally in the theory of renomalization \cite{KreimerCubical}; while Steenrod cup-$i$ products are utilized in the construction of effective actions of gapped systems \cite{kapustin2017fermionic}.
-This connection with physics motivated the development of effective versions of spin bordism \cites{brumfiel2016pontrjagin, brumfiel2018pontrjagin}, which prominently feature Steenrod cup-$i$ products and Cartan coboundaries.
-
-As in \cite{may70generalapproach}, we take a more general approach to Steenrod operations that also includes Araki-Kudo-Dyer-Lashof operations on the mod-$p$ homology of infinite loop spaces \cites{araki56squaring, dyer62lashof}.
-We use the language of operads \cite{may72geometry}  to describe at the chain level the integral structure required to define (co)homology operations at every prime.
-We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod-$p$ homology of their algebras; these are the Barratt-Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
-Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical products generalizing the \mbox{cup-$i$} products of Steenrod to every prime.
-An alternative approach based on the Eilenberg-Zilber contraction can be found in \cite{gonzalez2005hpt}.
-Up to now, although its existence is warrantied by acyclic model argument \cite{eilenberg1953acyclic}, no $E_\infty$-structure was known on the cochains of cubical sets.
-Using an $E_\infty$-bialgebra structure on the chains of the interval we effectively construct an $U(\mathcal M)$-algebra structure on them, and as a consequence provide a description of Steenrod products for cochains of cubical sets as well.
-The $p=2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2018axiomatic}, and in the cubical setting to the cup-$i$ products of  Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l-Pilarczy \cite{pilarczyk2016cubical}.
-
-We also contribute to a growing body of open source software \cites{manero2020effective, pilarczyk2015contraction, sagemath} resulting from an effort to rewrite key concepts from Homotopy Theory in effective forms.
-Uses in Applied Topology are motivating some of this work \cite{tauzin2020giottotda}, but the impetus also comes from Voevodsky's program for a comprehensive, computational foundation of mathematics based on the homotopical interpretation of type theory \cite{bauer2017hott}.
-A \texttt{Python} implementation of all the constructions in this article can be found in A.M-M.'s website.\footnote{Currently hosted at \url{https://www.medina-mardones.com/}}
-
-An outline of the article is described next.
-We first introduce, in Section~2, the conventions we will follow regarding chain complexes, simplicial sets and cubical sets.
-Then, in Section~3, we review the key notions from group homology we will use for cyclic and symmetric groups.
-Section~4 is devoted to the language of operads and related structures that we use, in Section~5, to define an integral structure at the chain level inducing Steenrod operations for every prime.
-Section~6, the bulk of this work, presents effective constructions of Steenrod-Adem structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
-It also describes a natural $U(\mathcal M)$-algebra structure on the cochains of simplicial and cubical sets inducing natural Steenrod-Adem structures on them.
-We end, in Section~7, with an overview of some connections of this work to important geometric and combinatorial structures, and provide an outline of future research directions.
-
-\section*{Acknowledgement}
-
-The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Greg Brumfiel, Dev Sinha, Jens Kjaer, Calista Bernard, and Andy Putnam, for insightful discussions and valuable comments, and to the anonymous referee for many helpful suggestions.
-
-\section{Preliminaries}
-
-\subsection{Chain complexes}
-\label{ssec: chain cpx}
-
-Let $R$ be a ring.
-We denote by $(\mathbf{Ch}_R, \otimes, R)$ the symmetric monoidal category of homologically graded chain complexes of $R$-modules.
-The set of $R$-linear maps between chain complexes as well as the tensor product of chain complexes are regarded as chain complexes in the usual way:
-\begin{equation*}
-\Hom(A, A^\prime)_n = \big\{f \ |\ a \in A_m \Rightarrow f(a) \in A^\prime_{m+n} \big\}, \qquad
-\partial f = \partial \circ f - (-1)^{|f|}f \circ \partial,
-\end{equation*}
-\begin{equation*}
-(A \otimes A^\prime)_n = \bigoplus_{p + q = n} A_p \otimes A^\prime_q, \qquad \partial (a \otimes a^\prime) = \partial a \otimes a^\prime + (-1)^{|a|} a \otimes \partial a^\prime.
-\end{equation*}
-We embed the category of $R$-modules as the full subcategory of $\mathbf{Ch}_R$ with objects concentrated in degree $0$.
-The endofunctor $\Hom(-, R)$ is referred to as the \textit{linear duality functor}.
-We notice that if a chain complex is concentrated in non-negative degrees then its linear dual is on non-positive ones.
-
-The rings we will mostly be interested in are the group rings $\Z[\mathrm G]$ and $\mathbb{F}_p[\mathrm G]$ of finite groups, where $p$ is prime and $\mathbb{F}_p$ is the field with $p$ elements.
-
-\subsection{Simplicial sets}
-
-The \textit{simplex category} $\triangle$ is defined to have an object $[n] = \{0, \dots, n\}$ for every $n \in \mathbb{N}$ and a morphism $[m] \to [n]$ for each order-preserving function from $[m]$ to $[n]$.
-The morphisms $\delta_i : [n-1] \to [n]$ and $\sigma_i : [n+1] \to [n]$ defined for $0 \leq i \leq n$ by
-\begin{equation*}
-\delta_i(k) = 
-\begin{cases} k & k < i, \\ k+1 & i \leq k, \end{cases}
-\quad \text{ and } \quad
-\sigma_i(k) = 
-\begin{cases} k & k \leq i, \\ k-1 & i < k, \end{cases}
-\end{equation*} 
-generate all morphisms in the simplex category.
-
-A \textit{simplicial set} $X$ is a contravariant functor from the simplex category to the category of sets and a simplicial map is a natural transformation between two simplicial sets.
-As is customary we use the notation
-\begin{equation*}
-X\big( [n] \big) = X_n, \qquad X(\delta_i) = d_i, \qquad X(\sigma_i) = s_i,
-\end{equation*}
-and refer to elements in the image of any $s_i$ as \textit{degenerate}.
-
-For each $n \in \mathbb{N}$, the simplicial set $\triangle^n$ is defined by
-\begin{equation*}
-\triangle^n_k  = \Hom_{\triangle} \big( [k], [n] \big), \qquad 
-d_i(x) = x \circ \delta_i, \qquad 
-s_i(x) = x \circ \sigma_i,
-\end{equation*}
-and any simplicial set can be expressed as a colimit of these
-\begin{equation*}
-X = \colim_{\triangle^n \to X} \triangle^n.
-\end{equation*}
-We represent the non-degenerate elements of $\triangle^n_k$ as an increasing sequence $[v_0, \dots, v_k]$ of non-negative integers each less than or equal to $n$.
-
-The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: 
-\begin{equation*}
-N_\bullet(X; R)_n = \frac{R \{ X_n \}}{R \{ s(X_{n-1}) \}}
-\end{equation*}
-where $s(X_{n-1}) = \bigcup_{i=0}^{n-1} s_i(X_{n-1})$, and $\partial_n : N_*(X)_n \to N_*(X)_{n-1}$ is given by
-\begin{equation*}
-\partial_n = \sum_{i=0}^{n} (-1)^id_{i}.
-\end{equation*}
-The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.
-
-It is convenient to emphasize that
-\begin{equation*}
-N_\bullet(X; R) = \colim_{\triangle^n \to X} N_\bullet(\triangle^n; R).
-\end{equation*}
-
-\subsection{Cubical sets}
-
-The \textit{cube category} $\square$ is the free strict monoidal category with a \textit{bipointed object}
-\begin{equation*}
-\begin{tikzcd}
-1 \arrow[r, bend left, "\delta^0"] \arrow[r, bend right, "\delta^1"'] & 2 \arrow[r, "\sigma"] & 1
-\end{tikzcd}
-\end{equation*}
-such that $\sigma \circ \delta^0 = \sigma \circ \delta^1 = \mathrm{id}$.
-Explicitly, it contains an object $2^n$ for each non-negative integer $n$ and its morphisms are generated by the \textit{coface} and \textit{codegeneracy maps} defined by
-\begin{align*}
-\delta_i^\varepsilon & = \mathrm{id}_{2^{i-1}} \times \delta^\varepsilon \times \mathrm{id}_{2^{n-1-i}} \colon 2^{n-1} \to 2^n, \\
-\sigma_i & = \mathrm{id}_{2^{i-1}} \times \, \sigma \times \mathrm{id}_{2^{n-i}} \colon 2^{n} \to 2^{n-1}.
-\end{align*}
-
-A \textit{cubical set} $X$ is a contravariant functor from the cube category to the category of sets and a cubical map is a natural transformation between two cubical sets.
-As is customary, we use the notation
-\begin{equation*}
-X\big( 2^n \big) = X_n \qquad X(\delta^\varepsilon_i) = d^\varepsilon_i \qquad X(\sigma_i) = s_i,
-\end{equation*}
-and refer to elements in the image of any $s_i$ as \textit{degenerate}.
-
-For each $n \in \mathbb{N}$, the cubical set $\square^n$ is defined by
-\begin{equation*}
-\square^n_k  = \Hom_{\square} \big( 2^k, 2^n \big), \qquad 
-d^\varepsilon_i(x) = x \circ \delta^\varepsilon_i, \qquad 
-s_i(x) = x \circ \sigma_i,
-\end{equation*}
-notice that iteratively
-\begin{equation*}
-\square^n = \overbrace{\square^1 \times \cdots \times \square^1}^{n \text{ times }}.
-\end{equation*}
-We represent the non-degenerate elements of $\square^n$ as sequences $x_1 \cdots\, x_n$ with each $x_i \in \{[0], [1], [0,1]\}$. Any cubical set can be expressed as a colimit of these
-\begin{equation*}
-X = \colim_{\square^n \to X} \square^n.
-\end{equation*}
-
-The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: The chain complex $N_\bullet(\square^1)$ is simply the cellular chain complex of the interval,
-isomorphic to
-\begin{equation*}
-\begin{tikzcd} [column sep = small, row sep = 0.1pt]
-R\{[0], [1]\}  & \arrow[l] R\{[0,1]\} \\
-{[1] - [0]} & \arrow[l, |->] \left[0,1\right].
-\end{tikzcd}
-\end{equation*}
-Set
-\begin{equation} \label{eq: chains on I^n}
-N_\bullet(\square^n; R) = N_\bullet(\square^1; R)^{\otimes n}
-\end{equation}
-and define
-\begin{equation*}
-N_\bullet(X; R) = \colim_{\square^n \to X} N_\bullet(\square^n; R).
-\end{equation*}
-
-The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.
-
-\section{Group homology}
-\label{sec: goup homology}
-
-Fixing notation, let $\mathrm{S}_n$ be the symmetric group of $n$ elements and $\mathrm{C}_n$ be the cyclic group of order $n$ thought of as the subgroup of $\mathrm{S}_n$ generated by an element~$\rho$.
-We denote this inclusion by $\iota : \mathrm C_r \to \mathrm S_r$.
-
-A \textit{resolution} in $\mathbf{Ch}_R$ is a quasi-isomorphism $P \to M$ with each $P_n$ a free \mbox{$R$-module}.
-We will use the fact, explained in Section 6.5 of \cite{jacobson1989algebra}, that such resolutions exist for any chain complex $M$ concentrated in non-negatively degrees, in particular, for the monoidal unit $R$.
-
-Let $\mathrm G$ be a group and $M$ an $R[\mathrm G]$-module, we define the \textit{homology of $\mathrm G$ with coefficients in $M$}, denoted $H(\mathrm G; M)$, as the homology of any chain complex $P \otimes_{R[\mathrm G]} M$ with $P \to R$ a resolution.
-We will be particularly interested in the case when $M = \mathbb F_p(q)$ is the trivial or sign $\mathbb F_p[\mathrm{S}_n]$-module depending on the parity of~$q$.
-
-We now review the group homology of finite cyclic groups. For any ring $R$ the elements
-\begin{align} \label{eq: T and R definition}
-T &= \rho - 1, \\
-N &= 1 + \rho + \cdots + \rho^{n-1},
-\end{align}
-in $R[\mathrm{C}_n]$ generate the ideal of annihilators of each other.
-Therefore, the chain complex $\mathcal W(n)$ concentrated in non-negative degrees with $\mathcal W(n)_d$ the free $\Z[\mathrm{C}_n]$-module generated by one element $e_d$, and differential
-\begin{equation*}
-\partial(e_d) = \begin{cases}
-Te_{d-1} & d \text{ odd,} \\
-Ne_{d-1} & d \text{ even,}
-\end{cases}
-\end{equation*}
-defines a resolution $\mathcal W(n) \to R$ in $\mathbf{Ch}_{R[\mathrm{C}_n]}$. It follow from a straightforward computation that for any prime $p$ and integer $q$
-\begin{equation*}
-H_i(\mathrm{C}_n; \mathbb{F}_p(q)) = \mathbb{F}_p.
-\end{equation*}
-
-The homology of $\mathrm{S}_n$ is harder to compute.
-With untwisted coefficients, the method of computation followed by several authors was to prove the injectivity of this homology into that of the infinite symmetric group and take advantage of a natural Hopf algebra structure on it.
-A powerful result stemming from the deep connection of this question with infinite loop space theory, is the existence of a homology isomorphism of spaces
-\begin{equation*}
-\Z \times B\mathrm{S}_\infty \to Q(S^0) = \Omega^\infty \Sigma^\infty (S^0)
-\end{equation*}
-credited to Dyer-Lashof \cite{dyer62lashof}, Barratt-Priddy and Quillen \cite{barratt1972priddy}.
-
-In this work, we are interested in the mod-$p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite{adem2004milgram} Corollary VI.1.4, is detected by the inclusion $\iota : \mathrm{C}_p \to \mathrm{S}_p$ whose homological kernel is described next.
-
-\begin{lemma} \label{lem: Thom's theorem}
-	Let $p$ be an odd prime and $q$ an integer. Consider
-	\begin{equation*}
-	(\iota_\ast)_n : H_n(\mathrm{C}_p; \mathbb{F}_p(q)) \to H_n(\mathrm{S}_p; \mathbb{F}_p(q))
-	\end{equation*}
-	then
-	\begin{enumerate}
-		\item If $q$ is even, $(\iota_\ast)_n = 0$ unless $n = 2t(p-1)$ or $n = 2t(p-1) - 1$,
-		\item If $q$ is odd, $(\iota_\ast)_n = 0$ unless $n = (2t+1)(p-1)$ or $n = (2t+1)(p-1)-1$,
-	\end{enumerate}
-	for some integer $t$.
-\end{lemma}
-
-\begin{proof}
-	This is proven as Theorem 4.1 in \cite{steenrod53cyclic} where Thom is also credited with a different proof.
-\end{proof}
-
-In section 5 we will see how the cohomology of symmetric groups defines operations on algebras that are commutative up to coherent homotopies.
-Preparing for that, we first developed the language of $\Gamma$-modules and operads, where the integral structure defining Steenrod operations is clearly expressed.
-
-\section{$\Gamma$-modules, operads and PROPs}
-
-In this section we set up a framework in which the structure responsible for Steenrod operations becomes most transparent.
-Given our applications, we consider $\mathbf{Ch}_R$ as the base category, remarking that all definitions in this section apply to general closed symmetric monoidal categories.
-
-\subsection{$\Gamma$-modules}
-Recall that a group $\mathrm G$ can be thought of as a category with a single object and only invertible morphisms, and that a chain complex of left (resp.
-right) $R[\mathrm G]$-modules is the same as a covariant (resp.
-contravariant) functor from $\mathrm G$ to $\mathbf{Ch}_R$.
-Right actions are more commonly used in the literature of operads so we emphasize that perspective.
-Taking inverses allows for the switch between these two conventions.
-
-A \textit{groupoid} is a small category where all morphisms are invertible.
-\begin{definition}
-	A \textit{$\Gamma$-module} is a contravariant functor to $\mathbf{Ch}_R$ from a groupoid $\Gamma$ with objects the natural numbers and morphisms satisfying $\Gamma(r,s) = \emptyset$ for $r \neq s$.
-We denote the category of $\Gamma$-modules and natural transformations by $\mathbf{Ch}_R^\Gamma$.
-\end{definition}
-
-We are mostly interested in two examples of $\Gamma$-modules, those associated to the groupoids $\mathrm{S}$ and $\mathrm{C}$ defined by
-\begin{equation*}
-\mathrm{S}(r, r) = \mathrm{S}_r, \qquad
-\mathrm{C}(r,r) = \mathrm{C}_r,
-\end{equation*}
-for every $r \in \mathbb{N}$. The inclusion $\mathrm{C}_r \to \mathrm{S}_r$ induces a forgetful functor
-\begin{equation*}
-\begin{tikzcd} [column sep = small]
-\mathbf{Ch}_R^\mathrm{S}  \arrow[r] & \mathbf{Ch}_R^\mathrm{C}.
-\end{tikzcd}
-\end{equation*}
-
-Given an object $A$ in $\mathbf{Ch}_R$ there are two important $\Gamma$-modules associated to it; an $\mathrm{S}$-module known as \textit{endomorphism $\mathrm{S}$-module} $\End_A$, and an $\mathrm{S}^{op}$-module known as \textit{coendomorphism $\mathrm{S}$-module} $\End^A$.
-These are defined by
-\begin{align*}	
-\End_A(r) &= \Hom(A^{\otimes r},A), \\
-\End^A(r) &= \Hom(A,A^{\otimes r}),
-\end{align*}
-with respective right and left actions defined by permutation of tensor factors.
-
-Another groupoid of importance to us is $\mathrm{S} \times \mathrm{S}^{op}$.
-Contravariant functors from it to $\mathbf{Ch}_R$ are called \textit{$\mathrm{S}$-bimodules} and their functor category is denoted $\mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}}$.
-Notice that the inclusions
-define forgetful functors
-\begin{equation*}
-\begin{tikzcd}[column sep=small, row sep=tiny]
-& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"'] \arrow[dr, "U_2"] & \\
-\mathbf{Ch}_R^{\mathrm{S}} &  & \mathbf{Ch}_R^{\mathrm{S}^{op}},
-\end{tikzcd}
-\end{equation*}
-and that for any object $A$ in $\mathbf{Ch}_R$, the canonical \textit{endomorphism bimodule}
-\begin{equation*}
-\End_A^A(r, s) = \Hom(A^{\otimes r}, A^{\otimes s})
-\end{equation*}
-forgets to $\End_A$ and $\End^A$.
-
-Using the groupoid automorphism sending every morphisms to its inverse we can identify $\Gamma$- and $\Gamma^{op}$- modules.
-In particular, the statement claiming that the linear duality functor induces a morphism of $\mathrm{S}$-modules
-\begin{equation*}
-\End^A \to \End_{\Hom(A, R)}
-\end{equation*}
-for every object $A$ in $\mathbf{Ch}_R$ is well defined and easily verified using this identification.
-
-A \textit{resolution} in $\mathbf{Ch}_R^\Gamma$ is a morphism $\phi$ of $\Gamma$-modules such that $\phi(r)$ is a resolution in the category of chain complexes of $R[\Gamma_r]$-modules for each $r \in \mathbb{N}$.
-A $\Gamma$-module $\mathcal R$ is said to be $E_\infty$ if $\mathcal R(0) = R$ and there exists a resolution $\mathcal R \to \underline{R}$ where $\underline{R}$ is the object in $\mathbf{Ch}_R^\Gamma$ defined by $\underline{R}(r) = R$ and $\underline{R}(\gamma) = \mathrm{id}_R$ for every $r \in \mathbb{N}$ and $\gamma \in \Gamma_r$.
-
-\begin{definition} \label{def: minimal cyclic resolution}
-	The \textit{minimal} $E_\infty$-$\mathrm{C}$-\textit{module} $\mathcal W$ is the functor in $\mathbf{Ch}_R^\mathrm{C}$ assigning to $r$ the chain complex
-	\begin{equation*}
-	\begin{tikzcd} [column sep = .5cm]
-	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] \cdots
-	\end{tikzcd}
-	\end{equation*}
-	concentrated in non-negative degrees.
-\end{definition}
-
-\subsection{Operads and PROPs}
-
-Operads an PROPs are respectively $\mathrm{S}$-modules and \mbox{$\mathrm{S}$-bimodules} enriched with further compositional structure.
-These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a PROP.
-
-Succinctly, an operad $\mathcal O$ is an $\mathrm{S}$-module together with a collection of $R$-linear maps
-\begin{equation*}
-\mathcal O(r) \otimes \mathcal O(s) \to \mathcal O(r+s-1)
-\end{equation*}
-satisfying suitable associativity, equivariance and unitality conditions. A PROP $\mathcal P$ is an $\mathrm{S}$-bimodule together with two types of compositions; horizontal
-\begin{equation*}
-\mathcal P(r_1, s_1) \otimes \mathcal P(r_2, s_2) \to \mathcal P(r_1 + r_2, s_1 + s_2)
-\end{equation*}
-and vertical
-\begin{equation*}
-\mathcal P(r,s) \otimes \mathcal P(s, t) \to \mathcal P(r, t)
-\end{equation*}
-satisfying their own versions of associativity, equivariance and unitality. For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008operads}.
-
-We have already mentioned that for any chain complex $A$, the $\mathrm{S}$-module $\End_A$ is naturally an operad and the $\mathrm{S}$-bimodule $\End_A^A$ is naturally a PROP.
-We add that considering $\End^A$ as an $\mathrm{S}$-module, its compositional structure also defines an operad structure on it.
-
-We remark that the compositional structure of a PROP $\mathcal P$ restricts to operad structures on $U_1(\mathcal P)$ and $U_2(\mathcal P)$.
-
-The type of operads that we are most interested in are $E_\infty$-operads which, as we will discuss in the next section, are used to describe commutativity up to coherent homotopies.
-
-\begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}]
-	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a PROP $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
-\end{definition}
-
-\subsection{Algebras, coalgebra and bialgebras}
-
-A morphisms of operads or of PROPs is simply a morphisms of their underlying $\mathrm{S}$-modules or $\mathrm{S}$-bimodules preserving the respective compositional structures.
-
-Given a chain complex $A$, an operad $\mathcal O$ and a PROP $\mathcal P$.
-An $\mathcal O$-\textit{algebra} (resp.
-$\mathcal O$-\textit{coalgebra}) structure on $A$ is an operad morphism $\mathcal O \to \End_A$ (resp.
-$\mathcal O \to \End^A$), and a $\mathcal P$-\textit{bialgebra} structure on $A$ is a PROP morphism $\mathcal P \to \End_A^A$.
-
-We remark that the linear duality functor naturally transforms an $\mathcal O$-coalgebra structure on a chain complex into an $\mathcal O$-algebra structure on its dual.
-
-Algebras over $E_\infty$-operads are the central objects of study in this work.
-To develop intuition for them, let us consider a chain complex $A$ with an algebra structure over $\underline{R}$, thought of as an operad with all compositions corresponding to the identity map $R \to R$.
-The $\underline{R}$-algebra structure on $A$ is generated by a linear map $\mu \colon A \otimes A \to A$ which is (strictly) commutative and associative, and a linear map $\eta \colon R \to A$ that determines a (two-sided) unit for $\mu$.
-Since $E_\infty$-operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies.
-The two main examples to keep in mind are the cochains of spaces and the chains of infinite loops spaces.
-
-\section{Steenrod-Adem structures}
-
-We now introduce an operadic formulation of a structure giving rise to Steenrod operations at every prime.
-It is based on \cites{steenrod47products, steenrod53symmetric, steenrod53cyclic, may70generalapproach}, and takes a viewpoint that emphasizes the integral structure needed to define them and prove their relations at every prime.
-For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}.
-
-\begin{definition} \label{def: Steenrod-Adem structure}
-	A \textit{Steenrod-Adem structure} on an operad $\mathcal O$ is a 
-	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad
-	\begin{equation*}
-	\begin{tikzcd}[column sep = normal, row sep = small]
-	& \mathcal R \arrow[dr, "\phi", out=0] & \\
-	\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \mathcal O
-	\end{tikzcd}
-	\end{equation*}
-	such that $\iota$ is a quasi-isomorphism and $\phi$ a morphism of operads.
-\end{definition}
-
-\begin{remark} \label{rmk: Deligne conjecture}
-	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$.
-In this language, a choice of factorization for a Steenrod-Adem structure defines in particular a \textit{commutative multiplication}.
-\end{remark}
-
-\begin{definition}
-	Let $A$ be a chain complex.
-A Steenrod-Adem structure on $\mathrm{End}_A$ is referred to as one on $A$.
-Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod} $(r, i)$-\textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
-\end{definition}
-
-\begin{remark}
-	Restricting a Steenrod-Adem structure on a chain complex $A$ to a given arity $r$ corresponds to specifying a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$.
-This pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ introduced in \cite{may70generalapproach} Definition 2.1.
-Furthermore, the restriction to arity $r^2$ enhances this pair to an \textit{Adem object} as described in Definition 4.1 loc.
-cit.
-\end{remark}
-
-A Steenrod-Adem structure on a chain complex $A$ allows us to define operations on its $\mathbb{F}_p$-homology for every prime $p$.
-These operations are structurally different if $p$ is even or odd.
-Using the previous Remark, the definitions below recover Steenrod's original definition for the cohomology of spaces and that of Araki-Kudo-Dyer-Lashof operations for the homology of infinite loop spaces.
-
-For the rest of this section $A$ is a chain complex equipped with a Steenrod-Adem structure.
-
-\begin{definition}
-	For any prime $p$, the $\mathbb{F}_p$-linear map
-	\begin{equation*}
-	D^p_i : (A \otimes \mathbb{F}_p) \to (A \otimes \mathbb{F}_p)
-	\end{equation*}
-	is defined by sending $a$ to the Steenrod \mbox{$(p, i)$-product} of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
-\end{definition}
-
-We notice that if $a$ is of degree $q$ then $D^p_i(a)$ is of degree $q + (p-1)q + i$.
-
-\begin{definition}
-	For any integer $s$, the \textit{Steenrod operation}
-	\begin{equation*}
-	P_s : H_\bullet(A; \mathbb{F}_2) \to H_{\bullet + s}(A; \mathbb{F}_2)
-	\end{equation*}
-	is defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_2)$ of degree $q$ to the class represented by $D^2_{s-q}(a)$.
-\end{definition}
-
-Notice that the Steenrod squares are determined by the Steenrod $(2,i)$-products with $\mathbb{F}_2$-coefficients.
-These binary operations are known as cup-$i$ products.
-In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod $\big(p, k(p-1)-\varepsilon\big)$-products for $\varepsilon \in \{0,1\}$.
-We can explain the appearance of these specific Steenrod products as follows.
-The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even an $(2t+1)(p-1) - \varepsilon$ if $q$ is odd.
-According to Lemma \ref{lem: Thom's theorem}, these are the only homologically non-trivial cases.
-
-\begin{definition} \label{def: Steenrod operations at odd prime}
-	For any integer $s$, the \textit{Steenrod operations}
-	\begin{equation*}
-	P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1)}(A; \mathbb{F}_p)
-	\end{equation*}
-	and
-	\begin{equation*}
-	\beta P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1) - 1}(A; \mathbb{F}_p)
-	\end{equation*}
-	are defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_p)$ of degree $q$ to the classes represented respectively for $\varepsilon \in\{0,1\}$ by
-	\begin{equation*}
-	(-1)^s \nu(q) D^p_{(2s-q)(p-1)-\varepsilon}(a)
-	\end{equation*}
-	where $\nu(q) = (-1)^{q(q-1)m/2}(m!)^q$ and $m = (p-1)/2$.
-\end{definition}
-
-\begin{remark}
-	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq.
-6.1.
-in \cite{steenrod53cyclic}).
-The notation $\beta P_s$ is motivated by the relationship of this operator and the Bockstein of the reduction $\mathbb Z \to \mathbb Z/p\mathbb Z$.
-\end{remark}
-
-Steenrod operations satisfy the Cartan and Adem relations.
-Below we state the subset of these relations that is most commonly used and refer to Sections 2 and 4 of \cite{may70generalapproach} for a complete list and proofs.
-\begin{lemma}
-	Let $A$ be equipped with a Steenrod-Adem structure. If $[\alpha], [\beta] \in H(A;\mathbb{F}_p)$ then
-	\begin{equation*}
-	P_s\big([\alpha] [\beta]\big) = \sum_{i+j=s} P_i\big( [\alpha] \big) P_j\big( [\beta] \big),
-	\end{equation*}
-	and
-	\begin{itemize}
-		\item If $p = 2$ and $a > 2b$
-		\begin{equation*}
-		P_{a}P_{b} = \sum_i {2i-a \choose a-b-i-1} P_{a+b-i}P_i,
-		\end{equation*}
-		\item If $p > 2$ and $a > pb$
-		\begin{equation*}
-		P_{a}P_{b} = \sum_i (-1)^{a+i}{pi-a \choose a-(p-1)b-i-1} P_{a+b-i}P_i.
-		\end{equation*}
-	\end{itemize}		
-\end{lemma}
-
-\begin{proof}
-	These are proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
-\end{proof}
-
-For the even prime, proofs at the chain level of these formulae have been given in \cite{medina2020cartan,brumfiel2020cochain}.
-For a different operadic approach to Steenrod operations at the even prime please consult \cite{chataur2005adem-cartan}.
-
-For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$, which we use in subsections 6.4 and 6.5.
-
-\section{Effective constructions}
-\label{sec: effective constructions}
-
-In this section we construct explicit Steenrod-Adem structures on three well know combinatorial $E_\infty$-operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-PROP $\mathcal M$ \cite{medina2020prop1}.
-We also define natural and effective Steenrod-Adem structure on the normalized cochains of any simplicial or cubical set, by describing a $U(\mathcal M)$-algebra structures on it.
-
-Figure~\ref{fig: bigsummary} presents a diagrammatical representation of the constructions in this section.
-
-\begin{figure}
-	\begin{tikzcd}
-	& & & U(\mathcal M) \arrow[dddr, bend left=10, "\phi^\triangle"'] \arrow[dddrr, bend left=20, "\phi^\square"'] & & \\
-	& & \mathcal X \arrow[ru, "SL"] & & & \\
-	& \mathcal E \arrow[ur, "TR"] & & & & \\
-	\mathcal W \arrow[rrrr, "\psi^\triangle", bend right=10] \arrow[rrrrr, "\psi^\square", bend right=20] \arrow[ur, "\psi_{\mathcal E}"] \arrow[uurr, "\psi_{\mathcal X}"', bend right=35, pos=.6] \arrow[uuurrr, "\psi_{U(\mathcal M)}"', bend right=45, pos=0.6] & & & & \End_{N^\bullet(X)} & \End_{N^\bullet(X)}
-	\end{tikzcd}
-	\caption{Summary of effective constructions: Steenrod-Adem structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural Steenrod-Adem structures on the normalized chains of simplicial and cubical sets.
-We are abusing notation since the maps $TR$ and $SL$ required different sign conventions.}
-	\label{fig: bigsummary}
-\end{figure}
-
-\subsection{Barratt-Eccles operad} In this subsection we effectively describe a Steenrod-Adem structure on the Barratt-Eccles operad.
-
-We begin by reviewing the $\mathrm{S}$-module structure underlying the Barratt-Eccles operad and, since will not use it in this work, refer to \cite{berger04combinatorial} for a description of if composition structure.
-For a non-negative integer $r$ define the simplicial set $E(\mathrm S_r)$ by
-\begin{equation} \label{eq: milnor model of symmetric}
-\begin{split}
-E(\mathrm S_r)_n &= \{ (\sigma_0, \dots, \sigma_n)\ |\ \sigma_i \in \mathrm{S}_r\}, \\
-d_i(\sigma_0, \dots, \sigma_n) &= (\sigma_0, \dots, \widehat{\sigma}_i, \dots, \sigma_n), \\
-s_i(\sigma_0, \dots, \sigma_n) &= (\sigma_0, \dots, \sigma_i, \sigma_i, \dots, \sigma_n) \\
-\end{split}
-\end{equation}
-with a left $\mathrm S_r$-action given by
-\begin{equation*}
-\sigma (\sigma_0, \dots, \sigma_n) = (\sigma \sigma_0, \dots, \sigma \sigma_n).
-\end{equation*} 
-The chain complex resulting from applying the functor of normalized integral chains to it is denoted $\mathcal E(r)$, which corresponds to the arity $r$ part of the Barratt-Eccles operad.
-
-\begin{definition} \label{def: Steenrod-Adem on Barratt-Eccles}
-	For every $r \geq 0$, let $\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined on basis elements by 
-	\begin{equation*}
-	\psi_{\mathcal E}(r)(e_{n}) = \begin{cases}
-	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \rho^{r_2}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m, \\
-	\displaystyle{\sum_{r_1, \dots, r_m}} \big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_{m}}, \rho^{r_{m}+1} \big) & n = 2m+1,
-	\end{cases}
-	\end{equation*}
-	where the sum is over all $r_1, \dots, r_m \in \{0, \dots, r-1\}$.
-\end{definition}
-
-\begin{theorem} \label{thm: Steenrod-Adem on Barratt-Eccles}
-	The morphism of $\mathrm{C}$-modules
-	\begin{equation*}
-	\psi_{\mathcal E} \colon \mathcal W \to \mathcal E
-	\end{equation*}
-	defines a Steenrod-Adem structure on the Barratt-Eccles operad.
-\end{theorem}
-
-\begin{proof}
-	This theorem follows from a computation which we defer to the appendix.
-\end{proof}
-
-\begin{example}
-	Table \ref{fig: Barratt-Eccles Steenrod products} shows $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$.
-\end{example}
-
-\begin{table}[h]
-	\centering
-	\resizebox{0.8\columnwidth}{!}{%
-		\renewcommand{\arraystretch}{1.2}
-		\begin{tabular}{|c||c|c|c|}
-			\hline
-			$r$ & $n=2$ & $n=3$ & $n=4$ \\
-			\hline
-			2 & (0,1,0) & (0,1,0,1) & (0,1,0,1,0) \\
-			\hline
-			3 & (0,1,2) + (0,2,0) & (0,1,2,0) + (0,1,0,1) & \phantom{+} (0,1,2,0,1) + (0,1,2,1,2) \\
-			& & & + (0,2,0,1,2) + (0,2,0,2,0) \\
-			\hline
-			4 & (0,1,2) + (0,2,3) & (0,1,2,3) + (0,1,3,0) & \phantom{+} (0,1,2,3,0) + (0,1,2,0,1) \\
-			& + (0,3,0) & + (0,1,0,1) & 
-			+ (0,1,2,1,2) + (0,2,3,0,1) \\
-			& & & + (0,2,3,1,2) + (0,2,3,2,3) \\
-			& & & + (0,3,0,1,2) + (0,3,0,2,3) \\
-			& & & + (0,3,0,3,0) \\
-			\hline  
-		\end{tabular}
-	}
-	\vspace*{3pt}
-	\caption{The elements $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$ where we are denoting $(\rho^{r_0}, \dots, \rho^{r_n})$ simply by $(r_0, \dots, r_n)$.}
-	\label{fig: Barratt-Eccles Steenrod products}
-\end{table}
-
-\begin{remark}
-	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota : \mathrm C_r \to \mathrm S_r$ induces a simplicial map $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ which extends to a quasi-isomorphism of $\mathrm C$-modules
-	\begin{equation*}
-	N_\bullet E(\iota) : N_\bullet E(\mathrm C) \to N_\bullet E(\mathrm S) = \mathcal E,
-	\end{equation*}
-	factoring
-	\begin{equation*}
-	\psi_{\mathcal E} :
-	\begin{tikzcd}
-	\mathcal W \arrow[r, "\phi_{\mathrm C}"] &[-3pt] N_\bullet E(\mathrm C) \arrow[r, "N_\bullet E(\iota)"] &[5pt] \mathcal E.
-	\end{tikzcd}
-	\end{equation*}
-\end{remark}
-
-\subsection{Surjection operad}
-
-In this subsection we introduce a Steenrod-Adem structures on the surjection operad.
-There are two widely used sign conventions for this operad respectively due to McClure-Smith \cite{mcclure03cochain} and Berger-Fresse \cite{berger04combinatorial}.
-Using the Berger-Fresse convention, we can define a Steenrod-Adem structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}.
-We define an Steenrod-Adem structure on the surjection operad in a convention independent way which recovers the table reduction Steenrod-Adem structure in the Berger-Fresse case.
-
-Let us start by recalling the definition of the surjection operad.
-For a non-negative integer $r$ let $\mathcal X(r)_n$ be the free abelian group generated by all functions from $\{1, \dots, n+r\}$ to $\{1, \dots, r\}$ modulo the subgroup generated by degenerate functions, i.e., those which are either non-surjective or have a pair of equal consecutive values.
-We only describe the McClure-Smith convention since we refer to it in subsequent sections.
-The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s : \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top dimensional generator in the chain complex
-\begin{equation} \label{eq: surjection boundary}
-\bigotimes_{i = 1}^r N_\bullet \big( \triangle^{s^{-1}(i)}; \Z \big).
-\end{equation}
-Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at the time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on.
-Since we do not use the composition structure we refer to \cite{mcclure03cochain} for it.
-
-Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure-Smith to prove $\mathcal X$ is an $E_\infty$-operad and whose introduction is credited to Benson \cite{benson1998rep}.
-Let the maps $i,\ p$ and $s$ be defined on basis elements, represented by sequences, as follows: $i : \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p : \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s : \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
-with a 1, then the new sequence is degenerate so $s$ takes it to $0$. These maps satisfy
-\begin{equation*}
-p  i = \mathrm{id}
-\qquad \text{ and } \qquad
-\mathrm{id} - i  p = \partial s + s \partial.
-\end{equation*}
-These maps define a contraction of $\mathcal X(r)$ onto $\mathcal X(1) \cong \Z$ with homotopy $h = s + i\, s\, p + \cdots + i^{r-1} s\, p^{r-1}$, satisfying
-\begin{equation*}
-\partial h + h \partial = \mathrm{id} - i^{r-1}\,p^{r-1}.
-\end{equation*}
-
-\begin{definition} \label{def: Steenrod-Adem on surjection}
-	For every $r \geq 0$, let $\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined recursively on basis elements by
-	\begin{align*}
-	\psi_{\mathcal X}(r)(e_0) & = (1, \dots, r), \\
-	\psi_{\mathcal X}(r)(e_{2m+1}) & = h\,T\,\psi_{\mathcal X}(r)(e_{2m}), \\
-	\psi_{\mathcal X}(r)(e_{2m}) & = h\,N\,\psi_{\mathcal X}(r)(e_{2m-1}),
-	\end{align*}
-	where $T$ and $R$ are defined in \eqref{eq: T and R definition}.
-\end{definition}
-
-\begin{theorem} \label{thm: Steenrod-Adem on surjection MS convention}
-	The morphism of $\mathrm{C}$-modules
-	\begin{equation*}
-	\psi_{\mathcal X} \colon \mathcal W \to \mathcal X
-	\end{equation*}
-	defines a Steenrod-Adem structure on the Surjection operad.
-\end{theorem}
-
-\begin{proof}
-	This theorem follows from a computation which we defer to the appendix.
-\end{proof}
-
-For the rest of the paper we use the McClure-Smith convention.
-
-\begin{example}
-	Table \ref{fig: surjection Steenrod products} shows $\psi_{\mathcal X}(r)(e_n)$ for small values of $r$ and $n$.
-\end{example}
-
-\begin{table}[h]
-	\centering
-	\resizebox{\columnwidth}{!}{%
-		\renewcommand{\arraystretch}{1.3}
-		\begin{tabular}{|c||c|c|c|}
-			\hline
-			$r$& $n=2$ & $n=3$ & $n=4$ \\
-			\hline
-			2 & (1,2,1,2) & (1,2,1,2,1) & (1,2,1,2,1,2) \\
-			\hline
-			3 & (1,2,3,1,2) + (1,3,1,2,3) & (1,2,3,1,2,3) + (1,2,1,2,3,1)  & \phantom{+} (1,2,3,1,2,3,1) + (1,2,3,2,3,1,2) \\
-			& + (1,2,3,2,3) & + (1,2,3,1,3,1) & + (1,2,3,1,2,1,2) + (1,3,1,2,3,1,2) \\
-			& & & + (1,3,1,3,1,2,3) + (1,2,3,2,3,2,3) \\
-			& & & + (1,3,1,2,3,2,3) \\
-			\hline
-			4 & \phantom{+} (1,2,3,4,1,2) + (1,3,4,1,2,3) & \phantom{+} (1,2,3,4,1,2,3) + (1,2,4,1,2,3,4) & \\
-			& + (1,2,3,4,2,3) + (1,4,1,2,3,4) & + (1,2,3,4,1,3,4) + (1,2,1,2,3,4,1) & 25 \text{ terms } \\
-			& + (1,2,4,2,3,4) + (1,2,3,4,3,4) & + (1,2,3,1,3,4,1) + (1,2,3,4,1,4,1) & \\
-			\hline  
-		\end{tabular}
-	}
-	\vspace*{2pt}
-	\caption{The values of $\psi_{\mathcal X}(r)(e_n)$ for small values of $r$ and $n$.}
-	\label{fig: surjection Steenrod products}
-\end{table}
-
-\subsection{The finitely presented $E_\infty$-PROP $\mathcal M$}
-
-We start by reviewing the finitely presented $E_\infty$-PROP introduced in \cite{medina2020prop1}. Let $\mathcal M$ be the PROP generated by 
-\begin{equation*}
-\counit \in \mathcal M(1,0)_0, \hspace*{.6cm} \coproduct \in \mathcal M(1,2)_0, \hspace*{.6cm} \product \in \mathcal M(2,1)_1,
-\end{equation*}
-with boundary
-\begin{equation*}
-\partial\ \counit = 0, \hspace*{.6cm} \partial \ \coproduct = 0, \hspace*{.6cm} \partial \ \product = \ \boundary \, ,
-\end{equation*}
-and restricted by the relations
-\begin{equation*}
-\productcounit, \hspace*{.6cm} \leftcounitality \, , \hspace*{.6cm} \rightcounitality \, .
-\end{equation*}
-
-Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$-prop in the terminology of Bordmann-Vogt \cite{boardman1973homotopy}.
-More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$-operad.
-For the remainder of this article we write $U(\mathcal M)$ instead of $U_2(\mathcal M)$.
-
-We will define a Steenrod-Adem structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the Steenrod-Adem structure $\psi_{\mathcal X} : \mathcal W \to \mathcal X$ with a morphism of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact)
-\begin{equation*}
-SL \colon \mathcal X \to U(\mathcal M)
-\end{equation*}
-that we now define. Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element
-\begin{center}
-	\begin{tikzpicture}[scale=.85]
-	\draw (0,0)--(0,-.6) node[below]{$\scriptstyle 1$};
-	\draw (0,0)--(.5,.5);
-	\draw (-.3, .3)-- (-.2,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_1$};
-	\draw (-.5,.5)--(0,0);
-	\node at (.11,.4){$...$};
-
-	\node at (1,0){$\scriptstyle \cdots$};
-	\node at (1,-.9){$\scriptstyle \cdots$};
-
-	\draw (2,0)--(2,-.68) node[below]{$\scriptstyle r$};
-	\draw (2,0)--(2.5,.5);
-	\draw (1.7, .3)-- (1.8,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_r$};
-	\draw (1.5,.5)--(2,0);
-	\node at (2.11,.4){$...$};
-
-	\draw (1,2.5)--(1,3) node[above]{$\scriptstyle 1$};
-	\draw (1,2.5)--(0,2) node[below]{$\scriptstyle 1$};
-	\draw (.25,2.125)--(.5,2) node[below]{$\scriptstyle 2$};
-	\draw (.5,2.25)--(1,2) node[below]{$\scriptstyle 3$};
-	\draw (1,2.5)--(2,2) node[below]{\quad $\scriptstyle n + r$};
-	\node at (1.5,1.75){$...$};
-
-	\node at (1,1.3) {$\vdots$};
-
-	\node at (2.85,0){};
-	\end{tikzpicture}
-\end{center}
-that has no internal vertices and such that the $n+r$ strands at the top are orderly connected to the strands at the bottom following the values of $s$.
-
-It can be directly verified using the presentation of $\mathcal M$ that the boundary of $SL(s)$ is obtained by removing strands one at the time in the order they are attached at the bottom.
-This is precisely the image of $SL(\partial s)$ according to \eqref{eq: surjection boundary}.
-Furthermore, relabeling the bottom edges agrees with the permutation of preimages of the associated surjection.
-Since both operads have the homology of a point and $(1, \dots, r)$ is sent to a representative of a homology generator we have proven the following
-
-\begin{theorem} \label{thm: Steenrod-Adem on U(M)}
-	The composition $\psi_{U(\mathcal M)}$
-	\begin{equation*}
-	\begin{tikzcd}[column sep = normal]
-	\mathcal W \arrow[r, "\psi_{\mathcal X}"] & \mathcal X \arrow[r, "SL"] & U(\mathcal M)
-	\end{tikzcd}
-	\end{equation*}
-	defines a Steenrod-Adem structure on $U(\mathcal M)$.
-\end{theorem}
-
-\begin{example}
-	Figure \ref{fig: cup 0,1,2} shows $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$.
-\end{example}
-
-\begin{figure}[h]
-	\centering
-	\boxed{
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-		\draw (1,3) to [out=-25, in=90] (2,0);
-
-		\node at (1,-.5){$n=0$};
-		\end{tikzpicture}\hspace*{1cm}
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-
-		\draw [shorten >= 0cm] (.6,2.73) to [out=-100, in=90] (2,0);
-		%\draw [shorten <= 0cm] (1,1.5) to [out=-60, in=90] (2,0);
-
-		\draw [shorten >= .15cm] (1,3) to [out=-25, in=30, distance=1.1cm] (1,1.5);
-		\draw [shorten <= .1cm] (1,1.5) to [out=210, in=20] (0,1);
-
-		\node at (1,-.5){$n=1$};
-		\end{tikzpicture}\hspace*{1cm}
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-		\draw (1,3) to [out=-25, in=90] (2,0);
-
-		\draw [shorten >= 0cm] (.6,2.73) to [out=210, in=135] (1,1.5);
-		\draw [shorten <= 0cm] (1,1.5) to [out=-45, in=170] (2,1);
-
-		\draw [shorten >= .1cm] (1.4,2.73) to [out=-30, in=45] (1,1.5);
-		\draw [shorten <= .1cm] (1,1.5) to [out=-135, in=10] (0,1);
-
-		\node at (1,-.5){$n=2$};
-		\end{tikzpicture}
-	}
-	\caption{The values of $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$.}
-	\label{fig: cup 0,1,2}
-\end{figure}
-
-\subsection{Cochains of simplicial sets}
-
-In this subsection we introduce a natural Steenrod-Adem structure on the normalized cochains of any simplicial set $X$.
-Since a Steenrod-Adem structure was constructed in the previous section for $U(\mathcal M)$, we only need to describe a natural $U(\mathcal M)$-algebra structure on $N^\bullet(X)$.
-Using the linear duality functor, it suffices to construct a natural $U(\mathcal M)$-coalgebra structure on $N_\bullet(X)$ which, in turn, can be derived via a Kan extension argument from one on each $N_\bullet(\triangle^n)$.
-We obtain these coalgebra structures by restricting a full $\mathcal M$-bialgebra structure.
-An $\mathcal M$-bialgebra structure is specified by three linear maps, the images of the generators
-\begin{equation*}
-\counit, \quad \coproduct, \quad \product,
-\end{equation*}
-satisfying the relations in the presentation of $\mathcal M$. For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
-(1) The counit $\epsilon \in \Hom(N_\bullet(\triangle^n), \Z)$ by
-\begin{equation*}
-\epsilon \big( [v_0, \dots, v_q] \big) = \begin{cases} 1 & \text{ if } q = 0, \\ 0 & \text{ if } q>0. \end{cases}
-\end{equation*}
-(2) The coproduct $\Delta \in \Hom(N_\bullet(\triangle^n), N_\bullet(\triangle^n)^{\otimes2})$ by
-\begin{equation*}
-\Delta \big( [v_0, \dots, v_q] \big) = \sum_{i=0}^q [v_0, \dots, v_i] \otimes [v_i, \dots, v_q].
-\end{equation*}
-(3) The product $\ast \in \Hom(N_\bullet(\triangle^n)^{\otimes 2}, N_\bullet(\triangle^n))$ by
-\begin{equation*}
-\left[v_0, \dots, v_p \right] \ast \left[v_{p+1}, \dots, v_q\right] = \begin{cases} (-1)^{p+|\pi|} \left[v_{\pi(0)}, \dots, v_{\pi(q)}\right] & \text{ if } v_i \neq v_j \text{ for } i \neq j, \\
-0 & \text{ if not}, \end{cases}
-\end{equation*}
-where $\pi$ is the permutation that orders the totally ordered set of vertices, and $(-1)^{|\pi|}$ its sign.
-
-\begin{theorem} \label{thm: simplicial chain bialgebra}
-	For every $n \in \mathbb{N}$, the assignment
-	\begin{equation*}
-	\counit \mapsto \epsilon, \quad \coproduct \mapsto \Delta, \quad \product \mapsto \ast,
-	\end{equation*}
-	defines a natural $\mathcal M$-bialgebra structure  on $N_\bullet(\triangle^n)$.
-\end{theorem}
-
-\begin{proof}
-	This statement is proven as Theorem 4.2 in \cite{medina2020prop1}.
-\end{proof}
-
-\begin{definition}
-	Let $X$ be a simplicial set.
-Denote by $\phi^\triangle : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem \ref{thm: simplicial chain bialgebra}.
-\end{definition}
-
-\begin{theorem}
-	The commutative diagram
-	\begin{equation*}
-	\begin{tikzcd}[column sep = small, row sep = small]
-	&[18pt] U(\mathcal M) \arrow[dr, "\phi^\triangle", out=0] &[-0pt] \\
-	\mathcal W \arrow[ur, "\psi_{U(\mathcal M)}", in=180] \arrow[rr, "\psi^\triangle"] & & \mathrm{End}_{N^\bullet (X)}
-	\end{tikzcd}
-	\end{equation*}
-	defines a natural Steenrod-Adem structure on $N^\bullet(X)$ for any simplicial set $X$.
-\end{theorem}
-
-\begin{remark}
-	The $E_\infty$-structure we described in Theorem \ref{thm: simplicial chain bialgebra}, depending solely on three fundamental maps, recovers the coalgebra structures of McClure-Smith \cite{mcclure03cochain} and, up to signs, that of Berger-Fresse \cite{berger04combinatorial}.
-\end{remark}
-
-\begin{example}
-	Let us consider the prime $2$. The value $P^1(x)\big([0,1,2,3,4]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^4)$ is equal to the value of $x^{\otimes 2}$ acting on
-	\begin{align*}
-	[0, 1, 2, 3] \otimes [0, 1, 3, 4] \ +\  & 
-	[0, 2, 3, 4] \otimes [0, 1, 2, 4] \\ \ +\ 
-	[0, 1, 2, 3] \otimes [1, 2, 3, 4] \ +\ &
-	[0, 1, 3, 4] \otimes [1, 2, 3, 4].
-	\end{align*}
-	Similarly, the value of $P^2(y)\big([0,1,2,3,4,5,6,7]\big)$ for a homogeneous cocycle $y$ in $N^{-5}(\triangle^7)$ is equal to the value of $y^{\otimes 2}$ acting on
-	\begin{align*}
-	[0, 1, 2, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] & \ +\
-	[0, 1, 2, 3, 6, 7] \otimes [0, 1, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 2, 3, 4, 7] \otimes [0, 1, 4, 5, 6, 7] & \ +\ 
-	[0, 2, 3, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] \\ \ +\ 
-	[0, 2, 3, 4, 6, 7] \otimes [0, 1, 2, 4, 5, 6] & \ +\ 
-	[0, 2, 3, 4, 5, 7] \otimes [0, 1, 2, 5, 6, 7] \\ \ +\ 
-	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 4, 5] & \ +\ 
-	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 5, 6] \\ \ +\ 
-	[0, 3, 4, 5, 6, 7] \otimes [0, 1, 2, 3, 6, 7] & \ +\ 
-	[0, 1, 2, 3, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 2, 3, 4, 7] \otimes [1, 2, 4, 5, 6, 7] & \ +\ 
-	[0, 1, 3, 4, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 3, 4, 5, 7] \otimes [1, 2, 3, 5, 6, 7] & \ +\ 
-	[0, 1, 4, 5, 6, 7] \otimes [1, 2, 3, 4, 5, 6] \\ \ +\ 
-	[0, 1, 4, 5, 6, 7] \otimes [1, 2, 3, 4, 6, 7] & \ +\ 
-	[0, 1, 2, 3, 4, 7] \otimes [2, 3, 4, 5, 6, 7] \\ \ +\ 
-	[0, 1, 2, 4, 5, 7] \otimes [2, 3, 4, 5, 6, 7] & \ +\ 
-	[0, 1, 2, 5, 6, 7] \otimes [2, 3, 4, 5, 6, 7].
-	\end{align*}
-\end{example}
-
-\begin{example}
-	Let us consider the prime $3$. The value $\beta P^1(x)\big([0,1,2,3,4,5,6,7,8]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^8)$ is equal to the value of $x^{\otimes 3}$ acting on
-	\begin{align*}
-	& \,-\, [0, 6, 7, 8] \otimes [0, 1, 2, 3] \otimes [3, 4, 5, 6] \,+\, [0, 1, 7, 8] \otimes [1, 2, 3, 4] \otimes [4, 5, 6, 7] \\ & \,-\, [0, 1, 2, 8] \otimes [2, 3, 4, 5] \otimes [5, 6, 7, 8].
-	\end{align*}
-	Similarly, the value of $P^1(y)\big([0,1,\dots,7]\big)$ for a homogeneous cocycle $y$ in $N^{-3}(\triangle^7)$ is equal to the value of $y^{\otimes 3}$ acting on
-	\begin{align*}
-	& \,-\, [0,3,4,5] \otimes [0,5,6,7] \otimes [0,1,2,3] \,-\, [0,4,5,6] \otimes [0,1,6,7] \otimes [1,2,3,4] \\ & \,-\, [0,5,6,7] \otimes [0,1,2,7] \otimes [2,3,4,5] \,-\, [0,1,4,5] \otimes [1,5,6,7] \otimes [1,2,3,4] \\ & \,+\, [0,1,5,6] \otimes [1,2,6,7] \otimes [2,3,4,5] \,-\, [0,1,6,7] \otimes [1,2,3,7] \otimes [3,4,5,6] \\ & \,-\, [0,1,2,5] \otimes [2,5,6,7] \otimes [2,3,4,5] \,-\, [0,1,2,6] \otimes [2,3,6,7] \otimes [3,4,5,6] \\ & \,-\, [0,1,2,7] \otimes [2,3,4,7] \otimes [4,5,6,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [0,1,6,7] \\ & \,+\, [0,2,3,4] \otimes [4,5,6,7] \otimes [0,1,2,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [1,2,6,7] \\ & \,-\, [0,1,3,4] \otimes [4,5,6,7] \otimes [1,2,3,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [2,3,6,7] \\ & \,+\, [0,1,2,4] \otimes [4,5,6,7] \otimes [2,3,4,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [3,4,6,7] \\ & \,-\, [0,1,2,3] \otimes [3,5,6,7] \otimes [3,4,5,7] \,+\, [0,1,2,3] \otimes [3,4,5,6] \otimes [4,5,6,7] \\ & \,+\, [0,1,2,3] \otimes [3,4,6,7] \otimes [4,5,6,7].
-	\end{align*}
-\end{example}
-
-\subsection{Cochains of cubical sets}
-
-In this subsection we introduce a natural Steenrod-Adem structure on the normalized cochains of any cubical set.
-It follows the structure of the previous subsection closely.
-By the same considerations, the desired construction will follow from a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$.
-These are determined by three linear maps satisfying the relations in the presentation of $\mathcal M$.
-For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
-(1) The counit $\epsilon \in \Hom(N_\bullet(\square^n), \Z)$ by
-\begin{equation*}
-\epsilon \left( x_1 \otimes \cdots \otimes x_d \right) = \epsilon(x_1) \cdots \, \epsilon(x_n),
-\end{equation*}
-where
-\begin{equation*}
-\epsilon([0]) = \epsilon([1]) = 1, \qquad \epsilon([0, 1]) = 0.
-\end{equation*} \vspace*{-6pt} \\
-(2) The coproduct $\Delta \in \Hom \left( N_\bullet(\square^n), N_\bullet(\square^n)^{\otimes 2} \right)$ by
-\begin{equation*}	
-\Delta (x_1 \otimes \cdots \otimes x_n) = 	
-\sum \pm \left( x_1^{(1)} \otimes \cdots \otimes x_n^{(1)} \right) \otimes 	
-\left( x_1^{(2)} \otimes \cdots \otimes x_n^{(2)} \right),	
-\end{equation*}	
-where the sign is determined using the Koszul convention, and we are using Sweedler's notation
-\begin{equation*}	
-\Delta(x_i) = \sum x_i^{(1)} \otimes x_i^{(2)}
-\end{equation*}
-for the chain map $\Delta \colon N_\bullet(\square^1) \to N_\bullet(\square^1)^{\otimes 2}$ defined by
-\begin{equation*}
-\Delta([0]) = [0] \otimes [0], \quad \Delta([1]) = [1] \otimes [1], \quad \Delta([0, 1]) = [0] \otimes [0, 1] + [0, 1] \otimes [1].
-\end{equation*}
-Using that $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$, $\Delta$ is the composition
-\begin{equation*}
-\begin{tikzcd}
-N_\bullet(\square^1)^{\otimes n} \arrow[r, "\Delta^{\otimes n}"] & \left( N_\bullet(\square^1)^{\otimes 2}  \right)^{\otimes n} \arrow[r, "sh"] & \left( N_\bullet(\square^1)^{\otimes n} \right)^{\otimes 2}
-\end{tikzcd}
-\end{equation*}
-where $sh$ is the shuffle map that places tensor factors in odd position first. \vspace*{5pt} \\
-(3) The product $\ast \in \Hom(N_\bullet(\square^n)^{\otimes 2}, N_\bullet(\square^n))$ by
-\begin{align*}
-(x_1 \otimes \cdots \otimes x_n) \ast (y_1 \otimes \cdots \otimes y_n) =
-(-1)^{|x|} \sum_{i=1}^n x_{<i} \epsilon(y_{<i}) \otimes x_i \ast y_i \otimes \epsilon(x_{>i})y_{>i},
-\end{align*}
-where
-\begin{align*}
-x_{<i} & = x_1 \otimes \cdots \otimes x_{i-1}, &
-y_{<i} & = y_1 \otimes \cdots \otimes y_{i-1}, \\
-x_{>i} & = x_{i+1} \otimes \cdots \otimes x_n, & 
-y_{>i} & = y_{i+1} \otimes \cdots \otimes y_n,
-\end{align*}
-with the convention
-\begin{equation*}
-x_{<1} = y_{<1} = x_{>n} = y_{>n} = 1 \in \Z,
-\end{equation*}
-and the only non-zero values of $x_i \ast y_i$ are
-\begin{equation*}
-\ast([0] \otimes [1]) = [0, 1], \qquad  \ast([1] \otimes [0]) = -[0, 1].
-\end{equation*}
-
-\begin{theorem} \label{thm: cubical chain bialgebra}
-	For every $n \in \mathbb{N}$, the assignment
-	\begin{equation*}
-	\counit \mapsto \epsilon, \quad \coproduct \mapsto \Delta, \quad \product \mapsto \ast,
-	\end{equation*}
-	defines a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$.
-\end{theorem}
-
-\begin{proof}
-	We present a proof of this statement in the appendix.
-\end{proof}
-
-\begin{remark}
-	We saw that for simplicial sets a natural algebraic $E_\infty$-structure was determined by basic maps in the standard simplices.
-For cubical sets, one such structure is constructed by naturally extending three maps defined just on the interval.
-\end{remark}
-
-\begin{definition}
-	Let $X$ be a cubical set.
-Denote by $\phi^\square : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem~\ref{thm: cubical chain bialgebra}.
-\end{definition}
-
-\begin{theorem}
-	The commutative diagram
-	\begin{equation*}
-	\begin{tikzcd}[column sep = small, row sep = small]
-	&[18pt] U(\mathcal M) \arrow[dr, "\phi^\square", out=0] &[-0pt] \\
-	\mathcal W \arrow[ur, "\psi_{U(\mathcal M)}", in=180] \arrow[rr, "\psi^\square"] & & \End_{N^\bullet (X)}
-	\end{tikzcd}
-	\end{equation*}
-	defines a natural Steenrod-Adem structure on $N^\bullet(X)$ for any cubical set $X$.
-\end{theorem}
-
-\begin{example}
-	Let us consider the prime $2$. The value $P^1(x)\big([01]^{4}\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\square^4)$ is equal to the value of $x^{\otimes 2}$ acting on
-	\begin{align*}&
-	[01]1[01][01] \otimes [01][01]0[01]\,+\,
-	[01][01][01]0 \otimes [01]0[01][01]\,+\, \\&
-	[01][01][01]0 \otimes 1[01][01][01]\,+\,
-	[01][01]1[01] \otimes [01]0[01][01]\,+\, \\&
-	[01][01]1[01] \otimes 1[01][01][01]\,+\,
-	[01][01][01]0 \otimes [01][01]1[01]\,+\, \\&
-	[01][01]0[01] \otimes [01][01][01]1\,+\,
-	[01]1[01][01] \otimes [01][01][01]1\,+\, \\&
-	0[01][01][01] \otimes [01][01][01]1\,+\,
-	0[01][01][01] \otimes [01][01]0[01]\,+\, \\&
-	0[01][01][01] \otimes [01]1[01][01]\,+\,
-	[01]0[01][01] \otimes 1[01][01][01].\,\phantom{+}\,
-	\end{align*}
-\end{example}
-
-\begin{example}
-	Let us consider the prime $3$. The value of $\beta P^0(x)\big([01]^2\big)$ for a homogeneous cocycle $x$ in $N^{-1}(\square^2)$ is equal to the value of $x^{\otimes 3}$ acting on
-	\begin{align*}
-	\,-\, [01]1 \otimes [01]0 \otimes 1[01] \,-\, 0[01] \otimes [01]0 \otimes 1[01] + [01]1 \otimes 0[01] \otimes [01]1 + 0[01] \otimes 0[01] \otimes [01]1.
-	\end{align*}
-\end{example}
-
-\section{Outlook}
-This article looked at Steenrod operations from an algebraic viewpoint, a subject with rich geometric and combinatorial components as well.
-For example, \cite{Postnikov} and \cite{medina2018prop2} independently introduced equivalent geometric representations of the cup-$i$ products in terms of stabilized arc surfaces \cite{KLP} and weighted ribbon graphs respectively.
-In fact, an entire $E_\infty$-operad (PROP) is constructed geometrically in this way.
-We can also interpret the Steenrod-Adem structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups ---a key ingredient in Definition \ref{def: minimal cyclic resolution}--- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.
-
-In Higher Category Theory, the paper \cite{medina2020globular} constructs a functor producing strict \mbox{$\infty$-cat}egories from group-like cup-$i$ coalgebras in a manner similar to \cite{steiner2004omega}.
-In particular, the cup-$i$ constructions described in this article for standard simplices and cubes define, respectively, the Street nerve and cubical nerve of strict $\infty$-categories.
-We anticipate that the more general Steenrod $(p,i)$-products constructed in this work will also have deep combinatorial interpretations.
-
-There is a functorial approach to the theory using the formalism of Feynman categories \cite{feynman},
-which renders all the structures and notions natural.
-This includes cyclic, planar cyclic as well as Berger's pre-operads \cite{BergerRecog}.
-Their interplay is of independent interest \cite{BergerKaufmann,feyrep} and will be linked directly to the constructions of this paper.
-
-In this article we have not focused on the operations that exist non-trivially for \mbox{$E_n$-algebras} with $n$ finite, see part III of \cite{may76homology}.
-A treatement close to ours for the $E_2$ case was given in \cite{Tourtchine}.
-Effective constructions for these Dyer-Lashof-Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang,sinha2013littledisks,berger04combinatorial,ayala2014configuration} and higher categories \cite{Bathigher,BalFiedSchwVogt,Rezkhigher}, and will appear elsewhere.
+\input{introduction}
+\input{preliminaries}
+\input{groups}
+\input{operads}
+\input{steenrod}
+\input{effective}
+\input{outlook}
+\input{proofs}
 
@@
 \appendix
-\section{Proofs}
-
-\subsection{Theorem \ref{thm: Steenrod-Adem on Barratt-Eccles}}
-
-We prove that the $\Z[\mathrm{C}_r]$-linear map
-\begin{equation*}
-\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)
-\end{equation*}
-introduced in Definition \ref{def: Steenrod-Adem on Barratt-Eccles} is a chain map for every $r \geq 0$.
-We simplify notation and write $\psi$ instead of $\psi_{\mathcal E}(r)$.
-To show $\psi$ is a chain map we proceed by induction.
-Notice that
-\begin{equation*}
-\psi(\partial e_0) = 0 = \partial \psi(e_0)
-\end{equation*}
-and assume $\psi(\partial e_{k-1}) = \partial \psi(e_{k-1})$. If $k = 2n$ we have
-\begin{align*}
-\partial \psi(e_{2n}) & = 
-\partial \sum_{r_1, \dots, r_n} 
-\big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
-\partial \sum_{r_2, \dots, r_n} \sum_{r_1 = 0}^{p-1}
-\big(\rho^0, \rho^{r_1} \, (\rho^0, \rho^{1}, \dots, \rho^{r_n-r_1}, \rho^{r_n - r_1 +1}) \big) \\ & =
-\partial \sum_{r_2, \dots, r_n}
-\big(\rho^0, N\, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1}) \big) \\ & =
-\sum_{r_2, \dots, r_n}
-N\, \big( \rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1} \big) \\ & -
-\sum_{r_2, \dots, r_n}
-\big(\rho^0, \partial \, N \, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n+1}) \big) \\ & =
-N \psi(e_{2n-1}) - (\rho^0, \partial N \psi (e_{2n-1})) \\ & =
-\psi(N e_{2n-1}) - (\rho^0, \psi (\partial N e_{2n-1})) \\ & =
-\psi(\partial e_{2n}) - (\rho^0, \psi (\partial^2 e_{2n})) \\ & =
-\psi(\partial e_{2n}).
-\end{align*}
-If $k = 2n+1$ we have
-\begin{align*}
-\partial \psi(e_{2n+1}) & = 
-\partial \sum_{r_1, \dots, r_n} 
-\big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
-\partial \sum_{r_1, \dots, r_n}
-\big(\rho^0, \rho^{1} \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-\partial \sum_{r_1, \dots, r_n}
-\big(\rho^0, T\, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-\sum_{r_1, \dots, r_n}
-T \, \big( \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n} \big) \\ & -
-\sum_{r_1, \dots, r_n}
-\big(\rho^0, \partial \, T \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
-T \psi(e_{2n}) - (\rho^0, \partial T \psi (e_{2n})) \\ & =
-\psi(T e_{2n}) - (\rho^0, \psi (\partial T e_{2n})) \\ & =
-\psi(\partial e_{2n+1}) - (\rho^0, \psi (\partial^2 e_{2n+1})) \\ & =
-\psi(\partial e_{2n+1})
-\end{align*}
-where for the third equality we used that for any $r_1, \dots, r_n$
-\begin{equation*}
-(\rho^0, \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) = 0.
-\end{equation*}
-This map is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0)$ represents a generator of the homology.
-
-\subsection{Theorem \ref{thm: Steenrod-Adem on surjection MS convention}}
-
-\begin{proof}
-	We prove that the $\Z[\mathrm{C}_r]$-linear map
-	\begin{equation*}
-	\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)
-	\end{equation*}
-	introduced in Definition \ref{def: Steenrod-Adem on surjection} is a chain map for every $r \geq 0$.
-We simplify notation and write $\psi$ instead of $\psi_{\mathcal X}(r)$.
-To show $\psi$ is a chain map we proceed by induction.
-Notice that
-	\begin{equation*}
-	\psi(\partial e_0) = 0 = \partial \psi(e_0)
-	\end{equation*}
-	and assume $\psi(\partial e_{n-1}) = \partial \psi(e_{n-1})$. For $n = 2m+1$ we have
-	\begin{align*}
-	\partial \psi(e_{2m+1}) 
-	& =
-	\partial\, h\, T\, \psi(e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - i^{r-1} p^{r-1}\, \psi(e_{2m}) -
-	h\, \partial\, T\, \psi(e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - 
-	h\, T\, \psi(\partial\, e_{2m}) \big) \\
-	& =
-	T\, \psi(e_{2m}) - 
-	h\, \psi(T\,N\, e_{2m-1}) \big) \\
-	& = 
-	T \psi(e_{2m}).
-	\end{align*}
-	For $n = 2m$ the proof is analogous. The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ is a generator of the homology.
-\end{proof}
-
-\subsection{Theorem \ref{thm: cubical chain bialgebra}}
-
-The only non-trivial relation we need to verify is
-\begin{equation*}
-\partial \product = \, \boundary \, .
-\end{equation*}
-Let us consider two basis elements of $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$
-\begin{align*}
-x & = x_1 \otimes \cdots \otimes x_n, \\
-y & = y_1 \otimes \cdots \otimes y_n.
-\end{align*}
-We need to show that
-\begin{equation*}
-\partial (x \otimes y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y = \epsilon(x) y - \epsilon(y) x.
-\end{equation*}
-We have
-\begin{equation*}
-x \ast y = \sum (-1)^{|x|} \epsilon(y_{<i})x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i})y_{>i}
-\end{equation*}
-and
-\begin{align*}
-\partial(x \ast y) & = 
-\sum (-1)^{|x|} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes \partial (x_i \ast y_i) \otimes \epsilon(x_{>i}) y_{>i} \\ & -
-\sum (-1)^{|x|+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{align*}
-Since
-\begin{equation*}
-|x| = |x_{<i}| + |x_i| + |x_{>i}|, \quad \epsilon(x_{>i}) \neq 0 \Leftrightarrow |x_{>i}| = 0, \quad \partial(x_i \ast y_i) \neq 0 \Rightarrow |x_i| = 0,
-\end{equation*}
-we have
-\begin{equation} \label{eq: boundary of product 1}
-\begin{split}
-\partial(x \ast y) & = 
-\sum (-1)^{|x|} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes \partial (x_i \ast y_i) \otimes \epsilon(x_{>i}) y_{>i} \\ & -
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{split}
-\end{equation}
-We also have
-\begin{align*}
-\partial x \ast y & = 
-\sum (-1)^{|x|-1} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|-1+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes \partial x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|x|-1+|x_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(\partial x_{>i}) y_{>i}.
-\end{align*}
-Since
-\begin{equation*}
-\epsilon(\partial x_{>i}) = 0, \quad \partial x_i \neq 0 \Leftrightarrow |x_i| = 1,
-\end{equation*}
-we have
-\begin{equation} \label{eq: boundary of product 2}
-\begin{split}
-\partial x \ast y & = 
-\sum (-1)^{|x|-1} \epsilon(y_{<i}) \partial x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes \partial x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i}.
-\end{split}
-\end{equation}
-We also have
-\begin{align*}
-(-1)^{|x|} x \ast \partial y & = 
-\sum \epsilon(\partial y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|y_{<i}|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast \partial y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum (-1)^{|y_{<i}|+|y_i|} \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i},
-\end{align*}
-which is equivalent to
-\begin{equation} \label{eq: boundary of product 3}
-\begin{split}
-(-1)^{|x|} x \ast \partial y & = 
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast \partial y_i \otimes \epsilon(x_{>i}) y_{>i} \\ & +
-\sum \epsilon(y_{<i}) x_{<i} \otimes x_i \ast y_i \otimes \epsilon(x_{>i}) \partial y_{>i}.
-\end{split}
-\end{equation}
-Putting identities \eqref{eq: boundary of product 1}, \eqref{eq: boundary of product 2} and \eqref{eq: boundary of product 3} together, we get
-\begin{multline*}
-\partial (x \otimes y) + \partial x \ast y + (-1)^{|x|}x \ast \partial y =
-\sum \epsilon(y_{<i}) x_{<i} \otimes \big(\partial(x_i \ast y_i) + \partial x_i \ast y_i + x_i \ast \partial y_i\big) \otimes \epsilon(x_{>i}) y_{>i}.
-\end{multline*}
-Since
-\begin{equation*}
-\partial(x_i \ast y_i) + \partial x_i \ast y_i + x_i \ast \partial y_i = \epsilon(x_i)y_i - \epsilon(y_i)x_i,
-\end{equation*}
-we have
-\begin{align*}
-\partial (x \otimes y) + \partial x \ast y + & (-1)^{|x|}x \ast \partial y \\ = &
-\sum \epsilon(y_{<i}) x_{<i} \otimes \epsilon(x_{\geq i}) y_{\geq i} - \epsilon(y_{\leq i}) x_{\leq i} \otimes \epsilon(x_{>i}) y_{>i} \\ = &
-\epsilon(x)y - \epsilon(y)x,
-\end{align*}
-as desired, where the last equality follows from a telescopic sum argument.
 

### 2021-05-07 operads.tex
Split sections into files

\section{$\Gamma$-modules, operads and PROPs}

In this section we set up a framework in which the structure responsible for Steenrod operations becomes most transparent. Given our applications, we consider $\mathbf{Ch}_R$ as the base category, remarking that all definitions in this section apply to general closed symmetric monoidal categories.

\subsection{$\Gamma$-modules}
Recall that a group $\mathrm G$ can be thought of as a category with a single object and only invertible morphisms, and that a chain complex of left (resp. right) $R[\mathrm G]$-modules is the same as a covariant (resp. contravariant) functor from $\mathrm G$ to $\mathbf{Ch}_R$. Right actions are more commonly used in the literature of operads so we emphasize that perspective. Taking inverses allows for the switch between these two conventions.

A \textit{groupoid} is a small category where all morphisms are invertible.
\begin{definition}
	A \textit{$\Gamma$-module} is a contravariant functor to $\mathbf{Ch}_R$ from a groupoid $\Gamma$ with objects the natural numbers and morphisms satisfying $\Gamma(r,s) = \emptyset$ for $r \neq s$. We denote the category of $\Gamma$-modules and natural transformations by $\mathbf{Ch}_R^\Gamma$.
\end{definition}

We are mostly interested in two examples of $\Gamma$-modules, those associated to the groupoids $\mathrm{S}$ and $\mathrm{C}$ defined by
\begin{equation*}
\mathrm{S}(r, r) = \mathrm{S}_r, \qquad
\mathrm{C}(r,r) = \mathrm{C}_r,
\end{equation*}
for every $r \in \mathbb{N}$. The inclusion $\mathrm{C}_r \to \mathrm{S}_r$ induces a forgetful functor
\begin{equation*}
\begin{tikzcd} [column sep = small]
\mathbf{Ch}_R^\mathrm{S}  \arrow[r] & \mathbf{Ch}_R^\mathrm{C}.
\end{tikzcd}
\end{equation*}

Given an object $A$ in $\mathbf{Ch}_R$ there are two important $\Gamma$-modules associated to it; an $\mathrm{S}$-module known as \textit{endomorphism $\mathrm{S}$-module} $\End_A$, and an $\mathrm{S}^{op}$-module known as \textit{coendomorphism $\mathrm{S}$-module} $\End^A$. These are defined by
\begin{align*}	
\End_A(r) &= \Hom(A^{\otimes r},A), \\
\End^A(r) &= \Hom(A,A^{\otimes r}),
\end{align*}
with respective right and left actions defined by permutation of tensor factors.

Another groupoid of importance to us is $\mathrm{S} \times \mathrm{S}^{op}$. Contravariant functors from it to $\mathbf{Ch}_R$ are called \textit{$\mathrm{S}$-bimodules} and their functor category is denoted $\mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}}$. Notice that the inclusions
define forgetful functors
\begin{equation*}
\begin{tikzcd}[column sep=small, row sep=tiny]
& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"'] \arrow[dr, "U_2"] & \\
\mathbf{Ch}_R^{\mathrm{S}} &  & \mathbf{Ch}_R^{\mathrm{S}^{op}},
\end{tikzcd}
\end{equation*}
and that for any object $A$ in $\mathbf{Ch}_R$, the canonical \textit{endomorphism bimodule}
\begin{equation*}
\End_A^A(r, s) = \Hom(A^{\otimes r}, A^{\otimes s})
\end{equation*}
forgets to $\End_A$ and $\End^A$.

Using the groupoid automorphism sending every morphisms to its inverse we can identify $\Gamma$- and $\Gamma^{op}$- modules. In particular, the statement claiming that the linear duality functor induces a morphism of $\mathrm{S}$-modules
\begin{equation*}
\End^A \to \End_{\Hom(A, R)}
\end{equation*}
for every object $A$ in $\mathbf{Ch}_R$ is well defined and easily verified using this identification.

A \textit{resolution} in $\mathbf{Ch}_R^\Gamma$ is a morphism $\phi$ of $\Gamma$-modules such that $\phi(r)$ is a resolution in the category of chain complexes of $R[\Gamma_r]$-modules for each $r \in \mathbb{N}$. A $\Gamma$-module $\mathcal R$ is said to be $E_\infty$ if $\mathcal R(0) = R$ and there exists a resolution $\mathcal R \to \underline{R}$ where $\underline{R}$ is the object in $\mathbf{Ch}_R^\Gamma$ defined by $\underline{R}(r) = R$ and $\underline{R}(\gamma) = \mathrm{id}_R$ for every $r \in \mathbb{N}$ and $\gamma \in \Gamma_r$.

\begin{definition} \label{def: minimal cyclic resolution}
	The \textit{minimal} $E_\infty$-$\mathrm{C}$-\textit{module} $\mathcal W$ is the functor in $\mathbf{Ch}_R^\mathrm{C}$ assigning to $r$ the chain complex
	\begin{equation*}
	\begin{tikzcd} [column sep = .5cm]
	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,T"'] \cdots
	\end{tikzcd}
	\end{equation*}
	concentrated in non-negative degrees.
\end{definition}

\subsection{Operads and PROPs}

Operads an PROPs are respectively $\mathrm{S}$-modules and \mbox{$\mathrm{S}$-bimodules} enriched with further compositional structure. These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a PROP.

Succinctly, an operad $\mathcal O$ is an $\mathrm{S}$-module together with a collection of $R$-linear maps
\begin{equation*}
\mathcal O(r) \otimes \mathcal O(s) \to \mathcal O(r+s-1)
\end{equation*}
satisfying suitable associativity, equivariance and unitality conditions. A PROP $\mathcal P$ is an $\mathrm{S}$-bimodule together with two types of compositions; horizontal
\begin{equation*}
\mathcal P(r_1, s_1) \otimes \mathcal P(r_2, s_2) \to \mathcal P(r_1 + r_2, s_1 + s_2)
\end{equation*}
and vertical
\begin{equation*}
\mathcal P(r,s) \otimes \mathcal P(s, t) \to \mathcal P(r, t)
\end{equation*}
satisfying their own versions of associativity, equivariance and unitality. For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008operads}.

We have already mentioned that for any chain complex $A$, the $\mathrm{S}$-module $\End_A$ is naturally an operad and the $\mathrm{S}$-bimodule $\End_A^A$ is naturally a PROP. We add that considering $\End^A$ as an $\mathrm{S}$-module, its compositional structure also defines an operad structure on it.

We remark that the compositional structure of a PROP $\mathcal P$ restricts to operad structures on $U_1(\mathcal P)$ and $U_2(\mathcal P)$.

The type of operads that we are most interested in are $E_\infty$-operads which, as we will discuss in the next section, are used to describe commutativity up to coherent homotopies.

\begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}]
	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a PROP $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
\end{definition}

\subsection{Algebras, coalgebra and bialgebras}

A morphisms of operads or of PROPs is simply a morphisms of their underlying $\mathrm{S}$-modules or $\mathrm{S}$-bimodules preserving the respective compositional structures.

Given a chain complex $A$, an operad $\mathcal O$ and a PROP $\mathcal P$. An $\mathcal O$-\textit{algebra} (resp. $\mathcal O$-\textit{coalgebra}) structure on $A$ is an operad morphism $\mathcal O \to \End_A$ (resp. $\mathcal O \to \End^A$), and a $\mathcal P$-\textit{bialgebra} structure on $A$ is a PROP morphism $\mathcal P \to \End_A^A$.

We remark that the linear duality functor naturally transforms an $\mathcal O$-coalgebra structure on a chain complex into an $\mathcal O$-algebra structure on its dual.

Algebras over $E_\infty$-operads are the central objects of study in this work. To develop intuition for them, let us consider a chain complex $A$ with an algebra structure over $\underline{R}$, thought of as an operad with all compositions corresponding to the identity map $R \to R$. The $\underline{R}$-algebra structure on $A$ is generated by a linear map $\mu \colon A \otimes A \to A$ which is (strictly) commutative and associative, and a linear map $\eta \colon R \to A$ that determines a (two-sided) unit for $\mu$. Since $E_\infty$-operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies. The two main examples to keep in mind are the cochains of spaces and the chains of infinite loops spaces.

### 2021-05-07 outlook.tex
Split sections into files

\section{Outlook}

This article looked at Steenrod operations from an algebraic viewpoint, a subject with rich geometric and combinatorial components as well. For example, \cite{Postnikov} and \cite{medina2018prop2} independently introduced equivalent geometric representations of the cup-$i$ products in terms of stabilized arc surfaces \cite{KLP} and weighted ribbon graphs respectively. In fact, an entire $E_\infty$-operad (PROP) is constructed geometrically in this way. We can also interpret the Steenrod-Adem structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups ---a key ingredient in Definition \ref{def: minimal cyclic resolution}--- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.

In Higher Category Theory, the paper \cite{medina2020globular} constructs a functor producing strict \mbox{$\infty$-cat}egories from group-like cup-$i$ coalgebras in a manner similar to \cite{steiner2004omega}. In particular, the cup-$i$ constructions described in this article for standard simplices and cubes define, respectively, the Street nerve and cubical nerve of strict $\infty$-categories. We anticipate that the more general Steenrod $(p,i)$-products constructed in this work will also have deep combinatorial interpretations.

There is a functorial approach to the theory using the formalism of Feynman categories \cite{feynman},
which renders all the structures and notions natural. This includes cyclic, planar cyclic as well as Berger's pre-operads \cite{BergerRecog}. Their interplay is of independent interest \cite{BergerKaufmann,feyrep} and will be linked directly to the constructions of this paper.

In this article we have not focused on the operations that exist non-trivially for \mbox{$E_n$-algebras} with $n$ finite, see part III of \cite{may76homology}. A treatement close to ours for the $E_2$ case was given in \cite{Tourtchine}. Effective constructions for these Dyer-Lashof-Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang,sinha2013littledisks,berger04combinatorial,ayala2014configuration} and higher categories \cite{Bathigher, BalFiedSchwVogt, Rezkhigher}, and will appear elsewhere.

### 2021-05-07 preliminaries.tex
Split sections into files

\section{Preliminaries}

\subsection{Chain complexes}
\label{s s:chain cpx}

Let $R$ be a ring. We denote by $(\mathbf{Ch}_R, \otimes, R)$ the symmetric monoidal category of homologically graded chain complexes of $R$-modules. The set of $R$-linear maps between chain complexes as well as the tensor product of chain complexes are regarded as chain complexes in the usual way:
\begin{equation*}
\Hom(A, A^\prime)_n = \big\{f \ |\ a \in A_m \Rightarrow f(a) \in A^\prime_{m+n} \big\}, \qquad
\partial f = \partial \circ f - (-1)^{|f|}f \circ \partial,
\end{equation*}
\begin{equation*}
(A \otimes A^\prime)_n = \bigoplus_{p + q = n} A_p \otimes A^\prime_q, \qquad \partial (a \otimes a^\prime) = \partial a \otimes a^\prime + (-1)^{|a|} a \otimes \partial a^\prime.
\end{equation*}
We embed the category of $R$-modules as the full subcategory of $\mathbf{Ch}_R$ with objects concentrated in degree $0$. The endofunctor $\Hom(-, R)$ is referred to as the \textit{linear duality functor}. We notice that if a chain complex is concentrated in non-negative degrees then its linear dual is on non-positive ones.

The rings we will mostly be interested in are the group rings $\Z[\mathrm G]$ and $\mathbb{F}_p[\mathrm G]$ of finite groups, where $p$ is prime and $\mathbb{F}_p$ is the field with $p$ elements.

\subsection{Simplicial sets}

The \textit{simplex category} $\triangle$ is defined to have an object $[n] = \{0, \dots, n\}$ for every $n \in \mathbb{N}$ and a morphism $[m] \to [n]$ for each order-preserving function from $[m]$ to $[n]$. The morphisms $\delta_i : [n-1] \to [n]$ and $\sigma_i : [n+1] \to [n]$ defined for $0 \leq i \leq n$ by
\begin{equation*}
\delta_i(k) = 
\begin{cases} k & k < i, \\ k+1 & i \leq k, \end{cases}
\quad \text{ and } \quad
\sigma_i(k) = 
\begin{cases} k & k \leq i, \\ k-1 & i < k, \end{cases}
\end{equation*} 
generate all morphisms in the simplex category.

A \textit{simplicial set} $X$ is a contravariant functor from the simplex category to the category of sets and a simplicial map is a natural transformation between two simplicial sets. As is customary we use the notation
\begin{equation*}
X\big( [n] \big) = X_n, \qquad X(\delta_i) = d_i, \qquad X(\sigma_i) = s_i,
\end{equation*}
and refer to elements in the image of any $s_i$ as \textit{degenerate}.

For each $n \in \mathbb{N}$, the simplicial set $\triangle^n$ is defined by
\begin{equation*}
\triangle^n_k  = \Hom_{\triangle} \big( [k], [n] \big), \qquad 
d_i(x) = x \circ \delta_i, \qquad 
s_i(x) = x \circ \sigma_i,
\end{equation*}
and any simplicial set can be expressed as a colimit of these
\begin{equation*}
X = \colim_{\triangle^n \to X} \triangle^n.
\end{equation*}
We represent the non-degenerate elements of $\triangle^n_k$ as an increasing sequence $[v_0, \dots, v_k]$ of non-negative integers each less than or equal to $n$.

The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: 
\begin{equation*}
N_\bullet(X; R)_n = \frac{R \{ X_n \}}{R \{ s(X_{n-1}) \}}
\end{equation*}
where $s(X_{n-1}) = \bigcup_{i=0}^{n-1} s_i(X_{n-1})$, and $\partial_n : N_*(X)_n \to N_*(X)_{n-1}$ is given by
\begin{equation*}
\partial_n = \sum_{i=0}^{n} (-1)^id_{i}.
\end{equation*}
The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.

It is convenient to emphasize that
\begin{equation*}
N_\bullet(X; R) = \colim_{\triangle^n \to X} N_\bullet(\triangle^n; R).
\end{equation*}

\subsection{Cubical sets}

The \textit{cube category} $\square$ is the free strict monoidal category with a \textit{bipointed object}
\begin{equation*}
\begin{tikzcd}
1 \arrow[r, bend left, "\delta^0"] \arrow[r, bend right, "\delta^1"'] & 2 \arrow[r, "\sigma"] & 1
\end{tikzcd}
\end{equation*}
such that $\sigma \circ \delta^0 = \sigma \circ \delta^1 = \mathrm{id}$. Explicitly, it contains an object $2^n$ for each non-negative integer $n$ and its morphisms are generated by the \textit{coface} and \textit{codegeneracy maps} defined by
\begin{align*}
\delta_i^\varepsilon & = \mathrm{id}_{2^{i-1}} \times \delta^\varepsilon \times \mathrm{id}_{2^{n-1-i}} \colon 2^{n-1} \to 2^n, \\
\sigma_i & = \mathrm{id}_{2^{i-1}} \times \, \sigma \times \mathrm{id}_{2^{n-i}} \colon 2^{n} \to 2^{n-1}.
\end{align*}

A \textit{cubical set} $X$ is a contravariant functor from the cube category to the category of sets and a cubical map is a natural transformation between two cubical sets. As is customary, we use the notation
\begin{equation*}
X\big( 2^n \big) = X_n \qquad X(\delta^\varepsilon_i) = d^\varepsilon_i \qquad X(\sigma_i) = s_i,
\end{equation*}
and refer to elements in the image of any $s_i$ as \textit{degenerate}.

For each $n \in \mathbb{N}$, the cubical set $\square^n$ is defined by
\begin{equation*}
\square^n_k  = \Hom_{\square} \big( 2^k, 2^n \big), \qquad 
d^\varepsilon_i(x) = x \circ \delta^\varepsilon_i, \qquad 
s_i(x) = x \circ \sigma_i,
\end{equation*}
notice that iteratively
\begin{equation*}
\square^n = \overbrace{\square^1 \times \cdots \times \square^1}^{n \text{ times }}.
\end{equation*}
We represent the non-degenerate elements of $\square^n$ as sequences $x_1 \cdots\, x_n$ with each $x_i \in \{[0], [1], [0,1]\}$. Any cubical set can be expressed as a colimit of these
\begin{equation*}
X = \colim_{\square^n \to X} \square^n.
\end{equation*}

The functor $N_\bullet$ of \textit{normalized chains} (with $R$-coefficients) is defined as follows: The chain complex $N_\bullet(\square^1)$ is simply the cellular chain complex of the interval,
isomorphic to
\begin{equation*}
\begin{tikzcd} [column sep = small, row sep = 0.1pt]
R\{[0], [1]\}  & \arrow[l] R\{[0,1]\} \\
{[1] - [0]} & \arrow[l, |->] \left[0,1\right].
\end{tikzcd}
\end{equation*}
Set
\begin{equation} \label{eq: chains on I^n}
N_\bullet(\square^n; R) = N_\bullet(\square^1; R)^{\otimes n}
\end{equation}
and define
\begin{equation*}
N_\bullet(X; R) = \colim_{\square^n \to X} N_\bullet(\square^n; R).
\end{equation*}

The functor of \textit{normalized cochains} $N^\bullet$ is defined by composing $N_\bullet$ with the linear duality functor $\Hom(-, R)$.

### 2021-05-07 steenrod.tex
Split sections into files

\section{Steenrod-Adem structures}

We now introduce an operadic formulation of a structure giving rise to Steenrod operations at every prime. It is based on \cites{steenrod47products, steenrod53symmetric, steenrod53cyclic, may70generalapproach}, and takes a viewpoint that emphasizes the integral structure needed to define them and prove their relations at every prime. For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}.

\begin{definition} \label{def: Steenrod-Adem structure}
	A \textit{Steenrod-Adem structure} on an operad $\mathcal O$ is a 
	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad
	\begin{equation*}
	\begin{tikzcd}[column sep = normal, row sep = small]
	& \mathcal R \arrow[dr, "\phi", out=0] & \\
	\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \mathcal O
	\end{tikzcd}
	\end{equation*}
	such that $\iota$ is a quasi-isomorphism and $\phi$ a morphism of operads.
\end{definition}

\begin{remark} \label{rmk: Deligne conjecture}
	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$. In this language, a choice of factorization for a Steenrod-Adem structure defines in particular a \textit{commutative multiplication}.
\end{remark}

\begin{definition}
	Let $A$ be a chain complex. A Steenrod-Adem structure on $\mathrm{End}_A$ is referred to as one on $A$. Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod} $(r, i)$-\textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
\end{definition}

\begin{remark}
	Restricting a Steenrod-Adem structure on a chain complex $A$ to a given arity $r$ corresponds to specifying a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$. This pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ introduced in \cite{may70generalapproach} Definition 2.1. Furthermore, the restriction to arity $r^2$ enhances this pair to an \textit{Adem object} as described in Definition 4.1 loc. cit.
\end{remark}

A Steenrod-Adem structure on a chain complex $A$ allows us to define operations on its $\mathbb{F}_p$-homology for every prime $p$. These operations are structurally different if $p$ is even or odd. Using the previous Remark, the definitions below recover Steenrod's original definition for the cohomology of spaces and that of Araki-Kudo-Dyer-Lashof operations for the homology of infinite loop spaces.

For the rest of this section $A$ is a chain complex equipped with a Steenrod-Adem structure.

\begin{definition}
	For any prime $p$, the $\mathbb{F}_p$-linear map
	\begin{equation*}
	D^p_i : (A \otimes \mathbb{F}_p) \to (A \otimes \mathbb{F}_p)
	\end{equation*}
	is defined by sending $a$ to the Steenrod \mbox{$(p, i)$-product} of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
\end{definition}

We notice that if $a$ is of degree $q$ then $D^p_i(a)$ is of degree $q + (p-1)q + i$.

\begin{definition}
	For any integer $s$, the \textit{Steenrod operation}
	\begin{equation*}
	P_s : H_\bullet(A; \mathbb{F}_2) \to H_{\bullet + s}(A; \mathbb{F}_2)
	\end{equation*}
	is defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_2)$ of degree $q$ to the class represented by $D^2_{s-q}(a)$.
\end{definition}

Notice that the Steenrod squares are determined by the Steenrod $(2,i)$-products with $\mathbb{F}_2$-coefficients. These binary operations are known as cup-$i$ products. In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod $\big(p, k(p-1)-\varepsilon\big)$-products for $\varepsilon \in \{0,1\}$. We can explain the appearance of these specific Steenrod products as follows. The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even an $(2t+1)(p-1) - \varepsilon$ if $q$ is odd. According to Lemma \ref{lem: Thom's theorem}, these are the only homologically non-trivial cases.

\begin{definition} \label{def: Steenrod operations at odd prime}
	For any integer $s$, the \textit{Steenrod operations}
	\begin{equation*}
	P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1)}(A; \mathbb{F}_p)
	\end{equation*}
	and
	\begin{equation*}
	\beta P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1) - 1}(A; \mathbb{F}_p)
	\end{equation*}
	are defined by sending the class represented by a cycle $a \in (A \otimes \mathbb{F}_p)$ of degree $q$ to the classes represented respectively for $\varepsilon \in\{0,1\}$ by
	\begin{equation*}
	(-1)^s \nu(q) D^p_{(2s-q)(p-1)-\varepsilon}(a)
	\end{equation*}
	where $\nu(q) = (-1)^{q(q-1)m/2}(m!)^q$ and $m = (p-1)/2$.
\end{definition}

\begin{remark}
	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq. 6.1. in \cite{steenrod53cyclic}). The notation $\beta P_s$ is motivated by the relationship of this operator and the Bockstein of the reduction $\mathbb Z \to \mathbb Z/p\mathbb Z$.
\end{remark}

Steenrod operations satisfy the Cartan and Adem relations. Below we state the subset of these relations that is most commonly used and refer to Sections 2 and 4 of \cite{may70generalapproach} for a complete list and proofs.
\begin{lemma}
	Let $A$ be equipped with a Steenrod-Adem structure. If $[\alpha], [\beta] \in H(A;\mathbb{F}_p)$ then
	\begin{equation*}
	P_s\big([\alpha] [\beta]\big) = \sum_{i+j=s} P_i\big( [\alpha] \big) P_j\big( [\beta] \big),
	\end{equation*}
	and
	\begin{itemize}
		\item If $p = 2$ and $a > 2b$
		\begin{equation*}
		P_{a}P_{b} = \sum_i {2i-a \choose a-b-i-1} P_{a+b-i}P_i,
		\end{equation*}
		\item If $p > 2$ and $a > pb$
		\begin{equation*}
		P_{a}P_{b} = \sum_i (-1)^{a+i}{pi-a \choose a-(p-1)b-i-1} P_{a+b-i}P_i.
		\end{equation*}
	\end{itemize}		
\end{lemma}

\begin{proof}
	These are proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
\end{proof}

For the even prime, proofs at the chain level of these formulae have been given in \cite{medina2020cartan,brumfiel2020cochain}. For a different operadic approach to Steenrod operations at the even prime please consult \cite{chataur2005adem-cartan}.

For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$, which we use in subsections 6.4 and 6.5.

### 2021-05-25 effective.tex
Rename to May-Steenrod operations

@@
 
-In this section we construct explicit Steenrod-Adem structures on three well know combinatorial $E_\infty$-operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-PROP $\mathcal M$ \cite{medina2020prop1}.
-We also define natural and effective Steenrod-Adem structure on the normalized cochains of any simplicial or cubical set, by describing a $U(\mathcal M)$-algebra structures on it.
+In this section we construct explicit May-Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-PROP $\mathcal M$ \cite{medina2020prop1}.
+We also define natural and effective May-Steenrod structure on the normalized cochains of any simplicial or cubical set, by describing a $U(\mathcal M)$-algebra structures on it.
 
@@
 	\end{tikzcd}
-	\caption{Summary of effective constructions: Steenrod-Adem structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural Steenrod-Adem structures on the normalized chains of simplicial and cubical sets.
+	\caption{Summary of effective constructions: May-Steenrod structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May-Steenrod structures on the normalized chains of simplicial and cubical sets.
 We are abusing notation since the maps $TR$ and $SL$ required different sign conventions.}
@@
 
-\subsection{Barratt-Eccles operad} In this subsection we effectively describe a Steenrod-Adem structure on the Barratt-Eccles operad.
+\subsection{Barratt-Eccles operad} In this subsection we effectively describe a May-Steenrod structure on the Barratt-Eccles operad.
 
@@
 	\end{equation*}
-	defines a Steenrod-Adem structure on the Barratt-Eccles operad.
+	defines a May-Steenrod structure on the Barratt-Eccles operad.
 \end{theorem}
@@
 
-In this subsection we introduce a Steenrod-Adem structures on the surjection operad.
+In this subsection we introduce a May-Steenrod structures on the surjection operad.
 There are two widely used sign conventions for this operad respectively due to McClure-Smith \cite{mcclure03cochain} and Berger-Fresse \cite{berger04combinatorial}.
-Using the Berger-Fresse convention, we can define a Steenrod-Adem structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}.
-We define an Steenrod-Adem structure on the surjection operad in a convention independent way which recovers the table reduction Steenrod-Adem structure in the Berger-Fresse case.
+Using the Berger-Fresse convention, we can define a May-Steenrod structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}.
+We define an May-Steenrod structure on the surjection operad in a convention independent way which recovers the table reduction May-Steenrod structure in the Berger-Fresse case.
 
@@
 	\end{equation*}
-	defines a Steenrod-Adem structure on the Surjection operad.
+	defines a May-Steenrod structure on the Surjection operad.
 \end{theorem}
@@
 
-We will define a Steenrod-Adem structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the Steenrod-Adem structure $\psi_{\mathcal X} : \mathcal W \to \mathcal X$ with a morphism of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact)
+We will define a May-Steenrod structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the May-Steenrod structure $\psi_{\mathcal X} : \mathcal W \to \mathcal X$ with a morphism of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact)
 \begin{equation*}
@@
 	\end{equation*}
-	defines a Steenrod-Adem structure on $U(\mathcal M)$.
+	defines a May-Steenrod structure on $U(\mathcal M)$.
 \end{theorem}
@@
 
-In this subsection we introduce a natural Steenrod-Adem structure on the normalized cochains of any simplicial set $X$.
-Since a Steenrod-Adem structure was constructed in the previous section for $U(\mathcal M)$, we only need to describe a natural $U(\mathcal M)$-algebra structure on $N^\bullet(X)$.
+In this subsection we introduce a natural May-Steenrod structure on the normalized cochains of any simplicial set $X$.
+Since a May-Steenrod structure was constructed in the previous section for $U(\mathcal M)$, we only need to describe a natural $U(\mathcal M)$-algebra structure on $N^\bullet(X)$.
 Using the linear duality functor, it suffices to construct a natural $U(\mathcal M)$-coalgebra structure on $N_\bullet(X)$ which, in turn, can be derived via a Kan extension argument from one on each $N_\bullet(\triangle^n)$.
@@
 	\end{equation*}
-	defines a natural Steenrod-Adem structure on $N^\bullet(X)$ for any simplicial set $X$.
+	defines a natural May-Steenrod structure on $N^\bullet(X)$ for any simplicial set $X$.
 \end{theorem}
@@
 
-In this subsection we introduce a natural Steenrod-Adem structure on the normalized cochains of any cubical set.
+In this subsection we introduce a natural May-Steenrod structure on the normalized cochains of any cubical set.
 It follows the structure of the previous subsection closely.
@@
 	\end{equation*}
-	defines a natural Steenrod-Adem structure on $N^\bullet(X)$ for any cubical set $X$.
+	defines a natural May-Steenrod structure on $N^\bullet(X)$ for any cubical set $X$.
 \end{theorem}

### 2021-05-25 introduction.tex
Rename to May-Steenrod operations

@@
 Section~4 is devoted to the language of operads and related structures that we use, in Section~5, to define an integral structure at the chain level inducing Steenrod operations for every prime.
-Section~6, the bulk of this work, presents effective constructions of Steenrod-Adem structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
-It also describes a natural $U(\mathcal M)$-algebra structure on the cochains of simplicial and cubical sets inducing natural Steenrod-Adem structures on them.
+Section~6, the bulk of this work, presents effective constructions of May-Steenrod structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
+It also describes a natural $U(\mathcal M)$-algebra structure on the cochains of simplicial and cubical sets inducing natural May-Steenrod structures on them.
 We end, in Section~7, with an overview of some connections of this work to important geometric and combinatorial structures, and provide an outline of future research directions.

### 2021-05-25 outlook.tex
Rename to May-Steenrod operations

@@
 In fact, an entire $E_\infty$-operad (PROP) is constructed geometrically in this way.
-We can also interpret the Steenrod-Adem structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups ---a key ingredient in Definition \ref{def: minimal cyclic resolution}--- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.
+We can also interpret the May-Steenrod structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups ---a key ingredient in Definition \ref{def: minimal cyclic resolution}--- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.
 

### 2021-05-25 steenrod.tex
Rename to May-Steenrod operations

@@
-\section{Steenrod-Adem structures}
+\section{May-Steenrod structures}
 
@@
 
-\begin{definition} \label{def: Steenrod-Adem structure}
-	A \textit{Steenrod-Adem structure} on an operad $\mathcal O$ is a 
+\begin{definition} \label{def: May-Steenrod structure}
+	A \textit{May-Steenrod structure} on an operad $\mathcal O$ is a 
 	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad
@@
 	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$.
-In this language, a choice of factorization for a Steenrod-Adem structure defines in particular a \textit{commutative multiplication}.
+In this language, a choice of factorization for a May-Steenrod structure on $\mathcal O$ defines in particular a \textit{commutative multiplication} on~$\mathcal O$.
 \end{remark}
 
-\begin{definition}
+\begin{definition} \label{def: Steenrod products}
 	Let $A$ be a chain complex.
-A Steenrod-Adem structure on $\mathrm{End}_A$ is referred to as one on $A$.
+	A May-Steenrod structure on $\mathrm{End}_A$ is referred to as one on $A$.
 	Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod} $(r, i)$-\textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
@@
 
-\begin{remark}
-	Restricting a Steenrod-Adem structure on a chain complex $A$ to a given arity $r$ corresponds to specifying a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$.
-This pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ introduced in \cite{may70generalapproach} Definition 2.1.
-Furthermore, the restriction to arity $r^2$ enhances this pair to an \textit{Adem object} as described in Definition 4.1 loc.
+Let $A$ be equipped with a May-Steenrod structure
+%$\mathcal W \to \mathcal R \to \End_A$.
+\begin{equation*}
+\begin{tikzcd}[column sep = normal, row sep = small]
+& \mathcal R \arrow[dr, "\phi", out=0] & \\
+\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \End_A.
+\end{tikzcd}
+\end{equation*}
+We can relate this structure to the language of \cite{may70generalapproach} as follows.
+The morphism $\phi$ provides $A$ with the structure of a homotopy associative (and commutative) dg algebra defined by the image in $\Hom(A^{\otimes 2}, A)$ of a representative in $\mathcal R(2)$ of a generator of its $0\th$-homology.
+Restricting $\psi$ to arity $r$ defines a map $\theta \colon W(r) \otimes A^{\otimes r} \to A$ and the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ as presented in Definitions 2.1 op.
 cit.
-\end{remark}
+Explicitly, this is the claim that $\psi(e_0) \in \End_A(r)$ is $\mathrm C_r$-homotopic to the interated product $A^{\otimes r} \to A$.
+A claim that follows from the iterated product being a representative of a generator of the $0\th$-homology of $\mathrm R(r)$ and $\iota$ being a quasi-isomorphism of $\mathrm C$-modules.
+Furthermore, for $r$ equal to a prime $p$, tensoring the integers with $\F_p$ makes the pair $(A, \theta)$ an object in May's category $\mathfrak{C}(p, \infty)$.
+For elements in this category Definition 2.2 op. cit., reviewed below, defines operations on the mod-$p$ homology of $A$.
+In particular, if $A$ is given by the cochains of a space these products agree with Steenrod's original definitions, and for $A$ being the chains on an infinite loop spaces, with those defined by Araki-Kudo and Dyer-Lashof.
 
-A Steenrod-Adem structure on a chain complex $A$ allows us to define operations on its $\mathbb{F}_p$-homology for every prime $p$.
-These operations are structurally different if $p$ is even or odd.
-Using the previous Remark, the definitions below recover Steenrod's original definition for the cohomology of spaces and that of Araki-Kudo-Dyer-Lashof operations for the homology of infinite loop spaces.
-
-For the rest of this section $A$ is a chain complex equipped with a Steenrod-Adem structure.
+For the rest of this section $A$ is a chain complex equipped with a May-Steenrod structure.
 
@@
 \begin{definition}
-	For any integer $s$, the \textit{Steenrod operation}
+	For any integer $s$, the \textit{May-Steenrod operation}
 	\begin{equation*}
@@
 \begin{definition} \label{def: Steenrod operations at odd prime}
-	For any integer $s$, the \textit{Steenrod operations}
+	For any integer $s$, the \textit{May-Steenrod operations}
 	\begin{equation*}
@@
 
+BEING A CARTAN OBJECT IS LIKE MORE COMPLICATED AND NOT IMMEDIATE IT SEEMS
+
 Steenrod operations satisfy the Cartan and Adem relations.
@@
 \begin{lemma}
-	Let $A$ be equipped with a Steenrod-Adem structure. If $[\alpha], [\beta] \in H(A;\mathbb{F}_p)$ then
+	Let $A$ be equipped with a May-Steenrod structure. If $[\alpha], [\beta] \in H(A;\mathbb{F}_p)$ then
 	\begin{equation*}
@@
 \begin{proof}
-	These are proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
+	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(p, \infty)$.
+	Furthermore, this pair is in May's language both a Cartan and an Adem object, meaning that
+
+	and the claim of this lemma is proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
 \end{proof}

### 2021-06-10 main.tex
Rename to May-Steenrod operations
Add labels to sec's, fix adem/cartan claims, add keyword: operads

@@
 \documentclass[A4]{amsart}
-
 \usepackage{amsmath, amssymb, amsfonts}
@@
 
+% enviorenments
 \newtheorem{theorem}{Theorem}
@@
 
+% sets
 \newcommand{\Z}{\mathbb{Z}}
+\newcommand{\F}{\mathbb{F}}
+
+% funtors and operators
 \newcommand{\Hom}{\mathrm{Hom}}
@@
 
-\include{figures}
+% other
+\renewcommand{\th}{^{\mathrm{th}}}
 
+% paper shape
 \setlength{\textwidth}{\paperwidth}
@@
 
+\include{figures}
+
 \begin{document}
 
-\title{Chain level Steenrod operations}
+\title{Cochain level May-Steenrod operations}
 
@@
 \subjclass[2010]{55S05, 55U05, 55S10, 55S12; 55-04, 55U15, 55S15}
-\keywords{Steenrod operations, Dyer-Lashof operations, simplicial cochains, cubical cochains}
+\keywords{Steenrod operations, Dyer-Lashof operations, operads, simplicial cochains, cubical cochains}
 
@@
 In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having a definition of Steenrod operations that can be effectively computed in specific examples has become a key issue.
-This article provides such definition, at all primes, for well known $E_\infty$-algebras including the cochains of spaces expressed via simplicial or cubical cell structures.
+This article provides such definition, at all primes, using the operadic viewpoint of May for well known $E_\infty$-algebras including the cochains of spaces expressed via simplicial or cubical cell structures.
 \end{abstract}

### 2021-06-10 steenrod.tex
Add labels to sec's, fix adem/cartan claims, add keyword: operads

@@
-\section{May-Steenrod structures}
+\section{May-Steenrod structures} \label{s:steenrod}
 
@@
 
-BEING A CARTAN OBJECT IS LIKE MORE COMPLICATED AND NOT IMMEDIATE IT SEEMS
-
 Steenrod operations satisfy the Cartan and Adem relations.
@@
 	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(p, \infty)$.
-	Furthermore, this pair is in May's language both a Cartan and an Adem object, meaning that
-
-	and the claim of this lemma is proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
+	Furthermore, this pair is in May's language both a Cartan and an Adem object, and the claim of this lemma is proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
 \end{proof}

### 2021-06-30 main.tex
Improve abstract

@@
 	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander-Whitney's chain approximation to the diagonal.
-Later, following a viewpoint developed by Adem, Steenrod defined his homonymous operations for all primes using the homology of symmetric groups.
-This approach enhanced the conceptual understanding of the operations and allowed for many advances but lacked the concreteness of their definition at~$2$.
+He later defined his homonymous operations for all primes using the homology of symmetric groups.
+This approach enhanced the conceptual understanding of the operations and allowed for many advances, but lacked the concreteness of their definition at the even prime.
 In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having a definition of Steenrod operations that can be effectively computed in specific examples has become a key issue.
-This article provides such definition, at all primes, using the operadic viewpoint of May for well known $E_\infty$-algebras including the cochains of spaces expressed via simplicial or cubical cell structures.
+This article provides such definition at all primes using the operadic viewpoint of May for certain well known $E_\infty$-algebras, including the cochains of spaces expressed via simplicial or cubical cell structures, for which we also describe multioperations generalizing the cup-$i$ products of Steenrod.
 \end{abstract}

### 2021-06-30 effective.tex
Add labels to sec's, fix adem/cartan claims, add keyword: operads
Version before consistent line breaks

@@
-\section{Effective constructions} \label{s:effective constructions}
+\section{Effective constructions} \label{s:effective}
 
-In this section we construct explicit May-Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-PROP $\mathcal M$ \cite{medina2020prop1}.
+In this section we construct explicit May-Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-prop $\mathcal M$ \cite{medina2020prop1}.
 We also define natural and effective May-Steenrod structure on the normalized cochains of any simplicial or cubical set, by describing a $U(\mathcal M)$-algebra structures on it.
@@
 
-\subsection{The finitely presented $E_\infty$-PROP $\mathcal M$}
+\subsection{The finitely presented $E_\infty$-prop $\mathcal M$}
 
-We start by reviewing the finitely presented $E_\infty$-PROP introduced in \cite{medina2020prop1}. Let $\mathcal M$ be the PROP generated by 
+We start by reviewing the finitely presented $E_\infty$-prop introduced in \cite{medina2020prop1}. Let $\mathcal M$ be the prop generated by 
 \begin{equation*}

### 2021-06-30 introduction.tex
Version before consistent line breaks

@@
-\section{Introduction}
+\section{Introduction} \label{s:introduction}
 
@@
 The reason is that, given the representability of the cohomology functor, these operations together with the Bockstein homomorphism can be used to give a complete description of the algebraic structure naturally present on the mop-$p$ \mbox{cohomology} algebra of spaces.
-For the even prime, Steenrod squares were introduced in \cite{steenrod47products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander-Whitney's chain approximation to the diagonal.
-Later, for odd primes,	their definition was given non-effectively using arguments based on the mod-$p$ homology of symmetric groups \cites{steenrod53symmetric, steenrod53cyclic, steenrod62operations}.
-This viewpoint enhanced the conceptual understanding of the operations and allowed for many advances \cites{adem1952iteration, milnor1958dual, adams1995stable}, but lacked the concreteness of their definition at~$2$.
+For the even prime, Steenrod squares were introduced in \cite{steenrod47products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander-Whitney's chain approximation to the diagonal, the so called cup-$i$ products.
+Later, for odd primes, their definition was given non-effectively using arguments based on the mod $p$ homology of symmetric groups \cites{steenrod53symmetric, steenrod53cyclic, steenrod62operations}.
+This viewpoint enhanced the conceptual understanding of the operations and allowed for many advances \cites{adem1952iteration, milnor1958dual, adams1995stable}, but lacked the concreteness of their definition at the even prime.
+The purpose of this paper is to fill this gap in the literature, introducing effective descriptions of multioperations at the cochain level generalizing Steenrod's cup-$i$ products defining Steenrod operations at all primes.
 
 In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- the need to have a definition of Steenrod operations that can be effectively computed in specific examples has gain considerable importance.
-In Applied Topology, the use of Persistence Homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage,chan2013topology,lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of Persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
-In Quantum Field Theory, the BRST formalism \cites{BRS,Tyutin,KugoOjima} introduced cohomology to deal with gauge symmetries, and was further developed in the BV-formalism \cite{BV}.
-Master equations, introduced there, are also needed for the construction of viable actions in String Field Theory \cite{Zwiebach}, where fundamental chains are involved.
+In Applied Topology, the use of Persistence Homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage,chan2013topology,lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
 The chain level viewpoint for the study of homology operations was brought to the forefront by String Topology \cite{Sullivanoverview}, and as served as a major driver of innovation \cites{TZ, hoch2}.
-The cubical viewpoint appears in physics naturally in the theory of renomalization \cite{KreimerCubical}; while Steenrod cup-$i$ products are utilized in the construction of effective actions of gapped systems \cite{kapustin2017fermionic}.
-This connection with physics motivated the development of effective versions of spin bordism \cites{brumfiel2016pontrjagin, brumfiel2018pontrjagin}, which prominently feature Steenrod cup-$i$ products and Cartan coboundaries.
+In Lattice Field Theory, cup-$i$ products are used in the construction of effective actions \cite{gaiotto2016spin, bhardwaj2017state, kapustin2017fermionic}, and this connection with physics motivated the development of effective versions of spin bordism \cites{brumfiel2016pontrjagin, brumfiel2018pontrjagin} prominently featuring higher derived structures at the cochain level \cite{medina2020cartan, medina2020adem}.
 
-As in \cite{may70generalapproach}, we take a more general approach to Steenrod operations that also includes Araki-Kudo-Dyer-Lashof operations on the mod-$p$ homology of infinite loop spaces \cites{araki56squaring, dyer62lashof}.
-We use the language of operads \cite{may72geometry}  to describe at the chain level the integral structure required to define (co)homology operations at every prime.
-We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod-$p$ homology of their algebras; these are the Barratt-Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
-Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical products generalizing the \mbox{cup-$i$} products of Steenrod to every prime.
+Following \cite{may70generalapproach}, we take a more general approach to Steenrod operations that also includes Araki-Kudo-Dyer-Lashof operations on the mod $p$ homology of infinite loop spaces \cites{araki56squaring, dyer62lashof}.
+We use the language of operads \cite{may72geometry} to describe at the (co)chain level the integral structure required to define (co)homology operations at every prime.
+We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod $p$ homology of their algebras; these are the Barratt-Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
+Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical multioperations generalizing the \mbox{cup-$i$} products of Steenrod to every prime.
 An alternative approach based on the Eilenberg-Zilber contraction can be found in \cite{gonzalez2005hpt}.
-Up to now, although its existence is warrantied by acyclic model argument \cite{eilenberg1953acyclic}, no $E_\infty$-structure was known on the cochains of cubical sets.
-Using an $E_\infty$-bialgebra structure on the chains of the interval we effectively construct an $U(\mathcal M)$-algebra structure on them, and as a consequence provide a description of Steenrod products for cochains of cubical sets as well.
-The $p=2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2018axiomatic}, and in the cubical setting to the cup-$i$ products of  Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l-Pilarczy \cite{pilarczyk2016cubical}.
-
-We also contribute to a growing body of open source software \cites{manero2020effective, pilarczyk2015contraction, sagemath} resulting from an effort to rewrite key concepts from Homotopy Theory in effective forms.
-Uses in Applied Topology are motivating some of this work \cite{tauzin2020giottotda}, but the impetus also comes from Voevodsky's program for a comprehensive, computational foundation of mathematics based on the homotopical interpretation of type theory \cite{bauer2017hott}.
-A \texttt{Python} implementation of all the constructions in this article can be found in A.M-M.'s website.\footnote{Currently hosted at \url{https://www.medina-mardones.com/}}
+The $p = 2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2018axiomatic}, and in the cubical setting to the cup-$i$ products of Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l-Pilarczy \cite{pilarczyk2016cubical}.
+A \texttt{Python} implementation of all the constructions in this article can be found in the specialized computer algebra system \texttt{ComCH} \cite{medina2021computer}.
 
 An outline of the article is described next.
-We first introduce, in Section~2, the conventions we will follow regarding chain complexes, simplicial sets and cubical sets.
-Then, in Section~3, we review the key notions from group homology we will use for cyclic and symmetric groups.
-Section~4 is devoted to the language of operads and related structures that we use, in Section~5, to define an integral structure at the chain level inducing Steenrod operations for every prime.
-Section~6, the bulk of this work, presents effective constructions of May-Steenrod structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
+We first introduce, in Section~\ref{s:preliminaries}, the conventions we will follow regarding chain complexes, simplicial sets and cubical sets.
+Then, in Section~\ref{s:goup homology}, we review the key notions from group homology we will use for cyclic and symmetric groups.
+Section~\ref{s:operads} is devoted to the language of operads and related structures that we use, in Section~\ref{s:steenrod}, to define an integral structure at the (co)chain level inducing Steenrod operations for every prime.
+Section~\ref{s:effective}, the bulk of this work, presents effective constructions of May-Steenrod structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
 It also describes a natural $U(\mathcal M)$-algebra structure on the cochains of simplicial and cubical sets inducing natural May-Steenrod structures on them.
-We end, in Section~7, with an overview of some connections of this work to important geometric and combinatorial structures, and provide an outline of future research directions.
+We end, in Section~\ref{s:outlook}, with an overview of some connections of this work to certain geometric and combinatorial structures and provide an outline of future research directions.
 
@@
 
-The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Greg Brumfiel, Dev Sinha, Jens Kjaer, Calista Bernard, and Andy Putnam, for insightful discussions and valuable comments, and to the anonymous referee for many helpful suggestions.
+The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Dev Sinha, Greg Brumfiel, Jens Kjaer, Calista Bernard, and Andy Putnam for insightful discussions, and to the anonymous referee for many keen observations and helpful suggestions.

### 2021-06-30 main.tex
Version before consistent line breaks

@@
 This approach enhanced the conceptual understanding of the operations and allowed for many advances, but lacked the concreteness of their definition at the even prime.
-In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having a definition of Steenrod operations that can be effectively computed in specific examples has become a key issue.
-This article provides such definition at all primes using the operadic viewpoint of May for certain well known $E_\infty$-algebras, including the cochains of spaces expressed via simplicial or cubical cell structures, for which we also describe multioperations generalizing the cup-$i$ products of Steenrod.
+In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having definitions of Steenrod operations that can be effectively computed in specific examples has become a key issue.
+This article provides such definitions at all primes using the operadic viewpoint of May, defining multioperations that generalize the cup-$i$ products of Steenrod on the simplicial and cubical cochains of spaces.
 \end{abstract}

### 2021-06-30 operads.tex
Add labels to sec's, fix adem/cartan claims, add keyword: operads
Version before consistent line breaks

@@
-\section{$\Gamma$-modules, operads and PROPs}
+\section{$\Gamma$-modules, operads and props} \label{s:operads}
 
@@
 
-\subsection{Operads and PROPs}
+\subsection{Operads and props}
 
-Operads an PROPs are respectively $\mathrm{S}$-modules and \mbox{$\mathrm{S}$-bimodules} enriched with further compositional structure.
-These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a PROP.
+Operads an props are respectively $\mathrm{S}$-modules and \mbox{$\mathrm{S}$-bimodules} enriched with further compositional structure.
+These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a prop.
 
@@
 \end{equation*}
-satisfying suitable associativity, equivariance and unitality conditions. A PROP $\mathcal P$ is an $\mathrm{S}$-bimodule together with two types of compositions; horizontal
+satisfying suitable associativity, equivariance and unitality conditions. A prop $\mathcal P$ is an $\mathrm{S}$-bimodule together with two types of compositions; horizontal
 \begin{equation*}
@@
 
-We have already mentioned that for any chain complex $A$, the $\mathrm{S}$-module $\End_A$ is naturally an operad and the $\mathrm{S}$-bimodule $\End_A^A$ is naturally a PROP.
+We have already mentioned that for any chain complex $A$, the $\mathrm{S}$-module $\End_A$ is naturally an operad and the $\mathrm{S}$-bimodule $\End_A^A$ is naturally a prop.
 We add that considering $\End^A$ as an $\mathrm{S}$-module, its compositional structure also defines an operad structure on it.
 
-We remark that the compositional structure of a PROP $\mathcal P$ restricts to operad structures on $U_1(\mathcal P)$ and $U_2(\mathcal P)$.
+We remark that the compositional structure of a prop $\mathcal P$ restricts to operad structures on $U_1(\mathcal P)$ and $U_2(\mathcal P)$.
 
@@
 \begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}]
-	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a PROP $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
+	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a prop $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
 \end{definition}
@@
 
-A morphisms of operads or of PROPs is simply a morphisms of their underlying $\mathrm{S}$-modules or $\mathrm{S}$-bimodules preserving the respective compositional structures.
+A morphisms of operads or of props is simply a morphisms of their underlying $\mathrm{S}$-modules or $\mathrm{S}$-bimodules preserving the respective compositional structures.
 
-Given a chain complex $A$, an operad $\mathcal O$ and a PROP $\mathcal P$.
+Given a chain complex $A$, an operad $\mathcal O$ and a prop $\mathcal P$.
 An $\mathcal O$-\textit{algebra} (resp.
 $\mathcal O$-\textit{coalgebra}) structure on $A$ is an operad morphism $\mathcal O \to \End_A$ (resp.
-$\mathcal O \to \End^A$), and a $\mathcal P$-\textit{bialgebra} structure on $A$ is a PROP morphism $\mathcal P \to \End_A^A$.
+$\mathcal O \to \End^A$), and a $\mathcal P$-\textit{bialgebra} structure on $A$ is a prop morphism $\mathcal P \to \End_A^A$.
 

### 2021-06-30 steenrod.tex
Version before consistent line breaks

@@
 
-We now introduce an operadic formulation of a structure giving rise to Steenrod operations at every prime.
-It is based on \cites{steenrod47products, steenrod53symmetric, steenrod53cyclic, may70generalapproach}, and takes a viewpoint that emphasizes the integral structure needed to define them and prove their relations at every prime.
+We now introduce an operadic formulation of a structure giving rise to Steenrod operations.
+It is based on \cites{steenrod47products, steenrod53symmetric, steenrod53cyclic, may70generalapproach} and emphasizes the integral structure needed to define them at every prime.
 For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}.
@@
 	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$.
-In this language, a choice of factorization for a May-Steenrod structure on $\mathcal O$ defines in particular a \textit{commutative multiplication} on~$\mathcal O$.
+In this language, a choice of factorization $\phi \circ \iota$ of a May-Steenrod structure on $\mathcal O$ endows it with a \textit{commutative multiplication} $\phi$.
 \end{remark}
@@
 Let $A$ be equipped with a May-Steenrod structure
-%$\mathcal W \to \mathcal R \to \End_A$.
 \begin{equation*}
@@
 \end{equation*}
-We can relate this structure to the language of \cite{may70generalapproach} as follows.
-The morphism $\phi$ provides $A$ with the structure of a homotopy associative (and commutative) dg algebra defined by the image in $\Hom(A^{\otimes 2}, A)$ of a representative in $\mathcal R(2)$ of a generator of its $0\th$-homology.
+We can relate this structure on $A$ to those considered by May in \cite{may70generalapproach} as follows.
+The morphism $\phi$ provides $A$ with the structure of a homotopy associative algebra defined by the image in $\Hom(A^{\otimes 2}, A)$ of a representative in $\mathcal R(2)$ of a generator of its $0\th$-homology.
 Restricting $\psi$ to arity $r$ defines a map $\theta \colon W(r) \otimes A^{\otimes r} \to A$ and the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ as presented in Definitions 2.1 op.
@@
 Furthermore, for $r$ equal to a prime $p$, tensoring the integers with $\F_p$ makes the pair $(A, \theta)$ an object in May's category $\mathfrak{C}(p, \infty)$.
-For elements in this category Definition 2.2 op. cit., reviewed below, defines operations on the mod-$p$ homology of $A$.
+For any object $(A, \theta)$ in this category, Definition 2.2 op. cit. defines operations on the mod-$p$ homology of $A$, a construction we review below.
 In particular, if $A$ is given by the cochains of a space these products agree with Steenrod's original definitions, and for $A$ being the chains on an infinite loop spaces, with those defined by Araki-Kudo and Dyer-Lashof.
@@
 \begin{definition}
-	For any integer $s$, the \textit{May-Steenrod operation}
+	For any integer $s$, the \textit{Steenrod operation}
 	\begin{equation*}
@@
 \begin{definition} \label{def: Steenrod operations at odd prime}
-	For any integer $s$, the \textit{May-Steenrod operations}
+	For any integer $s$, the \textit{Steenrod operations}
 	\begin{equation*}

### 2021-07-06 referee_reply.tex
Version sent to the referee

\documentclass{article}
\usepackage{amsmath, amsfonts}
\usepackage{csquotes}
\usepackage[a4paper, total={6.5in, 9in}]{geometry}

% sets
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}

% funtors and operators
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\End}{\mathrm{End}}

% other
\renewcommand{\th}{^{\mathrm{th}}}

\begin{document}
	\title{Referee reply for ``Chain level Steenrod operations"}
	\date{\today}
	\maketitle

	We begin by thanking the referee for their careful reading and many valuable suggestions.
	Below we include a point-by-point reply to the report.

	\section{Points raised by the referee}

	\begin{enumerate}
		\item Thank you for pointing this typo.
		We have fixed it and many other similar mistakes.
		\item We have followed all the suggestions presented in this point.
		Explicitly,
		\begin{enumerate}
			\item Change the title from ``Chain level Steenrod operations" to ``Cochain level May-Steenrod operations".
			\item Rename ``Steenrod-Adem structures" to ``May-Steenrod structures''.
			\item Add a paragraph below Definition 7 explaining in more detail the relationship between our notion of May-Steenrod structure and those considered by May in his ``A general algebraic approach to Steenrod operations''.
		\end{enumerate}
		\item
		\begin{enumerate}
			\item We greatly expanded the discussion of Adem and Cartan relations, making explicit their dependence on the proofs by May.
			We have also separated their treatment.
			The Adem relations are a consequence of the fact that a May-Steenrod structure demands a factorization with the second factor a morphism of operads.
			The (internal) Cartan relations require some compatibility with the coalgebra structure on the minimal resolution $\mathcal W$.
			Something that was missing in the previous version of this paper and that we have now corrected by introducing the notion of a ``comultiplicative May-Steenrod structure''.
			\item Add Remark 17 explaining that our map $\mathcal W \to \mathcal E$ factors through the (unreduced) bar resolution of $\mathrm C$, with the second map in the factorization induced from the chosen inclusions $\iota \colon \mathrm C_r \to \mathrm S_r$.
		\end{enumerate}
	\end{enumerate}

	\section{Other changes}
	\begin{enumerate}
		\item We have removed the appendix containing two proofs and a sketch of a third one.
		Specifically, we have moved the proof of Theorem 15 and 24 from the appendix to right below their statement, and replaced the sketch of proof of Proposition 28 with a reference to a complete proof.
		\item To motivate the consideration of the cubical viewpoint, we have included a paragraph in the introduction mentioning Baues' cubical reformulation of Adams' cobar construction.
		This implies that the constructions of this paper provides explicit descriptions of Steenrod operations on the cobar construction of chains of (reduced) simplicial sets
	\end{enumerate}
\end{document}

### 2021-07-06 effective.tex
Version sent to the referee

@@
 
-In this section we construct explicit May-Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-prop $\mathcal M$ \cite{medina2020prop1}.
-We also define natural and effective May-Steenrod structure on the normalized cochains of any simplicial or cubical set, by describing a $U(\mathcal M)$-algebra structures on it.
+In this section we construct explicit May-Steenrod structures on three well know combinatorial $E_\infty$ operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$ prop $\mathcal M$ introduced in \cite{medina2020prop1}.
+We also define natural and effective May-Steenrod structure on the normalized cochains of any simplicial or cubical set using that these are algebras over the operad $U(\mathcal M)$.
 
@@
 	\caption{Summary of effective constructions: May-Steenrod structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May-Steenrod structures on the normalized chains of simplicial and cubical sets.
-We are abusing notation since the maps $TR$ and $SL$ required different sign conventions.}
+We remark that the maps $TR$ and $SL$ required different sign conventions.}
 	\label{fig: bigsummary}
@@
 \begin{definition} \label{def: Steenrod-Adem on Barratt-Eccles}
-	For every $r \geq 0$, let $\psi_{\mathcal E}(r) : \mathcal W(r) \to \mathcal E(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined on basis elements by 
+	For every $r \geq 0$, let $\psi_{\mathcal E}(r) \colon \mathcal W(r) \to \mathcal E(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined on basis elements by 
 	\begin{equation*}
@@
 \begin{proof}
-	This theorem follows from a computation which we defer to the appendix.
+	Since $\mathcal X$ is an $E_\infty$ operad, we simply need to prove that the $\Z[\mathrm{C}_r]$-linear map
+	\begin{equation*}
+	\psi_{\mathcal E}(r) \colon \mathcal W(r) \to \mathcal E(r)
+	\end{equation*}
+	is a chain map for every $r \geq 0$.
+	We simplify notation and write $\psi$ instead of $\psi_{\mathcal E}(r)$. To show $\psi$ is a chain map we proceed by induction.
+	Notice that
+	\begin{equation*}
+	\psi(\partial e_0) = 0 = \partial \psi(e_0)
+	\end{equation*}
+	and assume $\psi(\partial e_{k-1}) = \partial \psi(e_{k-1})$. If $k = 2n$ we have
+	\begin{align*}
+	\partial \psi(e_{2n}) & = 
+	\partial \sum_{r_1, \dots, r_n} 
+	\big(\rho^0, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
+	\partial \sum_{r_2, \dots, r_n} \sum_{r_1 = 0}^{p-1}
+	\big(\rho^0, \rho^{r_1} \, (\rho^0, \rho^{1}, \dots, \rho^{r_n-r_1}, \rho^{r_n - r_1 +1}) \big) \\ & =
+	\partial \sum_{r_2, \dots, r_n}
+	\big(\rho^0, N\, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1}) \big) \\ & =
+	\sum_{r_2, \dots, r_n}
+	N\, \big( \rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n + 1} \big) \\ & -
+	\sum_{r_2, \dots, r_n}
+	\big(\rho^0, \partial \, N \, (\rho^{0}, \rho^{1}, \dots, \rho^{r_n}, \rho^{r_n+1}) \big) \\ & =
+	N \psi(e_{2n-1}) - (\rho^0, \partial N \psi (e_{2n-1})) \\ & =
+	\psi(N e_{2n-1}) - (\rho^0, \psi (\partial N e_{2n-1})) \\ & =
+	\psi(\partial e_{2n}) - (\rho^0, \psi (\partial^2 e_{2n})) \\ & =
+	\psi(\partial e_{2n}).
+	\end{align*}
+	If $k = 2n+1$ we have
+	\begin{align*}
+	\partial \psi(e_{2n+1}) & = 
+	\partial \sum_{r_1, \dots, r_n} 
+	\big(\rho^0, \rho^1, \rho^{r_1}, \rho^{r_1+1}, \dots, \rho^{r_n}, \rho^{r_n+1} \big)  \\ & =
+	\partial \sum_{r_1, \dots, r_n}
+	\big(\rho^0, \rho^{1} \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
+	\partial \sum_{r_1, \dots, r_n}
+	\big(\rho^0, T\, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
+	\sum_{r_1, \dots, r_n}
+	T \, \big( \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n} \big) \\ & -
+	\sum_{r_1, \dots, r_n}
+	\big(\rho^0, \partial \, T \, (\rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) \big) \\ & =
+	T \psi(e_{2n}) - (\rho^0, \partial T \psi (e_{2n})) \\ & =
+	\psi(T e_{2n}) - (\rho^0, \psi (\partial T e_{2n})) \\ & =
+	\psi(\partial e_{2n+1}) - (\rho^0, \psi (\partial^2 e_{2n+1})) \\ & =
+	\psi(\partial e_{2n+1})
+	\end{align*}
+	where for the third equality we used that for any $r_1, \dots, r_n$
+	\begin{equation*}
+	(\rho^0, \rho^0, \rho^{r_1-1}, \rho^{r_1}, \dots, \rho^{r_n - 1}, \rho^{r_n}) = 0.
+	\end{equation*}
+	This map is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0)$ represents a generator of the homology.
 \end{proof}
@@
 \begin{remark}
-	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota : \mathrm C_r \to \mathrm S_r$ induces a simplicial map $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ which extends to a quasi-isomorphism of $\mathrm C$-modules
+	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota \colon \mathrm C_r \to \mathrm S_r$ induces both; a simplicial inclusion $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ and one of $\mathrm C$-modules
 	\begin{equation*}
-	N_\bullet E(\iota) : N_\bullet E(\mathrm C) \to N_\bullet E(\mathrm S) = \mathcal E,
+	N_\bullet E(\iota) \colon N_\bullet E(\mathrm C) \to N_\bullet E(\mathrm S) = \mathcal E.
 	\end{equation*}
-	factoring
+	We remark that the image of our map $\psi_{\mathcal E}$ lies in the subcomplex $N_\bullet E(\mathrm C)$, so the map $\psi_{\mathcal E}$ factors as
 	\begin{equation*}
-	\psi_{\mathcal E} :
+	\psi_{\mathcal E} \colon
 	\begin{tikzcd}
-	\mathcal W \arrow[r, "\phi_{\mathrm C}"] &[-3pt] N_\bullet E(\mathrm C) \arrow[r, "N_\bullet E(\iota)"] &[5pt] \mathcal E.
+	\mathcal W \arrow[r] &[-3pt] N_\bullet E(\mathrm C) \arrow[r, "N_\bullet E(\iota)"] &[5pt] \mathcal E.
 	\end{tikzcd}
@@
 We only describe the McClure-Smith convention since we refer to it in subsequent sections.
-The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s : \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top dimensional generator in the chain complex
+The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top dimensional generator in the chain complex
 \begin{equation} \label{eq: surjection boundary}
@@
 
-Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure-Smith to prove $\mathcal X$ is an $E_\infty$-operad and whose introduction is credited to Benson \cite{benson1998rep}.
-Let the maps $i,\ p$ and $s$ be defined on basis elements, represented by sequences, as follows: $i : \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p : \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s : \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
-with a 1, then the new sequence is degenerate so $s$ takes it to $0$. These maps satisfy
+Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure-Smith to prove $\mathcal X$ is an $E_\infty$ operad and whose introduction is credited to Benson \cite{benson1998rep}.
+Let the maps $i,\ p$ and $s$ be defined on basis elements, represented by sequences, as follows: $i \colon \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p \colon \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurrence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s \colon \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
+with a 1, then the new sequence is degenerate so $s$ takes it to $0$.
+These maps satisfy
 \begin{equation*}
@@
 \end{equation*}
-These maps define a contraction of $\mathcal X(r)$ onto $\mathcal X(1) \cong \Z$ with homotopy $h = s + i\, s\, p + \cdots + i^{r-1} s\, p^{r-1}$, satisfying
+The compositions $i^{r-1}$ and $s^{r-1}$ define a contraction of $\mathcal X(r)$ onto $\mathcal X(1) \cong \Z$ with homotopy
 \begin{equation*}
+h = s + i\, s\, p + \cdots + i^{r-1} s\, p^{r-1},
+\end{equation*}
+i.e., they satisfy
+\begin{equation*}
+p^{r-1} i^{r-1} = \mathrm{id}
+\qquad \text{ and } \qquad
 \partial h + h \partial = \mathrm{id} - i^{r-1}\,p^{r-1}.
@@
 \begin{definition} \label{def: Steenrod-Adem on surjection}
-	For every $r \geq 0$, let $\psi_{\mathcal X}(r) : \mathcal W(r) \to \mathcal X(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined recursively on basis elements by
+	For every $r \geq 0$, let $\psi_{\mathcal X}(r) \colon \mathcal W(r) \to \mathcal X(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined recursively on basis elements by
 	\begin{align*}
@@
 \begin{proof}
-	This theorem follows from a computation which we defer to the appendix.
+	Since $\mathcal X$ is an $E_\infty$ operad, we simply need to prove that the $\Z[\mathrm{C}_r]$-linear map
+	\begin{equation*}
+	\psi_{\mathcal X}(r) \colon \mathcal W(r) \to \mathcal X(r)
+	\end{equation*}
+	introduced in Definition \ref{def: Steenrod-Adem on surjection} is a chain map for every $r \geq 0$.
+We simplify notation and write $\psi$ instead of $\psi_{\mathcal X}(r)$.
+To show $\psi$ is a chain map we proceed by induction.
+Notice that
+	\begin{equation*}
+	\psi(\partial e_0) = 0 = \partial \psi(e_0)
+	\end{equation*}
+	and assume $\psi(\partial e_{n-1}) = \partial \psi(e_{n-1})$. For $n = 2m+1$ we have
+	\begin{align*}
+	\partial \psi(e_{2m+1}) 
+	& =
+	\partial\, h\, T\, \psi(e_{2m}) \big) \\
+	& =
+	T\, \psi(e_{2m}) - i^{r-1} p^{r-1}\, \psi(e_{2m}) -
+	h\, \partial\, T\, \psi(e_{2m}) \big) \\
+	& =
+	T\, \psi(e_{2m}) - 
+	h\, T\, \psi(\partial\, e_{2m}) \big) \\
+	& =
+	T\, \psi(e_{2m}) - 
+	h\, \psi(T\,N\, e_{2m-1}) \big) \\
+	& = 
+	T \psi(e_{2m}).
+	\end{align*}
+	For $n = 2m$ the proof is analogous. The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ is a generator of the homology.
 \end{proof}
@@
 
-\subsection{The finitely presented $E_\infty$-prop $\mathcal M$}
+\subsection{The $E_\infty$ prop $\mathcal M$}
 
-We start by reviewing the finitely presented $E_\infty$-prop introduced in \cite{medina2020prop1}. Let $\mathcal M$ be the prop generated by 
+We start by reviewing the finitely presented $E_\infty$ prop introduced in \cite{medina2020prop1}.
+Let $\mathcal M$ be the prop generated by 
 \begin{equation*}
@@
 
-Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$-prop in the terminology of Bordmann-Vogt \cite{boardman1973homotopy}.
-More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$-operad.
+Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$ prop as introduced in Definition~\ref{def: e-infinity operad and prop}.
+More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$ operad.
 For the remainder of this article we write $U(\mathcal M)$ instead of $U_2(\mathcal M)$.
 
-We will define a May-Steenrod structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the May-Steenrod structure $\psi_{\mathcal X} : \mathcal W \to \mathcal X$ with a morphism of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact)
-\begin{equation*}
-SL \colon \mathcal X \to U(\mathcal M)
-\end{equation*}
-that we now define. Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element
+We will define a May-Steenrod structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the May-Steenrod structure $\psi_{\mathcal X} \colon \mathcal W \to \mathcal X$ with a morphism $SL \colon \mathcal X \to U(\mathcal M)$ of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact) that we now define.
+Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element represented by the connected $(1,r)$-graph
 \begin{center}
@@
 \end{equation*}
-satisfying the relations in the presentation of $\mathcal M$. For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
+satisfying the relations in the presentation of $\mathcal M$.
+For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
 (1) The counit $\epsilon \in \Hom(N_\bullet(\triangle^n), \Z)$ by
@@
 
-\begin{theorem} \label{thm: simplicial chain bialgebra}
+\begin{proposition}[\cite{medina2020prop1}] \label{prop: simplicial chain bialgebra}
 	For every $n \in \mathbb{N}$, the assignment
@@
 	\end{equation*}
-	defines a natural $\mathcal M$-bialgebra structure  on $N_\bullet(\triangle^n)$.
-\end{theorem}
+	defines a natural $\mathcal M$-bialgebra structure  on $N_\bullet(\triangle^n)$, and, through a Kan extension argument, a natural $U(\mathcal M)$-algebra structure $\phi^\triangle \colon U(\mathcal M) \to \End_{N^\bullet (X)}$ on the cochains of any simplicial set $X$.
+\end{proposition}
 
-\begin{proof}
-	This statement is proven as Theorem 4.2 in \cite{medina2020prop1}.
-\end{proof}
-
-\begin{definition}
-	Let $X$ be a simplicial set.
-Denote by $\phi^\triangle : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem \ref{thm: simplicial chain bialgebra}.
-\end{definition}
+Composing the algebra structure $\phi^\triangle$ with the May-Steenrod structure on $U(\mathcal M)$ gives a natural May-Steenrod structure on $N^\bullet(X)$.
+We record this observation in the following.
 
@@
 \begin{remark}
-	The $E_\infty$-structure we described in Theorem \ref{thm: simplicial chain bialgebra}, depending solely on three fundamental maps, recovers the coalgebra structures of McClure-Smith \cite{mcclure03cochain} and, up to signs, that of Berger-Fresse \cite{berger04combinatorial}.
+	The $E_\infty$ structure we described in Proposition~\ref{prop: simplicial chain bialgebra}, depending solely on three fundamental maps, generalizes the coalgebra structures of McClure-Smith \cite{mcclure03cochain} and Berger-Fresse \cite{berger04combinatorial}, please consult \cite{medina2020prop1} for more details.
 \end{remark}
 
+We will now give examples of how this May-Steenrod structure defines representatives of Steenrod operations for simplicial cochains.
+For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$ for Steenrod operations.
+
 \begin{example}
-	Let us consider the prime $2$. The value $P^1(x)\big([0,1,2,3,4]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^4)$ is equal to the value of $x^{\otimes 2}$ acting on
+	Let us consider the prime $2$.
+	The value $P^1(x)\big([0,1,2,3,4]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^4)$ is equal to the value of $x^{\otimes 2}$ acting on
 	\begin{align*}
@@
 \begin{example}
-	Let us consider the prime $3$. The value $\beta P^1(x)\big([0,1,2,3,4,5,6,7,8]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^8)$ is equal to the value of $x^{\otimes 3}$ acting on
+	Let us consider the prime $3$.
+	The value $\beta P^1(x)\big([0,1,2,3,4,5,6,7,8]\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\triangle^8)$ is equal to the value of $x^{\otimes 3}$ acting on
 	\begin{align*}
@@
 
-In this subsection we introduce a natural May-Steenrod structure on the normalized cochains of any cubical set.
-It follows the structure of the previous subsection closely.
+In this subsection we introduce, closely following the presentation of the previous subsection, a natural May-Steenrod structure on the normalized cochains of any cubical set.
 By the same considerations, the desired construction will follow from a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$.
@@
 
-\begin{theorem} \label{thm: cubical chain bialgebra}
+\begin{proposition}[\cite{medina2021cubical}] \label{prop: cubical chain bialgebra}
 	For every $n \in \mathbb{N}$, the assignment
@@
 	\end{equation*}
-	defines a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$.
-\end{theorem}
+	defines a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$, and, through a Kan extension argument, a natural $U(\mathcal M)$-algebra structure $\phi^\square \colon U(\mathcal M) \to \End_{N^\bullet (X)}$ on the cochains of any cubical set $X$.
+\end{proposition}
 
-\begin{proof}
-	We present a proof of this statement in the appendix.
-\end{proof}
-
-\begin{remark}
-	We saw that for simplicial sets a natural algebraic $E_\infty$-structure was determined by basic maps in the standard simplices.
-For cubical sets, one such structure is constructed by naturally extending three maps defined just on the interval.
-\end{remark}
-
-\begin{definition}
-	Let $X$ be a cubical set.
-Denote by $\phi^\square : U(\mathcal M) \to \End_{N^\bullet (X)}$ the algebra structure obtained by dualizing the coalgebra structure induced by the restrictions of the natural $\mathcal M$-bialgebras of Theorem~\ref{thm: cubical chain bialgebra}.
-\end{definition}
+Composing the algebra structure $\phi^\square$ with the May-Steenrod structure on $U(\mathcal M)$ gives a natural May-Steenrod structure on $N^\bullet(X)$.
+We record this observation in the following.
 
@@
 
+We will now give examples of how this May-Steenrod structure defines representatives of Steenrod operations for cubical cochains.
+Recall the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$ for Steenrod operations used when studying the cohomology of spaces.
+
 \begin{example}
-	Let us consider the prime $2$. The value $P^1(x)\big([01]^{4}\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\square^4)$ is equal to the value of $x^{\otimes 2}$ acting on
+	Let us consider the prime $2$.
+	The value $P^1(x)\big([01]^{4}\big)$ for a homogeneous cocycle $x$ in $N^{-3}(\square^4)$ is equal to the value of $x^{\otimes 2}$ acting on
 	\begin{align*}&
@@
 \begin{example}
-	Let us consider the prime $3$. The value of $\beta P^0(x)\big([01]^2\big)$ for a homogeneous cocycle $x$ in $N^{-1}(\square^2)$ is equal to the value of $x^{\otimes 3}$ acting on
+	Let us consider the prime $3$.
+	The value of $\beta P^0(x)\big([01]^2\big)$ for a homogeneous cocycle $x$ in $N^{-1}(\square^2)$ is equal to the value of $x^{\otimes 3}$ acting on
 	\begin{align*}

### 2021-07-06 groups.tex
Version sent to the referee

@@
 
-Fixing notation, let $\mathrm{S}_n$ be the symmetric group of $n$ elements and $\mathrm{C}_n$ be the cyclic group of order $n$ thought of as the subgroup of $\mathrm{S}_n$ generated by an element~$\rho$.
-We denote this inclusion by $\iota : \mathrm C_r \to \mathrm S_r$.
+Fixing notation, let $\mathrm{S}_r$ be the symmetric group of $r$ elements and $\mathrm{C}_r$ be the cyclic group of order $n$ thought of as the subgroup of $\mathrm{S}_r$ generated by an element~$\rho$.
+We denote this inclusion by $\iota \colon \mathrm C_r \to \mathrm S_r$.
 
-A \textit{resolution} in $\mathbf{Ch}_R$ is a quasi-isomorphism $P \to M$ with each $P_n$ a free \mbox{$R$-module}.
+A \textit{resolution} in $\mathbf{Ch}_R$ is a quasi-isomorphism $P \to M$ with each $P_r$ a free \mbox{$R$-module}.
 We will use the fact, explained in Section 6.5 of \cite{jacobson1989algebra}, that such resolutions exist for any chain complex $M$ concentrated in non-negatively degrees, in particular, for the monoidal unit $R$.
@@
 Let $\mathrm G$ be a group and $M$ an $R[\mathrm G]$-module, we define the \textit{homology of $\mathrm G$ with coefficients in $M$}, denoted $H(\mathrm G; M)$, as the homology of any chain complex $P \otimes_{R[\mathrm G]} M$ with $P \to R$ a resolution.
-We will be particularly interested in the case when $M = \mathbb F_p(q)$ is the trivial or sign $\mathbb F_p[\mathrm{S}_n]$-module depending on the parity of~$q$.
+We will be particularly interested in the case when $M = \mathbb F_p(q)$ is the trivial or sign $\mathbb F_p[\mathrm{S}_r]$-module depending on the parity of~$q$.
 
-We now review the group homology of finite cyclic groups. For any ring $R$ the elements
+We now review the group homology of finite cyclic groups.
+For any ring $R$ the elements
 \begin{equation} \label{eq: T and R definition}
@@
 \end{equation}
-in $R[\mathrm{C}_n]$ generate the ideal of annihilators of each other.
-Therefore, the chain complex $\mathcal W(n)$ concentrated in non-negative degrees with $\mathcal W(n)_d$ the free $\Z[\mathrm{C}_n]$-module generated by one element $e_d$, and differential
+in $R[\mathrm{C}_r]$ generate the ideal of annihilators of each other.
+Therefore, the chain complex of $R[\mathrm{C}_r]$-modules
+\begin{equation} \label{eq: minimal resolution}
+\begin{tikzcd} [column sep = .5cm]
+\mathcal W(r) = R[\mathrm{C}_r]\{e_0\} & \arrow[l, "\,T"'] R[\mathrm{C}_r]\{e_1\} & \arrow[l, "\,N"'] R[\mathrm{C}_r]\{e_2\} & \arrow[l, "\,T"'] \cdots
+\end{tikzcd}
+\end{equation}
+concentrated in non-negative degrees, with $\mathcal W(r)_d$ the free $R[\mathrm{C}_r]$-module generated by an element $e_d$, and differential induced from
 \begin{equation*}
@@
 \end{equation*}
-defines a resolution $\mathcal W(n) \to R$ in $\mathbf{Ch}_{R[\mathrm{C}_n]}$. It follow from a straightforward computation that for any prime $p$ and integer $q$
+defines a resolution $\mathcal W(r) \to R$ in $\mathbf{Ch}_{R[\mathrm{C}_r]}$.
+
+It follow from a straightforward computation that for any prime $p$ and integer $q$
 \begin{equation*}
@@
 
-The homology of $\mathrm{S}_n$ is harder to compute.
+The homology of $\mathrm{S}_r$ is harder to compute.
 With untwisted coefficients, the method of computation followed by several authors was to prove the injectivity of this homology into that of the infinite symmetric group and take advantage of a natural Hopf algebra structure on it.
@@
 
-In this work, we are interested in the mod-$p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite{adem2004milgram} Corollary VI.1.4, is detected by the inclusion $\iota : \mathrm{C}_p \to \mathrm{S}_p$ whose homological kernel is described next.
+In this work, we are interested in the mod $p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite[Corollary~VI.1.4]{adem2004milgram}, is detected by the inclusion $\iota \colon \mathrm{C}_p \to \mathrm{S}_p$., i.e., $\iota$ induces a surjection in mod $p$ homology.
+We now describe the kernel of this surjection.
 
 \begin{lemma} \label{lem: Thom's theorem}
-	Let $p$ be an odd prime and $q$ an integer. Consider
+	Let $p$ be an odd prime and $q$ an integer.
+	Consider
 	\begin{equation*}
-	(\iota_\ast)_n : H_n(\mathrm{C}_p; \mathbb{F}_p(q)) \to H_n(\mathrm{S}_p; \mathbb{F}_p(q))
+	(\iota_\ast)_d \colon H_d(\mathrm{C}_p; \mathbb{F}_p(q)) \to H_d(\mathrm{S}_p; \mathbb{F}_p(q))
 	\end{equation*}
@@
 	\begin{enumerate}
-		\item If $q$ is even, $(\iota_\ast)_n = 0$ unless $n = 2t(p-1)$ or $n = 2t(p-1) - 1$,
-		\item If $q$ is odd, $(\iota_\ast)_n = 0$ unless $n = (2t+1)(p-1)$ or $n = (2t+1)(p-1)-1$,
+		\item If $q$ is even, $(\iota_\ast)_d = 0$ unless $d = 2t(p-1)$ or $d = 2t(p-1) - 1$,
+		\item If $q$ is odd, $(\iota_\ast)_d = 0$ unless $d = (2t+1)(p-1)$ or $d = (2t+1)(p-1)-1$,
 	\end{enumerate}
@@
 
-In section 5 we will see how the cohomology of symmetric groups defines operations on algebras that are commutative up to coherent homotopies.
-Preparing for that, we first developed the language of $\Gamma$-modules and operads, where the integral structure defining Steenrod operations is clearly expressed.
+In section 5 we will see how the mod $p$ homology of symmetric groups defines operations on the mod $p$ homology of algebras that are commutative up to coherent homotopies.
+Preparing for that, we first developed the language of $\Gamma$-modules, operads, and props.

### 2021-07-06 introduction.tex
Version sent to the referee

@@
 In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- the need to have a definition of Steenrod operations that can be effectively computed in specific examples has gain considerable importance.
-In Applied Topology, the use of Persistence Homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage,chan2013topology,lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
+In Applied Topology, the use of persistence homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage,chan2013topology,lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
 The chain level viewpoint for the study of homology operations was brought to the forefront by String Topology \cite{Sullivanoverview}, and as served as a major driver of innovation \cites{TZ, hoch2}.
@@
 We use the language of operads \cite{may72geometry} to describe at the (co)chain level the integral structure required to define (co)homology operations at every prime.
-We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod $p$ homology of their algebras; these are the Barratt-Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
+We then describe effective constructions of this structure on three prominent models of the $E_\infty$ operad, identifying elements in them that represent Steenrod operations in the mod $p$ homology of their algebras; these are the Barratt-Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
 Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical multioperations generalizing the \mbox{cup-$i$} products of Steenrod to every prime.
 An alternative approach based on the Eilenberg-Zilber contraction can be found in \cite{gonzalez2005hpt}.
-The $p = 2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2018axiomatic}, and in the cubical setting to the cup-$i$ products of Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l-Pilarczy \cite{pilarczyk2016cubical}.
-A \texttt{Python} implementation of all the constructions in this article can be found in the specialized computer algebra system \texttt{ComCH} \cite{medina2021computer}.
+The $p = 2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2021newformulas}, and in the cubical setting to the cup-$i$ products of Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l-Pilarczy \cite{pilarczyk2016cubical}.
 
-An outline of the article is described next.
+A context where the cubical viewpoint arises naturally is the study of loop spaces.
+This is through Baues' geometric generalization of Adams' cobar construction \cite{baues1980geometry, adams1957cobar}.
+Using Baues' work, an application of the constructions presented in this paper is the explicit descriptions of Steenrod operations on the cobar construction on the coalgebra of chains of reduced simplicial sets \cite{medina2021cobar}.
+
+Emphasizing their constructive nature, an implementation of all the constructions in this article can be found in the specialized computer algebra system \texttt{ComCH} \cite{medina2021computer}.
+
+An outline of the article is presented next.
 We first introduce, in Section~\ref{s:preliminaries}, the conventions we will follow regarding chain complexes, simplicial sets and cubical sets.
-Then, in Section~\ref{s:goup homology}, we review the key notions from group homology we will use for cyclic and symmetric groups.
-Section~\ref{s:operads} is devoted to the language of operads and related structures that we use, in Section~\ref{s:steenrod}, to define an integral structure at the (co)chain level inducing Steenrod operations for every prime.
+Then, in Section~\ref{s:goup homology}, we review the key notions from group homology which we will use mainly for cyclic and symmetric groups.
+Section~\ref{s:operads} is devoted to the language of operads and related structures, which we use in Section~\ref{s:steenrod} to introduce the notion of May-Steenrod structure, an integral structure at the (co)chain level inducing Steenrod operations for every prime.
 Section~\ref{s:effective}, the bulk of this work, presents effective constructions of May-Steenrod structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
@@
 
-The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Dev Sinha, Greg Brumfiel, Jens Kjaer, Calista Bernard, and Andy Putnam for insightful discussions, and to the anonymous referee for many keen observations and helpful suggestions.
+The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Dev Sinha, Greg Brumfiel, Federico Cantero-Mor\'an, Jens Kjaer, Calista Bernard, and Andy Putnam for insightful discussions, and to the anonymous referee for many keen observations and helpful suggestions.

### 2021-07-06 main.tex
Version sent to the referee

@@
 \usepackage{graphics}
+% hyperref
 \usepackage[bookmarks=true, linktocpage=true,
@@
 }
+\usepackage[capitalize, noabbrev]{cleveref}
 \usepackage[alphabetic]{amsrefs}
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{proposition}[theorem]{Proposition}
 \theoremstyle{definition}
@@
 \author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
-\address{Laboratory for Topology and Neuroscience, École Polytechnique Fédérale de Lausanne, Switzerland}
-\address{Department of Mathematics, University of Notre Dame du Lac, Notre Dame, IN, USA}
+\address{Laboratory for Topology and Neuroscience, EPFL \and
+Department of Mathematics, University of Notre Dame}
 \email{amedinam@nd.edu}
-\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Max Plank Institute for Mathematics.}
+\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Max Plank Institute for Mathematics where part of this work developed.}
 
@@
 This approach enhanced the conceptual understanding of the operations and allowed for many advances, but lacked the concreteness of their definition at the even prime.
-In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- having definitions of Steenrod operations that can be effectively computed in specific examples has become a key issue.
-This article provides such definitions at all primes using the operadic viewpoint of May, defining multioperations that generalize the cup-$i$ products of Steenrod on the simplicial and cubical cochains of spaces.
+In recent years, thanks to the development of new applications of cohomology, having definitions of Steenrod operations that can be effectively computed in specific examples has become a key issue.
+This article provides such definitions at all primes using the operadic viewpoint of May, and defines multioperations that generalize the cup-$i$ products of Steenrod on the simplicial and cubical cochains of spaces.
 \end{abstract}
@@
 \input{outlook}
-\input{proofs}
-
-\newpage
-\appendix
-
-\bibliographystyle{alpha} 
-\bibliography{bib}
+\bibliography{bibliography}
 

### 2021-07-06 operads.tex
Version sent to the referee

@@
 contravariant) functor from $\mathrm G$ to $\mathbf{Ch}_R$.
-Right actions are more commonly used in the literature of operads so we emphasize that perspective.
-Taking inverses allows for the switch between these two conventions.
+%Right actions are more commonly used in the literature of operads so we emphasize that perspective.
+Taking inverses allows for the switch between left and right conventions.
 
@@
 \begin{definition}
-	A \textit{$\Gamma$-module} is a contravariant functor to $\mathbf{Ch}_R$ from a groupoid $\Gamma$ with objects the natural numbers and morphisms satisfying $\Gamma(r,s) = \emptyset$ for $r \neq s$.
+	A \textit{$\Gamma$-module} is a covariant functor to $\mathbf{Ch}_R$ from a groupoid $\Gamma$ with objects the natural numbers and morphisms satisfying $\Gamma(r,s) = \emptyset$ for $r \neq s$.
 	We denote the category of $\Gamma$-modules and natural transformations by $\mathbf{Ch}_R^\Gamma$.
@@
 \end{equation*}
-for every $r \in \mathbb{N}$. The inclusion $\mathrm{C}_r \to \mathrm{S}_r$ induces a forgetful functor
+for every $r \in \mathbb{N}$.
+The inclusion $\mathrm{C}_r \to \mathrm{S}_r$ induces a forgetful functor
 \begin{equation*}
@@
 
-Given an object $A$ in $\mathbf{Ch}_R$ there are two important $\Gamma$-modules associated to it; an $\mathrm{S}$-module known as \textit{endomorphism $\mathrm{S}$-module} $\End_A$, and an $\mathrm{S}^{op}$-module known as \textit{coendomorphism $\mathrm{S}$-module} $\End^A$.
+Given an object $A$ in $\mathbf{Ch}_R$ there are two important $\Gamma$-modules associated to it; an $\mathrm{S}^{op}$-module known as \textit{endomorphism $\mathrm{S}^{op}$-module} $\End_A$, and an $\mathrm{S}$-module known as \textit{coendomorphism $\mathrm{S}$-module} $\End^A$.
 These are defined by
@@
 
-Another groupoid of importance to us is $\mathrm{S} \times \mathrm{S}^{op}$.
-Contravariant functors from it to $\mathbf{Ch}_R$ are called \textit{$\mathrm{S}$-bimodules} and their functor category is denoted $\mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}}$.
-Notice that the inclusions
-define forgetful functors
+Another groupoid of importance to us is $\mathrm{S} \times \mathrm{S}^{op}$ with covariant functors from it to $\mathbf{Ch}_R$ referred to as \textit{$\mathrm{S}$-bimodules}.
+Notice that the inclusions $\mathrm{S} \to \mathrm{S} \times \mathrm{S}^{op}$ induced by $r \mapsto (r,1)$ and $r \mapsto (1,r)$ define forgetful functors
 \begin{equation*}
@@
 & \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"'] \arrow[dr, "U_2"] & \\
-\mathbf{Ch}_R^{\mathrm{S}} &  & \mathbf{Ch}_R^{\mathrm{S}^{op}},
+\mathbf{Ch}_R^{\mathrm{S}^{op}} &  & \mathbf{Ch}_R^{\mathrm{S}},
 \end{tikzcd}
 \end{equation*}
-and that for any object $A$ in $\mathbf{Ch}_R$, the canonical \textit{endomorphism bimodule}
+and that for any object $A$ in $\mathbf{Ch}_R$ the canonical \textit{endomorphism bimodule}
 \begin{equation*}
@@
 \end{equation*}
-forgets to $\End_A$ and $\End^A$.
+forgets via $U_1$ and $U_2$ to $\End_A$ and $\End^A$ respectively.
 
-Using the groupoid automorphism sending every morphisms to its inverse we can identify $\Gamma$- and $\Gamma^{op}$- modules.
-In particular, the statement claiming that the linear duality functor induces a morphism of $\mathrm{S}$-modules
+Using the groupoid automorphism sending every morphisms to its inverse we can identify $\Gamma$- and $\Gamma^{op}$-modules, and prove that the linear duality functor induces a morphism of $\mathrm{S}$-modules
 \begin{equation*}
@@
 \end{equation*}
-for every object $A$ in $\mathbf{Ch}_R$ is well defined and easily verified using this identification.
+for every object $A$ in $\mathbf{Ch}_R$.
+We will use this identification freely in what follows.
 
@@
 
+We have the following evident generalization to the context of groupoids of the resolutions introduced in \eqref{eq: minimal resolution}.
+
 \begin{definition} \label{def: minimal cyclic resolution}
-	The \textit{minimal} $E_\infty$-$\mathrm{C}$-\textit{module} $\mathcal W$ is the functor in $\mathbf{Ch}_R^\mathrm{C}$ assigning to $r$ the chain complex
+	The \textit{minimal} $E_\infty$ $\mathrm{C}$-\textit{module} $\mathcal W$ is the functor in $\mathbf{Ch}_R^\mathrm{C}$ assigning to $r$ the chain complex
 	\begin{equation*}
 	\begin{tikzcd} [column sep = .5cm]
-	R[\mathrm{C}_r] & \arrow[l, "\,T"'] R[\mathrm{C}_r] & \arrow[l, "\,N"'] R[\mathrm{C}_r] & \arrow[l, "\,T"'] \cdots
+	\mathcal W(r) = R[\mathrm{C}_r]\{e_0\} & \arrow[l, "\,T"'] R[\mathrm{C}_r]\{e_1\} & \arrow[l, "\,N"'] R[\mathrm{C}_r]\{e_2\} & \arrow[l, "\,T"'] \cdots
 	\end{tikzcd}
@@
 Operads an props are respectively $\mathrm{S}$-modules and \mbox{$\mathrm{S}$-bimodules} enriched with further compositional structure.
-These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a prop.
+These structures are best understood by abstracting the compositional structure naturally present in the coendomorphism $\mathrm{S}$-module $\End^A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a prop.
 
@@
 \end{equation*}
-satisfying suitable associativity, equivariance and unitality conditions. A prop $\mathcal P$ is an $\mathrm{S}$-bimodule together with two types of compositions; horizontal
+satisfying suitable associativity, equivariance and unitality conditions.
+A prop $\mathcal P$ is an $\mathrm{S}$-bimodule together with two types of compositions; horizontal
 \begin{equation*}
@@
 \end{equation*}
-satisfying their own versions of associativity, equivariance and unitality. For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008operads}.
+satisfying their own versions of associativity, equivariance and unitality.
+For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008operads}.
 
-We have already mentioned that for any chain complex $A$, the $\mathrm{S}$-module $\End_A$ is naturally an operad and the $\mathrm{S}$-bimodule $\End_A^A$ is naturally a prop.
-We add that considering $\End^A$ as an $\mathrm{S}$-module, its compositional structure also defines an operad structure on it.
+We add that for any prop $\mathcal P$, the compositional structure of $\mathcal P$ defines an operad structure on $U_1(\mathcal P)$ and $U_2(\mathcal P)$.
+We will use this automorphism without further notice when dealing with $\mathrm{S}^{op}$-modules.
 
-We remark that the compositional structure of a prop $\mathcal P$ restricts to operad structures on $U_1(\mathcal P)$ and $U_2(\mathcal P)$.
+We now introduce the type of operads that we are most interested in which, as we will discuss in the next section, are used to describe commutativity up to coherent homotopies.
 
-The type of operads that we are most interested in are $E_\infty$-operads which, as we will discuss in the next section, are used to describe commutativity up to coherent homotopies.
-
-\begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}]
-	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a prop $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
+\begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}] \label{def: e-infinity operad and prop}
+	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a prop $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U_2(\mathcal P)$ is an \mbox{$E_\infty$ operad}.
 \end{definition}
@@
 
-Algebras over $E_\infty$-operads are the central objects of study in this work.
-To develop intuition for them, let us consider a chain complex $A$ with an algebra structure over $\underline{R}$, thought of as an operad with all compositions corresponding to the identity map $R \to R$.
+Algebras over $E_\infty$ operads are the central objects of study in this work.
+To develop intuition for them, let us consider a chain complex $A$ with an algebra structure over the constant functor $\underline{R}$, thought of as an operad with all compositions corresponding to the identity map $R \to R$.
 The $\underline{R}$-algebra structure on $A$ is generated by a linear map $\mu \colon A \otimes A \to A$ which is (strictly) commutative and associative, and a linear map $\eta \colon R \to A$ that determines a (two-sided) unit for $\mu$.
-Since $E_\infty$-operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies.
+Since $E_\infty$ operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies.
 The two main examples to keep in mind are the cochains of spaces and the chains of infinite loops spaces.

### 2021-07-06 outlook.tex
Add labels to sec's, fix adem/cartan claims, add keyword: operads
Version sent to the referee

@@
-\section{Outlook}
+\section{Outlook} \label{s:outlook}
 
@@
 For example, \cite{Postnikov} and \cite{medina2018prop2} independently introduced equivalent geometric representations of the cup-$i$ products in terms of stabilized arc surfaces \cite{KLP} and weighted ribbon graphs respectively.
-In fact, an entire $E_\infty$-operad (PROP) is constructed geometrically in this way.
+In fact, an entire $E_\infty$ operad (prop) is constructed geometrically in this way.
 We can also interpret the May-Steenrod structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups ---a key ingredient in Definition \ref{def: minimal cyclic resolution}--- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.
@@
 In this article we have not focused on the operations that exist non-trivially for \mbox{$E_n$-algebras} with $n$ finite, see part III of \cite{may76homology}.
-A treatement close to ours for the $E_2$ case was given in \cite{Tourtchine}.
+A treatment close to ours for the $E_2$ case was given in \cite{Tourtchine}.
 Effective constructions for these Dyer-Lashof-Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang,sinha2013littledisks,berger04combinatorial,ayala2014configuration} and higher categories \cite{Bathigher, BalFiedSchwVogt, Rezkhigher}, and will appear elsewhere.

### 2021-07-06 preliminaries.tex
Add labels to sec's, fix adem/cartan claims, add keyword: operads
Version sent to the referee

@@
-\section{Preliminaries}
+\section{Preliminaries} \label{s:preliminaries}
 
-\subsection{Chain complexes}
-\label{s s:chain cpx}
+\subsection{Chain complexes} \label{s s:chain cpx}
 
@@
 We embed the category of $R$-modules as the full subcategory of $\mathbf{Ch}_R$ with objects concentrated in degree $0$.
-The endofunctor $\Hom(-, R)$ is referred to as the \textit{linear duality functor}.
-We notice that if a chain complex is concentrated in non-negative degrees then its linear dual is on non-positive ones.
+The endofunctor $\Hom(-, R)$ is referred to as \textit{linear duality}.
+We notice that if a chain complex is concentrated in non-negative degrees then its linear dual concentrates on non-positive ones.
 
@@
 The \textit{simplex category} $\triangle$ is defined to have an object $[n] = \{0, \dots, n\}$ for every $n \in \mathbb{N}$ and a morphism $[m] \to [n]$ for each order-preserving function from $[m]$ to $[n]$.
-The morphisms $\delta_i : [n-1] \to [n]$ and $\sigma_i : [n+1] \to [n]$ defined for $0 \leq i \leq n$ by
+The morphisms $\delta_i \colon [n-1] \to [n]$ and $\sigma_i \colon [n+1] \to [n]$ defined for $0 \leq i \leq n$ by
 \begin{equation*}
@@
 
-A \textit{simplicial set} $X$ is a contravariant functor from the simplex category to the category of sets and a simplicial map is a natural transformation between two simplicial sets.
+A \textit{simplicial set} $X$ is a contravariant functor from the simplex category to the category of sets, and a simplicial map is a natural transformation between two simplicial sets.
 As is customary we use the notation
@@
 \end{equation*}
-where $s(X_{n-1}) = \bigcup_{i=0}^{n-1} s_i(X_{n-1})$, and $\partial_n : N_*(X)_n \to N_*(X)_{n-1}$ is given by
+where $s(X_{n-1}) = \bigcup_{i=0}^{n-1} s_i(X_{n-1})$, and $\partial_n \colon N_\bullet(X)_n \to N_\bullet(X)_{n-1}$ is given by
 \begin{equation*}
@@
 
-A \textit{cubical set} $X$ is a contravariant functor from the cube category to the category of sets and a cubical map is a natural transformation between two cubical sets.
+A \textit{cubical set} $X$ is a contravariant functor from the cube category to the category of, sets and a cubical map is a natural transformation between two cubical sets.
 As is customary, we use the notation
@@
 d^\varepsilon_i(x) = x \circ \delta^\varepsilon_i, \qquad 
-s_i(x) = x \circ \sigma_i,
+s_i(x) = x \circ \sigma_i.
 \end{equation*}
-notice that iteratively
-\begin{equation*}
-\square^n = \overbrace{\square^1 \times \cdots \times \square^1}^{n \text{ times }}.
-\end{equation*}
-We represent the non-degenerate elements of $\square^n$ as sequences $x_1 \cdots\, x_n$ with each $x_i \in \{[0], [1], [0,1]\}$. Any cubical set can be expressed as a colimit of these
+%notice that iteratively
+%\begin{equation*}
+%\square^n = \overbrace{\square^1 \times \cdots \times \square^1}^{n \text{ times }}.
+%\end{equation*}
+We represent the non-degenerate elements of $\square^n$ as sequences $x_1 \cdots\, x_n$ with each $x_i \in \big\{[0], [1], [0,1]\big\}$.
+For example, $[0][01][1]$ represents $\delta^1 \times \mathrm{id} \times \delta^0$.
+Any cubical set can be expressed as a colimit of these
 \begin{equation*}
@@
 Set
-\begin{equation} \label{eq: chains on I^n}
+\begin{equation*}
 N_\bullet(\square^n; R) = N_\bullet(\square^1; R)^{\otimes n}
-\end{equation}
+\end{equation*}
 and define

### 2021-07-06 steenrod.tex
Version sent to the referee

@@
 
-We now introduce an operadic formulation of a structure giving rise to Steenrod operations.
-It is based on \cites{steenrod47products, steenrod53symmetric, steenrod53cyclic, may70generalapproach} and emphasizes the integral structure needed to define them at every prime.
-For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}.
+We now introduce an operadic structure giving rise to Steenrod operations based in \cite{may70generalapproach}.
+In our presentation we emphasize the integral structure needed to define them at every prime.
+For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}, and for a different operadic approach at the even prime to \cite{chataur2005adem-cartan}.
 
+Let us assume the ground ring to be $\Z$ unless stated otherwise.
 \begin{definition} \label{def: May-Steenrod structure}
 	A \textit{May-Steenrod structure} on an operad $\mathcal O$ is a 
-	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad
+	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$ operad
 	\begin{equation*}
@@
 The morphism $\phi$ provides $A$ with the structure of a homotopy associative algebra defined by the image in $\Hom(A^{\otimes 2}, A)$ of a representative in $\mathcal R(2)$ of a generator of its $0\th$-homology.
-Restricting $\psi$ to arity $r$ defines a map $\theta \colon W(r) \otimes A^{\otimes r} \to A$ and the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ as presented in Definitions 2.1 op.
+Restricting $\psi$ to arity $r$ defines a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$ and the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ as presented in Definitions 2.1 op.
 cit.
-Explicitly, this is the claim that $\psi(e_0) \in \End_A(r)$ is $\mathrm C_r$-homotopic to the interated product $A^{\otimes r} \to A$.
-A claim that follows from the iterated product being a representative of a generator of the $0\th$-homology of $\mathrm R(r)$ and $\iota$ being a quasi-isomorphism of $\mathrm C$-modules.
-Furthermore, for $r$ equal to a prime $p$, tensoring the integers with $\F_p$ makes the pair $(A, \theta)$ an object in May's category $\mathfrak{C}(p, \infty)$.
-For any object $(A, \theta)$ in this category, Definition 2.2 op. cit. defines operations on the mod-$p$ homology of $A$, a construction we review below.
+Explicitly, this pair is such that $\psi(e_0) \in \End_A(r)$ is $\mathrm C_r$-homotopic to the iterated product $A^{\otimes r} \to A$.
+A claim that follows from the iterated product being a representative of a generator of the $0\th$-homology of $\mathcal R(r)$, and $\iota$ being a quasi-isomorphism of $\mathrm C$-modules.
+Furthermore, for $r$ equal to a prime $p$, tensoring the integers with $\F_p$ makes the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
+For any object $(A, \theta)$ in this category, Definition 2.2 in \cite{may70generalapproach} defines operations on the mod $p$ homology of $A$, a construction we review below.
 In particular, if $A$ is given by the cochains of a space these products agree with Steenrod's original definitions, and for $A$ being the chains on an infinite loop spaces, with those defined by Araki-Kudo and Dyer-Lashof.
 
-For the rest of this section $A$ is a chain complex equipped with a May-Steenrod structure.
+For the rest of this section $A$ denotes a chain complex equipped with a May-Steenrod structure.
 
@@
 	\begin{equation*}
-	D^p_i : (A \otimes \mathbb{F}_p) \to (A \otimes \mathbb{F}_p)
+	D^p_i \colon (A \otimes \mathbb{F}_p) \to (A \otimes \mathbb{F}_p)
 	\end{equation*}
@@
 	\begin{equation*}
-	P_s : H_\bullet(A; \mathbb{F}_2) \to H_{\bullet + s}(A; \mathbb{F}_2)
+	P_s \colon H_\bullet(A; \mathbb{F}_2) \to H_{\bullet + s}(A; \mathbb{F}_2)
 	\end{equation*}
@@
 Notice that the Steenrod squares are determined by the Steenrod $(2,i)$-products with $\mathbb{F}_2$-coefficients.
-These binary operations are known as cup-$i$ products.
+These binary operations are known as cup-$i$ products \cite{steenrod47products, medina2021newformulas}.
 In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod $\big(p, k(p-1)-\varepsilon\big)$-products for $\varepsilon \in \{0,1\}$.
@@
 	\begin{equation*}
-	P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1)}(A; \mathbb{F}_p)
+	P_s \colon H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1)}(A; \mathbb{F}_p)
 	\end{equation*}
@@
 	\begin{equation*}
-	\beta P_s : H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1) - 1}(A; \mathbb{F}_p)
+	\beta P_s \colon H_\bullet(A; \mathbb{F}_p) \to H_{\bullet + 2s(p-1) - 1}(A; \mathbb{F}_p)
 	\end{equation*}
@@
 \begin{remark}
-	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq.
-6.1.
-in \cite{steenrod53cyclic}).
+	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq. 6.1. in \cite{steenrod53cyclic}).
 	The notation $\beta P_s$ is motivated by the relationship of this operator and the Bockstein of the reduction $\mathbb Z \to \mathbb Z/p\mathbb Z$.
@@
 
-Steenrod operations satisfy the Cartan and Adem relations.
-Below we state the subset of these relations that is most commonly used and refer to Sections 2 and 4 of \cite{may70generalapproach} for a complete list and proofs.
+Steenrod operations defined as above satisfy the so called \textit{Adem relations}.
+Below we present its most common form and refer to Theorem 4.7 in \cite{may70generalapproach} for a complete list.
+
 \begin{lemma}
-	Let $A$ be equipped with a May-Steenrod structure. If $[\alpha], [\beta] \in H(A;\mathbb{F}_p)$ then
-	\begin{equation*}
-	P_s\big([\alpha] [\beta]\big) = \sum_{i+j=s} P_i\big( [\alpha] \big) P_j\big( [\beta] \big),
-	\end{equation*}
-	and
-	\begin{itemize}
+	Let $A$ be equipped with a May-Steenrod structure.
+	Then,
+	\begin{enumerate}
 		\item If $p = 2$ and $a > 2b$
@@
 		\end{equation*}
-	\end{itemize}		
+	\end{enumerate}		
 \end{lemma}
@@
 \begin{proof}
-	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(p, \infty)$.
-	Furthermore, this pair is in May's language both a Cartan and an Adem object, and the claim of this lemma is proven as part of Corollary 2.7 and Theorem 4.7 in \cite{may70generalapproach}.
+	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
+	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\phi$ an operad map from an $E_\infty$ operad to $\End_A$, this is an \textit{Adem object} in the sense of Definition 4.1 of \cite{may70generalapproach}.
+	The statement presented here is stated and proven as part of Theorem 4.7 loc. cit.
 \end{proof}
 
-For the even prime, proofs at the chain level of these formulae have been given in \cite{medina2020cartan,brumfiel2020cochain}.
-For a different operadic approach to Steenrod operations at the even prime please consult \cite{chataur2005adem-cartan}.
+So far we have considered $\mathrm{C}$-modules, operads and related structures over the category of chain complexes.
+It is also useful to consider them over the category of coalgebras, that is to say, requiring each chain complex to be equipped with a coproduct and all structure maps to be morphisms of coalgebras.	
+As described in Definition~1.2 of \cite{may70generalapproach}, the $\mathrm{C}$-module $\mathcal W$ lifts to this category.
+A \textit{comultiplicative May-Steenrod structure} on an operad $\mathcal O$ is a morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$ operad over the category of coalgebras
+\begin{equation*}
+\begin{tikzcd}[column sep = normal, row sep = small]
+& \mathcal R \arrow[dr, "\phi", out=0] & \\
+\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \mathcal O
+\end{tikzcd}
+\end{equation*}
+such that $\iota$ is a quasi-isomorphism over the category of coalgebras and $\phi$ is a morphism of operads.
 
-For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$, which we use in subsections 6.4 and 6.5.
+Chain complexes equipped with a comultiplicative May-Steenrod structure satisfy the so called \textit{Cartan relations}.
+
+\begin{lemma}
+	Let $A$ be equipped with a comultiplicative May-Steenrod structure.
+	For any two mod $p$ homology classes $[\alpha]$ and $[\beta]$ we have
+	\begin{equation*}
+	P_s\big([\alpha] [\beta]\big) = \sum_{i+j=s} P_i\big( [\alpha] \big) P_j\big( [\beta] \big),
+	\end{equation*}
+\end{lemma}
+
+\begin{proof}
+	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
+	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\iota$ a quasi-isomorphism in the category of $\mathrm{C}$-modules over the category of coalgebras, this is a \textit{Cartan object} as defined in pag.
+161 of \cite{may70generalapproach}.
+	The statement presented here is stated in pag. 165 loc. cit.
+\end{proof}
+
+For the even prime, constructive proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{brumfiel2020cochain} and \cite{medina2020cartan}.

### 2021-07-30 steenrod.tex
Fix broken ref to medina2021adem and update bib of my papers

@@
 
-For the even prime, constructive proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{brumfiel2020cochain} and \cite{medina2020cartan}.
+For the even prime, constructive proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{medina2020adem} and \cite{medina2020cartan}.

### 2021-07-30 effective.tex
Replace May-Steenrod by May--Steenrod

@@
 
-In this section we construct explicit May-Steenrod structures on three well know combinatorial $E_\infty$ operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$ prop $\mathcal M$ introduced in \cite{medina2020prop1}.
-We also define natural and effective May-Steenrod structure on the normalized cochains of any simplicial or cubical set using that these are algebras over the operad $U(\mathcal M)$.
+In this section we construct explicit May--Steenrod structures on three well know combinatorial $E_\infty$ operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$ prop $\mathcal M$ introduced in \cite{medina2020prop1}.
+We also define natural and effective May--Steenrod structure on the normalized cochains of any simplicial or cubical set using that these are algebras over the operad $U(\mathcal M)$.
 
@@
 	\end{tikzcd}
-	\caption{Summary of effective constructions: May-Steenrod structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May-Steenrod structures on the normalized chains of simplicial and cubical sets.
+	\caption{Summary of effective constructions: May--Steenrod structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May--Steenrod structures on the normalized chains of simplicial and cubical sets.
 We remark that the maps $TR$ and $SL$ required different sign conventions.}
@@
 
-\subsection{Barratt-Eccles operad} In this subsection we effectively describe a May-Steenrod structure on the Barratt-Eccles operad.
+\subsection{Barratt-Eccles operad} In this subsection we effectively describe a May--Steenrod structure on the Barratt-Eccles operad.
 
@@
 	\end{equation*}
-	defines a May-Steenrod structure on the Barratt-Eccles operad.
+	defines a May--Steenrod structure on the Barratt-Eccles operad.
 \end{theorem}
@@
 
-In this subsection we introduce a May-Steenrod structures on the surjection operad.
+In this subsection we introduce a May--Steenrod structures on the surjection operad.
 There are two widely used sign conventions for this operad respectively due to McClure-Smith \cite{mcclure03cochain} and Berger-Fresse \cite{berger04combinatorial}.
-Using the Berger-Fresse convention, we can define a May-Steenrod structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}.
-We define an May-Steenrod structure on the surjection operad in a convention independent way which recovers the table reduction May-Steenrod structure in the Berger-Fresse case.
+Using the Berger-Fresse convention, we can define a May--Steenrod structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}.
+We define an May--Steenrod structure on the surjection operad in a convention independent way which recovers the table reduction May--Steenrod structure in the Berger-Fresse case.
 
@@
 	\end{equation*}
-	defines a May-Steenrod structure on the Surjection operad.
+	defines a May--Steenrod structure on the Surjection operad.
 \end{theorem}
@@
 
-We will define a May-Steenrod structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the May-Steenrod structure $\psi_{\mathcal X} \colon \mathcal W \to \mathcal X$ with a morphism $SL \colon \mathcal X \to U(\mathcal M)$ of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact) that we now define.
+We will define a May--Steenrod structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the May--Steenrod structure $\psi_{\mathcal X} \colon \mathcal W \to \mathcal X$ with a morphism $SL \colon \mathcal X \to U(\mathcal M)$ of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact) that we now define.
 Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element represented by the connected $(1,r)$-graph
@@
 	\end{equation*}
-	defines a May-Steenrod structure on $U(\mathcal M)$.
+	defines a May--Steenrod structure on $U(\mathcal M)$.
 \end{theorem}
@@
 
-In this subsection we introduce a natural May-Steenrod structure on the normalized cochains of any simplicial set $X$.
-Since a May-Steenrod structure was constructed in the previous section for $U(\mathcal M)$, we only need to describe a natural $U(\mathcal M)$-algebra structure on $N^\bullet(X)$.
+In this subsection we introduce a natural May--Steenrod structure on the normalized cochains of any simplicial set $X$.
+Since a May--Steenrod structure was constructed in the previous section for $U(\mathcal M)$, we only need to describe a natural $U(\mathcal M)$-algebra structure on $N^\bullet(X)$.
 Using the linear duality functor, it suffices to construct a natural $U(\mathcal M)$-coalgebra structure on $N_\bullet(X)$ which, in turn, can be derived via a Kan extension argument from one on each $N_\bullet(\triangle^n)$.
@@
 
-Composing the algebra structure $\phi^\triangle$ with the May-Steenrod structure on $U(\mathcal M)$ gives a natural May-Steenrod structure on $N^\bullet(X)$.
+Composing the algebra structure $\phi^\triangle$ with the May--Steenrod structure on $U(\mathcal M)$ gives a natural May--Steenrod structure on $N^\bullet(X)$.
 We record this observation in the following.
@@
 	\end{equation*}
-	defines a natural May-Steenrod structure on $N^\bullet(X)$ for any simplicial set $X$.
+	defines a natural May--Steenrod structure on $N^\bullet(X)$ for any simplicial set $X$.
 \end{theorem}
@@
 
-We will now give examples of how this May-Steenrod structure defines representatives of Steenrod operations for simplicial cochains.
+We will now give examples of how this May--Steenrod structure defines representatives of Steenrod operations for simplicial cochains.
 For applications related to the cohomology of spaces, it is convenient to introduce the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$ for Steenrod operations.
@@
 
-In this subsection we introduce, closely following the presentation of the previous subsection, a natural May-Steenrod structure on the normalized cochains of any cubical set.
+In this subsection we introduce, closely following the presentation of the previous subsection, a natural May--Steenrod structure on the normalized cochains of any cubical set.
 By the same considerations, the desired construction will follow from a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$.
@@
 
-Composing the algebra structure $\phi^\square$ with the May-Steenrod structure on $U(\mathcal M)$ gives a natural May-Steenrod structure on $N^\bullet(X)$.
+Composing the algebra structure $\phi^\square$ with the May--Steenrod structure on $U(\mathcal M)$ gives a natural May--Steenrod structure on $N^\bullet(X)$.
 We record this observation in the following.
@@
 	\end{equation*}
-	defines a natural May-Steenrod structure on $N^\bullet(X)$ for any cubical set $X$.
+	defines a natural May--Steenrod structure on $N^\bullet(X)$ for any cubical set $X$.
 \end{theorem}
 
-We will now give examples of how this May-Steenrod structure defines representatives of Steenrod operations for cubical cochains.
+We will now give examples of how this May--Steenrod structure defines representatives of Steenrod operations for cubical cochains.
 Recall the notation $P^s = P_{-s}$ and $\beta P^s = \beta P_{-s}$ for Steenrod operations used when studying the cohomology of spaces.

### 2021-07-30 introduction.tex
Replace May-Steenrod by May--Steenrod

@@
 Then, in Section~\ref{s:goup homology}, we review the key notions from group homology which we will use mainly for cyclic and symmetric groups.
-Section~\ref{s:operads} is devoted to the language of operads and related structures, which we use in Section~\ref{s:steenrod} to introduce the notion of May-Steenrod structure, an integral structure at the (co)chain level inducing Steenrod operations for every prime.
-Section~\ref{s:effective}, the bulk of this work, presents effective constructions of May-Steenrod structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
-It also describes a natural $U(\mathcal M)$-algebra structure on the cochains of simplicial and cubical sets inducing natural May-Steenrod structures on them.
+Section~\ref{s:operads} is devoted to the language of operads and related structures, which we use in Section~\ref{s:steenrod} to introduce the notion of May--Steenrod structure, an integral structure at the (co)chain level inducing Steenrod operations for every prime.
+Section~\ref{s:effective}, the bulk of this work, presents effective constructions of May--Steenrod structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
+It also describes a natural $U(\mathcal M)$-algebra structure on the cochains of simplicial and cubical sets inducing natural May--Steenrod structures on them.
 We end, in Section~\ref{s:outlook}, with an overview of some connections of this work to certain geometric and combinatorial structures and provide an outline of future research directions.

### 2021-07-30 outlook.tex
Replace May-Steenrod by May--Steenrod

@@
 In fact, an entire $E_\infty$ operad (prop) is constructed geometrically in this way.
-We can also interpret the May-Steenrod structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups ---a key ingredient in Definition \ref{def: minimal cyclic resolution}--- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.
+We can also interpret the May--Steenrod structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups --~a key ingredient in Definition \ref{def: minimal cyclic resolution}~-- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.
 
@@
 This includes cyclic, planar cyclic as well as Berger's pre-operads \cite{BergerRecog}.
-Their interplay is of independent interest \cite{BergerKaufmann,feyrep} and will be linked directly to the constructions of this paper.
+Their interplay is of independent interest \cite{BergerKaufmann, feyrep} and will be linked directly to the constructions of this paper.
 
@@
 A treatment close to ours for the $E_2$ case was given in \cite{Tourtchine}.
-Effective constructions for these Dyer-Lashof-Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang,sinha2013littledisks,berger04combinatorial,ayala2014configuration} and higher categories \cite{Bathigher, BalFiedSchwVogt, Rezkhigher}, and will appear elsewhere.
+Effective constructions for these Dyer-Lashof-Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang, sinha2013littledisks, berger04combinatorial, ayala2014configuration} and higher categories \cite{Bathigher, BalFiedSchwVogt, Rezkhigher}, and will appear elsewhere.

### 2021-07-30 steenrod.tex
Replace May-Steenrod by May--Steenrod

@@
-\section{May-Steenrod structures} \label{s:steenrod}
+\section{May--Steenrod structures} \label{s:steenrod}
 
@@
 Let us assume the ground ring to be $\Z$ unless stated otherwise.
-\begin{definition} \label{def: May-Steenrod structure}
-	A \textit{May-Steenrod structure} on an operad $\mathcal O$ is a 
+\begin{definition} \label{def: May--Steenrod structure}
+	A \textit{May--Steenrod structure} on an operad $\mathcal O$ is a 
 	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$ operad
@@
 	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$.
-	In this language, a choice of factorization $\phi \circ \iota$ of a May-Steenrod structure on $\mathcal O$ endows it with a \textit{commutative multiplication} $\phi$.
+	In this language, a choice of factorization $\phi \circ \iota$ of a May--Steenrod structure on $\mathcal O$ endows it with a \textit{commutative multiplication} $\phi$.
 \end{remark}
@@
 	Let $A$ be a chain complex.
-	A May-Steenrod structure on $\mathrm{End}_A$ is referred to as one on $A$.
+	A May--Steenrod structure on $\mathrm{End}_A$ is referred to as one on $A$.
 	Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod} $(r, i)$-\textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
@@
 
-Let $A$ be equipped with a May-Steenrod structure
+Let $A$ be equipped with a May--Steenrod structure
 \begin{equation*}
@@
 
-For the rest of this section $A$ denotes a chain complex equipped with a May-Steenrod structure.
+For the rest of this section $A$ denotes a chain complex equipped with a May--Steenrod structure.
 
@@
 \begin{lemma}
-	Let $A$ be equipped with a May-Steenrod structure.
+	Let $A$ be equipped with a May--Steenrod structure.
 	Then,
@@
 As described in Definition~1.2 of \cite{may70generalapproach}, the $\mathrm{C}$-module $\mathcal W$ lifts to this category.
-A \textit{comultiplicative May-Steenrod structure} on an operad $\mathcal O$ is a morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$ operad over the category of coalgebras
+A \textit{comultiplicative May--Steenrod structure} on an operad $\mathcal O$ is a morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$ operad over the category of coalgebras
 \begin{equation*}
@@
 
-Chain complexes equipped with a comultiplicative May-Steenrod structure satisfy the so called \textit{Cartan relations}.
+Chain complexes equipped with a comultiplicative May--Steenrod structure satisfy the so called \textit{Cartan relations}.
 
 \begin{lemma}
-	Let $A$ be equipped with a comultiplicative May-Steenrod structure.
+	Let $A$ be equipped with a comultiplicative May--Steenrod structure.
 	For any two mod $p$ homology classes $[\alpha]$ and $[\beta]$ we have

### 2021-07-30 effective.tex
Replace other- between names by -- and replace E_infty X by E_ifty-X

@@
 
-In this section we construct explicit May--Steenrod structures on three well know combinatorial $E_\infty$ operads: the Barratt-Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$ prop $\mathcal M$ introduced in \cite{medina2020prop1}.
+In this section we construct explicit May--Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt--Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-prop $\mathcal M$ introduced in \cite{medina2020prop1}.
 We also define natural and effective May--Steenrod structure on the normalized cochains of any simplicial or cubical set using that these are algebras over the operad $U(\mathcal M)$.
@@
 	\end{tikzcd}
-	\caption{Summary of effective constructions: May--Steenrod structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May--Steenrod structures on the normalized chains of simplicial and cubical sets.
+	\caption{Summary of effective constructions: May--Steenrod structures on the Barratt--Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May--Steenrod structures on the normalized chains of simplicial and cubical sets.
 We remark that the maps $TR$ and $SL$ required different sign conventions.}
@@
 
-\subsection{Barratt-Eccles operad} In this subsection we effectively describe a May--Steenrod structure on the Barratt-Eccles operad.
+\subsection{Barratt--Eccles operad} In this subsection we effectively describe a May--Steenrod structure on the Barratt--Eccles operad.
 
-We begin by reviewing the $\mathrm{S}$-module structure underlying the Barratt-Eccles operad and, since will not use it in this work, refer to \cite{berger04combinatorial} for a description of if composition structure.
+We begin by reviewing the $\mathrm{S}$-module structure underlying the Barratt--Eccles operad and, since will not use it in this work, refer to \cite{berger04combinatorial} for a description of if composition structure.
 For a non-negative integer $r$ define the simplicial set $E(\mathrm S_r)$ by 
@@
 \end{equation*} 
-The chain complex resulting from applying the functor of normalized integral chains to it is denoted $\mathcal E(r)$, which corresponds to the arity $r$ part of the Barratt-Eccles operad.
+The chain complex resulting from applying the functor of normalized integral chains to it is denoted $\mathcal E(r)$, which corresponds to the arity $r$ part of the Barratt--Eccles operad.
 
-\begin{definition} \label{def: Steenrod-Adem on Barratt-Eccles}
+\begin{definition} \label{def: Steenrod-Adem on Barratt--Eccles}
 	For every $r \geq 0$, let $\psi_{\mathcal E}(r) \colon \mathcal W(r) \to \mathcal E(r)$ be the $\Z[\mathrm{C}_r]$-linear map defined on basis elements by 
@@
 
-\begin{theorem} \label{thm: Steenrod-Adem on Barratt-Eccles}
+\begin{theorem} \label{thm: Steenrod-Adem on Barratt--Eccles}
 	The morphism of $\mathrm{C}$-modules
@@
 	\end{equation*}
-	defines a May--Steenrod structure on the Barratt-Eccles operad.
+	defines a May--Steenrod structure on the Barratt--Eccles operad.
 \end{theorem}
@@
 \begin{proof}
-	Since $\mathcal X$ is an $E_\infty$ operad, we simply need to prove that the $\Z[\mathrm{C}_r]$-linear map
+	Since $\mathcal X$ is an $E_\infty$-operad, we simply need to prove that the $\Z[\mathrm{C}_r]$-linear map
 	\begin{equation*}
@@
 	is a chain map for every $r \geq 0$.
-	We simplify notation and write $\psi$ instead of $\psi_{\mathcal E}(r)$. To show $\psi$ is a chain map we proceed by induction.
+	We simplify notation and write $\psi$ instead of $\psi_{\mathcal E}(r)$.
+	To show $\psi$ is a chain map we proceed by induction.
 	Notice that
@@
 	\end{equation*}
-	and assume $\psi(\partial e_{k-1}) = \partial \psi(e_{k-1})$. If $k = 2n$ we have
+	and assume $\psi(\partial e_{k-1}) = \partial \psi(e_{k-1})$.
+	If $k = 2n$ we have
 	\begin{align*}
@@
 \begin{example}
-	Table \ref{fig: Barratt-Eccles Steenrod products} shows $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$.
+	Table \ref{fig: Barratt--Eccles Steenrod products} shows $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$.
 \end{example}
@@
 	\caption{The elements $\psi_{\mathcal E}(r)(e_n)$ for small values of $r$ and $n$ where we are denoting $(\rho^{r_0}, \dots, \rho^{r_n})$ simply by $(r_0, \dots, r_n)$.}
-	\label{fig: Barratt-Eccles Steenrod products}
+	\label{fig: Barratt--Eccles Steenrod products}
 \end{table}
@@
 	\begin{tikzcd}
-	\mathcal W \arrow[r] &[-3pt] N_\bullet E(\mathrm C) \arrow[r, "N_\bullet E(\iota)"] &[5pt] \mathcal E.
+	\mathcal W \arrow[r] &[-3pt] N_\bullet E(\mathrm C) \arrow[r, "N_\bullet E(\iota)\,"] &[5pt] \mathcal E.
 	\end{tikzcd}
@@
 In this subsection we introduce a May--Steenrod structures on the surjection operad.
-There are two widely used sign conventions for this operad respectively due to McClure-Smith \cite{mcclure03cochain} and Berger-Fresse \cite{berger04combinatorial}.
-Using the Berger-Fresse convention, we can define a May--Steenrod structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}.
-We define an May--Steenrod structure on the surjection operad in a convention independent way which recovers the table reduction May--Steenrod structure in the Berger-Fresse case.
+There are two widely used sign conventions for this operad respectively due to McClure--Smith \cite{mcclure03cochain} and Berger--Fresse \cite{berger04combinatorial}.
+Using the Berger--Fresse convention, we can define a May--Steenrod structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}.
+We define an May--Steenrod structure on the surjection operad in a convention independent way which recovers the table reduction May--Steenrod structure in the Berger--Fresse case.
 
@@
 For a non-negative integer $r$ let $\mathcal X(r)_n$ be the free abelian group generated by all functions from $\{1, \dots, n+r\}$ to $\{1, \dots, r\}$ modulo the subgroup generated by degenerate functions, i.e., those which are either non-surjective or have a pair of equal consecutive values.
-We only describe the McClure-Smith convention since we refer to it in subsequent sections.
+We only describe the McClure--Smith convention since we refer to it in subsequent sections.
 The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top dimensional generator in the chain complex
@@
 
-Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure-Smith to prove $\mathcal X$ is an $E_\infty$ operad and whose introduction is credited to Benson \cite{benson1998rep}.
+Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure--Smith to prove $\mathcal X$ is an $E_\infty$-operad and whose introduction is credited to Benson \cite{benson1998rep}.
 Let the maps $i,\ p$ and $s$ be defined on basis elements, represented by sequences, as follows: $i \colon \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p \colon \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurrence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s \colon \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
@@
 	\end{equation*}
-	and assume $\psi(\partial e_{n-1}) = \partial \psi(e_{n-1})$. For $n = 2m+1$ we have
+	and assume $\psi(\partial e_{n-1}) = \partial \psi(e_{n-1})$.
+	For $n = 2m+1$ we have
 	\begin{align*}
@@
 	\end{align*}
-	For $n = 2m$ the proof is analogous. The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ is a generator of the homology.
+	For $n = 2m$ the proof is analogous.
+	The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ is a generator of the homology.
 \end{proof}
 
-For the rest of the paper we use the McClure-Smith sign convention on $\mathcal X$.
+For the rest of the paper we use the McClure--Smith sign convention on $\mathcal X$.
 
@@
 
-\subsection{The $E_\infty$ prop $\mathcal M$}
+\subsection{The $E_\infty$-prop $\mathcal M$}
 
-We start by reviewing the finitely presented $E_\infty$ prop introduced in \cite{medina2020prop1}.
+We start by reviewing the finitely presented $E_\infty$-prop introduced in \cite{medina2020prop1}.
 Let $\mathcal M$ be the prop generated by 
@@
 
-Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$ prop as introduced in Definition~\ref{def: e-infinity operad and prop}.
-More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$ operad.
+Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$-prop as introduced in Definition~\ref{def: e-infinity operad and prop}.
+More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$-operad.
 For the remainder of this article we write $U(\mathcal M)$ instead of $U_2(\mathcal M)$.
@@
 \begin{remark}
-	The $E_\infty$ structure we described in Proposition~\ref{prop: simplicial chain bialgebra}, depending solely on three fundamental maps, generalizes the coalgebra structures of McClure-Smith \cite{mcclure03cochain} and Berger-Fresse \cite{berger04combinatorial}, please consult \cite{medina2020prop1} for more details.
+	The $E_\infty$-structure we described in Proposition~\ref{prop: simplicial chain bialgebra}, depending solely on three fundamental maps, generalizes the coalgebra structures of McClure--Smith \cite{mcclure03cochain} and Berger--Fresse \cite{berger04combinatorial}, please consult \cite{medina2020prop1} for more details.
 \end{remark}

### 2021-07-30 introduction.tex
Replace other- between names by -- and replace E_infty X by E_ifty-X

@@
 The reason is that, given the representability of the cohomology functor, these operations together with the Bockstein homomorphism can be used to give a complete description of the algebraic structure naturally present on the mop-$p$ \mbox{cohomology} algebra of spaces.
-For the even prime, Steenrod squares were introduced in \cite{steenrod47products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander-Whitney's chain approximation to the diagonal, the so called cup-$i$ products.
+For the even prime, Steenrod squares were introduced in \cite{steenrod47products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander--Whitney's chain approximation to the diagonal, the so called cup-$i$ products.
 Later, for odd primes, their definition was given non-effectively using arguments based on the mod $p$ homology of symmetric groups \cites{steenrod53symmetric, steenrod53cyclic, steenrod62operations}.
@@
 In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- the need to have a definition of Steenrod operations that can be effectively computed in specific examples has gain considerable importance.
-In Applied Topology, the use of persistence homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage,chan2013topology,lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
+In Applied Topology, the use of persistence homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage, chan2013topology, lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
 The chain level viewpoint for the study of homology operations was brought to the forefront by String Topology \cite{Sullivanoverview}, and as served as a major driver of innovation \cites{TZ, hoch2}.
@@
 
-Following \cite{may70generalapproach}, we take a more general approach to Steenrod operations that also includes Araki-Kudo-Dyer-Lashof operations on the mod $p$ homology of infinite loop spaces \cites{araki56squaring, dyer62lashof}.
+Following \cite{may70generalapproach}, we take a more general approach to Steenrod operations that also includes Araki--Kudo--Dyer--Lashof operations on the mod $p$ homology of infinite loop spaces \cites{araki56squaring, dyer62lashof}.
 We use the language of operads \cite{may72geometry} to describe at the (co)chain level the integral structure required to define (co)homology operations at every prime.
-We then describe effective constructions of this structure on three prominent models of the $E_\infty$ operad, identifying elements in them that represent Steenrod operations in the mod $p$ homology of their algebras; these are the Barratt-Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
+We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod $p$ homology of their algebras; these are the Barratt--Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
 Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical multioperations generalizing the \mbox{cup-$i$} products of Steenrod to every prime.
-An alternative approach based on the Eilenberg-Zilber contraction can be found in \cite{gonzalez2005hpt}.
-The $p = 2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2021newformulas}, and in the cubical setting to the cup-$i$ products of Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l-Pilarczy \cite{pilarczyk2016cubical}.
+An alternative approach based on the Eilenberg--Zilber contraction can be found in \cite{gonzalez2005hpt}.
+The $p = 2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2021newformulas}, and in the cubical setting to the cup-$i$ products of Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l--Pilarczy \cite{pilarczyk2016cubical}.
 
@@
 Section~\ref{s:operads} is devoted to the language of operads and related structures, which we use in Section~\ref{s:steenrod} to introduce the notion of May--Steenrod structure, an integral structure at the (co)chain level inducing Steenrod operations for every prime.
-Section~\ref{s:effective}, the bulk of this work, presents effective constructions of May--Steenrod structures on the Barratt-Eccles, surjection, and $U(\mathcal M)$ operads.
+Section~\ref{s:effective}, the bulk of this work, presents effective constructions of May--Steenrod structures on the Barratt--Eccles, surjection, and $U(\mathcal M)$ operads.
 It also describes a natural $U(\mathcal M)$-algebra structure on the cochains of simplicial and cubical sets inducing natural May--Steenrod structures on them.

### 2021-07-30 main.tex
Fix broken ref to medina2021adem and update bib of my papers
Replace May-Steenrod by May--Steenrod
Replace other- between names by -- and replace E_infty X by E_ifty-X

@@
-\documentclass[A4]{amsart}
+\documentclass{amsart}
 \usepackage{amsmath, amssymb, amsfonts}
@@
 
-\title{Cochain level May-Steenrod operations}
+\title{Cochain level May--Steenrod operations}
 
@@
 \subjclass[2010]{55S05, 55U05, 55S10, 55S12; 55-04, 55U15, 55S15}
-\keywords{Steenrod operations, Dyer-Lashof operations, operads, simplicial cochains, cubical cochains}
+\keywords{Steenrod operations, Dyer--Lashof operations, operads, simplicial cochains, cubical cochains}
 
 \begin{abstract}
-	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander-Whitney's chain approximation to the diagonal.
+	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander--Whitney's chain approximation to the diagonal.
 He later defined his homonymous operations for all primes using the homology of symmetric groups.

### 2021-07-30 operads.tex
Replace other- between names by -- and replace E_infty X by E_ifty-X

@@
 contravariant) functor from $\mathrm G$ to $\mathbf{Ch}_R$.
-%Right actions are more commonly used in the literature of operads so we emphasize that perspective.
 Taking inverses allows for the switch between left and right conventions.
@@
 \begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}] \label{def: e-infinity operad and prop}
-	An operad is said to be $E_\infty$ if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a prop $\mathcal P$ is said to be $E_\infty$ if either $U_1(\mathcal P)$ or $U_2(\mathcal P)$ is an \mbox{$E_\infty$ operad}.
+	An operad is said to be an $E_\infty$-operad if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a prop $\mathcal P$ is said to be an $E_\infty$-prop if either $U_1(\mathcal P)$ or $U_2(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
 \end{definition}
@@
 
-Algebras over $E_\infty$ operads are the central objects of study in this work.
+Algebras over $E_\infty$-operads are the central objects of study in this work.
 To develop intuition for them, let us consider a chain complex $A$ with an algebra structure over the constant functor $\underline{R}$, thought of as an operad with all compositions corresponding to the identity map $R \to R$.
 The $\underline{R}$-algebra structure on $A$ is generated by a linear map $\mu \colon A \otimes A \to A$ which is (strictly) commutative and associative, and a linear map $\eta \colon R \to A$ that determines a (two-sided) unit for $\mu$.
-Since $E_\infty$ operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies.
+Since $E_\infty$-operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies.
 The two main examples to keep in mind are the cochains of spaces and the chains of infinite loops spaces.

### 2021-07-30 outlook.tex
Replace other- between names by -- and replace E_infty X by E_ifty-X

@@
 For example, \cite{Postnikov} and \cite{medina2018prop2} independently introduced equivalent geometric representations of the cup-$i$ products in terms of stabilized arc surfaces \cite{KLP} and weighted ribbon graphs respectively.
-In fact, an entire $E_\infty$ operad (prop) is constructed geometrically in this way.
+In fact, an entire $E_\infty$-operad (prop) is constructed geometrically in this way.
 We can also interpret the May--Steenrod structure in $U(\mathcal M)$ from the ``oriented surface" perspective, where the norm map $N$ of cyclic groups --~a key ingredient in Definition \ref{def: minimal cyclic resolution}~-- was identified in \cite{KLP} with a Dehn twist operator in connection with Connes' cyclic complex.
@@
 A treatment close to ours for the $E_2$ case was given in \cite{Tourtchine}.
-Effective constructions for these Dyer-Lashof-Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang, sinha2013littledisks, berger04combinatorial, ayala2014configuration} and higher categories \cite{Bathigher, BalFiedSchwVogt, Rezkhigher}, and will appear elsewhere.
+Effective constructions for these Dyer--Lashof--Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang, sinha2013littledisks, berger04combinatorial, ayala2014configuration} and higher categories \cite{Bathigher, BalFiedSchwVogt, Rezkhigher}, and will appear elsewhere.

### 2021-07-30 steenrod.tex
Replace other- between names by -- and replace E_infty X by E_ifty-X

@@
 	A \textit{May--Steenrod structure} on an operad $\mathcal O$ is a 
-	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$ operad
+	morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad
 	\begin{equation*}
@@
 For any object $(A, \theta)$ in this category, Definition 2.2 in \cite{may70generalapproach} defines operations on the mod $p$ homology of $A$, a construction we review below.
-In particular, if $A$ is given by the cochains of a space these products agree with Steenrod's original definitions, and for $A$ being the chains on an infinite loop spaces, with those defined by Araki-Kudo and Dyer-Lashof.
+In particular, if $A$ is given by the cochains of a space these products agree with Steenrod's original definitions, and for $A$ being the chains on an infinite loop spaces, with those defined by Araki--Kudo and Dyer--Lashof.
 
@@
 	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
-	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\phi$ an operad map from an $E_\infty$ operad to $\End_A$, this is an \textit{Adem object} in the sense of Definition 4.1 of \cite{may70generalapproach}.
+	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\phi$ an operad map from an $E_\infty$-operad to $\End_A$, this is an \textit{Adem object} in the sense of Definition 4.1 of \cite{may70generalapproach}.
 	The statement presented here is stated and proven as part of Theorem 4.7 loc. cit.
@@
 As described in Definition~1.2 of \cite{may70generalapproach}, the $\mathrm{C}$-module $\mathcal W$ lifts to this category.
-A \textit{comultiplicative May--Steenrod structure} on an operad $\mathcal O$ is a morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$ operad over the category of coalgebras
+A \textit{comultiplicative May--Steenrod structure} on an operad $\mathcal O$ is a morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad over the category of coalgebras
 \begin{equation*}
@@
 161 of \cite{may70generalapproach}.
-	The statement presented here is stated in pag. 165 loc. cit.
+	The statement presented here is stated in pag.~165 loc.~cit.
 \end{proof}

### 2021-07-30 abstract.tex
Split-off abstract and update address and email

--- 2021-07-30 main.tex
@@
-\documentclass{amsart}
-\usepackage{amsmath, amssymb, amsfonts}
-\usepackage{tikz-cd}
-\usepackage{graphics}
-% hyperref
-\usepackage[bookmarks=true, linktocpage=true,
-bookmarksnumbered=true, breaklinks=true,
-pdfstartview=FitH, hyperfigures=false,
-plainpages=false, naturalnames=true,
-colorlinks=true, pagebackref=true,
-pdfpagelabels]{hyperref}
-\hypersetup{
-	colorlinks,
-	citecolor=blue,
-	filecolor=blue,
-	linkcolor=blue,
-	urlcolor=blue
-}
-\usepackage[capitalize, noabbrev]{cleveref}
-\usepackage[alphabetic]{amsrefs}
-
-% enviorenments
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-
-% sets
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\F}{\mathbb{F}}
-
-% funtors and operators
-\newcommand{\Hom}{\mathrm{Hom}}
-\newcommand{\End}{\mathrm{End}}
-\DeclareMathOperator*{\colim}{colim}
-
-% other
-\renewcommand{\th}{^{\mathrm{th}}}
-
-% paper shape
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.6in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
-\calclayout
-
-\include{figures}
-
-\begin{document}
-
-\title{Cochain level May--Steenrod operations}
-
-\author[R. Kaufmann]{Ralph M.\ Kaufmann}
-\address{Department of Mathematics, Department of Physics and Astronomy, Purdue University}
-\email{rkaufman@purdue.edu}
-
-\author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
-\address{Laboratory for Topology and Neuroscience, EPFL \and
-Department of Mathematics, University of Notre Dame}
-\email{amedinam@nd.edu}
-\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Max Plank Institute for Mathematics where part of this work developed.}
-
-\subjclass[2010]{55S05, 55U05, 55S10, 55S12; 55-04, 55U15, 55S15}
-\keywords{Steenrod operations, Dyer--Lashof operations, operads, simplicial cochains, cubical cochains}
-
 \begin{abstract}
@@
 \end{abstract}
-
-\maketitle
-
-\tableofcontents
-\input{introduction}
-\input{preliminaries}
-\input{groups}
-\input{operads}
-\input{steenrod}
-\input{effective}
-\input{outlook}
-\bibliography{bibliography}
-
-\end{document}

### 2021-07-30 main.tex
Split-off abstract and update address and email

@@
 \author[R. Kaufmann]{Ralph M.\ Kaufmann}
-\address{Department of Mathematics, Department of Physics and Astronomy, Purdue University}
+\address{R. Kaufmann, Department of Mathematics, Department of Physics and Astronomy, Purdue University}
 \email{rkaufman@purdue.edu}
@@
 \author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
-\address{Laboratory for Topology and Neuroscience, EPFL \and
-Department of Mathematics, University of Notre Dame}
-\email{amedinam@nd.edu}
-\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Max Plank Institute for Mathematics where part of this work developed.}
+\address{A. Medina-Mardones, Max Planck Institute for Mathematics \and
+University of Notre Dame du Lac}
+\email{ammedmar@mpim-bonn.mpg.de}
+\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Laboratory for Topology and Neuroscience at EPFL.}
 
 \subjclass[2010]{55S05, 55U05, 55S10, 55S12; 55-04, 55U15, 55S15}
+
 \keywords{Steenrod operations, Dyer--Lashof operations, operads, simplicial cochains, cubical cochains}
 
-\begin{abstract}
-	Steenrod defined in 1947 the Steenrod squares on the mod 2 cohomology of spaces using explicit cochain formulae for the cup-$i$ products; a family of coherent homotopies derived from the broken symmetry of Alexander--Whitney's chain approximation to the diagonal.
-He later defined his homonymous operations for all primes using the homology of symmetric groups.
-This approach enhanced the conceptual understanding of the operations and allowed for many advances, but lacked the concreteness of their definition at the even prime.
-In recent years, thanks to the development of new applications of cohomology, having definitions of Steenrod operations that can be effectively computed in specific examples has become a key issue.
-This article provides such definitions at all primes using the operadic viewpoint of May, and defines multioperations that generalize the cup-$i$ products of Steenrod on the simplicial and cubical cochains of spaces.
-\end{abstract}
+\input{abstract}
 
@@
 
+\setcounter{tocdepth}{1}
 \tableofcontents
+
 \input{introduction}
@@
 \input{outlook}
+
 \bibliography{bibliography}

### 2021-07-30 introduction.tex
Improve some commutative diagrams

@@
 
-In recent years, thanks to the development of new applications of cohomology ---most notably in Applied Topology and Quantum Field Theory--- the need to have a definition of Steenrod operations that can be effectively computed in specific examples has gain considerable importance.
+In recent years, thanks to the development of new applications of cohomology --~most notably in Applied Topology and Quantum Field Theory~-- the need to have a definition of Steenrod operations that can be effectively computed in specific examples has gain considerable importance.
 In Applied Topology, the use of persistence homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage, chan2013topology, lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.

### 2021-07-30 operads.tex
Improve some commutative diagrams

@@
 \begin{tikzcd}[column sep=small, row sep=tiny]
-& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"'] \arrow[dr, "U_2"] & \\
+& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"', out=180, in=55] \arrow[dr, "U_2", out=0, in=125] & \\
 \mathbf{Ch}_R^{\mathrm{S}^{op}} & & \mathbf{Ch}_R^{\mathrm{S}},

### 2021-08-19 main.tex
Minor improvements

@@
 \documentclass{amsart}
-\usepackage{amsmath, amssymb, amsfonts}
+\usepackage{amssymb}
 \usepackage{tikz-cd}
@@
 \email{ammedmar@mpim-bonn.mpg.de}
-\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Laboratory for Topology and Neuroscience at EPFL.}
+\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Laboratory for Topology and Neuroscience at EPFL}
 

### 2021-08-20 aux/abstract.tex
Structural refactoring using new template

--- 2021-07-30 abstract.tex
@@
 This approach enhanced the conceptual understanding of the operations and allowed for many advances, but lacked the concreteness of their definition at the even prime.
-In recent years, thanks to the development of new applications of cohomology, having definitions of Steenrod operations that can be effectively computed in specific examples has become a key issue.
+In recent years, thanks to the development of new applications of cohomology,the need to have an effectively computable definition of Steenrod operations has become a key issue.
 This article provides such definitions at all primes using the operadic viewpoint of May, and defines multioperations that generalize the cup-$i$ products of Steenrod on the simplicial and cubical cochains of spaces.

### 2021-08-20 may_st.tex
Structural refactoring using new template

--- 2021-08-19 main.tex
@@
 \documentclass{amsart}
-\usepackage{amssymb}
-\usepackage{tikz-cd}
-\usepackage{graphics}
-% hyperref
-\usepackage[bookmarks=true, linktocpage=true,
-bookmarksnumbered=true, breaklinks=true,
-pdfstartview=FitH, hyperfigures=false,
-plainpages=false, naturalnames=true,
-colorlinks=true, pagebackref=true,
-pdfpagelabels]{hyperref}
-\hypersetup{
-	colorlinks,
-	citecolor=blue,
-	filecolor=blue,
-	linkcolor=blue,
-	urlcolor=blue
-}
-\usepackage[capitalize, noabbrev]{cleveref}
-\usepackage[alphabetic]{amsrefs}
-
-% enviorenments
-\newtheorem{theorem}{Theorem}
-\newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{proposition}[theorem]{Proposition}
-\theoremstyle{definition}
-\newtheorem{definition}[theorem]{Definition}
-\newtheorem{example}[theorem]{Example}
-\newtheorem{remark}[theorem]{Remark}
-
-% sets
-\newcommand{\Z}{\mathbb{Z}}
-\newcommand{\F}{\mathbb{F}}
-
-% funtors and operators
-\newcommand{\Hom}{\mathrm{Hom}}
-\newcommand{\End}{\mathrm{End}}
-\DeclareMathOperator*{\colim}{colim}
-
-% other
-\renewcommand{\th}{^{\mathrm{th}}}
-
-% paper shape
-\setlength{\textwidth}{\paperwidth}
-\addtolength{\textwidth}{-1.6in}
-\setlength{\textheight}{\paperheight}
-\addtolength{\textheight}{-1.8in}
-\calclayout
-
-\include{figures}
-
-\begin{document}
+\include{aux/style}
+\include{aux/usualcmds}
 
@@
 \email{ammedmar@mpim-bonn.mpg.de}
-\thanks{A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT - 1}, and the hospitality of the Laboratory for Topology and Neuroscience at EPFL}
 
@@
 
-\input{abstract}
+\include{aux/figures}
 
+\begin{document}
+	\input{aux/abstract}
 	\maketitle
-
-\setcounter{tocdepth}{1}
-\tableofcontents
-
-\input{introduction}
-\input{preliminaries}
-\input{groups}
-\input{operads}
-\input{steenrod}
-\input{effective}
-\input{outlook}
-
-\bibliography{bibliography}
-
+	\input{sec/introduction}
+	\input{sec/preliminaries}
+	\input{sec/groups}
+	\input{sec/operads}
+	\input{sec/steenrod}
+	\input{sec/effective}
+	\input{sec/outlook}
+	\printbibliography
 \end{document}

### 2021-08-20 sec/effective.tex
Structural refactoring using new template

--- 2021-07-30 effective.tex
@@
 
-In this section we construct explicit May--Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt--Eccles operad $\mathcal E$ \cite{berger04combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure03cochain}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-prop $\mathcal M$ introduced in \cite{medina2020prop1}.
+In this section we construct explicit May--Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt--Eccles operad $\mathcal E$ \cite{berger2004combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure2003multivariable}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-prop $\mathcal M$ introduced in \cite{medina2020prop1}.
 We also define natural and effective May--Steenrod structure on the normalized cochains of any simplicial or cubical set using that these are algebras over the operad $U(\mathcal M)$.
@@
 
-We begin by reviewing the $\mathrm{S}$-module structure underlying the Barratt--Eccles operad and, since will not use it in this work, refer to \cite{berger04combinatorial} for a description of if composition structure.
+We begin by reviewing the $\mathrm{S}$-module structure underlying the Barratt--Eccles operad and, since will not use it in this work, refer to \cite{berger2004combinatorial} for a description of if composition structure.
 For a non-negative integer $r$ define the simplicial set $E(\mathrm S_r)$ by
@@
 In this subsection we introduce a May--Steenrod structures on the surjection operad.
-There are two widely used sign conventions for this operad respectively due to McClure--Smith \cite{mcclure03cochain} and Berger--Fresse \cite{berger04combinatorial}.
-Using the Berger--Fresse convention, we can define a May--Steenrod structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger04combinatorial}.
+There are two widely used sign conventions for this operad respectively due to McClure--Smith \cite{mcclure2003multivariable} and Berger--Fresse \cite{berger2004combinatorial}.
+Using the Berger--Fresse convention, we can define a May--Steenrod structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger2004combinatorial}.
 We define an May--Steenrod structure on the surjection operad in a convention independent way which recovers the table reduction May--Steenrod structure in the Berger--Fresse case.
@@
 Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at the time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on.
-Since we do not use the composition structure we refer to \cite{mcclure03cochain} for it.
+Since we do not use the composition structure we refer to \cite{mcclure2003multivariable} for it.
 
@@
 We will define a May--Steenrod structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the May--Steenrod structure $\psi_{\mathcal X} \colon \mathcal W \to \mathcal X$ with a morphism $SL \colon \mathcal X \to U(\mathcal M)$ of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact) that we now define.
-Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element represented by the connected $(1,r)$-graph
+Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element represented by the immersed connected $(1,r)$-graph
+
 \begin{center}
-	\begin{tikzpicture}[scale=.85]
-	\draw (0,0)--(0,-.6) node[below]{$\scriptstyle 1$};
-	\draw (0,0)--(.5,.5);
-	\draw (-.3, .3)-- (-.2,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_1$};
-	\draw (-.5,.5)--(0,0);
-	\node at (.11,.4){$...$};
+	\input{aux/surjection_like}
+\end{center}
 
-	\node at (1,0){$\scriptstyle \cdots$};
-	\node at (1,-.9){$\scriptstyle \cdots$};
-
-	\draw (2,0)--(2,-.68) node[below]{$\scriptstyle r$};
-	\draw (2,0)--(2.5,.5);
-	\draw (1.7, .3)-- (1.8,.5) node[above]{\quad $\scriptstyle 1\ 2\, ...\, k_r$};
-	\draw (1.5,.5)--(2,0);
-	\node at (2.11,.4){$...$};
-
-	\draw (1,2.5)--(1,3) node[above]{$\scriptstyle 1$};
-	\draw (1,2.5)--(0,2) node[below]{$\scriptstyle 1$};
-	\draw (.25,2.125)--(.5,2) node[below]{$\scriptstyle 2$};
-	\draw (.5,2.25)--(1,2) node[below]{$\scriptstyle 3$};
-	\draw (1,2.5)--(2,2) node[below]{\quad $\scriptstyle n + r$};
-	\node at (1.5,1.75){$...$};
-
-	\node at (1,1.3) {$\vdots$};
-
-	\node at (2.85,0){};
-	\end{tikzpicture}
-\end{center}
 that has no internal vertices and such that the $n+r$ strands at the top are orderly connected to the strands at the bottom following the values of $s$.
@@
 \begin{example}
-	Figure \ref{fig: cup 0,1,2} shows $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$.
+	The following immersed $(1,2)$-graphs are the elements $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$:
+	\begin{center}
+		\input{aux/cupi_graphs}
+	\end{center}
 \end{example}
-
-\begin{figure}[h]
-	\centering
-	\boxed{
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-		\draw (1,3) to [out=-25, in=90] (2,0);
-
-		\node at (1,-.5){$n=0$};
-		\end{tikzpicture}\hspace*{1cm}
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-
-		\draw [shorten >= 0cm] (.6,2.73) to [out=-100, in=90] (2,0);
-		%\draw [shorten <= 0cm] (1,1.5) to [out=-60, in=90] (2,0);
-
-		\draw [shorten >= .15cm] (1,3) to [out=-25, in=30, distance=1.1cm] (1,1.5);
-		\draw [shorten <= .1cm] (1,1.5) to [out=210, in=20] (0,1);
-
-		\node at (1,-.5){$n=1$};
-		\end{tikzpicture}\hspace*{1cm}
-		\begin{tikzpicture}[scale=.55]
-		\draw (1,3.7) to (1,3);
-
-		\draw (1,3) to [out=205, in=90] (0,0);
-		\draw (1,3) to [out=-25, in=90] (2,0);
-
-		\draw [shorten >= 0cm] (.6,2.73) to [out=210, in=135] (1,1.5);
-		\draw [shorten <= 0cm] (1,1.5) to [out=-45, in=170] (2,1);
-
-		\draw [shorten >= .1cm] (1.4,2.73) to [out=-30, in=45] (1,1.5);
-		\draw [shorten <= .1cm] (1,1.5) to [out=-135, in=10] (0,1);
-
-		\node at (1,-.5){$n=2$};
-		\end{tikzpicture}
-	}
-	\caption{The values of $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$.}
-	\label{fig: cup 0,1,2}
-\end{figure}
 
@@
 \begin{remark}
-	The $E_\infty$-structure we described in Proposition~\ref{prop: simplicial chain bialgebra}, depending solely on three fundamental maps, generalizes the coalgebra structures of McClure--Smith \cite{mcclure03cochain} and Berger--Fresse \cite{berger04combinatorial}, please consult \cite{medina2020prop1} for more details.
+	The $E_\infty$-structure we described in Proposition~\ref{prop: simplicial chain bialgebra}, depending solely on three fundamental maps, generalizes the coalgebra structures of McClure--Smith \cite{mcclure2003multivariable} and Berger--Fresse \cite{berger2004combinatorial}, please consult \cite{medina2020prop1} for more details.
 \end{remark}
@@
 	\begin{align*}
-	\,-\, [01]1 \otimes [01]0 \otimes 1[01] \,-\, 0[01] \otimes [01]0 \otimes 1[01] + [01]1 \otimes 0[01] \otimes [01]1 + 0[01] \otimes 0[01] \otimes [01]1.
+	&\,-\, [01]1 \otimes [01]0 \otimes 1[01] \,-\, 0[01] \otimes [01]0 \otimes 1[01] \\
+	&\,+\, [01]1 \otimes 0[01] \otimes [01]1 + 0[01] \otimes 0[01] \otimes [01]1.
 	\end{align*}

### 2021-08-20 sec/groups.tex
Structural refactoring using new template

--- 2021-07-06 groups.tex
@@
 \end{equation*}
-credited to Dyer-Lashof \cite{dyer62lashof}, Barratt-Priddy and Quillen \cite{barratt1972priddy}.
+credited to Dyer--Lashof \cite{dyer62lashof}, Barratt--Priddy and Quillen \cite{barratt1972priddyquillen}.
 
@@
 \begin{proof}
-	This is proven as Theorem 4.1 in \cite{steenrod53cyclic} where Thom is also credited with a different proof.
+	This is proven as Theorem 4.1 in \cite{steenrod1953cyclic} where Thom is also credited with a different proof.
 \end{proof}

### 2021-08-20 sec/introduction.tex
Structural refactoring using new template

--- 2021-07-30 introduction.tex
@@
 
-The role Steenrod operations play in Stable Homotopy Theory is hard to overstate.
+The role Steenrod operations play in stable homotopy theory is hard to overstate.
 The reason is that, given the representability of the cohomology functor, these operations together with the Bockstein homomorphism can be used to give a complete description of the algebraic structure naturally present on the mop-$p$ \mbox{cohomology} algebra of spaces.
-For the even prime, Steenrod squares were introduced in \cite{steenrod47products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander--Whitney's chain approximation to the diagonal, the so called cup-$i$ products.
-Later, for odd primes, their definition was given non-effectively using arguments based on the mod $p$ homology of symmetric groups \cites{steenrod53symmetric, steenrod53cyclic, steenrod62operations}.
-This viewpoint enhanced the conceptual understanding of the operations and allowed for many advances \cites{adem1952iteration, milnor1958dual, adams1995stable}, but lacked the concreteness of their definition at the even prime.
+For the even prime, Steenrod squares were introduced in \cite{steenrod1947products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander--Whitney's chain approximation to the diagonal, the so called cup-$i$ products.
+Later, for odd primes, their definition was given non-effectively using arguments based on the mod $p$ homology of symmetric groups \cite{steenrod1952reduced, steenrod1962cohomology, steenrod1962cohomology}.
+This viewpoint enhanced the conceptual understanding of the operations and allowed for many advances \cite{adem1952iteration, milnor1958dual, adams1995stable}, but lacked the concreteness of their definition at the even prime.
 The purpose of this paper is to fill this gap in the literature, introducing effective descriptions of multioperations at the cochain level generalizing Steenrod's cup-$i$ products defining Steenrod operations at all primes.
 
-In recent years, thanks to the development of new applications of cohomology --~most notably in Applied Topology and Quantum Field Theory~-- the need to have a definition of Steenrod operations that can be effectively computed in specific examples has gain considerable importance.
-In Applied Topology, the use of persistence homology \cites{carlsson2009data, edelsbrunner2008persistent} has open many new interdisciplinary research directions \cites{de2007coverage, chan2013topology, lee2017quantifying}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
-The chain level viewpoint for the study of homology operations was brought to the forefront by String Topology \cite{Sullivanoverview}, and as served as a major driver of innovation \cites{TZ, hoch2}.
-In Lattice Field Theory, cup-$i$ products are used in the construction of effective actions \cite{gaiotto2016spin, bhardwaj2017state, kapustin2017fermionic}, and this connection with physics motivated the development of effective versions of spin bordism \cites{brumfiel2016pontrjagin, brumfiel2018pontrjagin} prominently featuring higher derived structures at the cochain level \cite{medina2020cartan, medina2020adem}.
+In recent years, thanks to the development of new applications of cohomology, most notably in applied topology and topological quantum field theories, the need to have an effectively computable definition of Steenrod operations has gain considerable importance.
 
-Following \cite{may70generalapproach}, we take a more general approach to Steenrod operations that also includes Araki--Kudo--Dyer--Lashof operations on the mod $p$ homology of infinite loop spaces \cites{araki56squaring, dyer62lashof}.
-We use the language of operads \cite{may72geometry} to describe at the (co)chain level the integral structure required to define (co)homology operations at every prime.
-We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod $p$ homology of their algebras; these are the Barratt--Eccles \cite{berger04combinatorial}, surjection \cite{mcclure03cochain}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
+In applied topology, the use of persistence homology \cite{edelsbrunner2002topological, carlsson2005barcode} has open many new interdisciplinary research directions \cite{chan2013viral, hess2017cliques}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
+
+The chain level viewpoint for the study of homology operations was brought to the forefront by string topology \cite{sullivan2007presentstate}, and as served as a major driver of innovation \cite{tradler2007string, hoch2}.
+
+In lattice field theory, cup-$i$ products are used in the construction of effective actions \cite{gaiotto2016spin, bhardwaj2017fermionic, kapustin2017fermionic}, and this connection with physics motivated the development of effective versions of spin bordism \cite{brumfiel2016pontrjagin, brumfiel2018quadratic} prominently featuring higher derived structures at the cochain level \cite{medina2020cartan, medina2021adem}.
+
+Following \cite{may1970general}, we take a more general approach to Steenrod operations that also includes Araki--Kudo--Dyer--Lashof operations on the mod $p$ homology of infinite loop spaces \cite{araki56squaring, dyer62lashof}.
+We use the language of operads \cite{may1972geometry} to describe at the (co)chain level the integral structure required to define (co)homology operations at every prime.
+We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod $p$ homology of their algebras; these are the Barratt--Eccles \cite{berger2004combinatorial}, surjection \cite{mcclure2003multivariable}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
 Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical multioperations generalizing the \mbox{cup-$i$} products of Steenrod to every prime.
-An alternative approach based on the Eilenberg--Zilber contraction can be found in \cite{gonzalez2005hpt}.
-The $p = 2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod47products} and recovered by several authors \cites{mcclure03cochain, berger04combinatorial, medina2021newformulas}, and in the cubical setting to the cup-$i$ products of Kadeishvili \cite{kadeishvili1998dg} and Kr\v{c}\'{a}l--Pilarczy \cite{pilarczyk2016cubical}.
+An alternative approach based on the Eilenberg--Zilber contraction can be found in \cite{gonzalez2005cocyclic}.
+The $p = 2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod1947products} and recovered by several authors \cite{mcclure2003multivariable, berger2004combinatorial, medina2021newformulas}, and in the cubical setting to the cup-$i$ products of Kadeishvili \cite{kadeishvili2003cupi} and Kr\v{c}\'{a}l--Pilarczy \cite{pilarczyk2016cubical}.
 
 A context where the cubical viewpoint arises naturally is the study of loop spaces.
-This is through Baues' geometric generalization of Adams' cobar construction \cite{baues1980geometry, adams1957cobar}.
+This is through Baues' geometric generalization of Adams' cobar construction \cite{adams1956cobar, baues1998hopf}.
 Using Baues' work, an application of the constructions presented in this paper is the explicit descriptions of Steenrod operations on the cobar construction on the coalgebra of chains of reduced simplicial sets \cite{medina2021cobar}.
@@
 
-An outline of the article is presented next.
+\subsection{Outline}
+
 We first introduce, in Section~\ref{s:preliminaries}, the conventions we will follow regarding chain complexes, simplicial sets and cubical sets.
@@
 The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Dev Sinha, Greg Brumfiel, Federico Cantero-Mor\'an, Jens Kjaer, Calista Bernard, and Andy Putnam for insightful discussions, and to the anonymous referee for many keen observations and helpful suggestions.
+
+A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1}, and the hospitality of the \textit{Laboratory for Topology and Neuroscience} at EPFL

### 2021-08-20 sec/operads.tex
Structural refactoring using new template

--- 2021-07-30 operads.tex
@@
-\section{$\Gamma$-modules, operads and props} \label{s:operads}
+\section{\texorpdfstring{$\Gamma$}{Gamma}-modules, operads and props} \label{s:operads}
 
@@
 satisfying their own versions of associativity, equivariance and unitality.
-For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008operads}.
+For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008props}.
 
@@
 
-\begin{definition} [\cite{may72geometry}, \cite{boardman1973homotopy}] \label{def: e-infinity operad and prop}
+\begin{definition} [\cite{may1972geometry}, \cite{boardman1973homotopy}] \label{def: e-infinity operad and prop}
 	An operad is said to be an $E_\infty$-operad if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a prop $\mathcal P$ is said to be an $E_\infty$-prop if either $U_1(\mathcal P)$ or $U_2(\mathcal P)$ is an \mbox{$E_\infty$-operad}.

### 2021-08-20 sec/outlook.tex
Structural refactoring using new template

--- 2021-07-30 outlook.tex
@@
 
-In Higher Category Theory, the paper \cite{medina2020globular} constructs a functor producing strict \mbox{$\infty$-cat}egories from group-like cup-$i$ coalgebras in a manner similar to \cite{steiner2004omega}.
+In Higher Category Theory, the paper \cite{medina2020globular} constructs a functor producing strict $\infty$-categories from group-like cup-$i$ coalgebras in a manner similar to \cite{steiner2004omega}.
 In particular, the cup-$i$ constructions described in this article for standard simplices and cubes define, respectively, the Street nerve and cubical nerve of strict $\infty$-categories.
@@
 In this article we have not focused on the operations that exist non-trivially for \mbox{$E_n$-algebras} with $n$ finite, see part III of \cite{may76homology}.
-A treatment close to ours for the $E_2$ case was given in \cite{Tourtchine}.
-Effective constructions for these Dyer--Lashof--Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang, sinha2013littledisks, berger04combinatorial, ayala2014configuration} and higher categories \cite{Bathigher, BalFiedSchwVogt, Rezkhigher}, and will appear elsewhere.
+A treatment close to ours for the $E_2$ case was given in \cite{tourtchine2006cohen}.
+Effective constructions for these Dyer--Lashof--Cohen operations should be related to the geometry and combinatorial structure of configuration spaces \cite{KZhang, sinha2013littledisks, berger2004combinatorial, ayala2014configuration} and higher categories \cite{Bathigher, BalFiedSchwVogt, Rezkhigher}, and will appear elsewhere.

### 2021-08-20 sec/steenrod.tex
Structural refactoring using new template

--- 2021-07-30 steenrod.tex
@@
 
-We now introduce an operadic structure giving rise to Steenrod operations based in \cite{may70generalapproach}.
+We now introduce an operadic structure giving rise to Steenrod operations based in \cite{may1970general}.
 In our presentation we emphasize the integral structure needed to define them at every prime.
-For a more geometric treatment we refer the reader to \cites{may72geometry, may76homology, lawson2020n}, and for a different operadic approach at the even prime to \cite{chataur2005adem-cartan}.
+For a more geometric treatment we refer the reader to \cite{may1972geometry, may76homology, lawson2020dyerlashof}, and for a different operadic approach at the even prime to \cite{chataur2005adem-cartan}.
 
@@
 & \mathcal R \arrow[dr, "\phi", out=0] & \\
-\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \End_A.
+\mathcal W \arrow[ur, "\iota", out=55, in=180] \arrow[rr, "\psi"] & & \End_A.
 \end{tikzcd}
 \end{equation*}
-We can relate this structure on $A$ to those considered by May in \cite{may70generalapproach} as follows.
+We can relate this structure on $A$ to those considered by May in \cite{may1970general} as follows.
 The morphism $\phi$ provides $A$ with the structure of a homotopy associative algebra defined by the image in $\Hom(A^{\otimes 2}, A)$ of a representative in $\mathcal R(2)$ of a generator of its $0\th$-homology.
@@
 A claim that follows from the iterated product being a representative of a generator of the $0\th$-homology of $\mathcal R(r)$, and $\iota$ being a quasi-isomorphism of $\mathrm C$-modules.
-Furthermore, for $r$ equal to a prime $p$, tensoring the integers with $\F_p$ makes the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
-For any object $(A, \theta)$ in this category, Definition 2.2 in \cite{may70generalapproach} defines operations on the mod $p$ homology of $A$, a construction we review below.
+Furthermore, for $r$ equal to a prime $p$, tensoring the integers with $\Fp$ makes the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
+For any object $(A, \theta)$ in this category, Definition 2.2 in \cite{may1970general} defines operations on the mod $p$ homology of $A$, a construction we review below.
 In particular, if $A$ is given by the cochains of a space these products agree with Steenrod's original definitions, and for $A$ being the chains on an infinite loop spaces, with those defined by Araki--Kudo and Dyer--Lashof.
@@
 Notice that the Steenrod squares are determined by the Steenrod $(2,i)$-products with $\mathbb{F}_2$-coefficients.
-These binary operations are known as cup-$i$ products \cite{steenrod47products, medina2021newformulas}.
+These binary operations are known as cup-$i$ products \cite{steenrod1947products, medina2021newformulas}.
 In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod $\big(p, k(p-1)-\varepsilon\big)$-products for $\varepsilon \in \{0,1\}$.
@@
 \begin{remark}
-	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq. 6.1. in \cite{steenrod53cyclic}).
+	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq. 6.1. in \cite{steenrod1953cyclic}).
 	The notation $\beta P_s$ is motivated by the relationship of this operator and the Bockstein of the reduction $\mathbb Z \to \mathbb Z/p\mathbb Z$.
@@
 Steenrod operations defined as above satisfy the so called \textit{Adem relations}.
-Below we present its most common form and refer to Theorem 4.7 in \cite{may70generalapproach} for a complete list.
+Below we present its most common form and refer to Theorem 4.7 in \cite{may1970general} for a complete list.
 
@@
 		\begin{equation*}
-		P_{a}P_{b} = \sum_i {2i-a \choose a-b-i-1} P_{a+b-i}P_i,
+		P_{a} P_{b} = \sum_i \binom{2i-a}{a-b-i-1} P_{a+b-i}P_i,
 		\end{equation*}
@@
 		\begin{equation*}
-		P_{a}P_{b} = \sum_i (-1)^{a+i}{pi-a \choose a-(p-1)b-i-1} P_{a+b-i}P_i.
+		P_{a} P_{b} = \sum_i (-1)^{a+i} \binom{pi-a}{a-(p-1)b-i-1} P_{a+b-i}P_i.
 		\end{equation*}
@@
 	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
-	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\phi$ an operad map from an $E_\infty$-operad to $\End_A$, this is an \textit{Adem object} in the sense of Definition 4.1 of \cite{may70generalapproach}.
+	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\phi$ an operad map from an $E_\infty$-operad to $\End_A$, this is an \textit{Adem object} in the sense of Definition 4.1 of \cite{may1970general}.
 	The statement presented here is stated and proven as part of Theorem 4.7 loc. cit.
@@
 It is also useful to consider them over the category of coalgebras, that is to say, requiring each chain complex to be equipped with a coproduct and all structure maps to be morphisms of coalgebras.
-As described in Definition~1.2 of \cite{may70generalapproach}, the $\mathrm{C}$-module $\mathcal W$ lifts to this category.
+As described in Definition~1.2 of \cite{may1970general}, the $\mathrm{C}$-module $\mathcal W$ lifts to this category.
 A \textit{comultiplicative May--Steenrod structure} on an operad $\mathcal O$ is a morphism of $\mathrm{C}$-modules $\psi \colon \mathcal W \to \mathcal O$ for which there exists a factorization through an $E_\infty$-operad over the category of coalgebras
@@
 & \mathcal R \arrow[dr, "\phi", out=0] & \\
-\mathcal W \arrow[ur, "\iota", in=180] \arrow[rr, "\psi"] & & \mathcal O
+\mathcal W \arrow[ur, "\iota", out=55, in=180] \arrow[rr, "\psi"] & & \mathcal O
 \end{tikzcd}
@@
 	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\iota$ a quasi-isomorphism in the category of $\mathrm{C}$-modules over the category of coalgebras, this is a \textit{Cartan object} as defined in pag.
-161 of \cite{may70generalapproach}.
+161 of \cite{may1970general}.
 	The statement presented here is stated in pag.~165 loc.~cit.
@@
 
-For the even prime, constructive proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{medina2020adem} and \cite{medina2020cartan}.
+For the even prime, constructive proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{medina2021adem} and \cite{medina2020cartan}.

### 2021-08-21 sec/groups.tex
Update references and split-off acks

@@
 
-A \textit{resolution} in $\mathbf{Ch}_R$ is a quasi-isomorphism $P \to M$ with each $P_r$ a free \mbox{$R$-module}.
+A \textit{resolution} in $\mathbf{Ch}_R$ is a quasi-isomorphism $P \to M$ with each $P_r$ a free $R$-module.
 We will use the fact, explained in Section 6.5 of \cite{jacobson1989algebra}, that such resolutions exist for any chain complex $M$ concentrated in non-negatively degrees, in particular, for the monoidal unit $R$.
@@
 
-In this work, we are interested in the mod $p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite[Corollary~VI.1.4]{adem2004milgram}, is detected by the inclusion $\iota \colon \mathrm{C}_p \to \mathrm{S}_p$., i.e., $\iota$ induces a surjection in mod $p$ homology.
+In this work, we are interested in the mod $p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite[Corollary~VI.1.4]{adem2004milgram}, is detected by the inclusion $\iota \colon \mathrm{C}_p \to \mathrm{S}_p$, i.e., $\iota$ induces a surjection in mod $p$ homology.
 We now describe the kernel of this surjection.

### 2021-08-21 sec/introduction.tex
Update references and split-off acks

@@
 The role Steenrod operations play in stable homotopy theory is hard to overstate.
-The reason is that, given the representability of the cohomology functor, these operations together with the Bockstein homomorphism can be used to give a complete description of the algebraic structure naturally present on the mop-$p$ \mbox{cohomology} algebra of spaces.
+The reason is that, given the representability of the cohomology functor, these operations together with the Bockstein homomorphism can be used to give a complete description of the algebraic structure naturally present on the mop-$p$ cohomology algebra of spaces.
 For the even prime, Steenrod squares were introduced in \cite{steenrod1947products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander--Whitney's chain approximation to the diagonal, the so called cup-$i$ products.
@@
 This viewpoint enhanced the conceptual understanding of the operations and allowed for many advances \cite{adem1952iteration, milnor1958dual, adams1995stable}, but lacked the concreteness of their definition at the even prime.
-The purpose of this paper is to fill this gap in the literature, introducing effective descriptions of multioperations at the cochain level generalizing Steenrod's cup-$i$ products defining Steenrod operations at all primes.
+The purpose of this paper is to fill this gap in the literature, introducing effective descriptions of multioperations at the cochain level -- generalizations of the Steenrod's cup-$i$ products -- that define Steenrod operations at all primes.
 
-In recent years, thanks to the development of new applications of cohomology, most notably in applied topology and topological quantum field theories, the need to have an effectively computable definition of Steenrod operations has gain considerable importance.
+In recent years, thanks to the development of new applications of cohomology in areas such as applied topology and topological quantum field theories, the need to have an effectively computable definition of Steenrod operations has gain considerable importance.
 
@@
 
-The chain level viewpoint for the study of homology operations was brought to the forefront by string topology \cite{sullivan2007presentstate}, and as served as a major driver of innovation \cite{tradler2007string, hoch2}.
-
-In lattice field theory, cup-$i$ products are used in the construction of effective actions \cite{gaiotto2016spin, bhardwaj2017fermionic, kapustin2017fermionic}, and this connection with physics motivated the development of effective versions of spin bordism \cite{brumfiel2016pontrjagin, brumfiel2018quadratic} prominently featuring higher derived structures at the cochain level \cite{medina2020cartan, medina2021adem}.
+In physics, cup-$i$ products are used in the construction of actions for lattice theories whose fields are cochains \cite{gaiotto2016spin, bhardwaj2017fermionic, kapustin2017fermionic}.
+This connection with physics motivated the development of effective versions of spin bordism \cite{brumfiel2016pontrjagin, brumfiel2018pontrjagin} prominently featuring higher derived structures at the cochain level \cite{medina2020cartan, medina2021adem}.
 
@@
 We then describe effective constructions of this structure on three prominent models of the $E_\infty$-operad, identifying elements in them that represent Steenrod operations in the mod $p$ homology of their algebras; these are the Barratt--Eccles \cite{berger2004combinatorial}, surjection \cite{mcclure2003multivariable}, and $U(\mathcal M)$ \cite{medina2020prop1} operads.
-Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical multioperations generalizing the \mbox{cup-$i$} products of Steenrod to every prime.
+Since the cochains of simplicial sets are equipped with effective and compatible algebra structures over each of these operads, we are able to explicitly describe canonical multioperations at the cochain level representing Steenrod operations at every prime, generalizing Steenrod's original cup-$i$ products \cite{steenrod1947products}.
 An alternative approach based on the Eilenberg--Zilber contraction can be found in \cite{gonzalez2005cocyclic}.
-The $p = 2$ part of our constructions specialize in the simplicial context to the definition of cup-$i$ products given by Steenrod \cite{steenrod1947products} and recovered by several authors \cite{mcclure2003multivariable, berger2004combinatorial, medina2021newformulas}, and in the cubical setting to the cup-$i$ products of Kadeishvili \cite{kadeishvili2003cupi} and Kr\v{c}\'{a}l--Pilarczy \cite{pilarczyk2016cubical}.
 
-A context where the cubical viewpoint arises naturally is the study of loop spaces.
-This is through Baues' geometric generalization of Adams' cobar construction \cite{adams1956cobar, baues1998hopf}.
-Using Baues' work, an application of the constructions presented in this paper is the explicit descriptions of Steenrod operations on the cobar construction on the coalgebra of chains of reduced simplicial sets \cite{medina2021cobar}.
+The operad $\UM$ also acts effectively on cubical cochains \cite{medina2021cubical}, so we obtain explicit cochain level multioperations representing the Steenrod operations in this setting, which generalize the cup-$i$ constructions of Kadeishvili \cite{kadeishvili2003cupi} and Kr\v{c}\'{a}l--Pilarczy \cite{pilarczyk2016cubical}.
+A context where the cubical viewpoint arises naturally is the study of base loop spaces.
+This is through Baues' cubical generalization of Adams' cobar construction \cite{adams1956cobar, baues1998hopf}.
+Using Baues' work, an application of the constructions presented in this paper is the explicit descriptions, at the chain level, of Steenrod operations on the cobar construction of the coalgebra of chains on a reduced simplicial set \cite{medina2021cobar}.
 
@@
 
-\subsection{Outline}
+\subsection*{Outline}
 
@@
 We end, in Section~\ref{s:outlook}, with an overview of some connections of this work to certain geometric and combinatorial structures and provide an outline of future research directions.
-
-\section*{Acknowledgement}
-
-The authors thank Dennis Sullivan, Kathryn Hess, Clemens Berger, John Morgan, Dev Sinha, Greg Brumfiel, Federico Cantero-Mor\'an, Jens Kjaer, Calista Bernard, and Andy Putnam for insightful discussions, and to the anonymous referee for many keen observations and helpful suggestions.
-
-A.M-M. acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1}, and the hospitality of the \textit{Laboratory for Topology and Neuroscience} at EPFL

### 2021-08-21 sec/operads.tex
Update references and split-off acks

@@
 \begin{tikzcd}[column sep=small, row sep=tiny]
-& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"', out=180, in=55] \arrow[dr, "U_2", out=0, in=125] & \\
+& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"', out=-120, in=0] \arrow[dr, "U_2", out=-60, in=180] & \\
 \mathbf{Ch}_R^{\mathrm{S}^{op}} & & \mathbf{Ch}_R^{\mathrm{S}},
@@
 
-Operads an props are respectively $\mathrm{S}$-modules and \mbox{$\mathrm{S}$-bimodules} enriched with further compositional structure.
+Operads an props are respectively $\mathrm{S}$-modules and $\mathrm{S}$-bimodules enriched with further compositional structure.
 These structures are best understood by abstracting the compositional structure naturally present in the coendomorphism $\mathrm{S}$-module $\End^A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a prop.
@@
 \begin{definition} [\cite{may1972geometry}, \cite{boardman1973homotopy}] \label{def: e-infinity operad and prop}
-	An operad is said to be an $E_\infty$-operad if its underlying \mbox{$\mathrm{S}$-module} is $E_\infty$, and a prop $\mathcal P$ is said to be an $E_\infty$-prop if either $U_1(\mathcal P)$ or $U_2(\mathcal P)$ is an \mbox{$E_\infty$-operad}.
+	An operad is said to be an $E_\infty$-operad if its underlying $\mathrm{S}$-module is $E_\infty$, and a prop $\mathcal P$ is said to be an $E_\infty$-prop if either $U_1(\mathcal P)$ or $U_2(\mathcal P)$ is an $E_\infty$-operad.
 \end{definition}

### 2021-08-21 sec/outlook.tex
Update references and split-off acks

@@
 
-In this article we have not focused on the operations that exist non-trivially for \mbox{$E_n$-algebras} with $n$ finite, see part III of \cite{may76homology}.
+In this article we have not focused on the operations that exist non-trivially for $E_n$-algebras with $n$ finite, see part III of \cite{may76homology}.
 A treatment close to ours for the $E_2$ case was given in \cite{tourtchine2006cohen}.

### 2021-08-21 sec/preliminaries.tex
Structural refactoring using new template
Update references and split-off acks

--- 2021-07-06 preliminaries.tex
@@
 A \textit{simplicial set} $X$ is a contravariant functor from the simplex category to the category of sets, and a simplicial map is a natural transformation between two simplicial sets.
-As is customary we use the notation
+As is customary, we use the notation
 \begin{equation*}
@@
 \begin{equation*}
-X = \colim_{\triangle^n \to X} \triangle^n.
+X \cong \colim_{\triangle^n \to X} \triangle^n.
 \end{equation*}
@@
 \end{equation*}
-%notice that iteratively
-%\begin{equation*}
-%\square^n = \overbrace{\square^1 \times \cdots \times \square^1}^{n \text{ times }}.
-%\end{equation*}
 We represent the non-degenerate elements of $\square^n$ as sequences $x_1 \cdots\, x_n$ with each $x_i \in \big\{[0], [1], [0,1]\big\}$.
@@
 \begin{equation*}
-X = \colim_{\square^n \to X} \square^n.
+X \cong \colim_{\square^n \to X} \square^n.
 \end{equation*}

### 2021-08-21 sec/steenrod.tex
Update references and split-off acks

@@
 	\end{equation*}
-	is defined by sending $a$ to the Steenrod \mbox{$(p, i)$-product} of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
+	is defined by sending $a$ to the Steenrod $(p, i)$-product of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
 \end{definition}

### 2021-08-28 may_st.tex
Update references and split-off acks
Add hyperref to email addresses

@@
 
-\author[R. Kaufmann]{Ralph M.\ Kaufmann}
-\address{R. Kaufmann, Department of Mathematics, Department of Physics and Astronomy, Purdue University}
-\email{rkaufman@purdue.edu}
+\author[R.~Kaufmann]{Ralph~M.~Kaufmann}
+\address{R.K., Department of Mathematics, Department of Physics and Astronomy, Purdue University}
+\email{\href{mailto:rkaufman@purdue.edu}{rkaufman@purdue.edu}}
 
-\author[A. Medina-Mardones]{Anibal M. Medina-Mardones}
-\address{A. Medina-Mardones, Max Planck Institute for Mathematics \and
-	University of Notre Dame du Lac}
-\email{ammedmar@mpim-bonn.mpg.de}
+\author{Anibal~M.~Medina-Mardones}
+\address{A.M-M., Max Plank Institute for Mathematics \and University of Notre Dame}
+\email{\href{mailto:ammedmar@mpim-bonn.mpg.de}{ammedmar@mpim-bonn.mpg.de}}
 
@@
 	\input{sec/introduction}
+	\input{aux/acknowledgement}
 	\input{sec/preliminaries}

### 2021-08-28 sec/steenrod.tex
Use terminology cup-(r,i) products

@@
 	A May--Steenrod structure on $\mathrm{End}_A$ is referred to as one on $A$.
-	Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod} $(r, i)$-\textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
+	Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod cup-}$(r, i)$ \textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.
 \end{definition}
@@
 	\end{equation*}
-	is defined by sending $a$ to the Steenrod $(p, i)$-product of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
+	is defined by sending $a$ to the Steenrod cup-$(p, i)$ product of $(a \otimes \cdots \otimes a) \in (A \otimes \mathbb{F}_p)^{\otimes p}$ if $i \geq 0$ and to $0$ otherwise.
 \end{definition}
@@
 
-Notice that the Steenrod squares are determined by the Steenrod $(2,i)$-products with $\mathbb{F}_2$-coefficients.
+Notice that the Steenrod squares are determined by the Steenrod cup-$(2,i)$ products with $\mathbb{F}_2$-coefficients.
 These binary operations are known as cup-$i$ products \cite{steenrod1947products, medina2021newformulas}.
-In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod $\big(p, k(p-1)-\varepsilon\big)$-products for $\varepsilon \in \{0,1\}$.
-We can explain the appearance of these specific Steenrod products as follows.
+In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod cup-$\big(p, k(p-1)-\varepsilon\big)$ products for $\varepsilon \in \{0,1\}$.
+We can explain the appearance of these specific Steenrod cup-$(p,1)$products as follows.
 The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even an $(2t+1)(p-1) - \varepsilon$ if $q$ is odd.

### 2021-08-28 sec/outlook.tex
Add a physics par. to outlook

@@
 
-In Higher Category Theory, the paper \cite{medina2020globular} constructs a functor producing strict $\infty$-categories from group-like cup-$i$ coalgebras in a manner similar to \cite{steiner2004omega}.
-In particular, the cup-$i$ constructions described in this article for standard simplices and cubes define, respectively, the Street nerve and cubical nerve of strict $\infty$-categories.
-We anticipate that the more general Steenrod $(p,i)$-products constructed in this work will also have deep combinatorial interpretations.
-
-There is a functorial approach to the theory using the formalism of Feynman categories \cite{feynman},
-which renders all the structures and notions natural.
+There is a functorial approach to the theory using the formalism of Feynman categories \cite{feynman}.
 This includes cyclic, planar cyclic as well as Berger's pre-operads \cite{BergerRecog}.
 Their interplay is of independent interest \cite{BergerKaufmann, feyrep} and will be linked directly to the constructions of this paper.
+
+In higher category theory, the paper \cite{medina2020globular} constructs a functor producing strict $\infty$-categories from group-like cup-$i$ coalgebras in a manner similar to \cite{steiner2004omega}.
+In particular, the cup-$i$ constructions described in this article for standard simplices and cubes define, respectively, the Street nerve and cubical nerve of strict $\infty$-categories.
+We anticipate that the more general Steenrod cup-$(p,i)$ products constructed in this work will also have deep combinatorial interpretations.
+
+In physics, Gaiotto, Kapustin, Thorngren \cite{gaiotto2016spin,bhardwaj2017fermionic,kapustin2017fermionic} and others have considered cellular decompositions of spacetime and fields represented by simplicial and cubical cochains.
+In order to express subtle interactions between these fields, they have used cup-$i$ products to define relevant action functionals for topological field theories.
+We expect that new topological field theories of interest can be defined using Steenrod cup-$(p,i)$ products defined in this work.
 

### 2021-08-30 sec/effective.tex
Update references and split-off acks
Use terminology cup-(r,i) products
Improvements after Greg's proofreading

@@
 In this section we construct explicit May--Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt--Eccles operad $\mathcal E$ \cite{berger2004combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure2003multivariable}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-prop $\mathcal M$ introduced in \cite{medina2020prop1}.
-We also define natural and effective May--Steenrod structure on the normalized cochains of any simplicial or cubical set using that these are algebras over the operad $U(\mathcal M)$.
+We also define natural and effective May--Steenrod structures on the normalized cochains of any simplicial or cubical set using that these are algebras over the operad $U(\mathcal M)$.
 
@@
 
-\begin{figure}
+\begin{figure}[ht]
 	\begin{tikzcd}
-	& & & U(\mathcal M) \arrow[dddr, bend left=10, "\phi^\triangle"'] \arrow[dddrr, bend left=20, "\phi^\square"'] & & \\
+	& & & U(\mathcal M) \arrow[dddr, bend left=10, "\phi^\triangle_X"'] \arrow[dddrr, bend left=20, "\phi^\square_Y"'] & & \\
 	& & \mathcal X \arrow[ru, "SL"] & & & \\
 	& \mathcal E \arrow[ur, "TR"] & & & & \\
-	\mathcal W \arrow[rrrr, "\psi^\triangle", bend right=10] \arrow[rrrrr, "\psi^\square", bend right=20] \arrow[ur, "\psi_{\mathcal E}"] \arrow[uurr, "\psi_{\mathcal X}"', bend right=35, pos=.6] \arrow[uuurrr, "\psi_{U(\mathcal M)}"', bend right=45, pos=0.6] & & & & \End_{N^\bullet(X)} & \End_{N^\bullet(X)}
+	\mathcal W \arrow[rrrr, "\psi^\triangle_X", bend right=10] \arrow[rrrrr, "\psi^\square_Y", bend right=20] \arrow[ur, "\psi_{\mathcal E}"] \arrow[uurr, "\psi_{\mathcal X}"', bend right=35, pos=.6] \arrow[uuurrr, "\psi_{U(\mathcal M)}"', bend right=45, pos=0.6] & & & & \End_{N^\bullet_\triangle(X)} & \End_{N^\bullet_\square(Y)}
 	\end{tikzcd}
@@
 
-\subsection{Barratt--Eccles operad} In this subsection we effectively describe a May--Steenrod structure on the Barratt--Eccles operad.
+\subsection{Barratt--Eccles operad} In this subsection we effectively describe a May--Steenrod structure on the Barratt--Eccles operad via explicit formulae.
 
@@
 \end{equation*}
-The chain complex resulting from applying the functor of normalized integral chains to it is denoted $\mathcal E(r)$, which corresponds to the arity $r$ part of the Barratt--Eccles operad.
+The chain complex resulting from applying the functor of normalized integral chains to it is denoted $\mathcal E(r)$, which is the arity $r$ chain complex of the Barratt--Eccles operad.
 
@@
 \begin{proof}
-	Since $\mathcal X$ is an $E_\infty$-operad, we simply need to prove that the $\Z[\mathrm{C}_r]$-linear map
+	Since $\mathcal E$ is an $E_\infty$-operad, we simply need to prove that the $\Z[\mathrm{C}_r]$-linear map
 	\begin{equation*}
@@
 	\end{equation*}
-	is a chain map for every $r \geq 0$.
+	is a quasi-isomorphism for every $r \geq 0$.
 	We simplify notation and write $\psi$ instead of $\psi_{\mathcal E}(r)$.
@@
 \begin{remark}
-	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota \colon \mathrm C_r \to \mathrm S_r$ induces both; a simplicial inclusion $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ and one of $\mathrm C$-modules
+	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota \colon \mathrm C_r \to \mathrm S_r$ induces both a simplicial inclusion $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ and one of $\mathrm C$-modules
 	\begin{equation*}
@@
 Using the Berger--Fresse convention, we can define a May--Steenrod structure on the surjection operad by composing the map $\psi_{\mathcal E}$ with the \textit{table reduction} quasi-isomorphism $\mathcal E \to \mathcal X$ introduced in Section 1.3 of \cite{berger2004combinatorial}.
-We define an May--Steenrod structure on the surjection operad in a convention independent way which recovers the table reduction May--Steenrod structure in the Berger--Fresse case.
+We define a May--Steenrod structure on the surjection operad in a convention independent way which recovers the table reduction May--Steenrod structure in the Berger--Fresse case.
 
@@
 \end{equation}
-Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at the time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on.
+Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on.
 Since we do not use the composition structure we refer to \cite{mcclure2003multivariable} for it.
@@
 Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure--Smith to prove $\mathcal X$ is an $E_\infty$-operad and whose introduction is credited to Benson \cite{benson1998rep}.
-Let the maps $i,\ p$ and $s$ be defined on basis elements, represented by sequences, as follows: $i \colon \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p \colon \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurrence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s \colon \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
+Let the maps $i$, $p$, and $s$ be defined on basis elements, represented by sequences, as follows: $i \colon \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p \colon \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurrence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s \colon \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
 with a 1, then the new sequence is degenerate so $s$ takes it to $0$.
@@
 	\end{equation*}
-	introduced in Definition \ref{def: Steenrod-Adem on surjection} is a chain map for every $r \geq 0$.
+	introduced in Definition \ref{def: Steenrod-Adem on surjection} is a quasi-isomorphism for every $r \geq 0$.
 	We simplify notation and write $\psi$ instead of $\psi_{\mathcal X}(r)$.
@@
 We will define a May--Steenrod structure $\psi_{U(\mathcal M)} \colon \mathcal W \to U(\mathcal M)$ by composing the May--Steenrod structure $\psi_{\mathcal X} \colon \mathcal W \to \mathcal X$ with a morphism $SL \colon \mathcal X \to U(\mathcal M)$ of $\mathrm{C}$-modules ($\mathrm{S}$-modules in fact) that we now define.
-Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element represented by the immersed connected $(1,r)$-graph
+Given a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\}$ let $SL(s)$ be the element represented by the immersed connected $(1,r)$-graph:
 

### 2021-08-30 sec/groups.tex
Improvements after Greg's proofreading

@@
 
-Fixing notation, let $\mathrm{S}_r$ be the symmetric group of $r$ elements and $\mathrm{C}_r$ be the cyclic group of order $n$ thought of as the subgroup of $\mathrm{S}_r$ generated by an element~$\rho$.
+Fixing notation, let $\mathrm{S}_r$ be the symmetric group of $r$ elements and $\mathrm{C}_r$ be the cyclic group of order $r$ thought of as the subgroup of $\mathrm{S}_r$ generated by an element~$\rho$.
 We denote this inclusion by $\iota \colon \mathrm C_r \to \mathrm S_r$.
@@
 Let $\mathrm G$ be a group and $M$ an $R[\mathrm G]$-module, we define the \textit{homology of $\mathrm G$ with coefficients in $M$}, denoted $H(\mathrm G; M)$, as the homology of any chain complex $P \otimes_{R[\mathrm G]} M$ with $P \to R$ a resolution.
-We will be particularly interested in the case when $M = \mathbb F_p(q)$ is the trivial or sign $\mathbb F_p[\mathrm{S}_r]$-module depending on the parity of~$q$.
+We will be particularly interested in the case when $M = \mathbb F_p(q)$ is the trivial or sign $\mathbb F_p[\mathrm{S}_r]$-module depending on if the parity of~$q$ is even or odd respectively.
 
@@
 With untwisted coefficients, the method of computation followed by several authors was to prove the injectivity of this homology into that of the infinite symmetric group and take advantage of a natural Hopf algebra structure on it.
-A powerful result stemming from the deep connection of this question with infinite loop space theory, is the existence of a homology isomorphism of spaces
+A powerful result stemming from the deep connection of this question with infinite loop space theory is the existence of a homology isomorphism of spaces
 \begin{equation*}
@@
 
-In this work, we are interested in the mod $p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite[Corollary~VI.1.4]{adem2004milgram}, is detected by the inclusion $\iota \colon \mathrm{C}_p \to \mathrm{S}_p$, i.e., $\iota$ induces a surjection in mod $p$ homology.
+In this work, we are interested in the mod $p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite[Corollary~VI.1.4]{adem2004milgram}, is detected by a group inclusion $\iota \colon \mathrm{C}_p \to \mathrm{S}_p$, that is, the map induced in mod $p$ group homology is a surjection.
 We now describe the kernel of this surjection.

### 2021-08-30 sec/introduction.tex
Improvements after Greg's proofreading

@@
 For the even prime, Steenrod squares were introduced in \cite{steenrod1947products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander--Whitney's chain approximation to the diagonal, the so called cup-$i$ products.
-Later, for odd primes, their definition was given non-effectively using arguments based on the mod $p$ homology of symmetric groups \cite{steenrod1952reduced, steenrod1962cohomology, steenrod1962cohomology}.
+Later, for odd primes, their definition was given non-effectively using existence arguments based on the mod $p$ homology of symmetric groups \cite{steenrod1952reduced, steenrod1962cohomology, steenrod1962cohomology}.
 This viewpoint enhanced the conceptual understanding of the operations and allowed for many advances \cite{adem1952iteration, milnor1958dual, adams1995stable}, but lacked the concreteness of their definition at the even prime.
@@
 
-In applied topology, the use of persistence homology \cite{edelsbrunner2002topological, carlsson2005barcode} has open many new interdisciplinary research directions \cite{chan2013viral, hess2017cliques}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
+In applied topology, the use of persistence homology \cite{edelsbrunner2002topological, carlsson2005barcode} has created many interdisciplinary research directions \cite{chan2013viral, hess2017cliques}, and the availability of formulae for the cup-$i$ products allowed for the development of a theory of persistence Steenrod modules accessing finer features of the data \cite{medina2018persistence}.
 

### 2021-08-30 sec/operads.tex
Improvements after Greg's proofreading

@@
 & \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"', out=-120, in=0] \arrow[dr, "U_2", out=-60, in=180] & \\
-\mathbf{Ch}_R^{\mathrm{S}^{op}} & & \mathbf{Ch}_R^{\mathrm{S}},
+\mathbf{Ch}_R^{\mathrm{S}^{op}} & & \mathbf{Ch}_R^{\mathrm{S}}.
 \end{tikzcd}
 \end{equation*}
-and that for any object $A$ in $\mathbf{Ch}_R$ the canonical \textit{endomorphism bimodule}
+Explicitly, $U_1(\mathcal P)(r) = \mathcal P(r,1)$ and $U_2(\mathcal P)(r) = \mathcal P(1,r)$ for any $\mathcal P$ in $\mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}}$.
+Notice that for any object $A$ in $\mathbf{Ch}_R$ the canonical \textit{endomorphism bimodule}
 \begin{equation*}
@@
 
-A \textit{resolution} in $\mathbf{Ch}_R^\Gamma$ is a morphism $\phi$ of $\Gamma$-modules such that $\phi(r)$ is a resolution in the category of chain complexes of $R[\Gamma_r]$-modules for each $r \in \mathbb{N}$.
+A \textit{resolution} in $\mathbf{Ch}_R^\Gamma$ is a morphism $\phi$ of $\Gamma$-modules such that $\phi(r)$ is a resolution in the category of chain complexes of $R[\Gamma_r]$-modules for each $r \in \mathbb{N}$, where $\Gamma_r$ denotes $\Gamma(r,r)$.
 A $\Gamma$-module $\mathcal R$ is said to be $E_\infty$ if $\mathcal R(0) = R$ and there exists a resolution $\mathcal R \to \underline{R}$ where $\underline{R}$ is the object in $\mathbf{Ch}_R^\Gamma$ defined by $\underline{R}(r) = R$ and $\underline{R}(\gamma) = \mathrm{id}_R$ for every $r \in \mathbb{N}$ and $\gamma \in \Gamma_r$.
@@
 
-Operads an props are respectively $\mathrm{S}$-modules and $\mathrm{S}$-bimodules enriched with further compositional structure.
-These structures are best understood by abstracting the compositional structure naturally present in the coendomorphism $\mathrm{S}$-module $\End^A$, naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a prop.
+Operads and props are respectively $\mathrm{S}$-modules and $\mathrm{S}$-bimodules enriched with further compositional structure.
+These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$ (or $\End^A$), naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a prop.
 

### 2021-08-30 sec/outlook.tex
Improvements after Greg's proofreading

@@
 
-In physics, Gaiotto, Kapustin, Thorngren \cite{gaiotto2016spin,bhardwaj2017fermionic,kapustin2017fermionic} and others have considered cellular decompositions of spacetime and fields represented by simplicial and cubical cochains.
+In physics, Gaiotto, Kapustin, Thorngren \cite{gaiotto2016spin,bhardwaj2017fermionic,kapustin2017fermionic} and others have considered cellular decompositions of spacetime together with fields represented by cellular cochains.
 In order to express subtle interactions between these fields, they have used cup-$i$ products to define relevant action functionals for topological field theories.
-We expect that new topological field theories of interest can be defined using Steenrod cup-$(p,i)$ products defined in this work.
+We expect that new topological field theories of interest can be studied using the Steenrod cup-$(p,i)$ products introduced in this work.
 

### 2021-08-30 sec/preliminaries.tex
Improvements after Greg's proofreading

@@
 \end{equation*}
-We represent the non-degenerate elements of $\triangle^n_k$ as an increasing sequence $[v_0, \dots, v_k]$ of non-negative integers each less than or equal to $n$.
+We represent the non-degenerate elements of $\triangle^n_k$ as increasing sequences $[v_0, \dots, v_k]$ of non-negative integers each less than or equal to $n$.
 
@@
 
-A \textit{cubical set} $X$ is a contravariant functor from the cube category to the category of, sets and a cubical map is a natural transformation between two cubical sets.
+A \textit{cubical set} $X$ is a contravariant functor from the cube category to the category of sets, and a cubical map is a natural transformation between two cubical sets.
 As is customary, we use the notation

### 2021-08-30 sec/steenrod.tex
Improvements after Greg's proofreading

@@
 	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$.
-	In this language, a choice of factorization $\phi \circ \iota$ of a May--Steenrod structure on $\mathcal O$ endows it with a \textit{commutative multiplication} $\phi$.
+	In this language, a choice of factorization $\phi \circ \iota$ of a May--Steenrod structure on $\mathcal O$ endows it with $\phi$ a \textit{multiplication commutative up to coherent homotopies}.
 \end{remark}
@@
 The morphism $\phi$ provides $A$ with the structure of a homotopy associative algebra defined by the image in $\Hom(A^{\otimes 2}, A)$ of a representative in $\mathcal R(2)$ of a generator of its $0\th$-homology.
-Restricting $\psi$ to arity $r$ defines a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$ and the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ as presented in Definitions 2.1 op.
+Restricting $\psi$ to arity $r$ defines a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$ that makes the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ as presented in Definitions 2.1 op.
 cit.
-Explicitly, this pair is such that $\psi(e_0) \in \End_A(r)$ is $\mathrm C_r$-homotopic to the iterated product $A^{\otimes r} \to A$.
+Explicitly, this means that the pair is such that $\psi(e_0) \in \End_A(r)$ is $\mathrm C_r$-homotopic to the iterated product $A^{\otimes r} \to A$.
 A claim that follows from the iterated product being a representative of a generator of the $0\th$-homology of $\mathcal R(r)$, and $\iota$ being a quasi-isomorphism of $\mathrm C$-modules.
 Furthermore, for $r$ equal to a prime $p$, tensoring the integers with $\Fp$ makes the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
-For any object $(A, \theta)$ in this category, Definition 2.2 in \cite{may1970general} defines operations on the mod $p$ homology of $A$, a construction we review below.
+For any object $(A, \theta)$ in this category, Definition~2.2 in \cite{may1970general} defines operations on the mod $p$ homology of $A$, a construction we review below.
 In particular, if $A$ is given by the cochains of a space these products agree with Steenrod's original definitions, and for $A$ being the chains on an infinite loop spaces, with those defined by Araki--Kudo and Dyer--Lashof.
@@
 
-Notice that the Steenrod squares are determined by the Steenrod cup-$(2,i)$ products with $\mathbb{F}_2$-coefficients.
-These binary operations are known as cup-$i$ products \cite{steenrod1947products, medina2021newformulas}.
+Notice that the Steenrod operations above, corresponding to Steenrod squares in the context of spaces, are determined by the Steenrod cup-$(2,i)$ products with $\mathbb{F}_2$-coefficients.
+These binary operations are known as cup-$i$ products \cite{steenrod1947products, medina2021newformulas} in the space context.
 In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod cup-$\big(p, k(p-1)-\varepsilon\big)$ products for $\varepsilon \in \{0,1\}$.
-We can explain the appearance of these specific Steenrod cup-$(p,1)$products as follows.
-The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even an $(2t+1)(p-1) - \varepsilon$ if $q$ is odd.
+We can explain the appearance of these specific Steenrod cup-$(p,1)$ products as follows.
+The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even and $(2t+1)(p-1) - \varepsilon$ if $q$ is odd.
 According to Lemma \ref{lem: Thom's theorem}, these are the only homologically non-trivial cases.
@@
 	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
-	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\phi$ an operad map from an $E_\infty$-operad to $\End_A$, this is an \textit{Adem object} in the sense of Definition 4.1 of \cite{may1970general}.
+	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\phi$ an operad map from an $E_\infty$-operad to $\End_A$, the pair $(A, \theta)$ is an \textit{Adem object} in the sense of Definition 4.1 of \cite{may1970general}.
 	The statement presented here is stated and proven as part of Theorem 4.7 loc. cit.
@@
 So far we have considered $\mathrm{C}$-modules, operads and related structures over the category of chain complexes.
-It is also useful to consider them over the category of coalgebras, that is to say, requiring each chain complex to be equipped with a coproduct and all structure maps to be morphisms of coalgebras.
+It is also useful to consider them over the category of coalgebras, that is to say requiring each chain complex to be equipped with a coproduct and all structure maps to be morphisms of coalgebras.
 As described in Definition~1.2 of \cite{may1970general}, the $\mathrm{C}$-module $\mathcal W$ lifts to this category.
@@
 	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
-	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\iota$ a quasi-isomorphism in the category of $\mathrm{C}$-modules over the category of coalgebras, this is a \textit{Cartan object} as defined in pag.
-161 of \cite{may1970general}.
-	The statement presented here is stated in pag.~165 loc.~cit.
+	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\iota$ a quasi-isomorphism in the category of $\mathrm{C}$-modules over the category of coalgebras, this is a \textit{Cartan object} as defined in \cite[p.161]{may1970general}.
+	The statement presented here is stated in page~165 loc.~cit.
 \end{proof}
 
-For the even prime, constructive proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{medina2021adem} and \cite{medina2020cartan}.
+For the even prime, effective proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{medina2021adem} and \cite{medina2020cartan}.
+Explicitly, these proof construct cochains whose coboundaries descends to the relations in cohomology.

### 2021-10-04 other/proof_corrections.tex
Add dir for journal additional files

\documentclass{amsart}
% packages
\usepackage{tikz-cd}
\usepackage{fancyvrb}
\usepackage{biblatex}
\addbibresource{oldbib.bib}

% enviorenments
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{remark}[theorem]{Remark}

% sets
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\F}{\mathbb{F}}

% funtors and operators
\newcommand{\Hom}{\mathrm{Hom}}
\newcommand{\End}{\mathrm{End}}

% layout
\addtolength{\textwidth}{2in}
\addtolength{\textheight}{2in}
\calclayout

\begin{document}

We begin by thanking the reviewer for their careful reading and many valuable suggestions.
Below we include some changes to the proof.

\begin{enumerate}

\item Metadata \par
\begin{enumerate}
	\item \textit{Add Orcid for R.K.:}
0000-0002-7027-8329

\item \textit{Replace address of A.M-M.:}
Laboratory for Topology and Neuroscience, EPFL, Lausanne, Switzerland; and Max Planck Institute for Mathematics, Bonn, Germany

\item \textit{Replace email address of A.M-M.:}
ammedmar@mpim-bonn.mpg.de
\end{enumerate}

\item Abstract last sentence \par
\textit{Replace with:}
Using the operadic viewpoint of May, this article provides such definitions at all primes introducing multioperations that generalize the Steenrod cup-$i$ products on the simplicial and cubical cochains of spaces.

\item Update MSC from 2010 to 2020 \par
\textit{The listed reference codes do not change from the old to the new classification. In case it is useful, I include the code I use to update on amsclasses:} \\
\verb|\makeatletter| \\
\verb|\@namedef{subjclassname@2020}{%| \\
\verb|    \textup{2020} Mathematics Subject Classification}| \\
\verb|\makeatother|

\item Introduction par.2 last sentence \par
\textit{Make sure the citations is} \verb|medina2021adem| \textit{in:} ... at the cochain level \cite{medina2020cartan, medina2021adem}

\item Sect.2.1, first displayed equation: \par
\textit{Replace with:}

\begin{align*}
\Hom(A, A^\prime)_n & = \big\{f \ |\ a \in A_m \text{ implies } f(a) \in A^\prime_{m+n} \big\}, \\
\partial f & = \partial \circ f - (-1)^{|f|}f \circ \partial,
\end{align*}
and
\begin{align*}
(A \otimes A^\prime)_n & = \bigoplus_{p + q = n} A_p \otimes A^\prime_q, \\
\partial (a \otimes a^\prime) & = \partial a \otimes a^\prime + (-1)^{|a|} a \otimes \partial a^\prime.
\end{align*}

\item Sect.2.2 par.3 last sentence \par
\textit{Replace} as an increasing sequence \textit{with} as increasing sequences

\item Sect.3, par.1 first sentence: \par
\textit{Replace}  of order $n$ \textit{with} of order $r$

\item Sect.3, par.2 last sentence: \par
\textit{Remove:} in particular, for the monoidal unit $R$.

\item Sect.3, par.3: \par
\textit{Replace with:} Let $\mathrm G$ be a group and $M$ an $R[\mathrm G]$-module.
The \textit{homology of $\mathrm G$ with coefficients in $M$}, denoted by $H(\mathrm G; M)$, is defined as the homology of the chain complex $P \otimes_{R[\mathrm G]} M$ where $P \to R$ is any resolution in $\mathbf{Ch}_{R[\mathrm G]}$.
We will be particularly interested in the case when $M = \mathbb F_p(q)$ is the trivial or sign $\mathbb F_p[\mathrm{S}_r]$-module depending on if the parity of~$q$ is even or odd respectively.

\item Paragraph before Lemma 3.1: \par
\textit{Replace with:} In this work, we are interested in the mod $p$ homology of $\mathrm{S}_p$ (with $p$ a prime) which, as explained in \cite[Corollary~VI.1.4]{adem2004milgram}, is detected by a group inclusion $\iota \colon \mathrm{C}_p \to \mathrm{S}_p$, that is, the map induced in mod $p$ group homology by $\iota$ is a surjection.

\item Lemma 3.1: \par
\textit{Replace with:}
\begin{lemma} \label{lem: Thom's theorem}
	Let $p$ be an odd prime and $q$ an integer.
	Consider
	\begin{equation*}
	(\iota_\ast)_d \colon H_d(\mathrm{C}_p; \mathbb{F}_p(q)) \to H_d(\mathrm{S}_p; \mathbb{F}_p(q))
	\end{equation*}
	then
	\begin{enumerate}
		\item If $q$ is even, $(\iota_\ast)_d = 0$ unless there is an integer $t$ so that $d = 2t(p-1)$ or $d = 2t(p-1) - 1$.
		\item If $q$ is odd, $(\iota_\ast)_d = 0$ unless there is an integer $t$ so that $d = (2t+1)(p-1)$ or $d = (2t+1)(p-1) - 1$.
	\end{enumerate}
\end{lemma}

\item Sect.4.1 par. starting with ``Another groupoid of importance" \par
\textit{Partially replace with:}
... forgetful functors
\begin{equation*}
\begin{tikzcd}[column sep=small, row sep=tiny]
& \mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}} \arrow[dl, "U_1"', out=-120, in=0] \arrow[dr, "U_2", out=-60, in=180] & \\
\mathbf{Ch}_R^{\mathrm{S}^{op}} & & \mathbf{Ch}_R^{\mathrm{S}}.
\end{tikzcd}
\end{equation*}
Explicitly, $U_1(\mathcal P)(r) = \mathcal P(r,1)$ and $U_2(\mathcal P)(r) = \mathcal P(1,r)$ for any $\mathcal P$ in $\mathbf{Ch}_R^{\mathrm{S} \times \mathrm{S}^{op}}$.
Notice that for any object $A$ in $\mathbf{Ch}_R$ the canonical \textit{endomorphism bimodule}
\begin{equation*}
\End_A^A(r, s) = \Hom(A^{\otimes r}, A^{\otimes s})
\end{equation*}
forgets via $U_1$ and $U_2$ to $\End_A$ and $\End^A$ respectively.

\item Sect.4.1 par. starting with ``Another groupoid of importance". \par
\textit{Replace with:}
for each $r \in \mathbb{N}$, where $\Gamma_r$ denotes $\Gamma(r,r)$.

\item Two pars. above Definition 4.2 sentence 1. \par
\textit{Replace with:}
A \textit{resolution} in $\mathbf{Ch}_R^\Gamma$ is a morphism $\phi$ of $\Gamma$-modules such that $\phi(r)$ is a resolution in the category of chain complexes of $R[\Gamma_r]$-modules for each $r \in \mathbb{N}$, where $\Gamma_r$ denotes $\Gamma(r,r)$.

\item Sec.4.2 par.1 sentence 2: \par
\textit{Replace with:}
These structures are best understood by abstracting the compositional structure naturally present in the endomorphism $\mathrm{S}$-module $\End_A$ (or $\End^A$), naturally an operad, and the endomorphism $\mathrm{S}$-bimodule $\End_A^A$, naturally a prop.

\item Sec.4.3 par.2 \par
\textit{Replace with:}
Given a chain complex $A$, an operad $\mathcal O$ and a prop $\mathcal P$.
An $\mathcal O$-\textit{algebra} (resp. $\mathcal O$-\textit{coalgebra}) structure on $A$ is an operad morphism $\mathcal O \to \End_A$ (resp. $\mathcal O \to \End^A$), and a $\mathcal P$-\textit{bialgebra} structure on $A$ is a prop morphism $\mathcal P \to \End_A^A$.

\item Remark 5.2 sentence 2 \par
\textit{Replace with:}
In this language, a choice of factorization $\phi \circ \iota$ of a May-Steenrod structure on $\mathcal O$ endows it with an $E_\infty$ \textit{multiplication} $\phi$.

\item Definition 5.3 sentence 3 \par
\textit{Replace with:}
Given one such structure $\psi \colon \mathcal W \to \End_A$, the \textit{Steenrod cup-}$(r, i)$ \textit{product} of $A$ is defined for every $r, i \geq 0$ as the image in $ \mathrm{End}(A^{\otimes r}, A)$ of $\psi(e_i)$.

\item par. below Def 5.3 sentence 4 \par
\textit{Partially replace with:}
Restricting $\psi$ to arity $r$ defines a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$ that makes the pair $(A, \theta)$ into ...

\item par. below Def 5.3 sentence 5 \par
\textit{Partially replace with:}
Explicitly, this means that the pair is such that ...

\item Def 5.4 \par
\textit{Partially replace with:}
... is defined by sending $a$ to the Steenrod cup-$(p, i)$ product of ...

\item par. below Def 5.5 \par
\textit{Replace with:}
Notice that the Steenrod operations above, corresponding to Steenrod squares in the context of spaces, are determined by the Steenrod cup-$(2,i)$ products with $\mathbb{F}_2$-coefficients.
These binary operations are known as cup-$i$ products \cite{steenrod47products, medina2021newformulas} in the space context.
In a similar way, the operations $P$ and $\beta P$ defined below for odd primes are determined by the Steenrod cup-$\big(p, k(p-1)-\varepsilon\big)$ products for $\varepsilon \in \{0,1\}$.
We can explain the appearance of these specific Steenrod cup-$(p,1)$ products as follows.
The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even, and $(2t+1)(p-1) - \varepsilon$ if $q$ is odd.
According to Lemma \ref{lem: Thom's theorem}, these are the only homologically non-trivial cases.

\item Remark 5.7 \par
\textit{Replace} (6.1.) with (6.1)

\item Par. before Sec.6 \par
\textit{Replace with:}
For the even prime, effective proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{medina2021adem} and \cite{medina2020cartan}.
Explicitly, these construct cochains whose coboundaries descends to the relations in cohomology.

\textit{Please make sure the citation above is:} \verb|\cite{medina2021adem}|

\item Figure 1 \par
\textit{Replace with Figure \ref{fig: bigsummary} in here.}
\begin{figure}[ht]
	\begin{tikzcd}
	& & & U(\mathcal M) \arrow[dddr, bend left=10, "\phi^\triangle_X"'] \arrow[dddrr, bend left=20, "\phi^\square_Y"'] & & \\
	& & \mathcal X \arrow[ru, "SL"] & & & \\
	& \mathcal E \arrow[ur, "TR"] & & & & \\
	\mathcal W \arrow[rrrr, "\psi^\triangle_X", bend right=10] \arrow[rrrrr, "\psi^\square_Y", bend right=20] \arrow[ur, "\psi_{\mathcal E}"] \arrow[uurr, "\psi_{\mathcal X}"', bend right=35, pos=.6] \arrow[uuurrr, "\psi_{U(\mathcal M)}"', bend right=45, pos=0.6] & & & & \End_{N^\bullet_\triangle(X)} & \End_{N^\bullet_\square(Y)}
	\end{tikzcd}
	\caption{Summary of effective constructions: May-Steenrod structures on the Barratt-Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May-Steenrod structures on the normalized chains of a simplicial or cubical set. We remark that the maps $TR$ and $SL$ require different sign conventions.}
	\label{fig: bigsummary}
\end{figure}

\item Sec.6.1 first sentence \par
\textit{Replace with:}
In this subsection we effectively describe a May-Steenrod structure on the Barratt-Eccles operad via explicit formulae.

\item Sentence above Def 6.1 \par
\textit{Replace with:}
The chain complex resulting from applying the functor of normalized integral chains to it is the arity $r$ part of the Barratt-Eccles operad $\mathcal E$.

\item Proof thm 6.2 first sentence \par
\textit{Replace with:}
Since $\mathcal E$ is an $E_\infty$ operad, we simply need to prove that the $\Z[\mathrm{C}_r]$-linear map
\begin{equation*}
\psi_{\mathcal E}(r) \colon \mathcal W(r) \to \mathcal E(r)
\end{equation*}
is a quasi-isomorphism for every $r \geq 0$.

\item Proof thm 6.6 first sentence \par
\textit{Replace} chain map \textit{with} quasi-isomorphism

\item Proof thm 6.6 last sentence \par
\textit{Replace} is a generator \textit{with} represents a generator

\item Sec.6.3 par.3 sentence before display\par
\textit{Replace} represented by the connected \textit{with} represented by the immersed connected

\item Sect.6.3 par.2 sentence 2 \par
\textit{Replace} Medina-Mardones \textit{with} The second named author

\item Thm 6.8\par
\textit{Replace with:}
\begin{theorem} \label{thm: Steenrod-Adem on U(M)}
	The composition
	\begin{equation*}
	\psi_{U(\mathcal M)} \colon \mathcal W \xrightarrow{\psi_{\mathcal X}} \mathcal X \xrightarrow{SL} U(\mathcal M)
	\end{equation*}
	defines a May--Steenrod structure on $U(\mathcal M)$.
\end{theorem}

\item Example 6.9 \par
\textit{Remove Figure 2 and replace the example with:}

\begin{example}
	The following immersed $(1,2)$-graphs are the elements $\psi_{U(\mathcal M)}(2)(e_n)$ for small values of $n$:
\begin{center}
	\begin{tikzpicture}[scale=.55]
\draw (1,3.7) to (1,3);

\draw (1,3) to [out=205, in=90] (0,0);
\draw (1,3) to [out=-25, in=90] (2,0);

\node at (1,-.5){$n=0$};
\end{tikzpicture}\hspace*{1cm}
\begin{tikzpicture}[scale=.55]
\draw (1,3.7) to (1,3);

\draw (1,3) to [out=205, in=90] (0,0);

\draw [shorten >= 0cm] (.6,2.73) to [out=-100, in=90] (2,0);

\draw [shorten >= .15cm] (1,3) to [out=-25, in=30, distance=1.1cm] (1,1.5);
\draw [shorten <= .1cm] (1,1.5) to [out=210, in=20] (0,1);

\node at (1,-.5){$n=1$};
\end{tikzpicture}\hspace*{1cm}
\begin{tikzpicture}[scale=.55]
\draw (1,3.7) to (1,3);

\draw (1,3) to [out=205, in=90] (0,0);
\draw (1,3) to [out=-25, in=90] (2,0);

\draw [shorten >= 0cm] (.6,2.73) to [out=210, in=135] (1,1.5);
\draw [shorten <= 0cm] (1,1.5) to [out=-45, in=170] (2,1);

\draw [shorten >= .1cm] (1.4,2.73) to [out=-30, in=45] (1,1.5);
\draw [shorten <= .1cm] (1,1.5) to [out=-135, in=10] (0,1);

\node at (1,-.5){$n=2$};
\end{tikzpicture}
\end{center}
\end{example}

\item Answer to question in \textbf{Note 6} \par
It is intentional and they have different meanings indeed.

\item Sentences before Examples 6.13 and 6.17 \par
\textit{Replace} notations \textit{with} notation \par
\textit{According to Webster ``notation'' is a ``system'' so in this case it contains two pieces of notation.}

\item Sec. 7 \par
\textit{Add before last paragraph:}
In physics, Gaiotto, Kapustin, Thorngren \cite{gaiotto2016spin, kapustin2017fermionic, bhardwaj2017state} and others have considered cellular decompositions of spacetime together with fields represented by cellular cochains.
In order to express subtle interactions between these fields, they have used cup-$i$ products to define relevant action functionals for topological field theories.
We expect that new topological field theories of interest can be studied using the Steenrod cup-$(p,i)$ products introduced in this work.

\item Acknowledgment \par
\textit{Replace with:}
The authors thank Clemens Berger, Calista Bernard, Greg Brumfiel, Federico Cantero-Mor\'an, Greg Friedman, Kathryn Hess, Jens Kjaer, John Morgan, Andy Putman, Dev Sinha, and Dennis Sullivan for insightful discussions, and the anonymous referee for many keen observations and helpful suggestions.

\item Funding \par
\textit{Replace with:}
A. M. Medina-Mardones acknowledges financial support from Innosuisse grant \mbox{32875.1 IP-ICT-1}.

\item Bibliography \par
\textit{Please replace the corresponding entries:}
\begin{enumerate}
\item
\begin{Verbatim}
@article {adams1957cobar,
	AUTHOR = {Adams, J. F.},
	TITLE = {On the cobar construction},
	JOURNAL = {Proc. Nat. Acad. Sci. U.S.A.},
	FJOURNAL = {Proceedings of the National Academy of Sciences of the United
	States of America},
	VOLUME = {42},
	YEAR = {1956},
	PAGES = {409--412},
	ISSN = {0027-8424},
	MRCLASS = {55.0X},
	MRNUMBER = {79266},
	MRREVIEWER = {W. S. Massey},
	DOI = {10.1073/pnas.42.7.409},
	URL = {https://doi.org/10.1073/pnas.42.7.409},
}
\end{Verbatim}
\item
\begin{Verbatim}
@ARTICLE{medina2021adem,
	author={Brumfiel, Greg and {Medina-Mardones}, Anibal and Morgan, John},
	title={A cochain level proof of Adem relations in the mod 2 Steenrod algebra},
	JOURNAL = {J. Homotopy Relat. Struct.},
	FJOURNAL = {Journal of Homotopy and Related Structures},
	year={2021},
	day={19},
	issn={1512-2891},
	doi={10.1007/s40062-021-00287-3},
	url={https://doi.org/10.1007/s40062-021-00287-3}
}
\end{Verbatim}
\item
\begin{Verbatim}
@ARTICLE{medina2021computer,
	author = {{Medina-Mardones}, Anibal M.},
	title = "{A computer algebra system for the study of commutativity up to coherent homotopies}",
	journal = {arXiv e-prints},
	year = 2021,
	archivePrefix = {arXiv},
	eprint = {2102.07670},
	note = {To appear in Tbilisi Math. J.}
}
\end{Verbatim}

\item
\begin{Verbatim}
@ARTICLE{medina2021cobar,
	author = {{Medina-Mardones}, Anibal M. and {Rivera}, Manuel},
	title = "{The cobar construction as an $E_{\infty}$-bialgebra model of the based loop space}",
	journal = {arXiv e-prints},
	year = 2021,
	archivePrefix = {arXiv},
	eprint = {2108.02790},
}
\end{Verbatim}
\end{enumerate}
\end{enumerate}
\end{document}

### 2021-10-04 sec/effective.tex
After journal proof corrections

@@
 
-In this section we construct explicit May--Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt--Eccles operad $\mathcal E$ \cite{berger2004combinatorial}, the surjection operad $\mathcal X$ \cite{mcclure2003multivariable}, and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-prop $\mathcal M$ introduced in \cite{medina2020prop1}.
-We also define natural and effective May--Steenrod structures on the normalized cochains of any simplicial or cubical set using that these are algebras over the operad $U(\mathcal M)$.
+In this section we construct explicit May--Steenrod structures on three well know combinatorial $E_\infty$-operads: the Barratt--Eccles operad $\mathcal E$ (see \cite{berger2004combinatorial}), the surjection operad $\mathcal X$ (see \cite{mcclure2003multivariable}), and the operad $U(\mathcal M)$ associated to the finitely presented $E_\infty$-prop $\mathcal M$ introduced in \cite{medina2020prop1}.
+We also define a natural and effective May--Steenrod structures on the normalized cochains of any simplicial or cubical set using that these are algebras over the operad $U(\mathcal M)$.
 
@@
 	\end{tikzcd}
-	\caption{Summary of effective constructions: May--Steenrod structures on the Barratt--Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May--Steenrod structures on the normalized chains of simplicial and cubical sets.
-We remark that the maps $TR$ and $SL$ required different sign conventions.}
+	\caption{Summary of effective constructions: May--Steenrod structures on the Barratt--Eccles $\mathcal E$, surjection $\mathcal X$, and $U(\mathcal M)$ operads, and natural May--Steenrod structures on the normalized chains of a simplicial or cubical set.
+We remark that the maps $TR$ and $SL$ require different sign conventions.}
 	\label{fig: bigsummary}
@@
 
-\subsection{Barratt--Eccles operad} In this subsection we effectively describe a May--Steenrod structure on the Barratt--Eccles operad via explicit formulae.
+\subsection{Barratt--Eccles operad}
 
-We begin by reviewing the $\mathrm{S}$-module structure underlying the Barratt--Eccles operad and, since will not use it in this work, refer to \cite{berger2004combinatorial} for a description of if composition structure.
+In this subsection we effectively describe a May--Steenrod structure on the Barratt--Eccles operad via explicit formulae.
+
+We begin by reviewing the $\mathrm{S}$-module structure underlying the Barratt--Eccles operad and, since we will not use it in this work, refer to \cite{berger2004combinatorial} for a description of if composition structure.
 For a non-negative integer $r$ define the simplicial set $E(\mathrm S_r)$ by
@@
 \end{equation*}
-The chain complex resulting from applying the functor of normalized integral chains to it is denoted $\mathcal E(r)$, which is the arity $r$ chain complex of the Barratt--Eccles operad.
+The chain complex resulting from applying the functor of normalized integral chains to it is the arity $r$ part of the Barratt--Eccles operad $\mathcal E$.
 
@@
 
-\begin{table}[h]
+\begin{table}[ht]
 	\centering
@@
 \begin{remark}
-	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota \colon \mathrm C_r \to \mathrm S_r$ induces both a simplicial inclusion $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ and one of $\mathrm C$-modules
+	The natural construction \eqref{eq: milnor model of symmetric} is defined for any group, in particular, for finite cyclic groups, and the inclusion $\iota \colon \mathrm C_r \to \mathrm S_r$ induces both: a simplicial inclusion $E(\iota) \colon E(\mathrm C_r) \to E(\mathrm S_r)$ and one of $\mathrm C$-modules
 	\begin{equation*}
@@
 
-In this subsection we introduce a May--Steenrod structures on the surjection operad.
+In this subsection we introduce a May--Steenrod structure on the surjection operad.
 There are two widely used sign conventions for this operad respectively due to McClure--Smith \cite{mcclure2003multivariable} and Berger--Fresse \cite{berger2004combinatorial}.
@@
 We only describe the McClure--Smith convention since we refer to it in subsequent sections.
-The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top dimensional generator in the chain complex
+The boundary map and symmetric action in this case is defined using the Koszul convention regarding a surjection $s \colon \{1, \dots, n+r\} \to \{1, \dots, r\} $ as the top-dimensional generator in the chain complex
 \begin{equation} \label{eq: surjection boundary}
@@
 \end{equation}
-Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on.
+Explicitly, if we think of $s$ as a sequence of integers $\big( s(1), \dots, s(n+r) \big)$ the boundary of $s$ is the sum of sequences obtained by orderly removing one at a time the occurrences of $1$ with alternating signs, then those of $2$ with starting sign equal to that of the last removal of $1$, and so on.
 Since we do not use the composition structure we refer to \cite{mcclure2003multivariable} for it.
 
-Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure--Smith to prove $\mathcal X$ is an $E_\infty$-operad and whose introduction is credited to Benson \cite{benson1998rep}.
+Let us recall the chain contraction of $\mathcal X(r)$ onto $\mathcal X(r-1)$ used by McClure--Smith to prove that $\mathcal X$ is an $E_\infty$-operad and whose introduction is credited to Benson \cite{benson1998rep}.
 Let the maps $i$, $p$, and $s$ be defined on basis elements, represented by sequences, as follows: $i \colon \mathcal X(r-1) \to \mathcal X(r)$ places a $1$ at the beginning of the sequence and increases each of the original entries by $1$, $p \colon \mathcal X(r) \to \mathcal X(r-1)$ takes the sequence to $0$ unless it contains a single occurrence of $1$, in which case $p$ removes the $1$ and decreases each of the remaining entries by $1$, and finally, $s \colon \mathcal X(r) \to \mathcal X(r)$ places a 1 at the beginning of the sequence; if the sequence already begins
@@
 	We simplify notation and write $\psi$ instead of $\psi_{\mathcal X}(r)$.
-	To show $\psi$ is a chain map we proceed by induction.
+	To show that $\psi$ is a chain map we proceed by induction.
 	Notice that
@@
 	& =
-	\partial\, h\, T\, \psi(e_{2m}) \big) \\
+	\partial\, h\, T\, \psi(e_{2m}) \\
 	& =
 	T\, \psi(e_{2m}) - i^{r-1} p^{r-1}\, \psi(e_{2m}) -
-	h\, \partial\, T\, \psi(e_{2m}) \big) \\
+	h\, \partial\, T\, \psi(e_{2m}) \\
 	& =
 	T\, \psi(e_{2m}) -
-	h\, T\, \psi(\partial\, e_{2m}) \big) \\
+	h\, T\, \psi(\partial\, e_{2m}) \\
 	& =
 	T\, \psi(e_{2m}) -
-	h\, \psi(T\,N\, e_{2m-1}) \big) \\
+	h\, \psi(T\,N\, e_{2m-1}) \\
 	& =
@@
 	For $n = 2m$ the proof is analogous.
-	The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ is a generator of the homology.
+	The chain map $\psi$ is a quasi-isomorphism since both complexes have the homology of a point and $\psi(e_0) = (1, \dots, r)$ represents a generator of the homology.
 \end{proof}
 
-For the rest of the paper we use the McClure--Smith sign convention on $\mathcal X$.
+For the rest of this paper we use the McClure--Smith sign convention on $\mathcal X$.
 
@@
 
-Theorem 3.3 in \cite{medina2020prop1} established that $\mathcal M$ is an $E_\infty$-prop as introduced in Definition~\ref{def: e-infinity operad and prop}.
+The second named author established in \cite[Theorem 3.3]{medina2020prop1} that $\mathcal M$ is an $E_\infty$-prop as introduced in Definition~\ref{def: e-infinity operad and prop}.
 More precisely, it shows that the associated operad $U_2(\mathcal M) = \big\{ \mathcal M(1, r) \big\}_{r \geq 0}$ is an $E_\infty$-operad.
@@
 
-It can be directly verified using the presentation of $\mathcal M$ that the boundary of $SL(s)$ is obtained by removing strands one at the time in the order they are attached at the bottom.
+It can be directly verified using the presentation of $\mathcal M$ that the boundary of $SL(s)$ is obtained by removing strands one at a time in the order they are attached at the bottom.
 This is precisely the image of $SL(\partial s)$ according to \eqref{eq: surjection boundary}.
 Furthermore, relabeling the bottom edges agrees with the permutation of preimages of the associated surjection.
-Since both operads have the homology of a point and $(1, \dots, r)$ is sent to a representative of a homology generator we have proven the following
+Since both operads have the homology of a point and $(1, \dots, r)$ is sent to a representative of a homology generator we have proven the following theorem.
 
 \begin{theorem} \label{thm: Steenrod-Adem on U(M)}
-	The composition $\psi_{U(\mathcal M)}$
+	The composition
 	\begin{equation*}
-	\begin{tikzcd}[column sep = normal]
-	\mathcal W \arrow[r, "\psi_{\mathcal X}"] & \mathcal X \arrow[r, "SL"] & U(\mathcal M)
-	\end{tikzcd}
+	\psi_{U(\mathcal M)} \colon \mathcal W \xra{\psi_{\mathcal X}} \mathcal X \xra{SL} U(\mathcal M)
 	\end{equation*}
@@
 satisfying the relations in the presentation of $\mathcal M$.
-For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
-(1) The counit $\epsilon \in \Hom(N_\bullet(\triangle^n), \Z)$ by
+For $n \in \mathbb{N}$, define the following: \vspace*{5pt} \\
+(1) Define the counit $\epsilon \in \Hom(N_\bullet(\triangle^n), \Z)$ by
 \begin{equation*}
@@
 \end{equation*}
-(2) The coproduct $\Delta \in \Hom(N_\bullet(\triangle^n), N_\bullet(\triangle^n)^{\otimes2})$ by
+(2) Define the coproduct $\Delta \in \Hom(N_\bullet(\triangle^n), N_\bullet(\triangle^n)^{\otimes2})$ by
 \begin{equation*}
@@
 \end{equation*}
-(3) The product $\ast \in \Hom(N_\bullet(\triangle^n)^{\otimes 2}, N_\bullet(\triangle^n))$ by
+(3) Define the product $\ast \in \Hom(N_\bullet(\triangle^n)^{\otimes 2}, N_\bullet(\triangle^n))$ by
 \begin{equation*}
@@
 	\end{equation*}
-	defines a natural $\mathcal M$-bialgebra structure on $N_\bullet(\triangle^n)$, and, through a Kan extension argument, a natural $U(\mathcal M)$-algebra structure $\phi^\triangle \colon U(\mathcal M) \to \End_{N^\bullet (X)}$ on the cochains of any simplicial set $X$.
+	defines a natural $\mathcal M$-bialgebra structure on $N_\bullet(\triangle^n)$, and, via a Kan extension argument, a natural $U(\mathcal M)$-algebra structure $\phi^\triangle \colon U(\mathcal M) \to \End_{N^\bullet (X)}$ on the cochains of any simplicial set $X$.
 \end{proposition}
@@
 These are determined by three linear maps satisfying the relations in the presentation of $\mathcal M$.
-For $n \in \mathbb{N}$, define: \vspace*{5pt} \\
-(1) The counit $\epsilon \in \Hom(N_\bullet(\square^n), \Z)$ by
+For $n \in \mathbb{N}$, define the following: \vspace*{5pt} \\
+(1) Define the counit $\epsilon \in \Hom(N_\bullet(\square^n), \Z)$ by
 \begin{equation*}
@@
 \end{equation*} \vspace*{-6pt} \\
-(2) The coproduct $\Delta \in \Hom \left( N_\bullet(\square^n), N_\bullet(\square^n)^{\otimes 2} \right)$ by
+(2) Define the coproduct $\Delta \in \Hom \left( N_\bullet(\square^n), N_\bullet(\square^n)^{\otimes 2} \right)$ by
 \begin{equation*}
@@
 \end{equation*}
-Using that $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$, $\Delta$ is the composition
+By using that $N_\bullet(\square^n) = N_\bullet(\square^1)^{\otimes n}$, $\Delta$ is the composition
 \begin{equation*}
@@
 where $sh$ is the shuffle map that places tensor factors in odd position first. \vspace*{5pt} \\
-(3) The product $\ast \in \Hom(N_\bullet(\square^n)^{\otimes 2}, N_\bullet(\square^n))$ by
+(3) Define the product $\ast \in \Hom(N_\bullet(\square^n)^{\otimes 2}, N_\bullet(\square^n))$ by
 \begin{align*}
@@
 	\end{equation*}
-	defines a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$, and, through a Kan extension argument, a natural $U(\mathcal M)$-algebra structure $\phi^\square \colon U(\mathcal M) \to \End_{N^\bullet (X)}$ on the cochains of any cubical set $X$.
+	defines a natural $\mathcal M$-bialgebra structure on $N_\bullet(\square^n)$, and, via a Kan extension argument, a natural $U(\mathcal M)$-algebra structure $\phi^\square \colon U(\mathcal M) \to \End_{N^\bullet (X)}$ on the cochains of any cubical set $X$.
 \end{proposition}
@@
 Composing the algebra structure $\phi^\square$ with the May--Steenrod structure on $U(\mathcal M)$ gives a natural May--Steenrod structure on $N^\bullet(X)$.
-We record this observation in the following.
+We record this observation in the following theorem.
 

### 2021-10-04 sec/groups.tex
After journal proof corrections

@@
 
-Fixing notation, let $\mathrm{S}_r$ be the symmetric group of $r$ elements and $\mathrm{C}_r$ be the cyclic group of order $r$ thought of as the subgroup of $\mathrm{S}_r$ generated by an element~$\rho$.
+Fixing notation, let $\mathrm{S}_r$ be the symmetric group of $r$ elements and let $\mathrm{C}_r$ be the cyclic group of order $r$ thought of as the subgroup of $\mathrm{S}_r$ generated by an element~$\rho$.
 We denote this inclusion by $\iota \colon \mathrm C_r \to \mathrm S_r$.
 
-A \textit{resolution} in $\mathbf{Ch}_R$ is a quasi-isomorphism $P \to M$ with each $P_r$ a free $R$-module.
-We will use the fact, explained in Section 6.5 of \cite{jacobson1989algebra}, that such resolutions exist for any chain complex $M$ concentrated in non-negatively degrees, in particular, for the monoidal unit $R$.
+A \textit{resolution} in $\mathbf{Ch}_R$ is a quasi-isomorphism $P \to M$ with each $P_r$ being a free $R$-module.
+We will use the fact, explained in Section 6.5 of \cite{jacobson1989algebra}, that such resolutions exist for any chain complex $M$ concentrated in non-negative degrees.
 
-Let $\mathrm G$ be a group and $M$ an $R[\mathrm G]$-module, we define the \textit{homology of $\mathrm G$ with coefficients in $M$}, denoted $H(\mathrm G; M)$, as the homology of any chain complex $P \otimes_{R[\mathrm G]} M$ with $P \to R$ a resolution.
+Let $\mathrm G$ be a group and $M$ an $R[\mathrm G]$-module.
+The \textit{homology of $\mathrm G$ with coefficients in $M$}, denoted by $H(\mathrm G; M)$, is defined as the homology of the chain complex $P \otimes_{R[\mathrm G]} M$ where $P \to R$ is any resolution in $\Ch_{R[\mathrm G]}$.
 We will be particularly interested in the case when $M = \mathbb F_p(q)$ is the trivial or sign $\mathbb F_p[\mathrm{S}_r]$-module depending on if the parity of~$q$ is even or odd respectively.
@@
 \end{equation}
-concentrated in non-negative degrees, with $\mathcal W(r)_d$ the free $R[\mathrm{C}_r]$-module generated by an element $e_d$, and differential induced from
+concentrated in non-negative degrees, with $\mathcal W(r)_d$ the free $R[\mathrm{C}_r]$-module $\mathcal W(r)_d$ generated by an element $e_d$, and differential induced from
 \begin{equation*}
@@
 
-It follow from a straightforward computation that for any prime $p$ and integer $q$
+It follows from a straightforward computation that for any prime $p$ and integer $q$
 \begin{equation*}
@@
 
-In this work, we are interested in the mod $p$ homology of $\mathrm{S}_p$ ($p$ a prime) which, as explained in \cite[Corollary~VI.1.4]{adem2004milgram}, is detected by a group inclusion $\iota \colon \mathrm{C}_p \to \mathrm{S}_p$, that is, the map induced in mod $p$ group homology is a surjection.
+In this work, we are interested in the mod $p$ homology of $\mathrm{S}_p$ (with $p$ a prime) which, as explained in \cite[Corollary~VI.1.4]{adem2004milgram}, is detected by a group inclusion $\iota \colon \mathrm{C}_p \to \mathrm{S}_p$, that is, the map induced in mod $p$ group homology by $\iota$ is a surjection.
 We now describe the kernel of this surjection.
@@
 	\begin{enumerate}
-		\item If $q$ is even, $(\iota_\ast)_d = 0$ unless $d = 2t(p-1)$ or $d = 2t(p-1) - 1$,
-		\item If $q$ is odd, $(\iota_\ast)_d = 0$ unless $d = (2t+1)(p-1)$ or $d = (2t+1)(p-1)-1$,
+		\item If $q$ is even, $(\iota_\ast)_d = 0$ unless there is an integer $t$ so that $d = 2t(p-1)$ or $d = 2t(p-1) - 1$.
+		\item If $q$ is odd, $(\iota_\ast)_d = 0$ unless there is an integer $t$ so that $d = (2t+1)(p-1)$ or $d = (2t+1)(p-1)-1$.
 	\end{enumerate}
-	for some integer $t$.
 \end{lemma}
@@
 
-In section 5 we will see how the mod $p$ homology of symmetric groups defines operations on the mod $p$ homology of algebras that are commutative up to coherent homotopies.
-Preparing for that, we first developed the language of $\Gamma$-modules, operads, and props.
+In Section 5 we will see how the mod $p$ homology of symmetric groups defines operations on the mod $p$ homology of algebras that are commutative up to coherent homotopies.
+Preparing for that, we first develop the language of $\Gamma$-modules, operads, and props.

### 2021-10-04 sec/introduction.tex
After journal proof corrections

@@
 The reason is that, given the representability of the cohomology functor, these operations together with the Bockstein homomorphism can be used to give a complete description of the algebraic structure naturally present on the mop-$p$ cohomology algebra of spaces.
-For the even prime, Steenrod squares were introduced in \cite{steenrod1947products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander--Whitney's chain approximation to the diagonal, the so called cup-$i$ products.
+For the even prime, Steenrod squares were introduced in \cite{steenrod1947products} via an explicit choice of coherent homotopical corrections to the broken symmetry of Alexander--Whitney's chain approximation to the diagonal, the so-called cup-$i$ products.
 Later, for odd primes, their definition was given non-effectively using existence arguments based on the mod $p$ homology of symmetric groups \cite{steenrod1952reduced, steenrod1962cohomology, steenrod1962cohomology}.
@@
 
-In recent years, thanks to the development of new applications of cohomology in areas such as applied topology and topological quantum field theories, the need to have an effectively computable definition of Steenrod operations has gain considerable importance.
+In recent years, thanks to the development of new applications of cohomology in areas such as applied topology and topological quantum field theories, the need to have an effectively computable definition of Steenrod operations has gained considerable importance.
 
@@
 This is through Baues' cubical generalization of Adams' cobar construction \cite{adams1956cobar, baues1998hopf}.
-Using Baues' work, an application of the constructions presented in this paper is the explicit descriptions, at the chain level, of Steenrod operations on the cobar construction of the coalgebra of chains on a reduced simplicial set \cite{medina2021cobar}.
+By using Baues' work, an application of the constructions presented in this paper is the explicit description, at the chain level, of Steenrod operations on the cobar construction of the coalgebra of chains on a reduced simplicial set \cite{medina2021cobar}.
 

### 2021-10-04 sec/operads.tex
After journal proof corrections

@@
 \begin{definition}
-	A \textit{$\Gamma$-module} is a covariant functor to $\mathbf{Ch}_R$ from a groupoid $\Gamma$ with objects the natural numbers and morphisms satisfying $\Gamma(r,s) = \emptyset$ for $r \neq s$.
+	A \textit{$\Gamma$-module} is a covariant functor to $\mathbf{Ch}_R$ from a groupoid $\Gamma$ with objects being the natural numbers and morphisms satisfying $\Gamma(r,s) = \emptyset$ for $r \neq s$.
 	We denote the category of $\Gamma$-modules and natural transformations by $\mathbf{Ch}_R^\Gamma$.
@@
 satisfying their own versions of associativity, equivariance and unitality.
-For a complete presentation of these concepts we refer to Definition 11 and 54 of \cite{markl2008props}.
+For a complete presentation of these concepts we refer to \cite[Definitions 11 and 54]{markl2008props}.
 
@@
 
-\subsection{Algebras, coalgebra and bialgebras}
+\subsection{Algebras, coalgebras and bialgebras}
 
-A morphisms of operads or of props is simply a morphisms of their underlying $\mathrm{S}$-modules or $\mathrm{S}$-bimodules preserving the respective compositional structures.
+A morphism of operads or of props is simply a morphism of their underlying $\mathrm{S}$-modules or $\mathrm{S}$-bimodules preserving the respective compositional structures.
 
@@
 Since $E_\infty$-operads are resolutions of $\underline{R}$, their algebras can be thought of as usual unital algebras where the commutativity and associativity relations hold up to coherent homotopies.
-The two main examples to keep in mind are the cochains of spaces and the chains of infinite loops spaces.
+The two main examples to keep in mind are the cochains of spaces and the chains of infinite loop spaces.

### 2021-10-04 sec/outlook.tex
After journal proof corrections

@@
 
-In physics, Gaiotto, Kapustin, Thorngren \cite{gaiotto2016spin,bhardwaj2017fermionic,kapustin2017fermionic} and others have considered cellular decompositions of spacetime together with fields represented by cellular cochains.
+In physics, Gaiotto, Kapustin, Thorngren \cite{gaiotto2016spin, kapustin2017fermionic, bhardwaj2017fermionic} and others have considered cellular decompositions of spacetime together with fields represented by cellular cochains.
 In order to express subtle interactions between these fields, they have used cup-$i$ products to define relevant action functionals for topological field theories.

### 2021-10-04 sec/steenrod.tex
After journal proof corrections

@@
 	In \cite{GerstenhaberVoronov} an operad morphism $\mathcal{A}ssoc \to \mathcal O$ is referred to as a \textit{multiplication} on $\mathcal O$.
-	In this language, a choice of factorization $\phi \circ \iota$ of a May--Steenrod structure on $\mathcal O$ endows it with $\phi$ a \textit{multiplication commutative up to coherent homotopies}.
+	In this language, a choice of factorization $\phi \circ \iota$ of a May--Steenrod structure on $\mathcal O$ endows it with an $E_\infty$ \textit{multiplication} $\phi$.
 \end{remark}
@@
 We can relate this structure on $A$ to those considered by May in \cite{may1970general} as follows.
-The morphism $\phi$ provides $A$ with the structure of a homotopy associative algebra defined by the image in $\Hom(A^{\otimes 2}, A)$ of a representative in $\mathcal R(2)$ of a generator of its $0\th$-homology.
-Restricting $\psi$ to arity $r$ defines a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$ that makes the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ as presented in Definitions 2.1 op.
-cit.
-Explicitly, this means that the pair is such that $\psi(e_0) \in \End_A(r)$ is $\mathrm C_r$-homotopic to the iterated product $A^{\otimes r} \to A$.
-A claim that follows from the iterated product being a representative of a generator of the $0\th$-homology of $\mathcal R(r)$, and $\iota$ being a quasi-isomorphism of $\mathrm C$-modules.
+The morphism $\phi$ provides $A$ with the structure of a homotopy associative algebra defined by the image in $\Hom(A^{\otimes 2}, A)$ of a representative in $\mathcal R(2)$ of a generator of its $0^\th$-homology.
+Restricting $\psi$ to arity $r$ defines a map $\theta \colon \mathcal W(r) \otimes A^{\otimes r} \to A$ that makes the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_r, \infty, \Z)$ as presented in \cite[Definitions 2.1]{may1970general}.
+Explicitly, this means that the pair is such that $\psi(e_0) \in \End_A(r)$ is $\mathrm C_r$-homotopic to the iterated product $A^{\otimes r} \to A$; a claim that follows from the iterated product being a representative of a generator of the $0^\th$-homology of $\mathcal R(r)$, and $\iota$ being a quasi-isomorphism of $\mathrm C$-modules.
 Furthermore, for $r$ equal to a prime $p$, tensoring the integers with $\Fp$ makes the pair $(A, \theta)$ into an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
 For any object $(A, \theta)$ in this category, Definition~2.2 in \cite{may1970general} defines operations on the mod $p$ homology of $A$, a construction we review below.
-In particular, if $A$ is given by the cochains of a space these products agree with Steenrod's original definitions, and for $A$ being the chains on an infinite loop spaces, with those defined by Araki--Kudo and Dyer--Lashof.
+In particular, if $A$ is given by the cochains of a space these products agree with Steenrod's original definitions, and for $A$ being the chains on an infinite loop space, with those defined by Araki--Kudo and Dyer--Lashof.
 
@@
 We can explain the appearance of these specific Steenrod cup-$(p,1)$ products as follows.
-The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even and $(2t+1)(p-1) - \varepsilon$ if $q$ is odd.
+The increase on the degree of a $q$-cycle after applying $D^p_{k(p-1)-\varepsilon}$ to it is $(p-1)(q+k) - \varepsilon$, which can be rewritten as $2t(p-1) - \varepsilon$ if $q$ is even, and $(2t+1)(p-1) - \varepsilon$ if $q$ is odd.
 According to Lemma \ref{lem: Thom's theorem}, these are the only homologically non-trivial cases.
@@
 \begin{remark}
-	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see Eq. 6.1. in \cite{steenrod1953cyclic}).
+	The use of the coefficient function $\nu(q)$ is motivated by the identity $D_{q(p-1)}^p(a) = \nu(q)a$ in the case of spaces (see \cite[(6.1)]{steenrod1953cyclic}).
 	The notation $\beta P_s$ is motivated by the relationship of this operator and the Bockstein of the reduction $\mathbb Z \to \mathbb Z/p\mathbb Z$.
@@
 
-Steenrod operations defined as above satisfy the so called \textit{Adem relations}.
+Steenrod operations defined as above satisfy the so-called \textit{Adem relations}.
 Below we present its most common form and refer to Theorem 4.7 in \cite{may1970general} for a complete list.
@@
 	\begin{enumerate}
-		\item If $p = 2$ and $a > 2b$
+		\item If $p = 2$ and $a > 2b$, then
 		\begin{equation*}
@@
 		\end{equation*}
-		\item If $p > 2$ and $a > pb$
+		\item If $p > 2$ and $a > pb$, then
 		\begin{equation*}
@@
 	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
-	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\phi$ an operad map from an $E_\infty$-operad to $\End_A$, the pair $(A, \theta)$ is an \textit{Adem object} in the sense of Definition 4.1 of \cite{may1970general}.
-	The statement presented here is stated and proven as part of Theorem 4.7 loc. cit.
+	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\phi$ being an operad map from an $E_\infty$-operad to $\End_A$, the pair $(A, \theta)$ is an \textit{Adem object} in the sense of \cite[Definition 4.1]{may1970general} and the statement presented here is stated and proven as part of \cite[Theorem 4.7]{may1970general}.
 \end{proof}
@@
 
-Chain complexes equipped with a comultiplicative May--Steenrod structure satisfy the so called \textit{Cartan relations}.
+Chain complexes equipped with a comultiplicative May--Steenrod structure satisfy the so-called \textit{Cartan relations}.
 
@@
 	As described after Definition~\ref{def: Steenrod products}, for any prime $p$ the pair $(A, \theta)$ is an object in May's category $\mathfrak{C}(\mathrm C_p, \infty, \mathbb{F}_p)$.
-	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\iota$ a quasi-isomorphism in the category of $\mathrm{C}$-modules over the category of coalgebras, this is a \textit{Cartan object} as defined in \cite[p.161]{may1970general}.
+	Furthermore, since we are demanding a factorization $\phi \circ \iota$ with $\iota$ being a quasi-isomorphism in the category of $\mathrm{C}$-modules over the category of coalgebras, this is a \textit{Cartan object} as defined in \cite[p.161]{may1970general}.
 	The statement presented here is stated in page~165 loc.~cit.
@@
 For the even prime, effective proofs at the cochain level of the Adem and Cartan relations have been given respectively in \cite{medina2021adem} and \cite{medina2020cartan}.
-Explicitly, these proof construct cochains whose coboundaries descends to the relations in cohomology.
+Explicitly, these construct cochains whose coboundaries descends to the relations in cohomology.

### 2021-10-13 sec/abstract.tex
Published version

--- 2021-08-20 aux/abstract.tex
@@
 This approach enhanced the conceptual understanding of the operations and allowed for many advances, but lacked the concreteness of their definition at the even prime.
-In recent years, thanks to the development of new applications of cohomology,the need to have an effectively computable definition of Steenrod operations has become a key issue.
-This article provides such definitions at all primes using the operadic viewpoint of May, and defines multioperations that generalize the cup-$i$ products of Steenrod on the simplicial and cubical cochains of spaces.
+In recent years, thanks to the development of new applications of cohomology, the need to have an effectively computable definition of Steenrod operations has become a key issue.
+Using the operadic viewpoint of May, this article provides such definitions at all primes introducing multioperations that generalize the Steenrod cup-$i$ products on the simplicial and cubical cochains of spaces.
 \end{abstract}
